### 2018-05-28 Article - LaTeX files/collaborative_spatial_reuse_via_mabs.tex
Article (LaTeX files) to be submitted to Elsevier Ad-hoc Networks.

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

\usepackage{graphicx} 	  %% The graphicx package provides the includegraphics command.
\usepackage{amssymb} 	%% The amssymb package provides various useful mathematical symbols

\usepackage{color}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{fullpage}
\usepackage{algorithmic}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}
\algsetup{linenosize=\small}
\usepackage[table,xcdraw]{xcolor}
\usepackage{multirow}
\usepackage[super]{nth}
\usepackage{graphicx,adjustbox}
\usepackage{caption}
\usepackage[labelformat=simple]{subcaption}
\usepackage{comment}
\usepackage{setspace}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{siunitx}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{soul}
\usepackage{url}
\usepackage{tablefootnote}
\DeclareMathOperator{\E}{\mathbb{E}} % Expectation Symbol
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{footnote}
\usepackage[misc,geometry]{ifsym} 
\makesavenoteenv{tabular}

%% Other
\DeclarePairedDelimiter\abs{\lvert}{\rvert}

\renewcommand\thesubfigure{(\alph{subfigure})}
\let\OldTexttrademark\texttrademark
\renewcommand{\texttrademark}{\OldTexttrademark\xspace}%
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%\usepackage{authblk}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}
\usepackage{epsfig}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}
\newcommand{\francesc}[1]{\textcolor{blue}{#1}}
\newcommand{\francesco}[1]{\textcolor{orange}{#1}}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Computer Networks}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Collaborative Spatial Reuse in Wireless Networks via Selfish Multi-Armed Bandits}

\author[label1, label4]{Francesc Wilhelmi}\ead{francisco.wilhelmi@upf.edu}
\author[label2]{Cristina~Cano}
\author[label3]{Gergely~Neu}
\author[label1]{Boris~Bellalta} 
\author[label3]{Anders~Jonsson}
\author[label1]{Sergio~Barrachina-Mu\~noz}
\address[label1]{Wireless Networking Research Group (WN-UPF), 08002 Barcelona, Spain}
\address[label2]{Wireless Networks Research Group (WINE-UOC), 08860 Castelldefels (Barelona), Spain}
\address[label3]{Artificial Intelligence and Machine Learning Research Group (AIML-UPF), 08002 Barcelona, Spain}

\begin{abstract}
Next-generation wireless deployments are characterized by being dense and uncoordinated, which often leads to inefficient use of resources and poor performance. To solve this, we envision the utilization of completely decentralized mechanisms to enable Spatial Reuse (SR). In particular, we concentrate in Reinforcement Learning (RL), and more specifically, in Multi-Armed Bandits (MABs), to allow networks to modify both their transmission power and channel based on their experienced throughput. In this work, we study the exploration-exploitation trade-off by means of the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling action-selection strategies. Our results show that optimal proportional fairness can be achieved, even if no information about neighboring networks is available to the learners and WNs operate selfishly. However, there is high temporal variability in the throughput experienced by the individual networks, specially for $\varepsilon$-greedy and EXP3. We identify the cause of this variability to be the adversarial setting of our setup in which the set of most played actions provide intermittent good/poor performance depending on the neighboring decisions. We also show that this variability is reduced using UCB and Thompson sampling, which are parameter-free policies that perform exploration according to the reward distribution of each action.
\end{abstract}

\begin{keyword}
High-Density Wireless Networks, Interference, Decentralized learning, Multi Armed Bandits, Spatial Reuse, Resource Allocation.
\end{keyword}

\end{frontmatter}

%\vfill
%Francesc Wilhelmi (e-mail \href{francisco.wilhelmi@upf.edu}{francisco.wilhelmi@upf.edu}), Sergio Barrachina-Mu\~noz and Boris Bellalta are with the Wireless Networking Research Group, Universitat Pompeu Fabra, 08002 Barcelona, Spain. Cristina Cano is with the Wireless Networks Research Group, Universitat Oberta de Catalunya (UOC), 08860 Castelldefels (Barelona), Spain. Anders~Jonsson and Gergely~Neu are with the Artificial Intelligence and Machine Learning Research Group, Universitat Pompeu Fabra (UPF), 08002 Barcelona, Spain.

\newpage
%% \linenumbers

%%%%%%%%%%%%%%%%%%%%%%%
%%%  I. INTRODUCTION 
%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{section:introduction}
Due to the growing popularity of wireless deployments, especially the ones based on the IEEE 802.11 standard (i.e., Wi-Fi), it is very common to find independent overlapping Wireless Networks (WNs) sharing the same channel resources. Due to the decentralized nature of such kind of deployments, the lack of organization and/or agreement on sharing policies leads to inefficient resources allocation, both in spectral and spatial domains. An illustrative example about the inefficiency noticed in WNs regarding channel sharing can be found in \cite{akella2007self}, where the authors show that the power level used by wireless devices is typically set, by default, to the maximum, regardless of the distance between communicating nodes, and of the channel occupancy \cite{akella2007self}. In decentralized environments, providing a model to obtain the optimal solution can be extremely complex. In WNs, the interactions between devices depend on many features (such as position, environment, transmit power) and are hard to derive. On top of this, network dynamics, in terms of user arrivals and departures, makes the resource allocation problem even harder.

In order to address the SR problem in decentralized WNs, we focus attention on Reinforcement Learning (RL), which has recently become very popular to solve many well-known problems in wireless communications. Some examples can be found for packet routing \cite{littman1993distributed}, Access Point (AP) selection \cite{bojovic2011supervised, bojovic2012neural}, optimal rate sampling \cite{combes2014optimal}, or energy harvesting in heterogeneous networks \cite{miozzo2015distributed}. Using online learning, a learner (or agent) obtains data in a sequential order and uses it to predict future good-performing actions. Online learning is, therefore, useful to cope with complex and dynamic environments. This background encourages us to approach a solution for the decentralized SR problem in WNs through online learning techniques. In particular, we exploit dynamic channel selection and transmit power adjustment for dealing with the performance issues resulting from uncoordinated resource sharing in WNs. While a proper frequency planning allows to reduce the interference between wireless devices, tuning the transmit power adds an extra level of SR that can result in improved throughput and fairness.

From the family of online algorithms, we propose the utilization of Multi-Armed Bandits (MABs) \cite{BCB12}, which is a well-known model in the online learning literature for solving resource allocation problems. In MABs, a given agent seeks to learn a hidden reward distribution while maximizing the gains. This is known as the exploration-exploitation trade-off. %(exploitation focuses on obtaining the maximum instantaneous reward, while exploration aims to maximize the long-term reward)	
While exploitation selects actions with the goal of maximizing long-term reward given the current estimate, exploration selects actions with the goal of improving the estimate. Unlike for classical RL, MABs do not consider states\footnote{A state refers to a particular situation experienced by a given agent, which is defined by a set of conditions. By having an accurate knowledge on its current situation, an agent can define state-specific strategies that maximize its profits.} in general, which can be hard to define for the decentralized SR problem. On the one hand, spatial interference cannot be binary treated, thus leading to complex interactions between nodes. On the other hand, the adversarial setting unleashed by decentralized deployments increases the system complexity, since the state not only depends on the actions taken by a given node, but also on the adversaries behavior.

This work extends our previous results presented in \cite{wilhelmi2017implications}, which were obtained by applying a stateless variation of Q-learning to the SR problem in WNs. Here we generalize the contributions done by implementing several action-selection strategies to allow WNs choose the channel and transmit power to use based on the resulting performance. In this paper, then, we provide a tutorial-based application of MABs to the decentralized SR problem, in order to maximize performance while observing the result from using different SR settings. According to that, we aim to illustrate the main benefits and drawbacks of applying different well-known learning techniques in a selfish way, i.e., independent WNs base their strategy on their own experienced performance. On the one hand, we evaluate the impact of varying parameters intrinsic to the proposed algorithms on the resulting throughput and fairness. In addition, we analyze the effects of learning selfishly, in order to shed some light on the future of decentralized approaches. Notably, we observe that even though players act selfishly, there are algorithms %learn to play collaborative actions
learn to play actions that enhance the overall performance, some times at the cost of high temporal variability. Considering selfish WNs and still obtaining collaborative behaviors is appealing to typical chaotic and dynamic deployments as we get rid of the need for message passing, or inference of neighboring conditions.

The main contributions of this work are summarized below:
\begin{itemize}		
	\item We devise the feasibility of applying MAB algorithms as defined in the online learning literature to solve the resource allocation problem in WNs.
	\item We study the impact of different parameters intrinsic to the action-selection strategies considered (e.g., exploration coefficients, learning rates) on network performance.
	\item We show that there are algorithms learn to play collaborative actions even though the WNs act selfishly, which is appealing to practical application in chaotic and dynamic environments. In addition, we shed some light on the root causes of this phenomena. 
\end{itemize}

The remaining of this document is structured as follows: Section \ref{section:related_work} outlines relevant related work. Section \ref{section:mabs} introduces the proposed learning algorithms and their practical implementation for the resource allocation problem in WNs. Then, Section \ref{section:system_model} presents the simulation scenarios and the considerations taken into account. The simulation results are later presented in Section \ref{section:performance_evaluation}. Finally, Section \ref{section:conclusions} provides some final remarks.

%%%%%%%%%%%%%%%%%%%%%%%
%%%  II. RELATED WORK 
%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
\label{section:related_work} 		
In this paper we approach the decentralized SR problem through Dynamic Channel Allocation (DCA) and Transmit Power Control (TPC). While the former aims to allocate the available frequency range among potentially overlapping WNs, the latter attempts to increase the number of parallel transmissions by adjusting the power transmitted by each WN. While DCA operates at the frequency level, TPC deals with more complex spatial interactions. For that, an approach that dynamically tunes the transmit power may severely affect higher communication layers such as network (routing) or transport (congestion). TPC directly affects the transmission range, the data rate and the energy consumption, and it may create unidirectional links that unleash fairness issues. In fact, acknowledgments (ACKs) and RTS/CTS frames assume bidirectionality.

DCA has been extensively exploited from the centralized perspective, especially through techniques based on graph coloring \cite{riihijarvi2005frequency, mishra2005weighted}. Despite these kind of approaches allow to effectively reduce the interference between WNs, a certain degree of communication is required. Regarding decentralized methods, the authors in \cite{akl2007dynamic} propose a very simple approach in which each AP maintains an interference map of their neighbors, so that channel assignment is done through interference minimization. Unfortunately, the interactions between APs due to decentralization are not studied. Separately, \cite{chen2007improved} proposes two decentralized approaches that rely in the interference measured at both APs and STAs to calculate the best frequency channels for dynamic channel allocation. To do so, a WN, in addition to the interference sensed by its associated devices, considers other metrics such as the amount of traffic, so that some kind of coordination is required at the neighbor level (periodic reporting).

For the case of TPC, one of the first works in studying power management is \cite{elbatt2000power}, which shows that large improvements can be achieved if selecting the appropriate transmit power level in ad-hoc WNs. A centralized approach for TPC is presented in \cite{tang2014joint}, which performs power control and Rate Adaptation (RA) in subgroups of Wireless Local Area Networks (WLANs). The creation of clusters allows defining independent power levels between devices in the same group, which are useful to avoid asymmetric links. However, to represent all the possible combinations, graphs can become very large, specially in high-density deployments. Furthermore, we find a decentralized approach that relies on real-time channel measurements \cite{gandarillas2014dynamic}. The proposed mechanism (so called Dynamic Transmission Power Control) is based on a set of triggered thresholds that increase/decrease the transmit power according to the situation. The main problem is that thresholds are set empirically (based on simulations), so the mechanism may not always improve performance.

%------------------------
% Decentralised Learning: Previous work
%------------------------
\subsection{Solving WNs Resource Allocation Problems via Bandits}
\label{section:previous_work}
In the online learning literature, several MAB settings have been considered such as stochastic bandits \cite{thompson1933likelihood,lai1985asymptotically,auer2002finite}, adversarial bandits \cite{auer1995gambling,auer2002nonstochastic}, restless bandits \cite{whittle1988restless}, contextual bandits \cite{LCLS10} and linear bandits \cite{abe2003reinforcement,APS11}, and numerous exploration-exploitation strategies have been proposed such as \textit{$\varepsilon$-greedy} \cite{sutton1998reinforcement,auer2002finite}, \textit{upper confidence bound} (UCB) \cite{lai1985asymptotically,Agr95,BuKa96,auer2002finite}, \textit{exponential weight algorithm for exploration and exploitation} (EXP3) \cite{auer1995gambling,auer2002finite} and \textit{Thompson sampling} \cite{thompson1933likelihood}. The classical multi-armed bandit problem models a sequential interaction scheme between a learner and an environment. The learner sequentially selects one out of $K$ actions (often called \emph{arms} in this context) and earns some rewards determined by the chosen action and also influenced by the environment. Formally, the problem 
is defined as a repeated game where the following steps are repeated in each round $t=1,2,\dots,T$:
\begin{enumerate}
	\item The environment fixes an assignment of rewards $r_{a,t}$ for each action $a\in[K] \stackrel{\text{def}}{=} \left\{1,2,\dots,K\right\}$,
	\item the learner chooses action $a_t\in[K]$,
	\item the learner obtains and observes reward $r_{a_t,t}$.
\end{enumerate}
The bandit literature largely focuses on the perspective of the learner with the objective of coming up with learning algorithms that attempt to maximize the sum of the rewards gathered during the whole procedure (either with finite or infinite horizon). As noted above, this problem has been studied under various assumptions made on the environment and the structure of the arms. The most important basic cases are the \emph{stochastic} bandit problem where, for each particular arm $a$, the rewards are i.i.d.~realizations of random variables from a fixed (but unknown) distribution $\nu_a$, and the \emph{non-stochastic} (or \emph{adversarial}) bandit problem where the rewards are chosen arbitrarily by the environment. In both cases, the main challenge for the learner is the \emph{partial observability} of the rewards: the learner only gets to observe the reward associated with the chosen action $a_t$, but never observes the rewards realized for the other actions.

Let ${\rm r}_{a^*,t}$ and ${\rm r}_{a,t}$ be the rewards obtained at time $t$ from choosing actions $a^*$ (optimal) and $a$, respectively. Then, the performance of learning algorithms is typically measured by the \emph{total expected regret} defined as  \[R_T = \sum_{t=0}^{T} \mathbb{E}\left[\left({\rm r}_{a^*,t} - {\rm r}_{a,t}\right)\right].\]

An algorithm is said to \emph{learn} if it guarantees that the regret grows sublinearly in $T$, that is, if $R_T = o(T)$ is guaranteed as $T$ grows large, or, equivalently, that the average regret $R_T/T$ converges to zero. Intuitively, sublinear regret means that the learner eventually identifies the action with the highest long-term payoff. Note, as well, that the optimal action $a^*$ is the same across all the rounds. Most bandit algorithms come with some sort of a guaranteed upper bound on $R_T$ which allows for a principled comparison between various methods.

To the best of our knowledge, there is very little related work on applying multi-armed bandit techniques to the problem of resource allocation in WNs. In \cite{coucheney2015multi}, the authors propose modeling a resource allocation problem in LTE networks through MABs. In particular, a set of Base Stations (BS) learn the best configuration of Resource Blocks (RBs) in a decentralized way. For that purpose, a variation of EXP3 (so-called Q-EXP3) is proposed, which allows to reduce the strategy set. Despite a regret bound is provided, it is subject to the fact that an optimal resource allocation exists, i.e., every BS obtains the necessary resources. In addition, a large number of iterations is required to find the optimal solution in a relatively small scenario, thus revealing the difficulties shown by decentralized settings.

More related to the problem proposed here, the authors in \cite{maghsudi2015joint} show a channel selection and power control approach in infrastructureless networks, which is modeled through bandits. In particular, two different strategies are provided to improve the performance of two Device to Device (D2D) users (each one composed by a transmitter and a receiver), which must learn the best channel and transmit power to be selected. Similarly to our problem, users do not have any knowledge on the channel or the other's configuration, so they rely on the experienced performance in order to find the best configuration. An extension of \cite{maghsudi2015joint} is provided by the same authors in \cite{maghsudi2015channel}, which includes a calibrated predictor (referred in the work as \textit{forecaster}) to infer the behavior of the other devices in order to counter act their actions. In each agent, the information of the forecaster is used to choose the highest-rewarding action with a certain probability, while the rest of actions are randomly selected. Henceforth, assuming that all the networks use a given strategy $\mathcal{X}$, fast convergence is ensured. Results show that channel resources are optimally distributed in a very short time frame through a fully decentralized algorithm that does not require any kind of coordination. Both aforementioned works rely in the existence of a unique Nash Equilibrium, which favors convergence. In contrast, in this article we aim to extend Bandits utilization to denser deployments, and, what is more important, to scenarios with limited available resources in which there is not a unique Nash Equilibrium (NE) that allows fast-convergence. Thus, we aim to capture the effects of applying selfish strategies in a decentralized way (i.e., agent $i$ follows a strategy $\mathcal{X}_i$ that does not consider the strategies of the others) and we also provide insight about the importance of past information for learning in dense WNs, which has not been studied before.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%III. MABs APPLICATION									    %	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multi-Armed Bandits for Improving Spatial Reuse in WNs}
\label{section:mabs}	
The decentralized resource allocation problem in WNs we aim to solve in this work can be modeled as an approximation of contextual bandits. Originally, the contextual bandits problem considers the existence of a context (or a state) that influences the action-selection process. As a consequence, the set of available strategies varies with the context and the probability distribution of a given reward depends both on the chosen actions and also on the context. In the resource allocation problem at hand, the context could include information such as the number of neighboring WNs, their position, their current channel selection, the transmission power they use as well as their action-selection strategies, among other. However, we are interested in the case where no context can be inferred given that such information is hard and costly to obtain in practice, especially in dynamic scenarios. Thus, we model the decentralized SR problem in WNs as an adversarial bandit problem, in which the actions of a given WN affect the pay-off distributions of the others' actions. Such model requires the existence of a NE with a pure strategy,\footnote{A pure strategy NE is conformed by a set of strategies and payoffs, so that no player can obtain further benefits by deviating from its strategy.} which does not always hold for unplanned deployments due to the scarcity of the available resources and the number of overlapping WNs. Understanding the implications derived from such an adversarial setting in the absence of a NE is one the main goals of this paper, which, to the best of our knowledge, has been barely considered in the previous literature.

We model this adversarial problem as follows. Let arm $a \in \mathcal{A}$ (we denote the size of $\mathcal{A}$ with K) be a configuration that a WN may choose. Each configuration is a combination of channel and transmit power (e.g., $a_1$ = \{Channel: 1, TPC: 5 dBm\}), and grants a reward that depends on the others' configuration. Let $\Gamma_{i,t}$ be the throughput experienced by $\text{WN}_i$ at time $t$, and $\Gamma_{i}^*$ the maximum achievable throughput by $\text{WN}_i$ in case of isolation (i.e., no interference is experienced in the selected channel). We then define the reward $r_{i,t}$ experienced by $\text{WN}_i$ at time $t$ as:

\begin{equation}
r_{i,t} = {\frac{\Gamma_{i,t}}{{\Gamma_{i}^*}}} \leq 1,
\label{eq:reward_generation}
\nonumber
\end{equation}

For simplicity, we consider that each WN is composed by an AP and a single STA, so that downlink traffic is held. Note that in typical uncoordinated wireless deployments (e.g., residential buildings), STAs are typically close to the AP to which they are associated. Thus, having several STAs associated to the same AP does not significantly impact the inter-WNs interference we study in this work. According to that, $\Gamma_{i}^*$ is computed as $B \cdot \log_{2}(1 + \text{SNR}_{i})$, where $B$ is the bandwidth, and $\text{SNR}_{i}$ is the Signal-to-Noise ratio experienced by the STA of $\text{WN}_i$. We consider this model because it allows to properly capture the interference generated between WNs, which is sought to be minimized.

We have considered the \emph{$\varepsilon$-greedy}, \emph{EXP3}, \emph{UCB} and \emph{Thompson sampling} action-selection strategies, which are described next in this section. While $\varepsilon$-greedy and EXP3 explicitly include the concepts of \emph{exploration coefficient} and \emph{learning rate}, respectively, UCB and Thompson sampling are parameter-free policies that extend the concept of exploration (actions are explored according to their estimated value and not by commitment). Henceforth, we are able to study the effects of these different kind of policies on the WNs behavior. Moreover, we chose the aforementioned policies because they are widely spread and considered of remarkable importance in the MABs literature.

Furthermore, in order to provide a fair comparison, we have considered that all the policies use the same reward. Regarding the learning process, we assume that WNs select actions during the same time slot. The reward experienced by the WNs is computed once all of them have chosen their action for the current iteration. In practice the action-selection process at WNs will most probably not be synchronized but we leave the study of any possible effects of that desynchronization to future work.

%------------------------
% Bandits - e-greedy
%------------------------
\subsection{$\varepsilon$-greedy}
\label{section:bandits_egreedy}	
The \emph{$\varepsilon$-greedy} policy \cite{sutton1998reinforcement,auer2002finite} is arguably the simplest learning algorithm attempting to deal with exploration-exploitation trade-offs. In each round $t$, the $\varepsilon$-greedy algorithm explicitly decides whether to explore or exploit: with probability $\varepsilon$, the algorithm picks an arm uniformly at random (exploration), and otherwise it plays the arm with the highest empirical return $\hat{r}_{k,t}$ (exploitation).

In case $\varepsilon$ is fixed for the entire process, the expected regret is obviously going to grow linearly as $\Omega\left(\varepsilon T\right)$ in general. Therefore, in order to obtain a sublinear regret guarantee (and thus an asymptotically optimal growth rate for the total rewards), it is critical to properly adjust the exploration coefficient. Thus, in our implementation of the $\varepsilon$-greedy algorithm, we use a time-dependent exploration rate of $\varepsilon_t = \varepsilon_0 / \sqrt{t}$, as suggested in the literature \cite{auer2002finite}. The adaptation of this policy to our setting is shown as Algorithm \ref{alg:egreedy}.

\begin{algorithm}[H]	
	\SetAlgoLined
	\KwIn{SNR: information about the Signal-to-Noise Ratio received at the STA, $\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
	\textbf{Initialize:} $t=0$, $\varepsilon_t = \varepsilon_0$, $r_{k} = 0, \forall a_k \in \mathcal{A}$\\
	\While{active}{
		Select $a_k$  $\begin{cases}
		\underset{k=1,...,K}{\text{argmax }} r_{k,t},& \text{with prob. } 1 - \varepsilon\\
		k \sim \mathcal{U}(1, K),              & \text{otherwise}
		\end{cases}$\\
		Observe the throughput experienced $\Gamma_t$\\
		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
		%$p_{k,t} \leftarrow r_{k,t}$\\
		$\varepsilon_t \gets \varepsilon_0 / \sqrt{t}$ \\
		$ t \gets t + 1$
	}
	\caption{Implementation of Multi-Armed Bandits ($\varepsilon$-greedy) in a WN. $\mathcal{U}(1, K)$ is a uniform distribution that randomly chooses from 1 to $K$.}
	\label{alg:egreedy}			
\end{algorithm}

%\begin{algorithm}[h!]
%	\SetKwInOut{Input}{Input}
%	\SetKwInOut{Output}{Output}		
%	Function EXP3 $(\text{SNR},\mathcal{A})$\;
%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
%	initialize: $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 0, \forall a_k \in \mathcal{A}$\\
%	\While{active}
%	{
%		$p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
%		Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
%		Observe the throughput experienced $\Gamma_t$\\
%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
%		$\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
%		$w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
%		$w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
%		%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
%		$\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
%		$t \leftarrow t + 1$\\
%	}
%	\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
%	\label{alg:exp3}
%\end{algorithm}
%
%
%
%	\begin{algorithm}
%	\caption{Implementation of Multi-Armed Bandits ($\varepsilon$-greedy) in a WN. $\mathcal{U}(1, K)$ is a uniform distribution that randomly chooses from 1 to $K$.}
%	\label{alg:egreedy}		
%	\begin{algorithmic}[1]
%		%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
%		\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
%		\While{active}
%		\State Select $a_k$  $\begin{cases}
%		\underset{k=1,...,K}{\text{argmax }} r_{k,t},& \text{with prob. } 1 - \varepsilon\\
%		k \sim \mathcal{U}(1, K),              & \text{otherwise}
%		\end{cases}$\\
%		\State Observe the throughput experienced $\Gamma_t$\\
%		\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
%		%$p_{k,t} \leftarrow r_{k,t}$\\
%		\State $\varepsilon_t \gets \varepsilon_0 / \sqrt{t}$ \\
%		\State $ t \gets t + 1$
%		\EndWhile
%		%\EndProcedure
%	\end{algorithmic}
%\end{algorithm}

%------------------------
% Bandits - EXP3
%------------------------
\subsection{EXP3}
\label{section:bandits_exp3}	
The EXP3 algorithm \cite{auer1995gambling,auer2002nonstochastic} is an adaptation of the weighted majority algorithm of \cite{LW94,FS97} to the non-stochastic bandit problem. EXP3 maintains a set of non-negative weights assigned to each arm and picks the actions randomly with a probability proportional to their respective weights (initialized to 1 for all arms). The aim of EXP3 is to provide higher weights to the best actions as the learning procedure proceeds.

More formally, letting $w_{k,t}$ be the weight of arm $k$ at time $t \in \{1,2 ...\}$, EXP3 computes the probability $p_{k,t}$ of choosing arm $k$ in round $t$ as
\begin{equation}
\label{eq:exp3_prob}
p_{k,t} = (1-\gamma) \frac{w_{k,t}}{\sum_{i=1}^{\text{K}}w_{i,t}} + \frac{\gamma}{K},
\nonumber
\end{equation}
where $\gamma\in[0,1]$ is a parameter controlling the rate of exploration.
Having selected arm $a_t$, the learner observes the generated pay-off $r_{a_t,t}$ and computes the importance-weighted reward estimates
\begin{equation}
\label{eq:exp3_estimated_reward}
\widehat{r}_{k,t} = \frac{\mathbb{I}_{\left\{I_t = k\right\}}r_{k,t}}{p_{k,t}}
\nonumber
\end{equation}
for all $k\in[K]$, where $\mathbb{I}_{\left\{A \right\}}$ denoting the indicator function of the event $A$ taking a value of $1$ if $A$ is true and $0$ otherwise.
Finally, the weight of arm $k$ is updated as a function of the estimated reward:
\begin{equation}
\label{eq:exp3_weights}
w_{k,t+1}=w_{k,t} e^{\frac{\eta \cdot \widehat{r}_{k,t}}{K}},
\nonumber
\end{equation}	
where $\eta>0$ is a parameter of the algorithm often called the \emph{learning rate}. Intuitively, $\eta$ regulates the rate in which the algorithm incorporates new observations with large values of $\eta$ corresponding to more confident updates and smaller values leading to more conservative behavior. As we did for the exploration coefficient in \emph{$\varepsilon$-greedy}, we use a time-dependent learning rate of $\eta_t = \eta_0 / \sqrt{t}$ \cite{auer2002finite}. Our implementation of EXP3 to the WN problem is detailed in Algorithm \ref{alg:exp3}.
%\begin{algorithm}[h!]
%	Function EXP3 $(\text{SNR},\mathcal{A})$\\
%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}\\
%	initialize: $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 0, \forall a_k \in \mathcal{A}$\\
%	\While{active}
%	{
%		$p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
%		Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
%		Observe the throughput experienced $\Gamma_t$\\
%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
%		$\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
%		$w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
%		$w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
%		%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
%		$\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
%		$t \leftarrow t + 1$\\
%	}
%	\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
%	\label{alg:exp3}
%\end{algorithm}

\begin{algorithm}[H]	
	\SetAlgoLined
	\KwIn{SNR: information about the Signal-to-Noise Ratio received at the STA, $\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
	\textbf{Initialize:} $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 0, \forall a_k \in \mathcal{A}$\\
	\While{active}{
		$p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
		Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
		Observe the throughput experienced $\Gamma_t$\\
		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
		$\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
		$w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
		$w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
		%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
		$\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
		$t \leftarrow t + 1$\\
	}		
	\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
	\label{alg:exp3}	
\end{algorithm}
%	\begin{algorithm}
%		\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
%		\label{alg:exp3}
%		\begin{algorithmic}[1]
%			%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
%			\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
%			\While{active}
%			\State $p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
%			\State Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
%			\State Observe the throughput experienced $\Gamma_t$\\
%			\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
%			\State $\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
%			\State $w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
%			\State $w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
%			%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
%			\State $\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
%			\State $t \leftarrow t + 1$\\
%			\EndWhile
%			%\EndProcedure
%		\end{algorithmic}
%	\end{algorithm}

%------------------------
% Bandits - UCB
%------------------------
\subsection{UCB}
\label{section:bandits_ucb}		
The \emph{upper confidence bound} (UCB) action-selection strategy \cite{Agr95,BuKa96,auer2002finite} is based on the principle of \emph{optimism in face of uncertainty}: in each round, UCB selects the arm with the highest statistically feasible mean reward given the past observations. Statistical feasibility here is represented by an upper confidence bound on the mean rewards which shrinks around the empirical rewards as the number of observations increases. Intuitively, UCB trades off exploration and exploitation very effectively, as upon every time a suboptimal arm is chosen, the corresponding confidence bound will shrink significantly, thus quickly decreasing the probability of drawing this arm in the future. The width of the confidence intervals is chosen carefully so that the true best arm never gets discarded accidentally by the algorithm, yet suboptimal arms are not drawn as few times as possible. To obtain the first estimates, each arm is played once at the initialization.

Formally, let $n_k$ be the number of times that arm $k$ has been played, and $\Gamma_{k,t}$ the throughput obtained by playing arm $k$ at time $t$. The average experienced reward $\overline{r}_{k,t}$ by arm $k$ at time $t$ is therefore given by:
\begin{equation}
\label{eq:ucb}
\overline{r}_{k,t} = \frac{1}{n_k} \sum_{s=1}^{n_k} r_{k,s}
\nonumber
\end{equation}	
Based on these average rewards, UCB selects the action that maximizes $\overline{r}_{k,t} + \sqrt{\frac{2 \ln(t)}{n_k}}$. By doing so, UCB implicitly balances exploration and exploitation, as it focuses efforts on the arms that are $i)$ the most promising (with large estimated rewards) or $ii)$ not explored enough (with small $n_k$). Our implementation of UCB to the WN problem is detailed in Algorithm \ref{alg:ucb}.	
%Note as well, that UCB suffers a logarithmic regret, instead of the linear regret granted by ``$\varepsilon$-greedy" \cite{lai1985asymptotically}.	
% According to \cite{auer2002nonstochastic}, the UCB algorithm provides a logarithmic asymptotic regret $R_{T}$ for a given time period $T > 0$, as shown in (\ref{eq:ucb_regret}):
%	\begin{equation}
%	\label{eq:ucb_regret}
%	R_T = G_{max}(T)-\mathop{\mathbb{E}}(G_{\text{UCB}}(T)) \leq 8 \sum_{i:\mu_i < \mu^{*}} \frac{\ln T}{\Delta_i} + \Big(1+\frac{\pi^2}{3}\Big) \sum_{i=1}^{K}\Delta_i  ,
%	\end{equation}	
%	where $G_{max}(T)$ is the maximum achievable gain at $T$, $\mathbb{E}(G_{\text{UCB}}(T))$ is the expected gain obtained at $T$ by applying the UCB policy, $\Delta_i = \mu^{*} - \mu_i$ is the difference between the empirical mean of the best arm and the chosen one. In Equation \ref{eq:ucb_regret}, both expected losses and risks are embodied (first and second term, respectively). 
%\begin{algorithm}[h!]
%	\SetKwInOut{Input}{Input}
%	\SetKwInOut{Output}{Output}		
%	Function UCB $(\text{SNR},\mathcal{A})$\;
%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
%	initialize: $t=0$, play each arm $a_k \in \mathcal{A}$ once\\
%	\While{active}
%	{
%		Draw $a_k = \underset{k=1,...,K}{\text{argmax }} \overline{r}_{k} + \sqrt{\frac{2 ln(t)}{n_{k}}} $ \\
%		Observe the throughput experienced $\Gamma_t$\\			
%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
%		$n_k \leftarrow n_k + 1$\\
%		$ \overline{r}_{k} \leftarrow \frac{1}{n_{k}} \sum_{s=1}^{n_{k}} r_{k,s}$\\
%		$t \leftarrow t + 1$
%	}
%	\caption{Implementation of Multi-Armed Bandits (UCB) in a WN}
%	\label{alg:ucb}
%\end{algorithm}

\begin{algorithm}[]
	\SetAlgoLined
	\KwIn{SNR: information about the Signal-to-Noise Ratio received at the STA, $\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
	\textbf{Initialize:} $t=0$, play each arm $a_k \in \mathcal{A}$ once\\
	\While{active}{
		Draw $a_k = \underset{k=1,...,K}{\text{argmax }} \overline{r}_{k} + \sqrt{\frac{2 ln(t)}{n_{k}}} $ \\
		Observe the throughput experienced $\Gamma_t$\\			
		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
		$n_k \leftarrow n_k + 1$\\
		$ \overline{r}_{k} \leftarrow \frac{1}{n_{k}} \sum_{s=1}^{n_{k}} r_{k,s}$\\
		$t \leftarrow t + 1$
	}		
	\caption{Implementation of Multi-Armed Bandits (UCB) in a WN}
	\label{alg:ucb}			
\end{algorithm}	
%	\begin{algorithm}
%		\caption{Implementation of Multi-Armed Bandits (UCB) in a WN}
%		\label{alg:ucb}	
%		\begin{algorithmic}[1]
%			%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
%			\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
%			\While{active}
%			\State Draw $a_k = \underset{k=1,...,K}{\text{argmax }} \overline{r}_{k} + \sqrt{\frac{2 ln(t)}{n_{k}}} $ \\
%			\State Observe the throughput experienced $\Gamma_t$\\			
%			\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
%			\State $n_k \leftarrow n_k + 1$\\
%			\State $ \overline{r}_{k} \leftarrow \frac{1}{n_{k}} \sum_{s=1}^{n_{k}} r_{k,s}$\\
%			\State $t \leftarrow t + 1$
%			\EndWhile\label{euclidendwhile}
%			%\EndProcedure
%		\end{algorithmic}
%	\end{algorithm}

%------------------------
% Bandits - Thompson sampling
%------------------------
\subsection{Thompson sampling}
\label{section:bandits_thompsons}	
Thompson sampling \cite{thompson1933likelihood} is a well-studied action-selection technique that had been known for its excellent empirical performance \cite{CL11} and was recently proven to achieve strong performance guarantees, often better than those warranted by UCB \cite{AG12,KKM12,KKM13}. Thompson sampling is a Bayesian algorithm: it constructs a probabilistic model of the rewards and assumes a prior distribution of the parameters of said model. Given the data collected during the learning procedure, this policy keeps track of the posterior distribution of the rewards, and pulls arms randomly in a way that the drawing probability of each arm matches the probability of the particular arm being optimal. In practice, this is implemented by sampling the parameter corresponding to each arm from the posterior distribution, and pulling the arm yielding the maximal expected reward under the sampled parameter value.

For the sake of practicality, we aim to apply Thompson sampling using a Gaussian model for the rewards with a standard Gaussian prior as suggested in \cite{agrawal2013further}. By standard calculations, it can be verified that the posterior distribution of the rewards under this model is Gaussian with mean 
\begin{equation}
\hat{r}_k(t) = \frac{\sum_{w=1:k}^{t-1} r_k(t) }{n_k(t) + 1}
\nonumber
\end{equation}
and variance $\sigma_k^2(t) = \frac{1}{n_k + 1}$, where $n_k$ is the number of times that arm $k$ was drawn until the beginning of round $t$. Thus, implementing Thompson sampling in this model amounts to sampling a parameter $\theta_k$ from the Gaussian distribution $\mathcal{N}\left(\hat{r}_k(t),\sigma_k^2(t)\right)$ and choosing the action with the maximal parameter. Our implementation of Thompson sampling to the WN problem is detailed in Algorithm \ref{alg:thompsons}.	
%\begin{algorithm}[h!]
%	\SetKwInOut{Input}{Input}
%	\SetKwInOut{Output}{Output}		
%	Function Thompson sampling $(\text{SNR},\mathcal{A})$\;
%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
%	initialize: $t=0$,  for each arm $a_k \in \mathcal{A}$, set $\hat{r}_{k} = 0$ and $n_k = 0$ \\
%	\While{active}
%	{
%		For each arm $a_k \in \mathcal{A}$, sample $\theta_k(t)$ from normal distribution $\mathcal{N}(\hat{r}_{k}, \frac{1}{n_k + 1})$ \\
%		Play arm $a_{k} = \underset{k=1,...,K}{\text{argmax }} \theta_k(t) $ \\
%		Observe the throughput experienced $\Gamma_t$\\			
%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
%		$ \hat{r}_{k,t} \leftarrow \frac{\hat{r}_{k,t}  n_{k,t} + r_{k,t}}{n_{k,t} + 2}$\\
%		$n_{k,t} \leftarrow n_{k,t} + 1$\\
%		$t \leftarrow t + 1$
%	}
%	\caption{Implementation of Multi-Armed Bandits (Thompson sampling) in a WN}
%	\label{alg:thompsons}
%\end{algorithm}

\begin{algorithm}[]
	\SetAlgoLined
	\KwIn{SNR: information about the Signal-to-Noise Ratio received at the STA, $\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
	\textbf{Initialize:} $t=0$,  for each arm $a_k \in \mathcal{A}$, set $\hat{r}_{k} = 0$ and $n_k = 0$ \\
	\While{active}{
		For each arm $a_k \in \mathcal{A}$, sample $\theta_k(t)$ from normal distribution $\mathcal{N}(\hat{r}_{k}, \frac{1}{n_k + 1})$ \\
		Play arm $a_{k} = \underset{k=1,...,K}{\text{argmax }} \theta_k(t) $ \\
		Observe the throughput experienced $\Gamma_t$\\			
		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
		$ \hat{r}_{k,t} \leftarrow \frac{\hat{r}_{k,t}  n_{k,t} + r_{k,t}}{n_{k,t} + 2}$\\
		$n_{k,t} \leftarrow n_{k,t} + 1$\\
		$t \leftarrow t + 1$
	}		
	\caption{Implementation of Multi-Armed Bandits (Thompson sampling) in a WN}
	\label{alg:thompsons}
\end{algorithm}
%	\begin{algorithm}
%		\caption{Implementation of Multi-Armed Bandits (Thompson sampling) in a WN}
%		\label{alg:thompsons}
%		\begin{algorithmic}[1]
%			%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
%			\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
%			\While{active}
%			\State For each arm $a_k \in \mathcal{A}$, sample $\theta_k(t)$ from normal distribution $\mathcal{N}(\hat{r}_{k}, \frac{1}{n_k + 1})$ \\
%			\State Play arm $a_{k} = \underset{k=1,...,K}{\text{argmax }} \theta_k(t) $ \\
%			\State Observe the throughput experienced $\Gamma_t$\\			
%			\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
%			\State $ \hat{r}_{k,t} \leftarrow \frac{\hat{r}_{k,t}  n_{k,t} + r_{k,t}}{n_{k,t} + 2}$\\
%			\State $n_{k,t} \leftarrow n_{k,t} + 1$\\
%			\State $t \leftarrow t + 1$
%			\EndWhile
%			%\EndProcedure
%		\end{algorithmic}
%	\end{algorithm}

%%%%%%%%%%%%%%%
% III. SYSTEM MODEL %
%%%%%%%%%%%%%%%
\section{System model}
\label{section:system_model}

For the remainder of this work, we study the interactions between several WNs placed in a 3-D scenario that occur when applying MABs in a decentralized manner (with parameters described later in Section \ref{section:simulation_parameters}). For simplicity, we consider WNs to be composed by an Access Point (AP) transmitting to a single Station (STA) in a downlink manner. Additionally, to analyze the adversarial setting when WNs share scarce resources, we consider that the number of channels is equal to half the number of coexisting WNs, thus making the SR even more challenging.

%------------------------
% Channel modelling
%------------------------
\subsection{Channel modeling}
\label{section:channel_modelling}		
Path-loss and shadowing effects are modeled using the log-distance model for indoor communications. The path-loss between WN $i$ and WN $j$ is given by:	
\begin{equation}
\text{PL}_{i,j} = \text{P}_{{\rm tx},i} - \text{P}_{{\rm rx},j} = \text{PL}_0 + 10  \alpha  \log_{10}(d_{i,j}) + \text{G}_{{\rm s}} + \frac{d_{i,j}}{d_{{\rm obs}}} \text{G}_{{\rm o}}, \nonumber
\nonumber
\end{equation}
where $\text{P}_{{\rm tx},i}$ is the transmitted power in dBm by the AP in $\text{WN}_i$, $\alpha$ is the path-loss exponent, $\text{P}_{{\rm rx},j}$ is the power in dBm received at the STA in $\text{WN}_j$, $\text{PL}_0$ is the path-loss at one meter in dB, $d_{i,j}$ is the distance between the transmitter and the receiver in meters, $\text{G}_{{\rm s}}$ is the log-normal shadowing loss in dB, and $\text{G}_{{\rm o}}$ is the obstacles loss in dB. Note that we include the factor $d_{{\rm obs}}$, which is the average distance between two obstacles in meters.

%------------------------
% Throughput calculation
%------------------------
\subsection{Throughput calculation}
\label{section:throughput_calculation}
As previously mentioned, we use the power received and the interference to calculate the maximum theoretical throughput of each WN $i$ at time $t$ by using the Shannon Capacity,
\begin{equation}
\Gamma_{i,t} = B  \log_{2}(1 + \text{SINR}_{i, t}),
\nonumber
\label{eq:shannon_capacity}
\end{equation}
where $B$ is the channel width and the experienced Signal to Interference plus Noise Ratio (SINR) is given by:
\begin{equation}
\text{SINR}_{i,t} = \frac{\text{P}_{i,t}}{\text{I}_{i,t}+\text{N}},
\label{eq:sinr}
\nonumber
\end{equation}
where $\text{P}_{i,t}$ and $\text{I}_{i,t}$ are the received power and the sum of the interference at WN $i$ at time $t$, respectively, and N is the floor noise power. For each WN, we consider the interference to be the total power received from all the APs in the same channel. For capturing the worst-case scenario, we consider that all WNs are continuously transmitting (i.e., we do not consider empty channel periods left by the medium access procedure). Adjacent channel interference is also considered in $\text{I}_{i,t}$, so that the transmitted power leaked to adjacent channels is $20$ dBm lower for each extra channel separation.

%------------------------
% Simulation Parameters
%------------------------
\subsection{Simulation Parameters}
\label{section:simulation_parameters}
According to \cite{bellalta2016ax}, which provides an overview of the IEEE 802.11ax-2019 standard, a typical high-density scenario for residential buildings contains $0.0033 \text{APs}/\text{m}^3$ (i.e., 100 APs in a $100 \times 20 \times 15$ m area). Accordingly, for simulation purposes, we define a map scenario with dimensions $10\times5\times10$ m, containing from 2 to 8 APs. In addition, for the first part of the simulations, we consider a setting containing 4 WNs that form a grid topology. In it, STAs are placed at the maximum possible distance from the other networks.

Table \ref{tbl:simulation_parameters} details the parameters used.	
\begin{table}[h!]
	\centering
	%\resizebox{\columnwidth}{!}{
		\begin{tabular}{|l|l|}
			\hline
			\textbf{Parameter}             & \textbf{Value}                      \\ \hline
			Map size (m)                    & $10\times5\times10$                  \\ \hline
			Number of coexistent WNs      & \{2, 4, 6, 8\} \\ \hline
			APs/STAs per WN                    & 1 / 1                                     \\ \hline
			Distance AP-STA (m)     & $\sqrt{2}$                         \\ \hline
			Number of Channels              & 2                               \\ \hline
			Channel Bandwidth (MHz)         & 20                                    \\ \hline
			Initial channel selection model & Uniformly distributed 
			\\ \hline
			TPC Values (dBm)                & \{5, 10, 15, 20\}                      \\ \hline				
			$\text{PL}_0$ (dB)                   & 5
			\\ \hline
			$\text{G}_s$ (dB)                   & Normally distributed with mean 9.5 
			\\ \hline
			$\text{G}_o$ (dB)                  & Uniformly distributed with mean 30
			\\ \hline
			$d_{\rm obs}$  (meters between two obstacles)                 & 5                        
			\\ \hline
			Noise level (dBm)               & -100                                  \\ \hline
			Traffic model                   & Full buffer (downlink)             \\ \hline          
			Number of learning iterations                  & 10,000             \\ \hline   
	\end{tabular}%}
	\caption{Simulation parameters}
	\label{tbl:simulation_parameters}
\end{table}

%%%%%%%%%%%%%%
% V. SIMULATIONS   %
%%%%%%%%%%%%%%
\section{Performance Evaluation}
\label{section:performance_evaluation}	
In this Section, we evaluate the performance of each action-selection strategy presented in Section \ref{section:mabs} when applied to the decentralized SR problem in WNs.\footnote{All of the source code used in this work open \cite{fwilhelmi2017code}, encouraging sharing of algorithms between contributors and providing the ability for people to improve on the work of others under the GNU General Public License v3.0} For that purpose, we first evaluate the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling policies in a controlled environment. Without loss of generality, we consider a symmetric configuration in this scenario in order to analyze the competition effects when WNs have the same opportunities for accessing the channel. Then, in Section \ref{section:random}, we provide a performance comparison of the aforementioned scenarios with different densities and with randomly located WNs.

\subsection{Toy Grid Scenario}		
\label{section:toy_grid_scenario}	
We start considering a toy scenario consisting in a grid of 4 WNs, as illustrated in Figure \ref{fig:scenario}. This scenario has the particularity of being symmetric, so that adversarial WNs have the same opportunities to compete for the channel resources. Henceforth, this scenario allows us to \emph{i)} simplify the evaluation of the proposed algorithms, \emph{ii)} frame the competition between WNs on equal terms.

\begin{figure}[t!]
	\centering											
	\epsfig{file=images/4_WLANs_scenario.eps, width=8.5cm}
	\caption{Grid scenario containing 4 WNs, each one composed by an AP and a STA.}
	\label{fig:scenario}
\end{figure}

%------------------------
% Optimality study
%------------------------
\subsubsection{Optimal Solution}
\label{section:optimal_solution}	
Before presenting the simulation results of applying a particular action-selection policy, we introduce the optimal solutions that: \emph{i)} maximize the aggregate throughput and \emph{ii)} correspond to proportional fairness\footnote{The proportional fairness solutions satisfy $\underset{a_k \in \mathcal{A}}{\rm max} \sum_{i \in \mathcal{WN}} \log(\Gamma_{i,a_k})$.} for the considered grid scenario, shown in Figure \ref{fig:scenario}.  %Knowing the maximum achievable performance in the presented scenario allows us to provide a meaningful comparison of the introduced policies to be followed by the WNs.

Let actions range from $a_1$ to $a_8$, and map to \{channel number, transmit power (dBm)\}: $a_1$ = \{1, 5\}, $a_2$ = \{2, 5\}, $a_3$ = \{1, 10\}, $a_4$ = \{2, 10\}, $a_5$ = \{1, 15\}, $a_6$ = \{2, 15\}, $a_7$ = \{1, 20\} and $a_8$ = \{2, 20\}. According to our model, the joint configuration of the 4 WNs that grants the maximum aggregate throughput is any combination of actions \{$a_1$, $a_7$, $a_8$\}, subject to the condition of two close WNs using $a_1$. Despite the scenario is symmetric, the distance between APs is not the same in all the cases. For instance, $d_{\text{AP}_1,\text{AP}_2} > d_{\text{AP}_1,\text{AP}_4}$. It is important to emphasize that the proposed scenario does not consider asymmetries between WNs, so that dominance relationships are not present. In case of suffering from such asymmetries, the performance of a given WN would depend on the configuration of its neighboring networks but it won't be able to affect their behavior. For instance, a WN in the middle of two others may suffer from flow starvation if the WNs in the extremes do not sense each other. In such a situation, the WN in the middle is not able to fairly compete for channel resources due to the asymmetric situation it suffers.

In our symmetric scenario, the optimal aggregate throughput is 1124 Mbps, and is only achieved when two consecutive WNs sacrifice themselves by choosing a lower transmit power (action $a_1$). Moreover, to maximize the proportional fairness, the optimal joint configuration changes to any combination using the maximum transmit power (i.e., $a_7$ and $a_8$), so that frequency reuse is maximized; WNs using the same channel must be as much separated as possible. Such a configuration leads to an aggregate throughput of 891 Mbps, which is quite lower than in the former case, but allows experiencing a fairer configuration. Note that all WNs obtain the same throughput in this case as frequency reuse is achieved (closer WNs choose different channels), but power is kept equal for each WN and despite experiencing higher interference, none of the WNs sacrifice themselves. The aim of the following performance evaluation is to gain insight into whether a collaborative result, close to this equal division of resources given by the proportional fair action selection, is likely to be learned by the algorithms and if so, under which conditions.

%------------------------
% Study of MAB (e-greedy)
%------------------------
\subsubsection{Performance of the $\varepsilon$-greedy policy}
\label{section:egreedy_study}	
We first evaluate the performance of the $\varepsilon$-greedy policy when applied to the WNs problem, which allows us to study the purest form of the exploitation-exploration trade-off. First, we show the impact of modifying the initial exploration coefficient, $\varepsilon_0$ (recall that we have considered $\varepsilon_t = \varepsilon_0 / \sqrt{t}$), on the average throughput experienced by the overlapping WNs. Figure \ref{fig:egreedy_tuning_parameters} shows the aggregate throughput obtained in the grid scenario when applying $\varepsilon$-greedy during 10,000 iterations, and for each $\varepsilon_0$ value between 0 and 1 in 0.1 steps. The average and standard deviation of the throughput from 100 simulation runs are shown, which are compared with the optimal throughput presented in Section \ref{section:optimal_solution}.
\begin{figure}[t!]
	\centering							
	\epsfig{file=images/egreedy_tuning_parameters_zoom.eps, width=6.5cm}
	\caption{Average aggregate throughput and standard deviation obtained for each $\varepsilon_0$ value in $\varepsilon$-greedy. Results are from 100 simulations lasting 10,000 iterations each. The proportional fair solution is also shown (red dashed line).}
	\label{fig:egreedy_tuning_parameters}
\end{figure}		
As shown in the figure, the aggregate throughput obtained in average is quite similar for all the provided values of $\varepsilon_0$, except for the complete random case where no exploration is done ($\varepsilon_0 = 0$). The lower the $\varepsilon_0$ parameter, the less exploration is performed. Consequently, for low $\varepsilon_0$, the average throughput is highly dependent on how good/bad were the actions taken at the beginning of the learning process, which results in a higher standard deviation as $\varepsilon_0$ goes to 0.

Now, in order to provide a deeper analysis on the WNs behavior when implementing the $\varepsilon$-greedy policy, we focus on the actions probability and the temporal evolution of throughput derived from a single simulation run. To this aim, we use $\varepsilon_0 = \{0.1, 0.5, 1\}$, which correspond to three representative cases (low exploration, middle degree of exploration and intensive exploration). Figure \ref{fig:eg_actions_distr} shows the action probability distribution at each WN at the end of the 10,000 iteration-long simulation, and for each of the selected $\varepsilon_0$ values.

\begin{figure*}
	\centering
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e01} \\[\abovecaptionskip]
		\small (a) $\varepsilon_0$ = 0.1
		\label{fig:eg_e01_actions_distr}
	\end{tabular}	
	\hspace{\floatsep}	
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e05} \\[\abovecaptionskip]
		\small (b) $\varepsilon_0$ = 0.5
		\label{fig:eg_e05_actions_distr}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e1} \\[\abovecaptionskip]
		\small (c) $\varepsilon_0$ = 1
		\label{fig:eg_1_actions_distr}
	\end{tabular}
	\caption{Probability of taking a given action in $\varepsilon$-greedy for different $\varepsilon_0$ values after a simulation of 10,000 iterations.}
	\label{fig:eg_actions_distr}
\end{figure*}

We observe in this figure that more aggressive actions (i.e., the ones that use the maximum transmit power) are chosen with a higher rate in all the WNs as $\varepsilon_0$ increases. A higher degree of exploration allows WNs to observe the effects of the actions taken by the others, thus acting in consequence. Accordingly, WNs alternate good/poor performance depending on the actions of the others, which at the same time are also selected intermittently. Despite using a high transmit power allows obtaining a better SNR at the receivers, the generated interference at times becomes counter-productive in terms of individual and aggregate throughput.

On the other hand, as $\varepsilon_0$ decreases (refer to Figure \ref{fig:eg_actions_distr}(a)), WNs are prone to exploit the same action more frequently, which are the ones that provide the highest known performance. This low degree of exploration results also in a smaller usage of suboptimal actions.

Figure \ref{fig:eg_agg_tpt}  shows the aggregate throughput evolution, which suffers from higher temporal variability as $\varepsilon_0$ increases. The same observation can be done from the individual throughput evolution (shown in Figure \ref{fig:eg_ind_tpt}), which in addition shows larger differences between the individual patterns for lower $\varepsilon_0$ values. These differences correspond to unfair performance resulting from a low degree of exploration.
% e-greedy: aggregate throughput
\begin{figure*}
	\centering
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e01} \\[\abovecaptionskip]
		\small (a) $\varepsilon_0$ = 0.1
		\label{fig:eg_e01_agg_tpt}
	\end{tabular}	
	\hspace{\floatsep}	
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e05} \\[\abovecaptionskip]
		\small (b) $\varepsilon_0$ = 0.5
		\label{fig:eg_e05_agg_tpt}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e1} \\[\abovecaptionskip]
		\small (c) $\varepsilon_0$ = 1
		\label{fig:eg_e1_agg_tpt}
	\end{tabular}
	\caption{Aggregate throughput evolution for a single $\varepsilon$-greedy 10,000-iterations simulation and for different $\varepsilon_0$ values. The proportional fair result is also shown (red dashed line).}
	\label{fig:eg_agg_tpt}
\end{figure*}

% e-greedy: individual throughput
\begin{figure*}
	\centering
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e01} \\[\abovecaptionskip]
		\small (a) $\varepsilon_0$ = 0.1
		\label{fig:eg_e01_ind_tpt}
	\end{tabular}	
	\hspace{\floatsep}	
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e05} \\[\abovecaptionskip]
		\small (b) $\varepsilon_0$ = 0.5
		\label{fig:eg_e05_ind_tpt}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e1} \\[\abovecaptionskip]
		\small (c) $\varepsilon_0$ = 1
		\label{fig:eg_e1_ind_tpt}
	\end{tabular}
	\caption{Individual throughput evolution for a single $\varepsilon$-greedy 10,000-iterations simulation and for different $\varepsilon_0$ values. The proportional fair result is also shown (red dashed line).}
	\label{fig:eg_ind_tpt}
\end{figure*}

To gain further insight into fairness, we depict in Figure \ref{fig:eg_avg_tpt} the average  and standard deviation of the throughput at each WN. We have now concentrated in the last 5,000 iterations of the simulation, disregarding the instability provoked during the transitory regime, so that we get a better picture of the long-term behavior. We see that as $\varepsilon_0$ increases, the experienced fairness becomes higher due to the temporal fluctuation that occurs as a consequence of performing more exploratory actions. Moreover, we also observe that the standard deviation of the throughput is similar at each WN.

% e-greedy: average throughput
\begin{figure*}
	\centering
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e01} \\[\abovecaptionskip]
		\small (a) $\varepsilon_0$ = 0.1
		\label{fig:eg_e01_avg_tpt}
	\end{tabular}	
	\hspace{\floatsep}	
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e05} \\[\abovecaptionskip]
		\small (b) $\varepsilon_0$ = 0.5
		\label{fig:eg_e05_avg_tpt}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e1} \\[\abovecaptionskip]
		\small (c) $\varepsilon_0$ = 1
		\label{fig:eg_e1_avg_tpt}
	\end{tabular}
	\caption{Average throughput and standard deviation experienced per WN in the last 5,000 iterations of a single $\varepsilon$-greedy 10,000-iterations simulation run for different $\varepsilon_0$ values. The proportional fair result is also shown (red dashed line).}
	\label{fig:eg_avg_tpt}
\end{figure*}

To sum up, we have seen that tuning $\varepsilon_0$ clearly entails a trade-off between the fairness and the temporal variation of throughput. Choosing a low $\varepsilon_0$ value grants low variability, but WNs are prone to fall into local maximums, as the experienced performance is just a consequence of the randomness in taking particular actions. This also generates a fairness problem, since the unlucky WNs end up experiencing lower performance, as well as they are not able to discover the best throughput actions. On the other side, choosing a high $\varepsilon_0$ value results in higher throughput and better long-term fairness but at the expense of intermittent good/poor performance.

%------------------------
% Study of MAB (EXP3)
%------------------------
\subsubsection{Performance of the EXP3 policy}
\label{section:exp3_study}
We now evaluate the trade-off between fairness and temporal throughput variability in the EXP3 policy, which includes the learning rate $\eta$, a parameter that controls how fast old beliefs are replaced by newer ones. In EXP3 we also find the $\gamma$ parameter, which regulates explicit exploration by tuning the importance of weights in the action-selection procedure. Setting $\gamma = 1$ results in completely neglecting weights (actions have the same probability to be chosen). On the other side, setting $\gamma = 0$, the effect of weights are  at its highest. Thus, in order to see clearly the effects of the EXP3 weights, which directly depend on $\eta$, we fix $\gamma$ to 0.

As we did before for $\varepsilon$-greedy, we start analyzing the impact of modifying the input parameters of EXP3 on the average aggregate throughput (Figure \ref{fig:exp3_tuning_parameters}). We vary the initial learning rate, $\eta_0$, between 0 and 1 in 0.1 steps. As it can be observed, setting $\eta_0$ to 0 results in the lowest average throughput, and a low variability is obtained. In this case, action weights are never updated and the arms are randomly chosen with the same probability. As $\eta_0$ increases, the proportional fair solution is approximated at the expense of a higher variability between experiments, since less exploration is performed when $\eta_0$ increases. Note, as well, that the maximum average network throughput is reached for $\eta_0 = 0.6$ in this particular scenario.

\begin{figure}[t!]
	\centering											
	\epsfig{file=images/exp3_tuning_parameters_zoom.eps, width=6.5cm}
	\caption{Average aggregate throughput and standard deviation obtained for each $\eta_0$ value in MAB (EXP3). The aggregate throughput of the proportional fair solution is also shown (red dashed line). Results are from 100 simulations lasting 10,000 iterations each.}
	\label{fig:exp3_tuning_parameters}
\end{figure}

Now, for a single 10,000-iteration simulation, we set $\eta_0 = \{0.1, 0.5, 1\}$ to closely study the implications of modifying the initial learning rate. Figure \ref{fig:exp3_actions_distr} compares the resulting actions probability for these low, medium and high $\eta_0$ values.
% EXP3: action probabilities
\begin{figure*}
	\centering
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta01} \\[\abovecaptionskip]
		\small (a) $\eta_0 = 0.1$
		\label{fig:exp3_eta01_actions_distr}
	\end{tabular}	
	\hspace{\floatsep}	
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta05} \\[\abovecaptionskip]
		\small (b) $\eta_0 = 0.5$
		\label{fig:exp3_eta05_actions_distr}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta1} \\[\abovecaptionskip]
		\small (c) $\eta_0 = 1$
		\label{fig:exp3_eta1_actions_distr}
	\end{tabular}
	\caption{Probability of taking a given action in EXP3 for different $\eta_0$ values after a simulation of 10,000 iterations.}
	\label{fig:exp3_actions_distr}
\end{figure*}

We see that actions are tried with similar probability for $\eta_0 = 0.1$, since the usage of a low learning rate entails a high similarity between weights. This situation is significantly improved for $\eta_0 = 0.5$, in which few actions are selected most of the times. The increased learning rate allows to rapidly capture the effects of the others' actions, since more exploration is carried out. As a consequence, actions using the highest transmit power are clearly preferred to overcome the adversarial setting. Note, as well, that optimal channel allocation is learned by WNs despite competing with each other. Finally, for $\eta_0 = 1$, a single action is clearly preferred by each WN. However, unfair situations eventually occur due to the lack of exploration. In particular, we observe that $\text{WN}_1$ and $\text{WN}_3$, which share the same channel, use very different power levels in their favorite actions (5 and 15 dBm, respectively). This, of course, generates a fairness imbalance that favors $\text{WN}_3$, which enjoys a higher SINR. As mentioned, this behavior occurs eventually, since the variability in the output can be understood as a consequence of a fast convergence achieved during the transitory learning phase. So, results from different simulations will significantly vary.

Figure \ref{fig:exp3_agg_tpt} shows the temporal aggregate throughput, which suffers from a higher variability when $\eta$ is lower. Regarding individual performance, the same behavior can be observed in the temporal throughput evolution (Figure \ref{fig:exp3_ind_tpt}). In this case, setting $\eta_0 = 1$ implies trusting best-performing actions for larger periods, i.e., higher weights are assigned even if actions are suboptimal. Therefore, as $\eta_0$ decreases, the temporal variability increases because the action-selection process becomes uniformly random. However, this variability does not entail that the proportional fair solution is approached. Thus, $\eta_0$ must be carefully set in order to provide a low temporal variability, at the same time that enough exploration is carried out for reaching the optimal fairness solution.

% EXP3: aggregate throughput
\begin{figure*}
	\centering
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta01} \\[\abovecaptionskip]
		\small (a) $\eta_0 = 0.1$
		\label{fig:exp3_eta01_agg_tpt}
	\end{tabular}	
	\hspace{\floatsep}	
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta05} \\[\abovecaptionskip]
		\small (b) $\eta_0 = 0.5$
		\label{fig:exp3_eta05_agg_tpt}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta1} \\[\abovecaptionskip]
		\small (c) $\eta_0 = 1$
		\label{fig:exp3_eta1_agg_tpt}
	\end{tabular}
	\caption{Aggregate throughput evolution for a single EXP3 10000-iterations simulation and for different $\eta_0$ values. The proportional fair result is also shown (red dashed line).}
	\label{fig:exp3_agg_tpt}
\end{figure*}

% EXP3: individual throughput
\begin{figure*}
	\centering
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta01} \\[\abovecaptionskip]
		\small (a) $\eta_0 = 0.1$
		\label{fig:exp3_eta01_ind_tpt}
	\end{tabular}	
	\hspace{\floatsep}	
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta05} \\[\abovecaptionskip]
		\small (b) $\eta_0 = 0.5$
		\label{fig:exp3_eta05_ind_tpt}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta1} \\[\abovecaptionskip]
		\small (c) $\eta_0 = 1$
		\label{fig:exp3_eta1_ind_tpt}
	\end{tabular}
	\caption{Individual throughput evolution for a single EXP3 10000-iterations simulation and for different $\eta_0$ values. The proportional fair result is also shown (red dashed line).}
	\label{fig:exp3_ind_tpt}
\end{figure*}

One can notice a fairness imbalance by observing the individual throughput for $\eta_0 = 1$ in Figure \ref{fig:exp3_ind_tpt}, which is further illustrated in Figure \ref{fig:exp3_avg_tpt} (again, we have considered the last 5,000 iterations to avoid capturing the transitory phase). The average throughput is more evenly distributed for $\eta_0 = 0.1$ and $\eta_0 = 0.5$, but at the expense of the experienced throughput variability seen above. The unfairness suffered for $\eta_0 = 0.1$ can be understood as a lack of exploration that prevents finding a fair resource distribution. Thus, we conclude that a similar trade-off experienced in $\varepsilon$-greedy appears in EXP3 with parameter $\eta_0$. The main difference is that, in this case, a random action-selection process is approximated as $\eta_0$ decreases.
% EXP3: average throughput
\begin{figure*}
	\centering
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta01} \\[\abovecaptionskip]
		\small (a) $\eta_0 = 0.1$
		\label{fig:exp3_eta01_avg_tpt}
	\end{tabular}	
	\hspace{\floatsep}	
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta05} \\[\abovecaptionskip]
		\small (b) $\eta_0 = 0.5$
		\label{fig:exp3_eta05_avg_tpt}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta1} \\[\abovecaptionskip]
		\small (c) $\eta_0 = 1$
		\label{fig:exp3_eta1_avg_tpt}
	\end{tabular}
	\caption{Average throughput and standard deviation experienced per WN in the last 5,000 iterations of a single EXP3 10000-iterations simulation for different $\eta_0$ values. The proportional fair result is also shown (red dashed line).}
	\label{fig:exp3_avg_tpt}
\end{figure*}

%------------------------
% Study of MAB (UCB)
%------------------------
\subsubsection{Performance of the UCB policy}
\label{section:ucb_study}		
Unlike $\varepsilon$-greedy and EXP3, the basic form of UCB does not include any input parameter to regulate variables such as the learning rate or the exploration coefficient. On the contrary, the action-selection process relies in the generated rewards only. We will study in this section how the previously seen trade-off between fair throughput and variability results for this parameter-free policy.

We start by showing the action probability distribution (shown in Figure \ref{fig:actions_probability_ucb}) derived from the UCB implementation. We observe that WNs clearly prefer playing the actions corresponding to proportional fairness (i.e., the actions with highest transmit power and that result in frequency reuse).

\begin{figure}[h!]
	\centering							
	\epsfig{file=images/NEW_actions_probability_UCB.eps, width=6.5cm}
	\caption{Probability of taking a given action in UCB for a simulation of 10,000 iterations.}
	\label{fig:actions_probability_ucb}
\end{figure}

Now, we concentrate in the temporal aggregate throughput (shown in Figure \ref{fig:ucb_agg_tpt}). The results show a very high variability, which slowly decreases as the number of iterations increases. 
The same observations can be done in the individual throughput evolution (Figure \ref{fig:ucb_tpt_evolution}). As a result, UCB provides long-term fairness but at the expense of a high temporal variability caused by exploration. In Figure \ref{fig:ucb_avg_individual} we show the average throughput experienced by each WN, as well as the standard deviation indicating the suffered variability (only for the last 5,000 iterations). As seen before, one can observe really high fairness but considerable variability due to the temporal evolution of throughput.

% UCB: aggregate and individual 
\begin{figure*}
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		%\rule{\linewidth}{\linewidth}
		\includegraphics[width=\textwidth]{images/NEW_temporal_aggregate_tpt_UCB}
		\caption{Aggregate}\label{fig:ucb_agg_tpt}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		%\rule{\linewidth}{\linewidth}
		\includegraphics[width=\textwidth]{images/NEW_temporal_individual_tpt_UCB}
		\caption{Individual}\label{fig:ucb_tpt_evolution}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		%\rule{\linewidth}{\linewidth}
		\includegraphics[width=\textwidth]{images/NEW_mean_tpt_UCB}
		\caption{Average}\label{fig:ucb_avg_individual}
	\end{subfigure}
	\caption{Performance achieved for a single UCB 10,000-iterations simulation. The proportional fair result is also shown (red dashed line). (a) Aggregate throughput evolution, (b) Individual throughput evolution, (c) Average individual throughput (the last 5,000 iterations are considered).}
	\label{fig:ucb_tpt}
\end{figure*}

Compared to $\varepsilon$-greedy and EXP3, UCB shows a clearer preference for selecting the proportional fair solutions. However, the intermittent good/poor performance of the actions due to the adversarial setting still keeps the degree of exploration very high, resulting in high temporal variability.

%------------------------
% Study of MAB (TS)
%------------------------
\subsubsection{Performance of the Thompson sampling policy}
\label{section:ts_study}
Similarly to UCB, in the basic form of Thompson sampling we do not have any tunable parameter. As with the other policies, we use a single 10,000-iteration simulation to show in detail the WNs behavior when applying Thompson sampling. We first show the actions probability in Figure \ref{fig:actions_probability_ts}. Note the well-pronounced preference for the proportional fair actions, which indicates fast convergence and little exploratory operations.

% TS: actions probability
\begin{figure}[t!]
	\centering							
	\epsfig{file=images/NEW_actions_probability_TS.eps, width=6.5cm}
	\caption{Probability of taking a given action in Thompson sampling for a simulation of 10,000 iterations.}
	\label{fig:actions_probability_ts}
\end{figure}

The temporal aggregate throughput is shown in Figure \ref{fig:ts_tpt_evolution}. As it can be observed, Thompson sampling achieves a lower variability in the temporal throughput with respect to UCB. The same observations can be done in the individual throughput evolution (Figure \ref{fig:ts_ind_tpt}). The low temporal variability observed on applying Thompson sampling is highlighted in Figure \ref{fig:ts_avg_individual}, which shows that the average experienced throughput enjoys a low standard deviation. Moreover, high fairness among WNs can be observed.

\begin{figure*}
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		%\rule{\linewidth}{\linewidth}
		\includegraphics[width=\textwidth]{images/NEW_temporal_aggregate_tpt_TS}
		\caption{Aggregate}\label{fig:ts_agg_tpt}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		%\rule{\linewidth}{\linewidth}
		\includegraphics[width=\textwidth]{images/NEW_temporal_individual_tpt_TS}
		\caption{Individual}\label{fig:ts_ind_tpt}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		%\rule{\linewidth}{\linewidth}
		\includegraphics[width=\textwidth]{images/NEW_mean_tpt_TS}
		\caption{Average}\label{fig:ts_avg_individual}
	\end{subfigure}
		\caption{Throughput evolution for a single Thompson sampling 10,000-iterations simulation. The proportional fair result is also shown (red dashed line). (a) Aggregate throughput evolution, (b) Individual throughput evolution, (c) Average individual throughput (the last 5,000 iterations are considered).}
		\label{fig:ts_tpt_evolution}
\end{figure*}

These results show that even though the rewards encourage selfish behavior, the adversarial setting makes Thompson sampling to converge to collaborative actions while keeping the degree of exploration low. Again, this property holds for scenarios where no asymmetries can be found. While the excellent performance we observe echoes other published results that show the superiority of Thompson sampling in various settings \cite{LCLS10}, we highlight that this outstanding empirical performance is actually rather unexpected in our \emph{non-stochastic} setting. Indeed, existing theoretical results only explain the excellent performance of Thompson sampling in \emph{stochastic} bandit problems. On the other hand, the randomization employed by Thompson sampling is at least superficially related to techniques used in game-theoretic online learning \cite{FS97,CBLu06:book}, with the connection made clear only in a special case \cite{Gop13}. The behavior observed in our experiments may indicate a more profound relationship with such game-theoretic algorithms. We leave the investigation of this matter as an exciting direction for future work.

%------------------------
% Random Scenarios - Scalability
%------------------------
\subsection{Random Scenarios}
\label{section:random}
After studying the WNs interactions in the grid scenario, we now evaluate whether the previous conclusions generalize to random scenarios with an arbitrary number of WNs. To this aim, we use the same $10\times5\times 10$ m scenario and randomly allocate $N = \{2, 4, 6, 8\}$ WNs. %Different topologies are captured by placing WNs randomly. With that, we are able to study how the presented policies maintain fairness for different densities and topologies.

We set $\varepsilon_0 = 1$ in $\varepsilon$-greedy, which is the value that granted the highest aggregate throughput in the experiment shown in Figure \ref{fig:egreedy_tuning_parameters}. We do the same for EXP3 and choose $\eta_0 = 0.6$, which grants the highest aggregate throughput in average (refer to Figure \ref{fig:exp3_tuning_parameters}). In Figure \ref{fig:hist_mean_tpt} we show, for each number of networks and action-selection strategy, an histogram of the mean throughput experienced by each WN during the last 5,000 iterations, and for each of the 100 repetitions.
% Histogram mean throughput
\begin{figure*}
	\centering
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_2_WNs} \\[\abovecaptionskip]
		\small (a) N = 2 WNs
		\label{fig:hist_mean_throughput_2}
	\end{tabular}	
	\hspace{\floatsep}	
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_4_WNs} \\[\abovecaptionskip]
		\small (b) N = 4 WNs
		\label{fig:hist_mean_throughput_4}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_6_WNs} \\[\abovecaptionskip]
		\small (c) N = 6 WNs
		\label{fig:hist_mean_throughput_6}
	\end{tabular}
	\hspace{\floatsep}
	\begin{tabular}{@{}c@{}}
		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_8_WNs} \\[\abovecaptionskip]
		\small (c) N = 8 WNs
		\label{fig:hist_imean_throughput_8}
	\end{tabular}
	\caption{Histogram of the average throughput experienced by each WN during the last 5,000 iterations. Results from 100 repetitions are considered.}
	\label{fig:hist_mean_tpt}
\end{figure*}

As we can observe, histograms of UCB and Thompson sampling are slightly narrower in almost all the cases, which indicates a higher fairness experienced by the WNs with respect to the other policies. Note, as well, that for the $N = 2$, results are similar for all the policies because finding a good-performing configuration in low-density environments is more likely to occur. Thus, fewer exploration is required than for higher densities. Note, as well, that the abovementioned collaborative behavior is still present in random scenarios. In accordance to that, WNs acting selfishly are prone to find a configuration whereby SR is improved in a fair manner. We find the main cause of this issue to be the inter-WN interference sensed at a given transmitter-receiver pair, which is very likely to be similar in both devices for the proposed scenarios. Such a property is given when STAs are close to their associated AP, thus allowing to palliate the effects of asymmetries.

To conclude, we evaluate temporal variability in random scenarios. For that, Table \ref{tbl:std_individual_tpt_experienced} shows the average standard deviation of the throughput experienced by each WN during the last 5,000 iterations (again, we concentrate on the regime after the initial learning phase). We consider the average results from 100 repetitions. With this, we are able to evaluate, for each network density, the variability in the temporal throughput provided by each of the policies in random topologies.
% Mean std of the individual throughput	
\begin{table}[h!]
	\centering
	%\resizebox{\columnwidth}{!}{%
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}Number of \\ WNs\end{tabular}}} & \multicolumn{4}{c|}{\textbf{$\overline{\sigma}(\Gamma_{i \in N})$ (Mbps)}} \\ \cline{2-5} 
			& \textbf{$\varepsilon$-greedy} & \textbf{EXP3} & \textbf{UCB} & \textbf{Thompson s.} \\ \hline
			\textbf{2} & 12.1314 & 31.2897 & 31.9422 & 12.2079 \\ \hline
			\textbf{4} & 83.7318 & 95.4976 & 73.9136 & 50.6985 \\ \hline
			\textbf{6} & 120.8570 & 81.3259 & 67.6045 & 62.8171 \\ \hline
			\textbf{8} & 130.0322 & 73.5171 & 63.2272 & 68.8547 \\ \hline
	\end{tabular}%}
	\caption{Mean standard deviation of the throughput experienced $\Gamma_{i \in N}$ by each $WN_i$ during the last 5,000 iterations. 100 repetitions are considered for averaging purposes.}
	\label{tbl:std_individual_tpt_experienced}
\end{table}

As previously seen in the toy grid scenario introduced in Section \ref{section:toy_grid_scenario}, both UCB and Thompson sampling provide the best results in terms of temporal throughput variability. Despite $\varepsilon$-greedy provides very good results for $N=2$, it does not properly scale up with the number of WNs.

%%%%%%%%%%%%%%%
%  VI. CONCLUSIONS  %
%%%%%%%%%%%%%%%
\section{Conclusions }
\label{section:conclusions}
In this paper, we provided a tutorial-like implementation of MABs to address the decentralized SR problem in dense WNs. Unlike previous literature, we have focused on a situation in which few resources are available, thus bringing out the competition issues raised from the adversarial setting. Our results show that decentralized learning allows improving SR in dense WN, so that collaborative results in symmetric scenarios, sometimes close to optimal proportional fairness, can be achieved. This result is achieved even though WNs act selfishly, aiming to maximize their own throughput. In addition, this behavior is observed for random scenarios, where the effects of asymmetries cannot be controlled. %However, using only local information in limited resources scenarios conducts to an adversarial setting in which a pure strategy does not exist, which prevents reaching a Nash Equilibrium. In the WNs case, applying decentralized learning in such an adversarial setting entails noticing a high temporal variability in the experienced throughput. 
These collaborative actions are, at times, accompanied by high temporal throughput variability, which can be understood as a consequence of the  rate at which networks change their configuration in response of the opponents behavior. A high temporal variability may provoke negative issues in a node's performance, as its effects may be propagated to higher layers of the protocol stack. For instance, a high throughput fluctuation may entail behavioral anomalies in protocols such as Transmission Control Protocol (TCP). %In this case, the temporal fluctuation of the throughput would directly affect the Contention Window (CW) used in TCP for congestion control, providing a poor performance. 
We have studied this trade-off between fair resource allocation and high temporal throughput variability in $\varepsilon$-greedy, EXP3, UCB and Thompson sampling action-selection strategies. Our results show that while this trade-off is hard to regulate via the learning parameters in $\varepsilon$-greedy and EXP3, UCB  and, especially, Thompson sampling are able to achieve fairness at a reduced temporal variability. We identify the root cause of this phenomena to the fact that both UCB and Thompson sampling consider the probability distribution of the rewards, and not only their magnitude.

We left as future work to further study the MABs application to WNs through distributed (with message passing) and centralized (with complete information) approaches with shared reward. Furthermore, we would like to extend this work to enhance both throughput and stability by inferring the actions of the opponents and acting in consequence. Defining the resource allocation problem as an adversarial game is one possibility to do so. Finally, we intend to particularize to IEEE 802.11 WLANs to study the effects of applying RL when using a medium access protocol such as CSMA. In fact, this would let us consider dynamic Carrier Sense Threshold (CST) to further enable SR.

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  ACKNOWLEDGEMENT  		  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%
% use section* for acknowledgment
% The Computer Society usually uses the plural form
\section*{Acknowledgments}
This work has been partially supported by the Spanish Ministry of Economy and Competitiveness under the Maria de Maeztu Units of Excellence Programme (MDM-2015-0502), by the European Regional Development Fund under grant TEC2015-71303-R (MINECO/FEDER), and by a Gift from CISCO University Research Program (CG\#890107) \& Silicon Valley Community Foundation.

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  BIBLIOGRAPHY    
%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliographystyle{unsrt}
\bibliography{references}

\end{document}

### 2018-09-06 OLD SUBMISSION/Article (Elsevier) - LaTeX files/collaborative_spatial_reuse_via_mabs.tex
New + old submission differentiation

--- 2018-05-28 Article - LaTeX files/collaborative_spatial_reuse_via_mabs.tex
@@
 Next-generation wireless deployments are characterized by being dense and uncoordinated, which often leads to inefficient use of resources and poor performance.
-To solve this, we envision the utilization of completely decentralized mechanisms to enable Spatial Reuse (SR).
+To solve this, we envision the utilization of completely decentralized mechanisms to \francesc{enable} Spatial Reuse (SR).
 In particular, we concentrate in Reinforcement Learning (RL), and more specifically, in Multi-Armed Bandits (MABs), to allow networks to modify both their transmission power and channel based on their experienced throughput.
@@
 \label{section:introduction}
-Due to the growing popularity of wireless deployments, especially the ones based on the IEEE 802.11 standard (i.e., Wi-Fi), it is very common to find independent overlapping Wireless Networks (WNs) sharing the same channel resources.
+Due to the growing popularity of wireless deployments, especially the ones based on the IEEE 802.11 standard (i.e., Wi-Fi), it is very common to find independent overlapping Wireless Networks (WNs) \francesc{sharing the same channel resources.
 Due to the decentralized nature of such kind of deployments, the lack of organization and/or agreement on sharing policies leads to inefficient resources allocation, both in spectral and spatial domains.
 An illustrative example about the inefficiency noticed in WNs regarding channel sharing can be found in \cite{akella2007self}, where the authors show that the power level used by wireless devices is typically set, by default, to the maximum, regardless of the distance between communicating nodes, and of the channel occupancy \cite{akella2007self}.
-In decentralized environments, providing a model to obtain the optimal solution can be extremely complex.
+In decentralized environments}, providing a model to obtain the optimal solution can be extremely complex.
 In WNs, the interactions between devices depend on many features (such as position, environment, transmit power) and are hard to derive.
@@
 
-In order to address the SR problem in decentralized WNs, we focus attention on Reinforcement Learning (RL), which has recently become very popular to solve many well-known problems in wireless communications.
-Some examples can be found for packet routing \cite{littman1993distributed}, Access Point (AP) selection \cite{bojovic2011supervised, bojovic2012neural}, optimal rate sampling \cite{combes2014optimal}, or energy harvesting in heterogeneous networks \cite{miozzo2015distributed}.
-Using online learning, a learner (or agent) obtains data in a sequential order and uses it to predict future good-performing actions.
-Online learning is, therefore, useful to cope with complex and dynamic environments.
+\francesc{In order to address the SR problem in decentralized WNs, we focus attention on Reinforcement Learning (RL), which has recently become very popular to solve many well-known problems in wireless communications.
+Some examples can be found for packet routing \cite{littman1993distributed}, Access Point (AP) selection \cite{bojovic2011supervised, bojovic2012neural}, optimal rate sampling \cite{combes2014optimal}, or energy harvesting in heterogeneous networks \cite{miozzo2015distributed}.} Using online learning, a learner (or agent) obtains data in a sequential order and uses it to predict future good-performing actions.
+Online learning is, therefore, useful to \francesc{cope with} complex and dynamic environments.
 This background encourages us to approach a solution for the decentralized SR problem in WNs through online learning techniques.
-In particular, we exploit dynamic channel selection and transmit power adjustment for dealing with the performance issues resulting from uncoordinated resource sharing in WNs.
-While a proper frequency planning allows to reduce the interference between wireless devices, tuning the transmit power adds an extra level of SR that can result in improved throughput and fairness.
-
-From the family of online algorithms, we propose the utilization of Multi-Armed Bandits (MABs) \cite{BCB12}, which is a well-known model in the online learning literature for solving resource allocation problems.
-In MABs, a given agent seeks to learn a hidden reward distribution while maximizing the gains.
+\francesc{In particular, we exploit dynamic \francesc{channel selection} and transmit power adjustment \francesc{for dealing} with the performance issues resulting from uncoordinated resource sharing in WNs.
+While a proper frequency planning allows to reduce the interference between wireless devices, tuning the transmit power adds an extra level of SR that can result in improved throughput and fairness.}
+
+From the family of online algorithms, we propose \francesc{the utilization of} Multi-Armed Bandits (MABs) \cite{BCB12}, which is a well-known model in the online learning literature for solving resource allocation problems.
+In MABs, \francesc{a given agent seeks} to learn a hidden reward distribution while maximizing the gains.
 This is known as the exploration-exploitation trade-off.
@@
 While exploitation selects actions with the goal of maximizing long-term reward given the current estimate, exploration selects actions with the goal of improving the estimate.
-Unlike for classical RL, MABs do not consider states\footnote{A state refers to a particular situation experienced by a given agent, which is defined by a set of conditions.
-By having an accurate knowledge on its current situation, an agent can define state-specific strategies that maximize its profits.} in general, which can be hard to define for the decentralized SR problem.
+\francesc{Unlike for classical RL, MABs do not consider states\footnote{\francesc{A state refers to a particular situation experienced by a given agent, which is defined by a set of conditions.
+By having an accurate knowledge on its current situation, an agent can define state-specific strategies that maximize its profits.}} in general, which can be hard to define for the decentralized SR problem.
 On the one hand, spatial interference cannot be binary treated, thus leading to complex interactions between nodes.
-On the other hand, the adversarial setting unleashed by decentralized deployments increases the system complexity, since the state not only depends on the actions taken by a given node, but also on the adversaries behavior.
+On the other hand, the adversarial setting unleashed by decentralized deployments increases the system complexity, since the state not only depends on the actions taken by a given node, but also on the adversaries behavior.}
 
@@
 Here we generalize the contributions done by implementing several action-selection strategies to allow WNs choose the channel and transmit power to use based on the resulting performance.
-In this paper, then, we provide a tutorial-based application of MABs to the decentralized SR problem, in order to maximize performance while observing the result from using different SR settings.
-According to that, we aim to illustrate the main benefits and drawbacks of applying different well-known learning techniques in a selfish way, i.e., independent WNs base their strategy on their own experienced performance.
+\francesc{In this paper, then, we provide a tutorial-based application of MABs to the decentralized SR problem, in order} to maximize performance while observing the result from using different SR settings.
+\francesc{According to that, we aim to illustrate the main benefits and drawbacks of applying different well-known learning techniques in a selfish way, i.e., independent WNs base their strategy on their own experienced performance.
 On the one hand, we evaluate the impact of varying parameters intrinsic to the proposed algorithms on the resulting throughput and fairness.
-In addition, we analyze the effects of learning selfishly, in order to shed some light on the future of decentralized approaches.
-Notably, we observe that even though players act selfishly, there are algorithms %learn to play collaborative actions
+In addition, we analyze the effects of learning selfishly, in order to shed some light on the future of decentralized approaches.} Notably, we observe that even though players act selfishly, there are algorithms %learn to play collaborative actions
 learn to play actions that enhance the overall performance, some times at the cost of high temporal variability.
 Considering selfish WNs and still obtaining collaborative behaviors is appealing to typical chaotic and dynamic deployments as we get rid of the need for message passing, or inference of neighboring conditions.
+%\francesco{As later shown, this condition holds as long as adversarial WNs are able to compete for channel resources on equal terms.
+Otherwise, selfish learning would lead to unfairness situations, since WNs in a dominant position would take advantage of their situation, thus harming the performance of WNs in weaker situations.}
+%	In particular, we exploit dynamic \francesc{channel selection} and transmit power adjustment \francesc{for dealing} with the performance issues resulting from uncoordinated resource sharing in WNs.
+While a proper frequency planning allows to reduce the interference between wireless devices, tuning the transmit power adds an extra level of SR that can result in improved throughput and fairness.
+%We aim to adjust both the channel allocation and transmit power by using local information only.
+This consideration models typical chaotic and dynamic deployments (e.g., residential buildings) without extra overhead (such as information sharing, additional software and/or hardware).
+%	We consider selfish WNs that aim to maximize their own throughput and evaluate the impact of this on the resulting throughput and fairness while varying parameters intrinsic to the algorithms.
 
@@
 \label{section:related_work} 		
-In this paper we approach the decentralized SR problem through Dynamic Channel Allocation (DCA) and Transmit Power Control (TPC).
+\francesc{In this paper we approach the decentralized SR problem through Dynamic Channel Allocation (DCA) and Transmit Power Control (TPC).
 While the former aims to allocate the available frequency range among potentially overlapping WNs, the latter attempts to increase the number of parallel transmissions by adjusting the power transmitted by each WN.
@@
 TPC directly affects the transmission range, the data rate and the energy consumption, and it may create unidirectional links that unleash fairness issues.
-In fact, acknowledgments (ACKs) and RTS/CTS frames assume bidirectionality.
-
-DCA has been extensively exploited from the centralized perspective, especially through techniques based on graph coloring \cite{riihijarvi2005frequency, mishra2005weighted}.
+In fact, acknowledgments (ACKs) and RTS/CTS frames assume bidirectionality.}
+
+\francesc{DCA has been extensively exploited from the centralized perspective, especially through techniques based on graph coloring \cite{riihijarvi2005frequency, mishra2005weighted}.
 Despite these kind of approaches allow to effectively reduce the interference between WNs, a certain degree of communication is required.
@@
 Unfortunately, the interactions between APs due to decentralization are not studied.
-Separately, \cite{chen2007improved} proposes two decentralized approaches that rely in the interference measured at both APs and STAs to calculate the best frequency channels for dynamic channel allocation.
-To do so, a WN, in addition to the interference sensed by its associated devices, considers other metrics such as the amount of traffic, so that some kind of coordination is required at the neighbor level (periodic reporting).
-
-For the case of TPC, one of the first works in studying power management is \cite{elbatt2000power}, which shows that large improvements can be achieved if selecting the appropriate transmit power level in ad-hoc WNs.
+Separately, \cite{chen2007improved} proposes two decentralized approaches
+%and one centralized 
+that rely in the interference measured at both APs and STAs to calculate the best frequency channels for dynamic channel allocation.
+To do so, a WN, in addition to the interference sensed by its associated devices, considers other metrics such as the amount of traffic, so that some kind of coordination is required at the neighbor level (periodic reporting).} %With respect to the centralized approach, which is shown to significantly improve the decentralized solutions, the main drawback is the requirement of a wired infrastructure for the management communication.
+Such deployment is often infeasible, especially in typical residential scenarios.
+
+\francesc{For the case of TPC, one of the first works in studying power management is \cite{elbatt2000power}, which shows that large improvements can be achieved if selecting the appropriate transmit power level in ad-hoc WNs.
 A centralized approach for TPC is presented in \cite{tang2014joint}, which performs power control and Rate Adaptation (RA) in subgroups of Wireless Local Area Networks (WLANs).
@@
 The proposed mechanism (so called Dynamic Transmission Power Control) is based on a set of triggered thresholds that increase/decrease the transmit power according to the situation.
-The main problem is that thresholds are set empirically (based on simulations), so the mechanism may not always improve performance.
+The main problem is that thresholds are set empirically (based on simulations), so the mechanism may not always improve performance.}
 
@@
 To the best of our knowledge, there is very little related work on applying multi-armed bandit techniques to the problem of resource allocation in WNs.
-In \cite{coucheney2015multi}, the authors propose modeling a resource allocation problem in LTE networks through MABs.
+\francesc{In \cite{coucheney2015multi}, the authors propose modeling a resource allocation problem in LTE networks through MABs.
 In particular, a set of Base Stations (BS) learn the best configuration of Resource Blocks (RBs) in a decentralized way.
@@
 Despite a regret bound is provided, it is subject to the fact that an optimal resource allocation exists, i.e., every BS obtains the necessary resources.
-In addition, a large number of iterations is required to find the optimal solution in a relatively small scenario, thus revealing the difficulties shown by decentralized settings.
-
-More related to the problem proposed here, the authors in \cite{maghsudi2015joint} show a channel selection and power control approach in infrastructureless networks, which is modeled through bandits.
+In addition, a large number of iterations is required to find the optimal solution in a relatively small scenario, thus revealing the difficulties shown by decentralized settings.}
+
+\francesc{More related to the problem proposed here,} the authors in \cite{maghsudi2015joint} show a channel selection and power control approach in infrastructureless networks, which is modeled through bandits.
 In particular, two different strategies are provided to improve the performance of two Device to Device (D2D) users (each one composed by a transmitter and a receiver), which must learn the best channel and transmit power to be selected.
@@
 However, we are interested in the case where no context can be inferred given that such information is hard and costly to obtain in practice, especially in dynamic scenarios.
-Thus, we model the decentralized SR problem in WNs as an adversarial bandit problem, in which the actions of a given WN affect the pay-off distributions of the others' actions.
-Such model requires the existence of a NE with a pure strategy,\footnote{A pure strategy NE is conformed by a set of strategies and payoffs, so that no player can obtain further benefits by deviating from its strategy.} which does not always hold for unplanned deployments due to the scarcity of the available resources and the number of overlapping WNs.
-Understanding the implications derived from such an adversarial setting in the absence of a NE is one the main goals of this paper, which, to the best of our knowledge, has been barely considered in the previous literature.
+Thus, we model the decentralized \francesc{SR} problem in WNs as an adversarial bandit problem, in which the actions of a given WN affect the pay-off distributions of the others' actions.
+Such model requires the existence of a NE with a pure strategy,\footnote{\francesc{A pure strategy NE is conformed by a set of strategies and payoffs, so that no player can obtain further benefits by deviating from its strategy.}} which \francesc{does not always hold for} unplanned deployments due to the scarcity of the available resources and the number of overlapping \francesc{WNs}.
+Understanding the implications derived from such an adversarial setting in the absence of a NE is one the main goals of this paper, \francesc{which, to the best of our knowledge, has been barely considered in the previous literature}.
 
@@
 
-For simplicity, we consider that each WN is composed by an AP and a single STA, so that downlink traffic is held.
+\francesc{For simplicity, we consider that each WN is composed by an AP and a single STA, so that downlink traffic is held.
 Note that in typical uncoordinated wireless deployments (e.g., residential buildings), STAs are typically close to the AP to which they are associated.
-Thus, having several STAs associated to the same AP does not significantly impact the inter-WNs interference we study in this work.
-According to that, $\Gamma_{i}^*$ is computed as $B \cdot \log_{2}(1 + \text{SNR}_{i})$, where $B$ is the bandwidth, and $\text{SNR}_{i}$ is the Signal-to-Noise ratio experienced by the STA of $\text{WN}_i$.
+Thus, having several STAs associated to the same AP does not significantly impact the inter-WNs interference we study in this work.} According to that, $\Gamma_{i}^*$ is computed as $B \cdot \log_{2}(1 + \text{SNR}_{i})$, where $B$ is the bandwidth, and $\text{SNR}_{i}$ is the Signal-to-Noise ratio experienced by the STA of $\text{WN}_i$.
 We consider this model because it allows to properly capture the interference generated between WNs, which is sought to be minimized.
@@
 
-For the remainder of this work, we study the interactions between several WNs placed in a 3-D scenario that occur when applying MABs in a decentralized manner (with parameters described later in Section \ref{section:simulation_parameters}).
+For the remainder of this work, \francesc{we study the interactions between several WNs placed in a 3-D scenario that occur when applying MABs in a decentralized manner} (with parameters described later in Section \ref{section:simulation_parameters}).
 For simplicity, we consider WNs to be composed by an Access Point (AP) transmitting to a single Station (STA) in a downlink manner.
-Additionally, to analyze the adversarial setting when WNs share scarce resources, we consider that the number of channels is equal to half the number of coexisting WNs, thus making the SR even more challenging.
+\francesc{Additionally, to analyze the adversarial setting when WNs share scarce resources,} we consider that the number of channels is equal to half the number of coexisting WNs, thus making the SR even more challenging.
 
@@
 In this Section, we evaluate the performance of each action-selection strategy presented in Section \ref{section:mabs} when applied to the decentralized SR problem in WNs.\footnote{All of the source code used in this work open \cite{fwilhelmi2017code}, encouraging sharing of algorithms between contributors and providing the ability for people to improve on the work of others under the GNU General Public License v3.0} For that purpose, we first evaluate the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling policies in a controlled environment.
-Without loss of generality, we consider a symmetric configuration in this scenario in order to analyze the competition effects when WNs have the same opportunities for accessing the channel.
+Without loss of generality, we consider a symmetric configuration in this scenario \francesc{in order to analyze the competition effects when WNs have the same opportunities for accessing the channel}.
 Then, in Section \ref{section:random}, we provide a performance comparison of the aforementioned scenarios with different densities and with randomly located WNs.
@@
 \label{section:toy_grid_scenario}	
-We start considering a toy scenario consisting in a grid of 4 WNs, as illustrated in Figure \ref{fig:scenario}.
+\francesc{We start considering a toy scenario consisting in a grid of 4 WNs, as illustrated in Figure \ref{fig:scenario}.
 This scenario has the particularity of being symmetric, so that adversarial WNs have the same opportunities to compete for the channel resources.
-Henceforth, this scenario allows us to \emph{i)} simplify the evaluation of the proposed algorithms, \emph{ii)} frame the competition between WNs on equal terms.
+Henceforth, this scenario allows us to \emph{i)} simplify the evaluation of the proposed algorithms, \emph{ii)} frame the competition between WNs on equal terms.}
 
@@
 Let actions range from $a_1$ to $a_8$, and map to \{channel number, transmit power (dBm)\}: $a_1$ = \{1, 5\}, $a_2$ = \{2, 5\}, $a_3$ = \{1, 10\}, $a_4$ = \{2, 10\}, $a_5$ = \{1, 15\}, $a_6$ = \{2, 15\}, $a_7$ = \{1, 20\} and $a_8$ = \{2, 20\}.
-According to our model, the joint configuration of the 4 WNs that grants the maximum aggregate throughput is any combination of actions \{$a_1$, $a_7$, $a_8$\}, subject to the condition of two close WNs using $a_1$.
+\francesc{According to our model, the joint configuration of the 4 WNs that grants the maximum aggregate throughput is any combination of actions \{$a_1$, $a_7$, $a_8$\}, subject to the condition of two close WNs using $a_1$.
 Despite the scenario is symmetric, the distance between APs is not the same in all the cases.
-For instance, $d_{\text{AP}_1,\text{AP}_2} > d_{\text{AP}_1,\text{AP}_4}$.
-It is important to emphasize that the proposed scenario does not consider asymmetries between WNs, so that dominance relationships are not present.
+For instance, $d_{\text{AP}_1,\text{AP}_2} > d_{\text{AP}_1,\text{AP}_4}$.} \francesco{It is important to emphasize that the proposed scenario does not consider asymmetries between WNs, so that dominance relationships are not present.
 In case of suffering from such asymmetries, the performance of a given WN would depend on the configuration of its neighboring networks but it won't be able to affect their behavior.
 For instance, a WN in the middle of two others may suffer from flow starvation if the WNs in the extremes do not sense each other.
-In such a situation, the WN in the middle is not able to fairly compete for channel resources due to the asymmetric situation it suffers.
-
-In our symmetric scenario, the optimal aggregate throughput is 1124 Mbps, and is only achieved when two consecutive WNs sacrifice themselves by choosing a lower transmit power (action $a_1$).
-Moreover, to maximize the proportional fairness, the optimal joint configuration changes to any combination using the maximum transmit power (i.e., $a_7$ and $a_8$), so that frequency reuse is maximized; WNs using the same channel must be as much separated as possible.
-Such a configuration leads to an aggregate throughput of 891 Mbps, which is quite lower than in the former case, but allows experiencing a fairer configuration.
+In such a situation, the WN in the middle is not able to fairly compete for channel resources due to the asymmetric situation it suffers.}
+
+\francesc{In our symmetric scenario, the optimal aggregate throughput is 1124 Mbps, and is only achieved when two consecutive WNs sacrifice themselves by choosing a lower transmit power (action $a_1$).
+Moreover, to maximize the proportional fairness, the optimal joint configuration changes to any combination using the maximum transmit power (i.e., $a_7$ and $a_8$), so that frequency reuse is maximized; WNs using the same channel must be as much separated as possible.} Such a configuration leads to an aggregate throughput of 891 Mbps, which is quite lower than in the former case, but allows experiencing a fairer configuration.
 Note that all WNs obtain the same throughput in this case as frequency reuse is achieved (closer WNs choose different channels), but power is kept equal for each WN and despite experiencing higher interference, none of the WNs sacrifice themselves.
@@
 \label{section:egreedy_study}	
-We first evaluate the performance of the $\varepsilon$-greedy policy when applied to the WNs problem, which allows us to study the purest form of the exploitation-exploration trade-off.
+We first \francesc{evaluate} the performance of the $\varepsilon$-greedy policy when applied to the WNs problem, which allows us to study the purest form of the exploitation-exploration trade-off.
 First, we show the impact of modifying the initial exploration coefficient, $\varepsilon_0$ (recall that we have considered $\varepsilon_t = \varepsilon_0 / \sqrt{t}$), on the average throughput experienced by the overlapping WNs.
@@
 As $\eta_0$ increases, the proportional fair solution is approximated at the expense of a higher variability between experiments, since less exploration is performed when $\eta_0$ increases.
-Note, as well, that the maximum average network throughput is reached for $\eta_0 = 0.6$ in this particular scenario.
+Note, as well, that the maximum average network throughput is reached for $\eta_0 = 0.6$ \francesc{in this particular scenario.}
 
@@
 These results show that even though the rewards encourage selfish behavior, the adversarial setting makes Thompson sampling to converge to collaborative actions while keeping the degree of exploration low.
-Again, this property holds for scenarios where no asymmetries can be found.
-While the excellent performance we observe echoes other published results that show the superiority of Thompson sampling in various settings \cite{LCLS10}, we highlight that this outstanding empirical performance is actually rather unexpected in our \emph{non-stochastic} setting.
+\francesco{Again, this property holds for scenarios where no asymmetries can be found.} While the excellent performance we observe echoes other published results that show the superiority of Thompson sampling in various settings \cite{LCLS10}, we highlight that this outstanding empirical performance is actually rather unexpected in our \emph{non-stochastic} setting.
 Indeed, existing theoretical results only explain the excellent performance of Thompson sampling in \emph{stochastic} bandit problems.
@@
 Thus, fewer exploration is required than for higher densities.
-Note, as well, that the abovementioned collaborative behavior is still present in random scenarios.
+\francesco{Note, as well, that the abovementioned collaborative behavior is still present in random scenarios.
 In accordance to that, WNs acting selfishly are prone to find a configuration whereby SR is improved in a fair manner.
 We find the main cause of this issue to be the inter-WN interference sensed at a given transmitter-receiver pair, which is very likely to be similar in both devices for the proposed scenarios.
-Such a property is given when STAs are close to their associated AP, thus allowing to palliate the effects of asymmetries.
+Such a property is given when STAs are close to their associated AP, thus allowing to palliate the effects of asymmetries.}
 
@@
 \label{section:conclusions}
-In this paper, we provided a tutorial-like implementation of MABs to address the decentralized SR problem in dense WNs.
+\francesc{In this paper, we provided a tutorial-like implementation of MABs to address the decentralized SR problem in dense WNs.
 Unlike previous literature, we have focused on a situation in which few resources are available, thus bringing out the competition issues raised from the adversarial setting.
-Our results show that decentralized learning allows improving SR in dense WN, so that collaborative results in symmetric scenarios, sometimes close to optimal proportional fairness, can be achieved.
+Our results show that} decentralized learning allows improving SR in dense WN, so that collaborative results \francesco{in symmetric scenarios}, sometimes close to optimal proportional fairness, can be achieved.
 This result is achieved even though WNs act selfishly, aiming to maximize their own throughput.
-In addition, this behavior is observed for random scenarios, where the effects of asymmetries cannot be controlled.
-%However, using only local information in limited resources scenarios conducts to an adversarial setting in which a pure strategy does not exist, which prevents reaching a Nash Equilibrium.
+\francesco{In addition, this behavior is observed for random scenarios, where the effects of asymmetries cannot be controlled.} %However, using only local information in limited resources scenarios conducts to an adversarial setting in which a pure strategy does not exist, which prevents reaching a Nash Equilibrium.
 In the WNs case, applying decentralized learning in such an adversarial setting entails noticing a high temporal variability in the experienced throughput.
@@
 Finally, we intend to particularize to IEEE 802.11 WLANs to study the effects of applying RL when using a medium access protocol such as CSMA.
-In fact, this would let us consider dynamic Carrier Sense Threshold (CST) to further enable SR.
+In fact, this would let us consider dynamic Carrier Sense Threshold (CST) to further \francesc{enable} SR.
 

### 2018-09-06 OLD SUBMISSION/Article (new version) - LaTeX files/collaborative_spatial_reuse_in_wireless_networks_via_selfish_mabs.tex
New + old submission differentiation

--- 2018-09-06 OLD SUBMISSION/Article (Elsevier) - LaTeX files/collaborative_spatial_reuse_via_mabs.tex
@@
-%% 
-%% Copyright 2007, 2008, 2009 Elsevier Ltd
-%% 
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
-%% SP 2008/03/01
-
-\documentclass[preprint,12pt]{elsarticle}
-
-\usepackage{graphicx} 	  %% The graphicx package provides the includegraphics command.
-\usepackage{amssymb} 	%% The amssymb package provides various useful mathematical symbols
-
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+
+\ifCLASSOPTIONcompsoc
+% IEEE Computer Society needs nocompress option
+% requires cite.sty v4.0 or later (November 2003)
+\usepackage[nocompress]{cite}
+\else
+% normal IEEE
+\usepackage{cite}
+\fi
+
+\usepackage[table,xcdraw]{xcolor}
 \usepackage{color}
@@
 \usepackage{mathtools}
-\usepackage{fullpage}
-\usepackage{algorithmic}
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\argmax}{argmax}
-\algsetup{linenosize=\small}
+%\usepackage{fullpage}
 \usepackage[table,xcdraw]{xcolor}
@@
 \usepackage[super]{nth}
-\usepackage{graphicx,adjustbox}
-\usepackage{caption}
-\usepackage[labelformat=simple]{subcaption}
 \usepackage{comment}
@@
 \usepackage{tablefootnote}
+\usepackage{booktabs}
+\usepackage[misc]{ifsym}
+\usepackage{bbding}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+\usepackage{authblk}
+
+\usepackage{caption}
+\usepackage{latexsym}
+\usepackage{mathtools}
+\usepackage{multirow}
+\usepackage{cprotect}
+
+%% The graphicx package provides the includegraphics command.
+\usepackage[]{graphicx}
+
+\usepackage{algorithm}% http://ctan.org/pkg/algorithm
+%\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
+
+\usepackage{caption}
+\usepackage{subcaption}
+
+\usepackage[algo2e]{algorithm2e}
+
+%\usepackage{lmodern}
+
+\DeclareMathOperator*{\argmin}{argmin}
 \DeclareMathOperator{\E}{\mathbb{E}} % Expectation Symbol
-\usepackage[linesnumbered,ruled]{algorithm2e}
-\usepackage{booktabs}
-\usepackage{hyperref}
-\usepackage[normalem]{ulem}
-\usepackage{footnote}
-\usepackage[misc,geometry]{ifsym} 
-\makesavenoteenv{tabular}
 
@@
 
-\renewcommand\thesubfigure{(\alph{subfigure})}
-\let\OldTexttrademark\texttrademark
-\renewcommand{\texttrademark}{\OldTexttrademark\xspace}%
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%\usepackage{authblk}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-\usepackage{epsfig}
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
 \newcommand{\francesc}[1]{\textcolor{blue}{#1}}
-\newcommand{\francesco}[1]{\textcolor{orange}{#1}}
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-\journal{Computer Networks}
+
+\makeatletter
+\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
+\makeatother
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
 
@@
 
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
 	\title{Collaborative Spatial Reuse in Wireless Networks via Selfish Multi-Armed Bandits}
 
-\author[label1, label4]{Francesc Wilhelmi}\ead{francisco.wilhelmi@upf.edu}
-\author[label2]{Cristina~Cano}
-\author[label3]{Gergely~Neu}
-\author[label1]{Boris~Bellalta} 
-\author[label3]{Anders~Jonsson}
-\author[label1]{Sergio~Barrachina-Mu\~noz}
-\address[label1]{Wireless Networking Research Group (WN-UPF), 08002 Barcelona, Spain}
-\address[label2]{Wireless Networks Research Group (WINE-UOC), 08860 Castelldefels (Barelona), Spain}
-\address[label3]{Artificial Intelligence and Machine Learning Research Group (AIML-UPF), 08002 Barcelona, Spain}
-
+	\author{\IEEEauthorblockN{
+		Francesc~Wilhelmi\Envelope,
+		Cristina~Cano,
+		Gergely~Neu, 
+		Boris~Bellalta,
+		Anders~Jonsson and
+		Sergio~Barrachina-Mu\~noz}}
+
+%	\thanks{F.
+Wilhelmi, B.
+Bellalta and S.
+Barrachina-Mu\~noz are with the Wireless Networking Research Group (WNRG) at Universitat Pompeu Fabra (UPF), Barcelona, 08018 Spain e-maill: francisco.wilhelmi@upf.edu.}
+%	\thanks{C. Cano is with the Wireless Networks Research Group (WINE) at Universitat Oberta de Catalunya (UOC), Castelldefels, 08060 Spain.}
+%	\thanks{G. Neu and A. Jonsson are with the Artificial Intelligence and Machine Learning Research Group (AIML) at Universitat Pompeu Fabra (UPF), Barcelona, 08018 Spain.}
+	%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
+
+	% The paper headers
+	\markboth{}%
+	{Francesc Wilhelmi \MakeLowercase{\textit{et al.}}: Collaborative Spatial Reuse in Wireless Networks via Selfish Multi-Armed Bandits}
+
+	\IEEEtitleabstractindextext{%
 		\begin{abstract}
@@
 We also show that this variability is reduced using UCB and Thompson sampling, which are parameter-free policies that perform exploration according to the reward distribution of each action.
+			%Next-generation wireless deployments are characterized by being dense and uncoordinated.
+The lack of self-adjustment mechanisms often leads to inefficient use of resources and poor performance.
+To solve this, we envision the utilization of completely decentralized mechanisms that enhance Spatial Reuse (SR).
+In particular, we concentrate in Reinforcement Learning (RL), and more specifically, in Multi-Armed Bandits (MABs), to allow networks to modify both their transmission power and channel based on their experienced throughput.
+In this work, we study the exploration-exploitation trade-off by means of the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling action-selection strategies.
+Our results show that optimal proportional fairness can be achieved, even if no information about neighboring networks is available to the learners.
+With that, we prove collaborative behaviors that favor a set of WNs can be obtained even if they operate in a selfish way, which is useful to avoid centralization costs (e.g., message passing, additional hardware).
+However, there is high temporal variability in the throughput experienced by the individual networks, specially for $\varepsilon$-greedy and EXP3.
+We identify the cause of this variability to be the adversarial setting of our setup in which the set of most played actions provide intermittent good/poor performance depending on the neighboring decisions.
+We also show that this variability is reduced using UCB and Thompson sampling, which are parameter-free policies that perform exploration according to the reward distribution of each action.
+In particular, Thompson sampling shows promising results regarding the achieved performance while keeping temporal variability low.
 		\end{abstract}
 
-\begin{keyword}
-High-Density Wireless Networks, Interference, Decentralized learning, Multi Armed Bandits, Spatial Reuse, Resource Allocation.
-\end{keyword}
-
-\end{frontmatter}
-
-%\vfill
-%Francesc Wilhelmi (e-mail \href{francisco.wilhelmi@upf.edu}{francisco.wilhelmi@upf.edu}), Sergio Barrachina-Mu\~noz and Boris Bellalta are with the Wireless Networking Research Group, Universitat Pompeu Fabra, 08002 Barcelona, Spain.
-Cristina Cano is with the Wireless Networks Research Group, Universitat Oberta de Catalunya (UOC), 08860 Castelldefels (Barelona), Spain.
-Anders~Jonsson and Gergely~Neu are with the Artificial Intelligence and Machine Learning Research Group, Universitat Pompeu Fabra (UPF), 08002 Barcelona, Spain.
-
-\newpage
-%% \linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%  I. INTRODUCTION 
-%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{section:introduction}
-Due to the growing popularity of wireless deployments, especially the ones based on the IEEE 802.11 standard (i.e., Wi-Fi), it is very common to find independent overlapping Wireless Networks (WNs) \francesc{sharing the same channel resources.
+		% Note that keywords are not normally used for peerreview papers.
+		\begin{IEEEkeywords}
+			High-Density Wireless Networks, Interference, Decentralized learning, Multi Armed Bandits, Resource Allocation.
+		\end{IEEEkeywords}}
+
+	\maketitle
+
+	\IEEEdisplaynontitleabstractindextext
+
+	\IEEEpeerreviewmaketitle
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	% I. INTRODUCTION											 %
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
+
+	\IEEEPARstart{D}{ue} to the growing popularity of wireless deployments, especially the ones based on the IEEE 802.11 standard (i.e., Wi-Fi), it is very common to find independent overlapping Wireless Networks (WNs) \francesc{sharing the same channel resources.
 Due to the decentralized nature of such kind of deployments, the lack of organization and/or agreement on sharing policies leads to inefficient resources allocation, both in spectral and spatial domains.
@@
 \francesc{Unlike for classical RL, MABs do not consider states\footnote{\francesc{A state refers to a particular situation experienced by a given agent, which is defined by a set of conditions.
-By having an accurate knowledge on its current situation, an agent can define state-specific strategies that maximize its profits.}} in general, which can be hard to define for the decentralized SR problem.
+By having an accurate knowledge on its current situation, an agent can define state-specific strategies that maximize its profits.}} in general, which can be hard define for the decentralized SR problem.
 On the one hand, spatial interference cannot be binary treated, thus leading to complex interactions between nodes.
-On the other hand, the adversarial setting unleashed by decentralized deployments increases the system complexity, since the state not only depends on the actions taken by a given node, but also on the adversaries behavior.}
+On the other hand, the adversarial setting unleashed by decentralized deployments increases the , since the state not only depends on the actions taken by a given node, but also on the adversaries behavior.}
 
@@
 Considering selfish WNs and still obtaining collaborative behaviors is appealing to typical chaotic and dynamic deployments as we get rid of the need for message passing, or inference of neighboring conditions.
-%\francesco{As later shown, this condition holds as long as adversarial WNs are able to compete for channel resources on equal terms.
-Otherwise, selfish learning would lead to unfairness situations, since WNs in a dominant position would take advantage of their situation, thus harming the performance of WNs in weaker situations.}
+
 %	In particular, we exploit dynamic \francesc{channel selection} and transmit power adjustment \francesc{for dealing} with the performance issues resulting from uncoordinated resource sharing in WNs.
@@
 
+	%------------------------
+	% Article Structure
+	%------------------------
+
 	The remaining of this document is structured as follows: Section \ref{section:related_work} outlines relevant related work.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%  II. RELATED WORK 
-%%%%%%%%%%%%%%%%%%%%%%%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	% II. RELATED WORK											 %
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 	\section{Related Work}
@@
 While the former aims to allocate the available frequency range among potentially overlapping WNs, the latter attempts to increase the number of parallel transmissions by adjusting the power transmitted by each WN.
-While DCA operates at the frequency level, TPC deals with more complex spatial interactions.
+While DCA operate at the frequency level, TPC deals with more complex spatial interactions.
 For that, an approach that dynamically tunes the transmit power may severely affect higher communication layers such as network (routing) or transport (congestion).
@@
 The main problem is that thresholds are set empirically (based on simulations), so the mechanism may not always improve performance.}
+
+%	Dynamic Channel Allocation (DCA) aims to allocate the available frequency range among overlapping wireless devices, so that interference is reduced and the aggregate throughput is maximized.
+We find many centralized solutions based on graph coloring techniques \cite{riihijarvi2005frequency, mishra2005weighted}, which result to be impractical in uncoordinated scenarios, since there is no communication between the implied nodes.
+
+	%The authors in \cite{akl2007dynamic} propose a very simple approach in which each AP maintains an interference map of their neighbors , such that channel assignment is done through interference minimization.
+Unfortunately, the interactions between APs due to decentralization are not studied.
+Separately, \cite{chen2007improved} proposes two decentralized approaches and one centralized that rely in the interference measured at both APs and STAs to calculate the best frequency channels for dynamic channel allocation.
+To do so, a WN, in addition to the interference sensed by its associated devices, considers other metrics such as the amount of traffic, so that some kind of coordination is required at the neighbor level (periodic reporting).
+With respect to the centralized approach, which is shown to significantly improve the decentralized solutions, the main drawback is the requirement of a wired infrastructure for the management communication.
+Such deployment is often infeasible, especially in typical residential scenarios.
+
+%	Regarding Transmit Power Control (TPC), it is possible to increase the number of parallel transmissions or reaching farther distances by adjusting the power transmitted by each WN.
+However, modifying the transmit power may severely affect higher communication layers such as network (routing) or transport (congestion).
+TPC directly affects the transmission range, the data rate and the energy consumption, and it may create unidirectional links that unleash fairness issues.
+In fact, acknowledgments (ACKs) and RTS/CTS frames assume bidirectionality.
+One of the first works in studying power management is \cite{elbatt2000power}, which shows that large improvements can be achieved if selecting the appropriate transmit power level in ad-hoc WNs.
+A centralized approach for TPC is presented in \cite{tang2014joint}, which performs power control and Rate Adaptation (RA) in subgroups of Wireless Local Area Networks (WLANs).
+The creation of clusters allows defining independent power levels between devices in the same group, which are useful to avoid asymmetric links.
+However, to represent all the possible combinations, graphs can become very large, specially in high-density deployments.
+Furthermore, we find a decentralized approach that relies on real-time channel measurements \cite{gandarillas2014dynamic}.
+The proposed mechanism (so called Dynamic Transmission Power Control) is based on a set of triggered thresholds that increase/decrease the transmit power according to the situation.
+The main problem is that thresholds are set empirically (based on simulations), so the mechanism may not always improve performance.
 
@@
 For that purpose, a variation of EXP3 (so-called Q-EXP3) is proposed, which allows to reduce the strategy set.
-Despite a regret bound is provided, it is subject to the fact that an optimal resource allocation exists, i.e., every BS obtains the necessary resources.
+Despite a regret bound is provided, it is subject to the fact that a perfect resource allocation exists.
 In addition, a large number of iterations is required to find the optimal solution in a relatively small scenario, thus revealing the difficulties shown by decentralized settings.}
 
-\francesc{More related to the problem proposed here,} the authors in \cite{maghsudi2015joint} show a channel selection and power control approach in infrastructureless networks, which is modeled through bandits.
+	\francesc{With a higher degree of relation to the problem proposed here,} the authors in \cite{maghsudi2015joint} show a channel selection and power control approach in infrastructureless networks, which is modeled through bandits.
 In particular, two different strategies are provided to improve the performance of two Device to Device (D2D) users (each one composed by a transmitter and a receiver), which must learn the best channel and transmit power to be selected.
@@
 
-\francesc{For simplicity, we consider that each WN is composed by an AP and a single STA, so that downlink traffic is held.
+	\francesc{For simplicity, we consider that each WN is composed by an AP and a single STA.
 Note that in typical uncoordinated wireless deployments (e.g., residential buildings), STAs are typically close to the AP to which they are associated.
-Thus, having several STAs associated to the same AP does not significantly impact the inter-WNs interference we study in this work.} According to that, $\Gamma_{i}^*$ is computed as $B \cdot \log_{2}(1 + \text{SNR}_{i})$, where $B$ is the bandwidth, and $\text{SNR}_{i}$ is the Signal-to-Noise ratio experienced by the STA of $\text{WN}_i$.
+Thus, having several STAs associated to the same AP does not significant impact to the inter-WNs interference that is aimed to be studied in this work.} According to that, $\Gamma_{i}^*$ is computed as $B \cdot \log_{2}(1 + \text{SNR}_{i})$, where $B$ is the bandwidth, and $\text{SNR}_{i}$ is the Signal-to-Noise ratio experienced by the STA of $\text{WN}_i$.
 We consider this model because it allows to properly capture the interference generated between WNs, which is sought to be minimized.
@@
 	%\end{algorithm}
-
 	\begin{algorithm}[H]	
@@
 
-For the remainder of this work, \francesc{we study the interactions between several WNs placed in a 3-D scenario that occur when applying MABs in a decentralized manner} (with parameters described later in Section \ref{section:simulation_parameters}).
+	For the remainder of this work, we consider several WNs placed in a 3-D scenario in order to study the effects of applying MABs in a decentralized manner (with parameters described later in Section \ref{section:simulation_parameters}).
 For simplicity, we consider WNs to be composed by an Access Point (AP) transmitting to a single Station (STA) in a downlink manner.
-\francesc{Additionally, to analyze the adversarial setting when WNs share scarce resources,} we consider that the number of channels is equal to half the number of coexisting WNs, thus making the SR even more challenging.
+We consider as well that the number of channels is equal to half the number of coexisting WNs, so that SR is challenging.
 
@@
 In it, STAs are placed at the maximum possible distance from the other networks.
-
+The 4-grid scenario is illustrated in Figure \ref{fig:scenario}.
+	\begin{figure}[t!]
+		\centering											
+		\epsfig{file=images/4_WLANs_scenario.eps, width=6.5cm}
+		\caption{Grid scenario containing 4 WNs, each one composed by an AP and a STA.}
+		\label{fig:scenario}
+	\end{figure}
 	Table \ref{tbl:simulation_parameters} details the parameters used.	
@@
 		\centering
-	%\resizebox{\columnwidth}{!}{
+		\resizebox{\columnwidth}{!}{
 			\begin{tabular}{|l|l|}
@@
 				Number of learning iterations                  & 10,000             \\ \hline   
-	\end{tabular}%}
+		\end{tabular}}
 		\caption{Simulation parameters}
@@
 	\label{section:performance_evaluation}	
-In this Section, we evaluate the performance of each action-selection strategy presented in Section \ref{section:mabs} when applied to the decentralized SR problem in WNs.\footnote{All of the source code used in this work open \cite{fwilhelmi2017code}, encouraging sharing of algorithms between contributors and providing the ability for people to improve on the work of others under the GNU General Public License v3.0} For that purpose, we first evaluate the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling policies in a controlled environment.
-Without loss of generality, we consider a symmetric configuration in this scenario \francesc{in order to analyze the competition effects when WNs have the same opportunities for accessing the channel}.
+	In this Section, we evaluate the performance of each action-selection strategy presented in Section \ref{section:mabs} when applied to the resource allocation problem in WNs.\footnote{All of the source code used in this work open \cite{fwilhelmi2017code}, encouraging sharing of algorithms between contributors and providing the ability for people to improve on the work of others under the GNU General Public License v3.0} For that purpose, we first evaluate the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling policies in a controlled environment (i.e., the scenario illustrated in Figure \ref{fig:scenario}).
+Without loss of generality, we consider a symmetric configuration in this scenario in order to simplify evaluation.
 Then, in Section \ref{section:random}, we provide a performance comparison of the aforementioned scenarios with different densities and with randomly located WNs.
@@
 	\label{section:toy_grid_scenario}
-\francesc{We start considering a toy scenario consisting in a grid of 4 WNs, as illustrated in Figure \ref{fig:scenario}.
-This scenario has the particularity of being symmetric, so that adversarial WNs have the same opportunities to compete for the channel resources.
-Henceforth, this scenario allows us to \emph{i)} simplify the evaluation of the proposed algorithms, \emph{ii)} frame the competition between WNs on equal terms.}
-
-\begin{figure}[t!]
-	\centering											
-	\epsfig{file=images/4_WLANs_scenario.eps, width=8.5cm}
-	\caption{Grid scenario containing 4 WNs, each one composed by an AP and a STA.}
-	\label{fig:scenario}
-\end{figure}
 
@@
 	\label{section:optimal_solution}	
-Before presenting the simulation results of applying a particular action-selection policy, we introduce the optimal solutions that: \emph{i)} maximize the aggregate throughput and \emph{ii)} correspond to proportional fairness\footnote{The proportional fairness solutions satisfy $\underset{a_k \in \mathcal{A}}{\rm max} \sum_{i \in \mathcal{WN}} \log(\Gamma_{i,a_k})$.} for the considered grid scenario, shown in Figure \ref{fig:scenario}.
+	Before presenting the simulation results of applying a particular action-selection policy, we introduce the optimal solutions that: \emph{a)} maximize the aggregate throughput and \emph{b)} correspond to proportional fairness for the considered grid scenario, shown in Figure \ref{fig:scenario}.
+The proportional fairness solutions satisfy $\underset{a_k \in \mathcal{A}}{\rm max} \sum_{i \in \mathcal{WN}} \log(\Gamma_{i,a_k})$.
 %Knowing the maximum achievable performance in the presented scenario allows us to provide a meaningful comparison of the introduced policies to be followed by the WNs.
@@
 	Let actions range from $a_1$ to $a_8$, and map to \{channel number, transmit power (dBm)\}: $a_1$ = \{1, 5\}, $a_2$ = \{2, 5\}, $a_3$ = \{1, 10\}, $a_4$ = \{2, 10\}, $a_5$ = \{1, 15\}, $a_6$ = \{2, 15\}, $a_7$ = \{1, 20\} and $a_8$ = \{2, 20\}.
-\francesc{According to our model, the joint configuration of the 4 WNs that grants the maximum aggregate throughput is any combination of actions \{$a_1$, $a_7$, $a_8$\}, subject to the condition of two close WNs using $a_1$.
-Despite the scenario is symmetric, the distance between APs is not the same in all the cases.
-For instance, $d_{\text{AP}_1,\text{AP}_2} > d_{\text{AP}_1,\text{AP}_4}$.} \francesco{It is important to emphasize that the proposed scenario does not consider asymmetries between WNs, so that dominance relationships are not present.
-In case of suffering from such asymmetries, the performance of a given WN would depend on the configuration of its neighboring networks but it won't be able to affect their behavior.
-For instance, a WN in the middle of two others may suffer from flow starvation if the WNs in the extremes do not sense each other.
-In such a situation, the WN in the middle is not able to fairly compete for channel resources due to the asymmetric situation it suffers.}
-
-\francesc{In our symmetric scenario, the optimal aggregate throughput is 1124 Mbps, and is only achieved when two consecutive WNs sacrifice themselves by choosing a lower transmit power (action $a_1$).
-Moreover, to maximize the proportional fairness, the optimal joint configuration changes to any combination using the maximum transmit power (i.e., $a_7$ and $a_8$), so that frequency reuse is maximized; WNs using the same channel must be as much separated as possible.} Such a configuration leads to an aggregate throughput of 891 Mbps, which is quite lower than in the former case, but allows experiencing a fairer configuration.
+According to our model, the action selection of the 4 WNs that grants the maximum aggregate throughput is any consecutive combination of \{$a_1$, $a_1$, $a_7$, $a_8$\}.
+	Despite the scenario is symmetric, the distance between WNs is not the same in all the cases.
+Henceforth, the optimal solution in terms of aggregate throughput requires that WNs using the maximum transmit power are located as closely as possible.
+In the case of proportional fairness, the optimal selection changes to any combination of \{$a_7$, $a_8$\} in which WNs using the same channel are located each other at the farthest possible distance.
+
+	The optimal aggregate throughput when throughput is maximized is 1124 Mbps.
+This is achieved when two of the WNs sacrifice themselves by choosing a lower transmit power (action $a_1$).
+%This result is then not likely to occur in an adversarial selfish setting.
+	On the other hand, when considering proportional fairness, the best configuration grants an aggregate throughput of 891 Mbps, which is quite lower than in the former case, but allows experiencing a fairer  configuration.
 Note that all WNs obtain the same throughput in this case as frequency reuse is achieved (closer WNs choose different channels), but power is kept equal for each WN and despite experiencing higher interference, none of the WNs sacrifice themselves.
@@
 	\label{section:egreedy_study}	
-We first \francesc{evaluate} the performance of the $\varepsilon$-greedy policy when applied to the WNs problem, which allows us to study the purest form of the exploitation-exploration trade-off.
+	We first study the performance of the $\varepsilon$-greedy policy when applied to the WNs problem, which allows us to study the purest form of the exploitation-exploration trade-off.
 First, we show the impact of modifying the initial exploration coefficient, $\varepsilon_0$ (recall that we have considered $\varepsilon_t = \varepsilon_0 / \sqrt{t}$), on the average throughput experienced by the overlapping WNs.
@@
 The lower the $\varepsilon_0$ parameter, the less exploration is performed.
-Consequently, for low $\varepsilon_0$, the average throughput is highly dependent on how good/bad were the actions taken at the beginning of the learning process, which results in a higher standard deviation as $\varepsilon_0$ goes to 0.
+Consequently, for low $\varepsilon_0$ the average throughput is highly dependent on how good/bad were the actions taken at the beginning of the learning process, which results in a higher standard deviation as $\varepsilon_0$ goes to 0.
 
@@
 To this aim, we use $\varepsilon_0 = \{0.1, 0.5, 1\}$, which correspond to three representative cases (low exploration, middle degree of exploration and intensive exploration).
+
 	Figure \ref{fig:eg_actions_distr} shows the action probability distribution at each WN at the end of the 10,000 iteration-long simulation, and for each of the selected $\varepsilon_0$ values. 
-
 	\begin{figure*}
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e01} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_actions_probability_e-greedy_e01} \\[\abovecaptionskip]
 			\small (a) $\varepsilon_0$ = 0.1
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e05} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_actions_probability_e-greedy_e05} \\[\abovecaptionskip]
 			\small (b) $\varepsilon_0$ = 0.5
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e1} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_actions_probability_e-greedy_e1} \\[\abovecaptionskip]
 			\small (c) $\varepsilon_0$ = 1
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e01} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e01} \\[\abovecaptionskip]
 			\small (a) $\varepsilon_0$ = 0.1
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e05} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e05} \\[\abovecaptionskip]
 			\small (b) $\varepsilon_0$ = 0.5
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e1} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e1} \\[\abovecaptionskip]
 			\small (c) $\varepsilon_0$ = 1
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e01} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e01} \\[\abovecaptionskip]
 			\small (a) $\varepsilon_0$ = 0.1
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e05} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e05} \\[\abovecaptionskip]
 			\small (b) $\varepsilon_0$ = 0.5
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e1} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e1} \\[\abovecaptionskip]
 			\small (c) $\varepsilon_0$ = 1
@@
 Moreover, we also observe that the standard deviation of the throughput is similar at each WN.
-
 	% e-greedy: average throughput
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e01} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_mean_tpt_e-greedy_e01} \\[\abovecaptionskip]
 			\small (a) $\varepsilon_0$ = 0.1
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e05} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_mean_tpt_e-greedy_e05} \\[\abovecaptionskip]
 			\small (b) $\varepsilon_0$ = 0.5
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e1} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_mean_tpt_e-greedy_e1} \\[\abovecaptionskip]
 			\small (c) $\varepsilon_0$ = 1
@@
 We vary the initial learning rate, $\eta_0$, between 0 and 1 in 0.1 steps.
-As it can be observed, setting $\eta_0$ to 0 results in the lowest average throughput, and a low variability is obtained.
-In this case, action weights are never updated and the arms are randomly chosen with the same probability.
-As $\eta_0$ increases, the proportional fair solution is approximated at the expense of a higher variability between experiments, since less exploration is performed when $\eta_0$ increases.
-Note, as well, that the maximum average network throughput is reached for $\eta_0 = 0.6$ \francesc{in this particular scenario.}
-
 	\begin{figure}[t!]
@@
 	\end{figure}	
+	As it can be observed, setting $\eta_0$ to 0 results in the lowest average throughput, and a low variability is obtained.
+In this case, action weights are never updated and the arms are randomly chosen with the same probability.
+As $\eta_0$ increases, the proportional fair solution is approximated at the expense of a higher variability between experiments, since less exploration is performed when $\eta_0$ increases.
+Note, as well, that the maximum average network throughput is reached for $\eta_0 = 0.6$.
 
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta01} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_actions_probability_EXP3_eta01} \\[\abovecaptionskip]
 			\small (a) $\eta_0 = 0.1$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta05} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_actions_probability_EXP3_eta05} \\[\abovecaptionskip]
 			\small (b) $\eta_0 = 0.5$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta1} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_actions_probability_EXP3_eta1} \\[\abovecaptionskip]
 			\small (c) $\eta_0 = 1$
@@
 Thus, $\eta_0$ must be carefully set in order to provide a low temporal variability, at the same time that enough exploration is carried out for reaching the optimal fairness solution.
-
 	% EXP3: aggregate throughput
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta01} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta01} \\[\abovecaptionskip]
 			\small (a) $\eta_0 = 0.1$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta05} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta05} \\[\abovecaptionskip]
 			\small (b) $\eta_0 = 0.5$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta1} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta1} \\[\abovecaptionskip]
 			\small (c) $\eta_0 = 1$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta01} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta01} \\[\abovecaptionskip]
 			\small (a) $\eta_0 = 0.1$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta05} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta05} \\[\abovecaptionskip]
 			\small (b) $\eta_0 = 0.5$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta1} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta1} \\[\abovecaptionskip]
 			\small (c) $\eta_0 = 1$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta01} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_mean_tpt_EXP3_eta01} \\[\abovecaptionskip]
 			\small (a) $\eta_0 = 0.1$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta05} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_mean_tpt_EXP3_eta05} \\[\abovecaptionskip]
 			\small (b) $\eta_0 = 0.5$
@@
 		\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta1} \\[\abovecaptionskip]
+			\includegraphics[width=.25\textwidth]{images/NEW_mean_tpt_EXP3_eta1} \\[\abovecaptionskip]
 			\small (c) $\eta_0 = 1$
@@
 
-We start by showing the action probability distribution (shown in Figure \ref{fig:actions_probability_ucb}) derived from the UCB implementation.
+	We start now by showing the action probability distribution (shown in Figure \ref{fig:actions_probability_ucb}) derived from the UCB implementation.
 We observe that WNs clearly prefer playing the actions corresponding to proportional fairness (i.e., the actions with highest transmit power and that result in frequency reuse).
-
 	\begin{figure}[h!]
 		\centering							
-	\epsfig{file=images/NEW_actions_probability_UCB.eps, width=6.5cm}
+		\epsfig{file=images/NEW_actions_probability_UCB.eps, width=6cm}
 		\caption{Probability of taking a given action in UCB for a simulation of 10,000 iterations.}
@@
 As a result, UCB provides long-term fairness but at the expense of a high temporal variability caused by exploration.
+	% UCB: aggregate and individual 
+	\begin{figure}[t!]
+		\centering							
+		\epsfig{file=images/NEW_temporal_aggregate_tpt_UCB.eps, width=6cm}
+		\caption{Aggregate throughput evolution for a single UCB 10,000-iterations simulation. The proportional fair result is also shown (red dashed line).}
+		\label{fig:ucb_agg_tpt}
+	\end{figure}
+
+	\begin{figure}[t!]
+		\centering							
+		\epsfig{file=images/NEW_temporal_individual_tpt_UCB.eps, width=6cm}
+		\caption{Individual throughput evolution for a single UCB 10,000-iterations simulation. The proportional fair result is also shown (red dashed line).}
+		\label{fig:ucb_tpt_evolution}
+	\end{figure}
+
+%	\begin{figure*}[h!]
+%		\centering
+%		\begin{tabular}{@{}c@{}}
+%			\includegraphics[width=.4\textwidth]{images/NEW_temporal_aggregate_tpt_UCB} \\[\abovecaptionskip]
+%			\small (a) Aggregate throughput
+%			\label{fig:ucb_agg_tpt}
+%		\end{tabular}	
+%		\hspace{\floatsep}	
+%		\begin{tabular}{@{}c@{}}
+%			\includegraphics[width=.4\textwidth]{images/NEW_temporal_individual_tpt_UCB} \\[\abovecaptionskip]
+%			\small (b) Individual throughput
+%			\label{fig:ucb_ind_tpt}
+%		\end{tabular}
+%		\caption{Throughput evolution for a single UCB 10,000-iterations simulation. The proportional fair result is also shown (red dashed line).}
+%		\label{fig:ucb_tpt_evolution}
+%	\end{figure*}
+
 	In Figure \ref{fig:ucb_avg_individual} we show the average throughput experienced by each WN, as well as the standard deviation indicating the suffered variability (only for the last 5,000 iterations).
@@
 
-% UCB: aggregate and individual 
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_aggregate_tpt_UCB}
-		\caption{Aggregate}\label{fig:ucb_agg_tpt}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_individual_tpt_UCB}
-		\caption{Individual}\label{fig:ucb_tpt_evolution}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_mean_tpt_UCB}
-		\caption{Average}\label{fig:ucb_avg_individual}
-	\end{subfigure}
-	\caption{Performance achieved for a single UCB 10,000-iterations simulation.
-The proportional fair result is also shown (red dashed line).
-(a) Aggregate throughput evolution, (b) Individual throughput evolution, (c) Average individual throughput (the last 5,000 iterations are considered).}
-	\label{fig:ucb_tpt}
-\end{figure*}
-
 	Compared to $\varepsilon$-greedy and EXP3, UCB shows a clearer preference for selecting the proportional fair solutions.
 However, the intermittent good/poor performance of the actions due to the adversarial setting still keeps the degree of exploration very high, resulting in high temporal variability.
+	% UCB: average throughput
+	\begin{figure}[t!]
+		\centering							
+		\epsfig{file=images/NEW_mean_tpt_UCB.eps, width=6cm}
+		\caption{Average throughput and standard deviation experienced per WN in the last 5,000 iterations of a single UCB 10,000-iterations simulation.
+The proportional fair result is also shown (red dashed line).}
+		\label{fig:ucb_avg_individual}
+	\end{figure}
+
+	%	% UCB: histogram individual throughput
+	%	\begin{figure}[h!]
+	%		\centering							
+	%		\epsfig{file=images/NEW_histogram_individual_throughput_ucb.eps, width=6cm}
+	%		\caption{Histogram of the individual throughput experienced per WN in a single UCB simulation. The proportional fair result is also shown (red dashed line).}
+	%		\label{fig:hist_ucb}
+	%	\end{figure}
 
@@
 Note the well-pronounced preference for the proportional fair actions, which indicates fast convergence and little exploratory operations.
-
 	% TS: actions probability
@@
 		\centering							
-	\epsfig{file=images/NEW_actions_probability_TS.eps, width=6.5cm}
+		\epsfig{file=images/NEW_actions_probability_TS.eps, width=6cm}
 		\caption{Probability of taking a given action in Thompson sampling for a simulation of 10,000 iterations.}
@@
 As it can be observed, Thompson sampling achieves a lower variability in the temporal throughput with respect to UCB.
-The same observations can be done in the individual throughput evolution (Figure \ref{fig:ts_ind_tpt}).
-The low temporal variability observed on applying Thompson sampling is highlighted in Figure \ref{fig:ts_avg_individual}, which shows that the average experienced throughput enjoys a low standard deviation.
+The same observations can be done in the individual throughput evolution (Figure \ref{fig:ts_ind_tpt_evolution}).
+	% TS: aggregate and individual throughput
+	\begin{figure}[t!]
+		\centering							
+		\epsfig{file=images/NEW_temporal_aggregate_tpt_TS.eps, width=6cm}
+		\caption{Aggregate throughput evolution for a single Thompson sampling 10,000-iterations simulation. The proportional fair result is also shown (red dashed line).}
+		\label{fig:ts_tpt_evolution}
+	\end{figure}
+
+	\begin{figure}[t!]
+		\centering							
+		\epsfig{file=images/NEW_temporal_individual_tpt_TS.eps, width=6cm}
+		\caption{Individual throughput evolution for a single Thompson sampling 10,000-iterations simulation. The proportional fair result is also shown (red dashed line)}
+		\label{fig:ts_ind_tpt_evolution}
+	\end{figure}
+
+%	\begin{figure*}
+%		\centering
+%		\begin{tabular}{@{}c@{}}
+%			\includegraphics[width=.4\textwidth]{images/NEW_temporal_aggregate_tpt_TS} \\[\abovecaptionskip]
+%			\small (a) Aggregate throughput
+%			\label{fig:ts_agg_tpt}
+%		\end{tabular}	
+%		\hspace{\floatsep}	
+%		\begin{tabular}{@{}c@{}}
+%			\includegraphics[width=.4\textwidth]{images/NEW_temporal_individual_tpt_TS} \\[\abovecaptionskip]
+%			\small (b) Individual throughput
+%			\label{fig:ts_ind_tpt}
+%		\end{tabular}
+%		\caption{Throughput evolution for a single Thompson sampling 10,000-iterations simulation. The proportional fair result is also shown (red dashed line).}
+%		\label{fig:ts_tpt_evolution}
+%	\end{figure*}
+
+	The abovementioned low temporal variability is highlighted in Figure \ref{fig:ts_avg_individual}, which shows that the average experienced throughput enjoys a low standard deviation.
 Moreover, high fairness among WNs can be observed.
-
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_aggregate_tpt_TS}
-		\caption{Aggregate}\label{fig:ts_agg_tpt}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_individual_tpt_TS}
-		\caption{Individual}\label{fig:ts_ind_tpt}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_mean_tpt_TS}
-		\caption{Average}\label{fig:ts_avg_individual}
-	\end{subfigure}
-		\caption{Throughput evolution for a single Thompson sampling 10,000-iterations simulation.
-The proportional fair result is also shown (red dashed line).
-(a) Aggregate throughput evolution, (b) Individual throughput evolution, (c) Average individual throughput (the last 5,000 iterations are considered).}
-		\label{fig:ts_tpt_evolution}
-\end{figure*}
+	% UCB: average throughput
+	\begin{figure}[h!]
+		\centering							
+		\epsfig{file=images/NEW_mean_tpt_TS.eps, width=6cm}
+		\caption{Average throughput and standard deviation experienced per WN in the last 5,000 iterations of a single Thompson sampling 10,000-iterations simulation.
+The proportional fair result is also shown (red dashed line).}
+		\label{fig:ts_avg_individual}
+	\end{figure}
 
 	These results show that even though the rewards encourage selfish behavior, the adversarial setting makes Thompson sampling to converge to collaborative actions while keeping the degree of exploration low.
-\francesco{Again, this property holds for scenarios where no asymmetries can be found.} While the excellent performance we observe echoes other published results that show the superiority of Thompson sampling in various settings \cite{LCLS10}, we highlight that this outstanding empirical performance is actually rather unexpected in our \emph{non-stochastic} setting.
+While the excellent performance we observe echoes other published results that show the superiority of Thompson sampling in various settings \cite{LCLS10}, we highlight that this outstanding empirical performance is actually rather unexpected in our \emph{non-stochastic} setting.
 Indeed, existing theoretical results only explain the excellent performance of Thompson sampling in \emph{stochastic} bandit problems.
@@
 We leave the investigation of this matter as an exciting direction for future work.
+	%    We argue that the cause for this is the fact that Thompson sampling considers not only the magnitude but also the distribution of rewards. %CC: more on this..
+
+	%	% TS: histogram individual throughput
+	%	\begin{figure}[h!]
+	%		\centering							
+	%		\epsfig{file=images/NEW_histogram_individual_throughput_ts.eps, width=6cm}
+	%		\caption{Histogram of the individual throughput experienced per WN in a single Thompson sampling simulation. The proportional fair result is also shown (red dashed line).}
+	%		\label{fig:hist_ts}
+	%	\end{figure}
 
@@
 We do the same for EXP3 and choose $\eta_0 = 0.6$, which grants the highest aggregate throughput in average (refer to Figure \ref{fig:exp3_tuning_parameters}).
+
 	In Figure \ref{fig:hist_mean_tpt} we show, for each number of networks and action-selection strategy, an histogram of the mean throughput experienced by each WN during the last 5,000 iterations, and for each of the 100 repetitions.
@@
 
+	%\begin{figure*}[h!]
+	%	\centering
+	%	\begin{subfigure}[b]{0.4\textwidth}
+	%		\includegraphics[width=\textwidth]{images/hist_mean_tpt_2_WNs}
+	%		\caption{N = 2 WNs}
+	%		\label{fig:hist_mean_throughput_2}
+	%	\end{subfigure}
+	%	\begin{subfigure}[b]{0.4\textwidth}
+	%		\includegraphics[width=\textwidth]{images/hist_mean_tpt_4_WNs}
+	%		\caption{N = 4 WNs}
+	%		\label{fig:hist_mean_throughput_4}
+	%	\end{subfigure}
+	%	\begin{subfigure}[b]{0.4\textwidth}
+	%		\includegraphics[width=\textwidth]{images/hist_mean_tpt_6_WNs}
+	%		\caption{N = 6 WNs}
+	%		\label{fig:hist_mean_throughput_6}
+	%	\end{subfigure}
+	%	\begin{subfigure}[b]{0.4\textwidth}
+	%		\includegraphics[width=\textwidth]{images/hist_mean_tpt_8_WNs}
+	%		\caption{N = 8 WNs}
+	%		\label{fig:hist_imean_throughput_8}
+	%	\end{subfigure}
+	%	\caption{Histogram of the average throughput experienced by each WN during the last 5,000 iterations. Results from 100 repetitions are considered.}
+	%	\label{fig:hist_mean_tpt}
+	%\end{figure*}	
 	As we can observe, histograms of UCB and Thompson sampling are slightly narrower in almost all the cases, which indicates a higher fairness experienced by the WNs with respect to the other policies.
@@
 Thus, fewer exploration is required than for higher densities.
-\francesco{Note, as well, that the abovementioned collaborative behavior is still present in random scenarios.
-In accordance to that, WNs acting selfishly are prone to find a configuration whereby SR is improved in a fair manner.
-We find the main cause of this issue to be the inter-WN interference sensed at a given transmitter-receiver pair, which is very likely to be similar in both devices for the proposed scenarios.
-Such a property is given when STAs are close to their associated AP, thus allowing to palliate the effects of asymmetries.}
-
-To conclude, we evaluate temporal variability in random scenarios.
-For that, Table \ref{tbl:std_individual_tpt_experienced} shows the average standard deviation of the throughput experienced by each WN during the last 5,000 iterations (again, we concentrate on the regime after the initial learning phase).
+
+	We now evaluate temporal variability.
+In Table \ref{tbl:std_individual_tpt_experienced} we show the average standard deviation of the throughput experienced by each WN during the last 5,000 iterations (again, we concentrate on the regime after the initial learning phase).
 We consider the average results from 100 repetitions.
@@
 		\centering
-	%\resizebox{\columnwidth}{!}{%
+		\resizebox{\columnwidth}{!}{%
 			\begin{tabular}{|c|c|c|c|c|}
@@
 				\textbf{8} & 130.0322 & 73.5171 & 63.2272 & 68.8547 \\ \hline
-	\end{tabular}%}
+		\end{tabular}}
 		\caption{Mean standard deviation of the throughput experienced $\Gamma_{i \in N}$ by each $WN_i$ during the last 5,000 iterations. 100 repetitions are considered for averaging purposes.}
@@
 	\end{table}	
-
 	As previously seen in the toy grid scenario introduced in Section \ref{section:toy_grid_scenario}, both UCB and Thompson sampling provide the best results in terms of temporal throughput variability.
 Despite $\varepsilon$-greedy provides very good results for $N=2$, it does not properly scale up with the number of WNs.
+
+	%	In Figure \ref{fig:hist_individual_tpt} we show, for each policy, an histogram of the individual throughputs obtained during the last 5,000 iterations from a total of 10,000 (again, we want to concentrate on the permanent phase).
+In addition, we repeat the experiment 100 times to analyse the variability in the results for different generated random scenarios.
+	%	% Histogram individual throughput
+	%	\begin{figure}[h!]
+	%		\centering
+	%		\begin{subfigure}[b]{0.4\textwidth}
+	%			\includegraphics[width=\textwidth]{images/hist_individual_tpt_2_WNs}
+	%			\caption{N = 2 WNs}
+	%			\label{fig:hist_individual_throughput_eg}
+	%		\end{subfigure}
+	%		\begin{subfigure}[b]{0.4\textwidth}
+	%			\includegraphics[width=\textwidth]{images/hist_individual_tpt_4_WNs}
+	%			\caption{N = 4 WNs}
+	%			\label{fig:hist_individual_throughput_exp3}
+	%		\end{subfigure}
+	%		\begin{subfigure}[b]{0.4\textwidth}
+	%			\includegraphics[width=\textwidth]{images/hist_individual_tpt_6_WNs}
+	%			\caption{N = 6 WNs}
+	%			\label{fig:hist_individual_throughput_ucb}
+	%		\end{subfigure}
+	%		\begin{subfigure}[b]{0.4\textwidth}
+	%			\includegraphics[width=\textwidth]{images/hist_individual_tpt_8_WNs}
+	%			\caption{N = 8 WNs}
+	%			\label{fig:hist_individual_throughput_ts}
+	%		\end{subfigure}
+	%		\caption{Histogram of the individual throughput experienced by each WN in each of the last 5,000 iterations of each policy. Results from 100 repetitions are considered.}
+	%		\label{fig:hist_individual_tpt}
+	%	\end{figure}
+	%
+	%	As previously seen, UCB and Thompson sampling provide better results in terms of variability, since the throughput experienced is concentrated around the same area.
+On the other hand, both $\varepsilon$-greedy and EXP3 generate
+	%	more dispersed results,
 
@@
 	\label{section:conclusions}
-\francesc{In this paper, we provided a tutorial-like implementation of MABs to address the decentralized SR problem in dense WNs.
-Unlike previous literature, we have focused on a situation in which few resources are available, thus bringing out the competition issues raised from the adversarial setting.
-Our results show that} decentralized learning allows improving SR in dense WN, so that collaborative results \francesco{in symmetric scenarios}, sometimes close to optimal proportional fairness, can be achieved.
+	We have shown that decentralized learning allows improving SR in dense WN, so that collaborative results, sometimes close to optimal proportional fairness can be achieved.
 This result is achieved even though WNs act selfishly, aiming to maximize their own throughput.
-\francesco{In addition, this behavior is observed for random scenarios, where the effects of asymmetries cannot be controlled.} %However, using only local information in limited resources scenarios conducts to an adversarial setting in which a pure strategy does not exist, which prevents reaching a Nash Equilibrium.
+%However, using only local information in limited resources scenarios conducts to an adversarial setting in which a pure strategy does not exist, which prevents reaching a Nash Equilibrium.
 In the WNs case, applying decentralized learning in such an adversarial setting entails noticing a high temporal variability in the experienced throughput.
@@
 Finally, we intend to particularize to IEEE 802.11 WLANs to study the effects of applying RL when using a medium access protocol such as CSMA.
-In fact, this would let us consider dynamic Carrier Sense Threshold (CST) to further \francesc{enable} SR.
+In fact, this would let us consider dynamic Carrier Sense Threshold (CST) to further improve SR.
 
@@
 	% use section* for acknowledgment
+	\ifCLASSOPTIONcompsoc
 	% The Computer Society usually uses the plural form
 	\section*{Acknowledgments}
+	\else
+	% regular IEEE prefers the singular form
+	\section*{Acknowledgment}
+	\fi
 	This work has been partially supported by the Spanish Ministry of Economy and Competitiveness under the Maria de Maeztu Units of Excellence Programme (MDM-2015-0502), by the European Regional Development Fund under grant TEC2015-71303-R (MINECO/FEDER), and by a Gift from CISCO University Research Program (CG\#890107) \& Silicon Valley Community Foundation.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%  BIBLIOGRAPHY    
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+	%\newpage
 	\bibliographystyle{unsrt}
-\bibliography{references}
-
+	\bibliography{bib}
+
+	%\vspace*{-30 mm}
+	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/fwilhelmi}}]{Francesc Wilhelmi} holds a B.Sc.
+degree in Telematics Engineering (2015) and a M.Sc.
+in Intelligent and Interactive Systems in (2016), both from Universitat Pompeu Fabra (UPF).
+He is currently a Ph.D Student in the Wireless Networking Research Group (WNRG) in the Department of Information and Communication Technologies (DTIC) at the UPF.
+His interests are related to online learning for enhancing Spatial Reuse (SR) in high-density wireless networks.
+	\end{IEEEbiography}
+	\vskip -20pt plus -1fil
+	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/ccano}}]{Cristina Cano} holds a Ph.D.
+(2011) in Information, Communication and Audiovisual Media Technologies from the Universitat Pompeu Fabra (UPF).
+She has been a research fellow in the Hamilton Institute of the National University of Ireland, Maynooth (2012-2014), in Trinity College Dublin (2015-2016) and in Inria- Lille in France (first half of 2016).
+Currently, she is with the WINE research group of the Universitat Oberta de Catalunya (UOC).
+Her research interests include coexistence of wireless heterogeneous networks, distributed resource allocation and online optimisation.
+	\end{IEEEbiography}
+	\vskip -20pt plus -1fil
+	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/gneu}}]{Gergely Neu} received his M.Sc.
+degree in Electrical Engineering and his Ph.D.
+degree in Computer Science from the Budapest University of Technology and Ecomomics (Hungary) in 2008 and 2013, respectively.
+He has worked as a postdoctoral researcher at the SequeL team of INRIA Lille -- Nord Europe (Lille, France, 2013--2015), and is currently a postdoctoral researcher at the Artificial Intelligence and Machine Learning Research group at Universitat Pompeu Fabra (Barcelona, Spain, 2013--).
+His main research interests are in machine learning theory, including reinforcement learning and online learning with limited feedback and/or very large action sets.
+	\end{IEEEbiography}	
+	\vskip -20pt plus -1fil
+	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/bbellalta}}]{Boris Bellalta} is an Associate Professor in the Department of Information and Communication Technologies (DTIC) at Universitat Pompeu Fabra (UPF).
+He is the head of the Wireless Networking research group at DTIC/UPF.
+His research interests are in the area of wireless networks, with emphasis on the design and performance evaluation of new architectures and protocols.
+	\end{IEEEbiography}
+	\vskip -20pt plus -1fil
+	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/ajonsson}}]{Anders Jonsson} is the director of the Artificial Intelligence and Machine Learning group at Universitat Pompeu Fabra (UPF) in Barcelona, Spain.
+He received his Ph.D in computer science in 2005 from the University of Massachusetts Amherst, USA, and has been at UPF ever since.
+Anders' main research focus is sequential decision making, formulated both as AI planning and as reinforcement learning, but he also conducts research in other areas of AI and machine learning.
+He is interested in many extensions of the problem of sequential decision making, such as regularization and exploration, hierarchical representations of decision strategies, problems involving multiple agents, and adapting existing techniques to lifelong learning, allowing a system to learn and explore during extended periods of time.
+	\end{IEEEbiography}
+	\vskip -20pt plus -1fil
+	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/sbarrachina}}]{Sergio Barrachina-Mu\~noz} obtained his B.Sc.
+degree in Telematics Engineering and his M.Sc.
+in Intelligent Interactive Systems in 2015 and 2016, respectively, both from Universitat Pompeu Fabra (UPF), Barcelona.
+Currently, he is a PhD student and teacher assistant in the Department of Information and Communication Technologies (DTIC) at Universitat Pompeu Fabra (UPF).
+His main research interests are focused on developing autonomous learning methods and techniques for improving the performance of next-generation wireless networks.
+	\end{IEEEbiography}
+	\vskip -20pt plus -1fil
 \end{document}

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Experiments/EXP3 Experiments/Experiment_2_1_individual_performance_EXP3_parameters_4_WN.m

@@ -1,0 +1,44 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% EXPERIMENT EXPLANATION:
+% By using a simple grid of 4 WLANs sharing 2 channels, we want to test the
+% EXP3 method if using different numbers of iterations. We fix eta to the 
+% value that generated better results in terms of proportional fairness in 
+% the Experiment_1
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('Power Management Methods/'));
+addpath(genpath('Throughput Calculation Methods/'));
+addpath(genpath('Network Generation Methods/'));
+addpath(genpath('Reinforcement Learning Methods/'));
+addpath(genpath('Reinforcement Learning Methods/Action Selection Methods/'));
+addpath(genpath('Auxiliary Methods/'));
+
+disp('-----------------------')
+disp('EXP3: Throughput Evolution')
+disp('-----------------------')
+
+constants
+
+% Define EXP3 parameters
+initialEta = 0;
+gamma = 0;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlan = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+    
+% Compute the throughput experienced per WLAN at each iteration
+[tpt_evolution_per_wlan_exp3, times_arm_has_been_played]  = exp3(wlan, gamma, initialEta);
+
+% Plot the results
+display_results_individual_performance(wlan, tpt_evolution_per_wlan_exp3, ...
+    times_arm_has_been_played, 'EXP3');
+
+% Save the workspace
+save('./Output/exp3_exp2_workspace.mat')

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Experiments/Performance Comparison/Experiment_1_Performance_Comparison_Random_Network.m

@@ -1,0 +1,512 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% EXPERIMENT EXPLANATION:
+% By using a simple grid of 4 WLANs sharing 2 channels, we want to find the
+% optimal configurations that mazimizes the aggregated throughput and the
+% proportional fairness, respectively
+
+%%
+clc
+clear all
+
+disp('-----------------------')
+disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
+disp('-----------------------')
+
+constants
+
+% Update the nWlans variable to define an array
+nWlans = [2 4 6 8];
+
+%totalIterations
+%minimumIterationToConsider
+%totalRepetitions
+
+% Initialize variables to store results
+throughputEvolutionPerWlanRandom = cell(size(nWlans, 2), totalRepetitions);
+throughputEvolutionPerWlanEgreedy = cell(size(nWlans, 2), totalRepetitions);
+throughputEvolutionPerWlanExp3 = cell(size(nWlans, 2), totalRepetitions);
+throughputEvolutionPerWlanUcb = cell(size(nWlans, 2), totalRepetitions);
+throughputEvolutionPerWlanTs = cell(size(nWlans, 2), totalRepetitions);
+
+fairness_evolution_random_transitory = cell(size(nWlans, 2), totalRepetitions);
+fairness_evolution_random_permanent = cell(size(nWlans, 2), totalRepetitions);
+aggregate_tpt_random_transitory = cell(size(nWlans, 2), totalRepetitions);
+aggregate_tpt_random_permanent = cell(size(nWlans, 2), totalRepetitions);
+
+fairness_evolution_eg_transitory = cell(size(nWlans, 2), totalRepetitions);
+fairness_evolution_eg_permanent = cell(size(nWlans, 2), totalRepetitions);
+aggregate_tpt_eg_transitory = cell(size(nWlans, 2), totalRepetitions);
[…]

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Experiments/e-greedy Experiments/Experiment_2_2_individual_performance_EG_parameters_4_WN.m

@@ -1,0 +1,47 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% EXPERIMENT EXPLANATION:
+% By using a simple grid of 4 WLANs sharing 2 channels, we want to test the
+% e-greedy method if using different numbers of iterations. We fix alpha,
+% gamma and initial epsilon to the values that generated better results in
+% terms of proportional fairness in the Experiment_1
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('Power Management Methods/'));
+addpath(genpath('Throughput Calculation Methods/'));
+addpath(genpath('Network Generation Methods/'));
+addpath(genpath('Reinforcement Learning Methods/'));
+addpath(genpath('Reinforcement Learning Methods/Action Selection Methods/'));
+addpath(genpath('Auxiliary Methods/'));
+
+disp('-----------------------')
+disp('e-greedy: Throughput Evolution')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+initialEpsilon = .5;
+
+policy = EG_POLICY;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+   
+% Compute the throughput experienced per WLAN at each iteration
+% [tpt_evolution_per_wlan_eg, times_arm_has_been_played]  = eGreedyMethod(wlan, MAX_CONVERGENCE_TIME, ...
+%     MAX_LEARNING_ITERATIONS, initial_epsilon, updateMode, actions_ch, actions_cca, actions_tpc, noise, printInfo);
+
+[tptEvolutionPerWlan, timesArmHasBeenPlayed] = egreedy( wlans, initialEpsilon );
+
+% Plot the results
[…]

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Experiments/e-greedy Experiments/Experiment_2_3_individual_performance_EG_parameters_4_WN.m

@@ -1,0 +1,47 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% EXPERIMENT EXPLANATION:
+% By using a simple grid of 4 WLANs sharing 2 channels, we want to test the
+% e-greedy method if using different numbers of iterations. We fix alpha,
+% gamma and initial epsilon to the values that generated better results in
+% terms of proportional fairness in the Experiment_1
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('Power Management Methods/'));
+addpath(genpath('Throughput Calculation Methods/'));
+addpath(genpath('Network Generation Methods/'));
+addpath(genpath('Reinforcement Learning Methods/'));
+addpath(genpath('Reinforcement Learning Methods/Action Selection Methods/'));
+addpath(genpath('Auxiliary Methods/'));
+
+disp('-----------------------')
+disp('e-greedy: Throughput Evolution')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+initialEpsilon = 1;
+
+policy = EG_POLICY;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+   
+% Compute the throughput experienced per WLAN at each iteration
+% [tpt_evolution_per_wlan_eg, times_arm_has_been_played]  = eGreedyMethod(wlan, MAX_CONVERGENCE_TIME, ...
+%     MAX_LEARNING_ITERATIONS, initial_epsilon, updateMode, actions_ch, actions_cca, actions_tpc, noise, printInfo);
+
+[tptEvolutionPerWlan, timesArmHasBeenPlayed] = egreedy( wlans, initialEpsilon );
+
+% Plot the results
[…]

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Network Generation Methods/draw_network_3D.m

@@ -1,0 +1,36 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function DrawNetwork3D(wlan)
+% DrawNetwork3D - Plots a 3D of the network 
+%   INPUT: 
+%       * wlan - contains information of each WLAN in the map. For instance,
+%       wlan(1) corresponds to the first one, so that it has unique
+%       parameters (x,y,z,BW,CCA,etc.)
+
+    MaxX=10;
+    MaxY=5; 
+    MaxZ=10;
+    for j=1:size(wlan,2)
+        x(j)=wlan(j).x;
+        y(j)=wlan(j).y;
+        z(j)=wlan(j).z;
+    end
+    figure
+    axes;
+    set(gca,'fontsize',16);
+    labels = num2str((1:size(y' ))','%d');    
+    for i=1:size(wlan,2)
+        scatter3(wlan(i).x, wlan(i).y, wlan(i).z, 70, [0 0 0], 'filled');
+        hold on;   
+        scatter3(wlan(i).xn, wlan(i).yn, wlan(i).zn, 30, [0 0 1], 'filled');
+        line([wlan(i).x, wlan(i).xn], [wlan(i).y, wlan(i).yn], [wlan(i).z, wlan(i).zn], 'Color', [0.4, 0.4, 1.0], 'LineStyle', ':');        
+    end
+    text(x,y,z,labels,'horizontal','left','vertical','bottom') 
+    xlabel('x [meters]','fontsize',14);
+    ylabel('y [meters]','fontsize',14);
+    zlabel('z [meters]','fontsize',14);
+    axis([0 MaxX 0 MaxY 0 MaxZ])
+end

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Network Generation Methods/generate_random_network_3D.m

@@ -1,0 +1,74 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function wlan = generate_random_network_3D( N_WLANs, NumChannels, printMap )
+    % DrawNetwork3D  Calculate interferences on WLANs.
+    %   Inputs:
+    %       * N_WLANs: number of WLANs on the studied environment
+    %       * NumChannels: number of available channels
+    %       * B: bandwidth available per WLAN (Hz)
+    %   Output:
+    %       * wlan: object containing the information of each wlan drawn
+        
+    % Dimensions of the 3D map
+    MaxX=10;
+    MaxY=5; 
+    MaxZ=10;
+    % Maximum range for a STA
+    MaxRangeX = 1;
+    MaxRangeY = 1;
+    MaxRangeZ = 1;
+%     % AP density
+%     disp('Density of APs');
+%     disp(N_WLANs / (MaxX * MaxY * MaxZ));
+ 
+    %% Locate elements on the map randomly
+    for j=1:N_WLANs    
+        % Assign Tx Power and CCA on the WLAN
+        wlan(j).TxPower = 20;
+        wlan(j).CCA = -82;
+        % Assign channel to the AP randomly
+        wlan(j).Channel = ceil(NumChannels*rand());
+        % Assign location to the AP on the 3D map
+        wlan(j).x = MaxX*rand();
+        wlan(j).y = MaxY*rand();
+        wlan(j).z = MaxZ*rand();  
+        % Build arrays of locations for each AP
+        x(j)=wlan(j).x;
+        y(j)=wlan(j).y;
+        z(j)=wlan(j).z;
+        % Assign a STA to each AP for throughput analysis
+        if(rand() < 0.5), xc = MaxRangeX.*rand();   %dnode*rand(); %what xc represents ? B: Is just an auxiliary variable to fix the position of the node around the AP, see below
+        else xc = -MaxRangeX.*rand();
+        end
[…]

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Reinforcement Learning Methods/Action Selection Methods/select_action_random.m

@@ -1,0 +1,39 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function arm = select_action_random(rewards_per_configuration, e)
+% selectActionEGreedy: returns the best possible arm given the current distribution
+%   OUTPUT:
+%       * arm - which represents the configuration composed by [channel,CCA,TPC]
+%   INPUT:
+%   	* rewards_per_configuration - rewards noticed at each configuration
+%       * e - epsilon (exploration coefficient)
+
+    indexes=[];  % empty array to include configurations with the same value    
+    
+    if rand() > e    % Check if we have to "exploit"
+        
+        [val,~] = max(rewards_per_configuration);
+        
+        % Break ties randomly
+        if sum(rewards_per_configuration==val)>1
+            if val ~= Inf
+                indexes = find(rewards_per_configuration==val);
+                arm = randsample(indexes,1);
+            else
+                arm = randsample(1:size(rewards_per_configuration,2),1);
+            end
+            
+        % Select arm with maximum reward
+        else
+            [~,arm] = max(rewards_per_configuration);
+        end
+        
+    else             % Check if we have to "explore"
+        
+        arm = randi([1 size(rewards_per_configuration,2)], 1, 1);
+        
+    end
+end

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Reinforcement Learning Methods/egreedy.m

@@ -1,0 +1,194 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% function [tptExperiencedByWlan, times_arm_has_been_played] = egreedy(wlan, totalIterations, ...
+%     MAX_LEARNING_ITERATIONS, initial_epsilon, updateMode, channelActions, ccaActions, txPowerActions, NOISE_DBM, printInfo)
+
+function [ tptExperiencedByWlan, timesArmHasBeenPlayed ] = egreedy( wlans, initialEpsilon, varargin )
+% EGREEDY - Given a WN, applies e-greedy to maximize the experienced throughput
+%
+%   OUTPUT: 
+%       * tptExperiencedByWlan - throughput experienced by each WLAN
+%         for each of the iterations done
+%       * timesArmHasBeenPlayed - times each action has been played
+%   INPUT: 
+%       * wlan - wlan object containing information about all the WLANs
+%       * initialEpsilon - initial exploration coefficient
+
+    constants
+    
+    try
+        if size(varargin, 2) == 3
+            % Update possible actions
+            nChannels = varargin{1};
+            channelActions = 1 : nChannels;
+            ccaActions = varargin{2};
+            txPowerActions = varargin{3};
+            % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
+            possibleActions = 1:(size(channelActions, 2) * ...
+                size(ccaActions, 2) * size(txPowerActions, 2));
+            K = size(possibleActions,2);   % Total number of actions
+            allCombs = allcomb(1:K, 1:K);    
+        end
+    catch
+        if size(varargin, 2) ~= 3
+            disp('Wrong number of input arguments')
+        end
+    end
+    
+    %% INITIALIZE ALGORITHM
+    % Use a copy of wlan to make operations
+    wlansAux = wlans;
+    nWlans = size(wlansAux, 2);
+
[…]

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Reinforcement Learning Methods/exp3.m

@@ -1,0 +1,215 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function [tptExperiencedByWlan, timesArmHasBeenPlayed] = exp3(wlans, gamma, initialEta, varargin)
+
+% EXP3MethodBasic Given an OBSS, applies EXP3 (basic formulation) to maximize the experienced throughput
+%
+%   OUTPUT: 
+%       * tptExperiencedByWlan - throughput experienced by each WLAN
+%         for each of the iterations done
+%       * timesArmHasBeenPlayed - times each action has been played
+%   INPUT: 
+%       * wlan - wlan object containing information about all the WLANs
+%       * gamma - weigths regulator EXP3
+%       * eta - learning rate EXP3
+
+    constants
+    
+    try
+        if size(varargin, 2) == 3
+            % Update possible actions
+            nChannels = varargin{1};
+            channelActions = 1 : nChannels;
+            ccaActions = varargin{2};
+            txPowerActions = varargin{3};
+            % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
+            possibleActions = 1:(size(channelActions, 2) * ...
+                size(ccaActions, 2) * size(txPowerActions, 2));
+            K = size(possibleActions,2);   % Total number of actions
+            allCombs = allcomb(1:K, 1:K);    
+        end   
+    catch
+        if size(varargin, 2) ~= 3
+            disp('Wrong number of input arguments')
+        end
+    end
+    
+    %% INITIALIZE ALGORITHM
+    % Use a copy of wlan to make operations
+    wlansAux = wlans;
+    nWlans = size(wlansAux, 2);
+
+    % Find the index of the initial action taken by each WLAN
+    initialActionIxPerWlan = zeros(1, nWlans);
+    for i=1:nWlans
+        [~,indexCca] = find(ccaActions==wlansAux(i).CCA);
[…]

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Throughput Calculation Methods/compute_max_bound_throughput.m

@@ -1,0 +1,25 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function optimalThroughputPerWlan = compute_max_bound_throughput(wlan, powerMatrix, noise, maxPower)
+% Given an WLAN (AP+STA), compute the maximum capacity achievable according
+% to the power obtained at the receiver without interference
+%
+% OUTPUT:
+%   * optimalThroughputPerWlan - maximum achievable throughput per WLAN (Mbps)
+% INPUT:
+%   * wlan - object containing all the WLANs information 
+%   * powerMatrix - power received from each AP
+%   * noise - floor noise in dBm
+
+    wlan_aux = wlan;
+    % Iterate for each WLAN
+    for i = 1 : size(wlan_aux,2)
+        wlan_aux(i).TxPower = maxPower;
+        optimalThroughputPerWlan(i) = compute_theoretical_capacity(wlan_aux(i).BW, ...
+            db2pow(powerMatrix(i,i) - noise))/1e6; % Mbps
+    end
+    
+end

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Throughput Calculation Methods/compute_theoretical_capacity.m

@@ -1,0 +1,17 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function C = compute_theoretical_capacity(B, sinr)
+% Computes the theoretical capacity given a bandwidth and a SINR
+%
+% OUTPUT:
+%   * C - capacity in bps
+% INPUT:
+%   * B - Available Bandwidth (Hz) 
+%   * sinr - Signal to Interference plus Noise Ratio (-)
+
+    C = B * log2(1 + sinr);
+
+end

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Throughput Calculation Methods/compute_throughput_all_combinations.m

@@ -1,0 +1,87 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function throughputPerConfiguration = compute_throughput_all_combinations...
+    (wlans, actions_ch, actions_cca, actions_tpc, noise)
+% Computes the throughput experienced by each WLAN for all the possible
+% combinations of Channels, CCA and TPC 
+%
+%   NOTE: the "allcomb" function does not hold big amounts of combinations 
+%   (a reasonable limit is 4 WLANs with 2 channels and 4 levels of TPC)
+%
+% OUTPUT:
+%   * throughputPerConfiguration - tpt achieved by each WLAN for each configuration (Mbps)
+% INPUT:
+%   * wlans - object containing all the WLANs information 
+%   * actions_ch - set of channels
+%   * actions_cca - set of carrier sense thresholds
+%   * actions_tpc - set of transmit power values
+%   * noise - floor noise in dBm
+
+    disp('      - Computing the throughput for all the combinations...')
+
+    % Each state represents an [i,j,k] combination for indexes on "channels", "CCA" and "TxPower"
+    possible_actions = 1:(size(actions_ch,2)*size(actions_cca,2)*size(actions_tpc,2));
+    % Set of possible combinations of configuration  
+    possible_comb = allcomb(possible_actions,possible_actions,possible_actions,possible_actions);
+
+    n_WLANs = size(wlans,2);
+    nChannels = size(actions_ch, 2);
+    
+    wlan_aux = wlans;    % Generate a copy of the WLAN object to make modifications
+
+    % Try all the combinations
+    for i = 1:size(possible_comb, 1)
+        % Change WLANs configuration 
+        for j = 1:n_WLANs 
+            [ch, ~, tpc_ix] = val2indexes(possible_comb(i,j), nChannels, size(actions_cca,2), size(actions_tpc,2));
+            wlan_aux(j).Channel = ch;   
[…]

### 2018-09-06 OLD SUBMISSION/Code/HPC workspace/code_mabs/Throughput Calculation Methods/compute_throughput_best_action_selection.m

@@ -1,0 +1,81 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Exploiting Spatial Reuse in Wireless Networks through Decentralised MABs
+% F. Wilhelmi, B. Bellalta, A. Jonsson, C. Cano, G. Neu, S. Barrachina
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+function throughputPerWlan = compute_throughput_best_action_selection...
+    (wlans, actions_ch, actions_cca, actions_tpc, noise, maxIter)
+% Computes the throughput for each WLAN if each one sequentially tries all 
+% its possible combinations once and then selects the one that provides higher throughput
+%
+% OUTPUT:
+%   * throughputPerWlan - throughput in Mbps obtained by each WLAN after all
+%   changed their configuration
+% INPUT:
+%   * wlans - object containing all the information of the WLANs
+%   * actions_ch - set of channels
+%   * actions_cca - set of carrier sense thresholds
+%   * actions_tpc - set of transmit power values
+%   * noise - floor noise in dBm
+%   * maxIter - number of iterations for applying Best Action Selection
+
+    % Each state represents an [i,j,k] combination for indexes on "channels", "CCA" and "TxPower"
+    possible_actions = 1:(size(actions_ch,2)*size(actions_cca,2)*size(actions_tpc,2));
+    % Total number of actions
+    K = size(possible_actions,2);
+
+    n_WLANs = size(wlans,2);
+    nChannels = size(actions_ch, 2);
+    
+    wlan_aux = wlans;
+
+    % Apply the algorithm sequentially for each WLAN
+    iteration = 1;
+    tpt_best_action = zeros(1, n_WLANs);
+    best_action = zeros(1, n_WLANs);
+
+    % CALCULATE TPT FOR EACH WLAN 
+    powMat = PowerMatrix(wlan_aux);            
+    tpt_start = computeTptPowMat(wlan_aux, powMat, noise); 
+    avg_tpt_start = mean(tpt_start);
+    fairness_start = JainsFairness(tpt_start);     
+
+    while(iteration < maxIter + 1)    
+        % Iterate for all the WLANs
[…]

### 2018-09-06 OLD SUBMISSION/Code/experiments/0. Optimal configurations 4-grid WN/Experiment_0_compute_optimal_configurations.m

@@ -1,0 +1,41 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% The script computes, given the 4-grid WN, the configurations that 
+%%% provide the optimal values of i) the aggregate throughput, and 
+%%% ii) the proportional fairness.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.1 Optimal Solution
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('4 WNs grid: Optimal Configuration')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+
+% Compute the optimal configuration to compare the approaches
+maximumAchievableThroughput = compute_throughput_all_combinations...
+    (wlans, channelActions, ccaActions, txPowerActions, NOISE_DBM);

### 2018-09-06 OLD SUBMISSION/Code/experiments/1. e-greedy Experiments/Experiment_1_EG_find_best_epsilon.m

@@ -1,0 +1,131 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we want to test 
+%%% several values of the initial exploration coefficient (epsilon) to 
+%%% evaluate the performance of e-greedy for each of them. We compare the 
+%%% obtained results with the optimal configurations in terms of proportional 
+%%% fairness.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.2 Performance of the e-greedy policy
+%%% - Figure 2
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('e-greedy: finding the best parameters')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+initialEpsilon = 0:.1:1;
+
+policy = EG_POLICY;
+  
+% Initialize variables at which to store information per repetition
[…]

### 2018-09-06 OLD SUBMISSION/Code/experiments/1. e-greedy Experiments/Experiment_2_1_individual_performance_EG_parameters_4_WN.m

@@ -1,0 +1,61 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of e-greedy for e_0 = 0.1. We display i) the
+%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
+%%% temporal individual throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.2 Performance of the e-greedy policy
+%%% - Figure 3
+%%% - Figure 4
+%%% - Figure 5
+%%% - Figure 6
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('e-greedy: Throughput Evolution')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+initialEpsilon = .1;
+
+policy = EG_POLICY;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+   
[…]

### 2018-09-06 OLD SUBMISSION/Code/experiments/1. e-greedy Experiments/Experiment_2_3_individual_performance_EG_parameters_4_WN.m

@@ -1,0 +1,61 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of e-greedy for e_0 = 1. We display i) the
+%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
+%%% temporal individual throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.2 Performance of the e-greedy policy
+%%% - Figure 3
+%%% - Figure 4
+%%% - Figure 5
+%%% - Figure 6
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('e-greedy: Throughput Evolution')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+initialEpsilon = 1;
+
+policy = EG_POLICY;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+   
[…]

### 2018-09-06 OLD SUBMISSION/Code/experiments/3. UCB Experiments/Experiment_1_individual_performance_UCB_4_WN.m

@@ -1,0 +1,54 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of UCB. We display i) the actions probabilities, 
+%%% ii) the temporal aggregate throughput, iii) the temporal individual 
+%%% throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.4 Performance of the UCB policy
+%%% - Figure 12
+%%% - Figure 13
+%%% - Figure 14
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('UCB: Throughput Evolution')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+    
+policy = UCB_POLICY;
+% Compute the throughput experienced per WLAN at each iteration
+[tptEvolutionPerWlan, timesArmHasBeenPlayed] = ucb(wlans);
+
+% Plot the results
+if plotResults
[…]

### 2018-09-06 OLD SUBMISSION/Code/experiments/5. Performance Comparison/Experiment_1_Performance_Comparison_Random_Network.m

@@ -1,0 +1,106 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% The script computes the performance of applying e-greedy, EXP3, UCB and
+%%% Thompson sampling in random scenarios. At the end, histograms of the 
+%%% average throughput experienced are displayed for each policy.
+
+%%% This Script generates the output shown in the article:
+%%% - Figure 18
+
+%%
+clc
+clear all
+
+disp('************************************************************************')
+disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
+disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
+disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
+disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
+disp('* GitHub repository:                                                   *')
+disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
+disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
+disp('************************************************************************')
+
+disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
+disp('-----------------------')
+
+% Load constants
+constants
+
+% Update the nWlans variable to define an array
+nWlans = [2 4 6 8];
+
+% % Initialize variables to store results:
+% % - Each cell contains the throughput evolution experienced with each policy
+% % - We store the tpt. evolution for each number of WNs and for each repetition
[…]

### 2018-09-06 OLD SUBMISSION/Code/framework_throughput_calculation/auxiliary_methods/display_results_scalability.m

@@ -1,0 +1,258 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function [] = display_results_scalability( wlansSizes, throughputEvolutionPerWlanEgreedy, ...
+    throughputEvolutionPerWlanExp3, throughputEvolutionPerWlanUcb, throughputEvolutionPerWlanTs)
+% display_results_scalability displays the results of
+% "Experiment_1_Performance_Comparison_Random_Network.m"
+%   INPUT: 
+%       * wlansSizes - array containing each size of WLANs (e.g. [2 4 6 8])
+%       * throughputEvolutionPerWlanEgreedy - cell containing, for each
+%       repetition, the results of applying the "e-greedy" strategy
+%       * throughputEvolutionPerWlanExp3 - cell containing, for each
+%       repetition, the results of applying the "EXP3" strategy
+%       * throughputEvolutionPerWlanUcb - cell containing, for each
+%       repetition, the results of applying the "UCB" strategy
+%       * throughputEvolutionPerWlanTs - cell containing, for each
+%       repetition, the results of applying the "TS" strategy
+
+    % Load constatns
+    load('constants.mat')
+    
+    % Set font type
+    set(0,'defaultUicontrolFontName','Times New Roman');
+    set(0,'defaultUitableFontName','Times New Roman');
+    set(0,'defaultAxesFontName','Times New Roman');
+    set(0,'defaultTextFontName','Times New Roman');
[…]

### 2018-09-06 OLD SUBMISSION/Code/framework_throughput_calculation/network_generation_methods/generate_network_3D.m

@@ -1,0 +1,240 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+function wlans = generate_network_3D(nWlans, topology, stasPosition, printMap)
+% GenerateNetwork3D - Generates a 3D network 
+%   OUTPUT: 
+%       * wlan - contains information of each WLAN in the map. For instance,
+%       wlan(1) corresponds to the first one, so that it has unique
+%       parameters (x,y,z,BW,CCA,etc.)
+%   INPUT: 
+%       * nWlans: number of WLANs on the studied environment
+%       * nChannels: number of available channels
+%       * topology: topology of the network ('ring', 'line' or 'grid')
+%       * stas_position: way STAs are placed (1 - "random", 2 - "safe" or 3 - "exposed")
+%       * printMap: flag for calling DrawNetwork3D at the end
+
+    load('constants.mat')
+    
+    if (topology == 'ring')
+        x0 = MaxX/2;
+        y0 = MaxY/2;
+        r = (MaxY-1)/2;
+        n=nWlans;
+        tet=linspace(-pi,pi,n+1);                
+        posX = r*cos(tet)+x0;
+        posY = r*sin(tet)+y0;
+    end
+    
+    gridPositions4 = [
+    (MaxX)/nWlans (MaxY)/nWlans MaxZ/2;
+    (MaxX)/nWlans 3*(MaxY)/nWlans MaxZ/2;
+    3*(MaxX)/nWlans (MaxY)/nWlans MaxZ/2;
+    3*(MaxX)/nWlans 3*(MaxY)/nWlans MaxZ/2;
+    ];
+             
+    gridPositions8 = [
+    (MaxX)/(nWlans/2) (MaxY)/(nWlans/2) MaxZ/(nWlans/2);
[…]

### 2018-09-06 OLD SUBMISSION/Code/framework_throughput_calculation/network_generation_methods/generate_random_network_3D.m

@@ -1,0 +1,79 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function wlan = generate_random_network_3D( N_WLANs, NumChannels, printMap )
+    % DrawNetwork3D  Calculate interferences on WLANs.
+    %   Inputs:
+    %       * N_WLANs: number of WLANs on the studied environment
+    %       * NumChannels: number of available channels
+    %       * B: bandwidth available per WLAN (Hz)
+    %   Output:
+    %       * wlan: object containing the information of each wlan drawn
+        
+    % Dimensions of the 3D map
+    MaxX=10;
+    MaxY=5; 
+    MaxZ=10;
+    % Maximum range for a STA
+    MaxRangeX = 1;
+    MaxRangeY = 1;
+    MaxRangeZ = 1;
+%     % AP density
+%     disp('Density of APs');
+%     disp(N_WLANs / (MaxX * MaxY * MaxZ));
+ 
+    %% Locate elements on the map randomly
+    for j=1:N_WLANs    
+        % Assign Tx Power and CCA on the WLAN
+        wlan(j).TxPower = 20;
+        wlan(j).CCA = -82;
+        % Assign channel to the AP randomly
+        wlan(j).Channel = ceil(NumChannels*rand());
+        % Assign location to the AP on the 3D map
+        wlan(j).x = MaxX*rand();
+        wlan(j).y = MaxY*rand();
+        wlan(j).z = MaxZ*rand();  
+        % Build arrays of locations for each AP
+        x(j)=wlan(j).x;
+        y(j)=wlan(j).y;
+        z(j)=wlan(j).z;
+        % Assign a STA to each AP for throughput analysis
[…]

### 2018-09-06 OLD SUBMISSION/Code/framework_throughput_calculation/power_management_methods/interferences.m

@@ -1,0 +1,41 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function interferences = Interferences(wlans, powerMatrix)
+% Interferences - Returns the interferences power received at each WLAN
+%   OUTPUT:
+%       * intMat: 1xN array (N is the number of WLANs) with the
+%       interferences noticed on each AP in mW
+%   INPUT:
+%       * wlans: contains information of each WLAN in the map. For instance,
+%       wlans(1) corresponds to the first one, so that it has unique
+%       parameters (x,y,z,BW,CCA,etc.).
+%       * powMat: matrix NxN (N is the number of WLANs) with the power
+%       received at each AP in dBm.
+
+% We assume that overlapping channels also create an interference with lower level (20dB/d) - 20 dB == 50 dBm
+
+    interferences = zeros(1, size(wlans, 2)); 
+    
+    for i = 1:size(wlans, 2)
+        
+        for j = 1:size(wlans, 2)
+            
+            if i ~= j && wlans(j).transmitting == 1
+                
+                interferences(i) = interferences(i) + db2pow(powerMatrix(i,j) - db2pow(20 * (abs(wlans(i).Channel - wlans(j).Channel))));
+            
+            end
+            
+        end
+        
+    end
+
+end

### 2018-09-06 OLD SUBMISSION/Code/framework_throughput_calculation/throughput_calculation_methods/compute_throughput_best_action_selection.m

@@ -1,0 +1,86 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function throughputPerWlan = compute_throughput_best_action_selection...
+    (wlans, actions_ch, actions_cca, actions_tpc, noise, maxIter)
+% Computes the throughput for each WLAN if each one sequentially tries all 
+% its possible combinations once and then selects the one that provides higher throughput
+%
+% OUTPUT:
+%   * throughputPerWlan - throughput in Mbps obtained by each WLAN after all
+%   changed their configuration
+% INPUT:
+%   * wlans - object containing all the information of the WLANs
+%   * actions_ch - set of channels
+%   * actions_cca - set of carrier sense thresholds
+%   * actions_tpc - set of transmit power values
+%   * noise - floor noise in dBm
+%   * maxIter - number of iterations for applying Best Action Selection
+
+    % Each state represents an [i,j,k] combination for indexes on "channels", "CCA" and "TxPower"
+    possible_actions = 1:(size(actions_ch,2)*size(actions_cca,2)*size(actions_tpc,2));
+    % Total number of actions
+    K = size(possible_actions,2);
+
+    n_WLANs = size(wlans,2);
+    nChannels = size(actions_ch, 2);
+    
+    wlan_aux = wlans;
+
+    % Apply the algorithm sequentially for each WLAN
+    iteration = 1;
+    tpt_best_action = zeros(1, n_WLANs);
+    best_action = zeros(1, n_WLANs);
+
+    % CALCULATE TPT FOR EACH WLAN 
+    powMat = PowerMatrix(wlan_aux);            
+    tpt_start = computeTptPowMat(wlan_aux, powMat, noise); 
+    avg_tpt_start = mean(tpt_start);
[…]

### 2018-09-06 OLD SUBMISSION/Code/reinforcement_learning_methods/action_selection_methods/select_action_ts.m

@@ -1,0 +1,41 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+function [ arm ] = select_action_ts( mu_hat, times_arm_has_been_played )
+% select_action_ts: returns the best possible arm given the current distribution
+%   OUTPUT:
+%       * arm - chosen arm to be played - configuration composed by {channel, CCA, TPC}
+%   INPUT:
+%       - mu_hat: estimates of each arm
+%       - times_arm_has_been_played: number of plays of each arm
+
+    % STEP 1. For each arm, sample theta_i(t) independently from the normal distribution
+    K = size(times_arm_has_been_played, 2);
+    for k = 1 : K
+        theta(k) = normrnd(mu_hat(k), 1/(1+times_arm_has_been_played(k)));         
+    end
+    
+    % STEP 2. Play arm i(t) that maximizes theta_i(t)
+    [val,~] = max(theta);
+    
+    % Break ties randomly
+    if sum(theta == val) > 1
+        if val ~= Inf
+            indexes = find(theta == val);
+            arm = randsample(indexes, 1);
+        else
+            arm = randsample(1:size(theta, 2), 1);
+        end
+        
+    % Select arm with maximum reward
+    else
+        [~, arm] = max(theta);
+    end
+    
+end

### 2018-10-09 Ordered Learning/ordered_learning.tex
Progress until 9th, October

--- 2018-05-28 Article - LaTeX files/collaborative_spatial_reuse_via_mabs.tex
@@
 
-\documentclass[preprint,12pt]{elsarticle}
+\documentclass[preprint,12pt]{article}
 
@@
 %% \usepackage{lineno}
-
-\journal{Computer Networks}
+\title{Asynchronous vs Synchronous Selfish Learning}
 
 \begin{document}
+\maketitle
 
-\begin{frontmatter}
+\section{Introduction}
 
-%% Title, authors and addresses
+\section{Results - Toy Scenario}
 
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
+\subsection{$\varepsilon$-greedy}
+\label{section:e-greedy}
 
-\title{Collaborative Spatial Reuse in Wireless Networks via Selfish Multi-Armed Bandits}
+\subsection{EXP3}
+\label{section:exp3}
 
-\author[label1, label4]{Francesc Wilhelmi}\ead{francisco.wilhelmi@upf.edu}
-\author[label2]{Cristina~Cano}
-\author[label3]{Gergely~Neu}
-\author[label1]{Boris~Bellalta} 
-\author[label3]{Anders~Jonsson}
-\author[label1]{Sergio~Barrachina-Mu\~noz}
-\address[label1]{Wireless Networking Research Group (WN-UPF), 08002 Barcelona, Spain}
-\address[label2]{Wireless Networks Research Group (WINE-UOC), 08860 Castelldefels (Barelona), Spain}
-\address[label3]{Artificial Intelligence and Machine Learning Research Group (AIML-UPF), 08002 Barcelona, Spain}
+\subsection{UCB}
+\label{section:ucb}
 
-\begin{abstract}
-Next-generation wireless deployments are characterized by being dense and uncoordinated, which often leads to inefficient use of resources and poor performance.
-To solve this, we envision the utilization of completely decentralized mechanisms to enable Spatial Reuse (SR).
-In particular, we concentrate in Reinforcement Learning (RL), and more specifically, in Multi-Armed Bandits (MABs), to allow networks to modify both their transmission power and channel based on their experienced throughput.
-In this work, we study the exploration-exploitation trade-off by means of the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling action-selection strategies.
-Our results show that optimal proportional fairness can be achieved, even if no information about neighboring networks is available to the learners and WNs operate selfishly.
-However, there is high temporal variability in the throughput experienced by the individual networks, specially for $\varepsilon$-greedy and EXP3.
-We identify the cause of this variability to be the adversarial setting of our setup in which the set of most played actions provide intermittent good/poor performance depending on the neighboring decisions.
-We also show that this variability is reduced using UCB and Thompson sampling, which are parameter-free policies that perform exploration according to the reward distribution of each action.
-\end{abstract}
+\subsection{Thompson sampling}
+\label{section:ts}
 
-\begin{keyword}
-High-Density Wireless Networks, Interference, Decentralized learning, Multi Armed Bandits, Spatial Reuse, Resource Allocation.
-\end{keyword}
-
-\end{frontmatter}
-
-%\vfill
-%Francesc Wilhelmi (e-mail \href{francisco.wilhelmi@upf.edu}{francisco.wilhelmi@upf.edu}), Sergio Barrachina-Mu\~noz and Boris Bellalta are with the Wireless Networking Research Group, Universitat Pompeu Fabra, 08002 Barcelona, Spain.
-Cristina Cano is with the Wireless Networks Research Group, Universitat Oberta de Catalunya (UOC), 08860 Castelldefels (Barelona), Spain.
-Anders~Jonsson and Gergely~Neu are with the Artificial Intelligence and Machine Learning Research Group, Universitat Pompeu Fabra (UPF), 08002 Barcelona, Spain.
-
-\newpage
-%% \linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%  I. INTRODUCTION 
-%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{section:introduction}
-Due to the growing popularity of wireless deployments, especially the ones based on the IEEE 802.11 standard (i.e., Wi-Fi), it is very common to find independent overlapping Wireless Networks (WNs) sharing the same channel resources.
-Due to the decentralized nature of such kind of deployments, the lack of organization and/or agreement on sharing policies leads to inefficient resources allocation, both in spectral and spatial domains.
-An illustrative example about the inefficiency noticed in WNs regarding channel sharing can be found in \cite{akella2007self}, where the authors show that the power level used by wireless devices is typically set, by default, to the maximum, regardless of the distance between communicating nodes, and of the channel occupancy \cite{akella2007self}.
-In decentralized environments, providing a model to obtain the optimal solution can be extremely complex.
-In WNs, the interactions between devices depend on many features (such as position, environment, transmit power) and are hard to derive.
-On top of this, network dynamics, in terms of user arrivals and departures, makes the resource allocation problem even harder.
-
-In order to address the SR problem in decentralized WNs, we focus attention on Reinforcement Learning (RL), which has recently become very popular to solve many well-known problems in wireless communications.
-Some examples can be found for packet routing \cite{littman1993distributed}, Access Point (AP) selection \cite{bojovic2011supervised, bojovic2012neural}, optimal rate sampling \cite{combes2014optimal}, or energy harvesting in heterogeneous networks \cite{miozzo2015distributed}.
-Using online learning, a learner (or agent) obtains data in a sequential order and uses it to predict future good-performing actions.
-Online learning is, therefore, useful to cope with complex and dynamic environments.
-This background encourages us to approach a solution for the decentralized SR problem in WNs through online learning techniques.
-In particular, we exploit dynamic channel selection and transmit power adjustment for dealing with the performance issues resulting from uncoordinated resource sharing in WNs.
-While a proper frequency planning allows to reduce the interference between wireless devices, tuning the transmit power adds an extra level of SR that can result in improved throughput and fairness.
-
-From the family of online algorithms, we propose the utilization of Multi-Armed Bandits (MABs) \cite{BCB12}, which is a well-known model in the online learning literature for solving resource allocation problems.
-In MABs, a given agent seeks to learn a hidden reward distribution while maximizing the gains.
-This is known as the exploration-exploitation trade-off.
-%(exploitation focuses on obtaining the maximum instantaneous reward, while exploration aims to maximize the long-term reward)
-While exploitation selects actions with the goal of maximizing long-term reward given the current estimate, exploration selects actions with the goal of improving the estimate.
-Unlike for classical RL, MABs do not consider states\footnote{A state refers to a particular situation experienced by a given agent, which is defined by a set of conditions.
-By having an accurate knowledge on its current situation, an agent can define state-specific strategies that maximize its profits.} in general, which can be hard to define for the decentralized SR problem.
-On the one hand, spatial interference cannot be binary treated, thus leading to complex interactions between nodes.
-On the other hand, the adversarial setting unleashed by decentralized deployments increases the system complexity, since the state not only depends on the actions taken by a given node, but also on the adversaries behavior.
-
-This work extends our previous results presented in \cite{wilhelmi2017implications}, which were obtained by applying a stateless variation of Q-learning to the SR problem in WNs.
-Here we generalize the contributions done by implementing several action-selection strategies to allow WNs choose the channel and transmit power to use based on the resulting performance.
-In this paper, then, we provide a tutorial-based application of MABs to the decentralized SR problem, in order to maximize performance while observing the result from using different SR settings.
-According to that, we aim to illustrate the main benefits and drawbacks of applying different well-known learning techniques in a selfish way, i.e., independent WNs base their strategy on their own experienced performance.
-On the one hand, we evaluate the impact of varying parameters intrinsic to the proposed algorithms on the resulting throughput and fairness.
-In addition, we analyze the effects of learning selfishly, in order to shed some light on the future of decentralized approaches.
-Notably, we observe that even though players act selfishly, there are algorithms %learn to play collaborative actions
-learn to play actions that enhance the overall performance, some times at the cost of high temporal variability.
-Considering selfish WNs and still obtaining collaborative behaviors is appealing to typical chaotic and dynamic deployments as we get rid of the need for message passing, or inference of neighboring conditions.
-
-The main contributions of this work are summarized below:
-\begin{itemize}		
-	\item We devise the feasibility of applying MAB algorithms as defined in the online learning literature to solve the resource allocation problem in WNs.
-	\item We study the impact of different parameters intrinsic to the action-selection strategies considered (e.g., exploration coefficients, learning rates) on network performance.
-	\item We show that there are algorithms learn to play collaborative actions even though the WNs act selfishly, which is appealing to practical application in chaotic and dynamic environments.
-In addition, we shed some light on the root causes of this phenomena.
-\end{itemize}
-
-The remaining of this document is structured as follows: Section \ref{section:related_work} outlines relevant related work.
-Section \ref{section:mabs} introduces the proposed learning algorithms and their practical implementation for the resource allocation problem in WNs.
-Then, Section \ref{section:system_model} presents the simulation scenarios and the considerations taken into account.
-The simulation results are later presented in Section \ref{section:performance_evaluation}.
-Finally, Section \ref{section:conclusions} provides some final remarks.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%  II. RELATED WORK 
-%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related Work}
-\label{section:related_work} 		
-In this paper we approach the decentralized SR problem through Dynamic Channel Allocation (DCA) and Transmit Power Control (TPC).
-While the former aims to allocate the available frequency range among potentially overlapping WNs, the latter attempts to increase the number of parallel transmissions by adjusting the power transmitted by each WN.
-While DCA operates at the frequency level, TPC deals with more complex spatial interactions.
-For that, an approach that dynamically tunes the transmit power may severely affect higher communication layers such as network (routing) or transport (congestion).
-TPC directly affects the transmission range, the data rate and the energy consumption, and it may create unidirectional links that unleash fairness issues.
-In fact, acknowledgments (ACKs) and RTS/CTS frames assume bidirectionality.
-
-DCA has been extensively exploited from the centralized perspective, especially through techniques based on graph coloring \cite{riihijarvi2005frequency, mishra2005weighted}.
-Despite these kind of approaches allow to effectively reduce the interference between WNs, a certain degree of communication is required.
-Regarding decentralized methods, the authors in \cite{akl2007dynamic} propose a very simple approach in which each AP maintains an interference map of their neighbors, so that channel assignment is done through interference minimization.
-Unfortunately, the interactions between APs due to decentralization are not studied.
-Separately, \cite{chen2007improved} proposes two decentralized approaches that rely in the interference measured at both APs and STAs to calculate the best frequency channels for dynamic channel allocation.
-To do so, a WN, in addition to the interference sensed by its associated devices, considers other metrics such as the amount of traffic, so that some kind of coordination is required at the neighbor level (periodic reporting).
-
-For the case of TPC, one of the first works in studying power management is \cite{elbatt2000power}, which shows that large improvements can be achieved if selecting the appropriate transmit power level in ad-hoc WNs.
-A centralized approach for TPC is presented in \cite{tang2014joint}, which performs power control and Rate Adaptation (RA) in subgroups of Wireless Local Area Networks (WLANs).
-The creation of clusters allows defining independent power levels between devices in the same group, which are useful to avoid asymmetric links.
-However, to represent all the possible combinations, graphs can become very large, specially in high-density deployments.
-Furthermore, we find a decentralized approach that relies on real-time channel measurements \cite{gandarillas2014dynamic}.
-The proposed mechanism (so called Dynamic Transmission Power Control) is based on a set of triggered thresholds that increase/decrease the transmit power according to the situation.
-The main problem is that thresholds are set empirically (based on simulations), so the mechanism may not always improve performance.
-
-%------------------------
-% Decentralised Learning: Previous work
-%------------------------
-\subsection{Solving WNs Resource Allocation Problems via Bandits}
-\label{section:previous_work}
-In the online learning literature, several MAB settings have been considered such as stochastic bandits \cite{thompson1933likelihood,lai1985asymptotically,auer2002finite}, adversarial bandits \cite{auer1995gambling,auer2002nonstochastic}, restless bandits \cite{whittle1988restless}, contextual bandits \cite{LCLS10} and linear bandits \cite{abe2003reinforcement,APS11}, and numerous exploration-exploitation strategies have been proposed such as \textit{$\varepsilon$-greedy} \cite{sutton1998reinforcement,auer2002finite}, \textit{upper confidence bound} (UCB) \cite{lai1985asymptotically,Agr95,BuKa96,auer2002finite}, \textit{exponential weight algorithm for exploration and exploitation} (EXP3) \cite{auer1995gambling,auer2002finite} and \textit{Thompson sampling} \cite{thompson1933likelihood}.
-The classical multi-armed bandit problem models a sequential interaction scheme between a learner and an environment.
-The learner sequentially selects one out of $K$ actions (often called \emph{arms} in this context) and earns some rewards determined by the chosen action and also influenced by the environment.
-Formally, the problem
-is defined as a repeated game where the following steps are repeated in each round $t=1,2,\dots,T$:
-\begin{enumerate}
-	\item The environment fixes an assignment of rewards $r_{a,t}$ for each action $a\in[K] \stackrel{\text{def}}{=} \left\{1,2,\dots,K\right\}$,
-	\item the learner chooses action $a_t\in[K]$,
-	\item the learner obtains and observes reward $r_{a_t,t}$.
-\end{enumerate}
-The bandit literature largely focuses on the perspective of the learner with the objective of coming up with learning algorithms that attempt to maximize the sum of the rewards gathered during the whole procedure (either with finite or infinite horizon).
-As noted above, this problem has been studied under various assumptions made on the environment and the structure of the arms.
-The most important basic cases are the \emph{stochastic} bandit problem where, for each particular arm $a$, the rewards are i.i.d.~realizations of random variables from a fixed (but unknown) distribution $\nu_a$, and the \emph{non-stochastic} (or \emph{adversarial}) bandit problem where the rewards are chosen arbitrarily by the environment.
-In both cases, the main challenge for the learner is the \emph{partial observability} of the rewards: the learner only gets to observe the reward associated with the chosen action $a_t$, but never observes the rewards realized for the other actions.
-
-Let ${\rm r}_{a^*,t}$ and ${\rm r}_{a,t}$ be the rewards obtained at time $t$ from choosing actions $a^*$ (optimal) and $a$, respectively.
-Then, the performance of learning algorithms is typically measured by the \emph{total expected regret} defined as  \[R_T = \sum_{t=0}^{T} \mathbb{E}\left[\left({\rm r}_{a^*,t} - {\rm r}_{a,t}\right)\right].\]
-
-An algorithm is said to \emph{learn} if it guarantees that the regret grows sublinearly in $T$, that is, if $R_T = o(T)$ is guaranteed as $T$ grows large, or, equivalently, that the average regret $R_T/T$ converges to zero.
-Intuitively, sublinear regret means that the learner eventually identifies the action with the highest long-term payoff.
-Note, as well, that the optimal action $a^*$ is the same across all the rounds.
-Most bandit algorithms come with some sort of a guaranteed upper bound on $R_T$ which allows for a principled comparison between various methods.
-
-To the best of our knowledge, there is very little related work on applying multi-armed bandit techniques to the problem of resource allocation in WNs.
-In \cite{coucheney2015multi}, the authors propose modeling a resource allocation problem in LTE networks through MABs.
-In particular, a set of Base Stations (BS) learn the best configuration of Resource Blocks (RBs) in a decentralized way.
-For that purpose, a variation of EXP3 (so-called Q-EXP3) is proposed, which allows to reduce the strategy set.
-Despite a regret bound is provided, it is subject to the fact that an optimal resource allocation exists, i.e., every BS obtains the necessary resources.
-In addition, a large number of iterations is required to find the optimal solution in a relatively small scenario, thus revealing the difficulties shown by decentralized settings.
-
-More related to the problem proposed here, the authors in \cite{maghsudi2015joint} show a channel selection and power control approach in infrastructureless networks, which is modeled through bandits.
-In particular, two different strategies are provided to improve the performance of two Device to Device (D2D) users (each one composed by a transmitter and a receiver), which must learn the best channel and transmit power to be selected.
-Similarly to our problem, users do not have any knowledge on the channel or the other's configuration, so they rely on the experienced performance in order to find the best configuration.
-An extension of \cite{maghsudi2015joint} is provided by the same authors in \cite{maghsudi2015channel}, which includes a calibrated predictor (referred in the work as \textit{forecaster}) to infer the behavior of the other devices in order to counter act their actions.
-In each agent, the information of the forecaster is used to choose the highest-rewarding action with a certain probability, while the rest of actions are randomly selected.
-Henceforth, assuming that all the networks use a given strategy $\mathcal{X}$, fast convergence is ensured.
-Results show that channel resources are optimally distributed in a very short time frame through a fully decentralized algorithm that does not require any kind of coordination.
-Both aforementioned works rely in the existence of a unique Nash Equilibrium, which favors convergence.
-In contrast, in this article we aim to extend Bandits utilization to denser deployments, and, what is more important, to scenarios with limited available resources in which there is not a unique Nash Equilibrium (NE) that allows fast-convergence.
-Thus, we aim to capture the effects of applying selfish strategies in a decentralized way (i.e., agent $i$ follows a strategy $\mathcal{X}_i$ that does not consider the strategies of the others) and we also provide insight about the importance of past information for learning in dense WNs, which has not been studied before.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%III. MABs APPLICATION									    %	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Multi-Armed Bandits for Improving Spatial Reuse in WNs}
-\label{section:mabs}	
-The decentralized resource allocation problem in WNs we aim to solve in this work can be modeled as an approximation of contextual bandits.
-Originally, the contextual bandits problem considers the existence of a context (or a state) that influences the action-selection process.
-As a consequence, the set of available strategies varies with the context and the probability distribution of a given reward depends both on the chosen actions and also on the context.
-In the resource allocation problem at hand, the context could include information such as the number of neighboring WNs, their position, their current channel selection, the transmission power they use as well as their action-selection strategies, among other.
-However, we are interested in the case where no context can be inferred given that such information is hard and costly to obtain in practice, especially in dynamic scenarios.
-Thus, we model the decentralized SR problem in WNs as an adversarial bandit problem, in which the actions of a given WN affect the pay-off distributions of the others' actions.
-Such model requires the existence of a NE with a pure strategy,\footnote{A pure strategy NE is conformed by a set of strategies and payoffs, so that no player can obtain further benefits by deviating from its strategy.} which does not always hold for unplanned deployments due to the scarcity of the available resources and the number of overlapping WNs.
-Understanding the implications derived from such an adversarial setting in the absence of a NE is one the main goals of this paper, which, to the best of our knowledge, has been barely considered in the previous literature.
-
-We model this adversarial problem as follows.
-Let arm $a \in \mathcal{A}$ (we denote the size of $\mathcal{A}$ with K) be a configuration that a WN may choose.
-Each configuration is a combination of channel and transmit power (e.g., $a_1$ = \{Channel: 1, TPC: 5 dBm\}), and grants a reward that depends on the others' configuration.
-Let $\Gamma_{i,t}$ be the throughput experienced by $\text{WN}_i$ at time $t$, and $\Gamma_{i}^*$ the maximum achievable throughput by $\text{WN}_i$ in case of isolation (i.e., no interference is experienced in the selected channel).
-We then define the reward $r_{i,t}$ experienced by $\text{WN}_i$ at time $t$ as:
-
-\begin{equation}
-r_{i,t} = {\frac{\Gamma_{i,t}}{{\Gamma_{i}^*}}} \leq 1,
-\label{eq:reward_generation}
-\nonumber
-\end{equation}
-
-For simplicity, we consider that each WN is composed by an AP and a single STA, so that downlink traffic is held.
-Note that in typical uncoordinated wireless deployments (e.g., residential buildings), STAs are typically close to the AP to which they are associated.
-Thus, having several STAs associated to the same AP does not significantly impact the inter-WNs interference we study in this work.
-According to that, $\Gamma_{i}^*$ is computed as $B \cdot \log_{2}(1 + \text{SNR}_{i})$, where $B$ is the bandwidth, and $\text{SNR}_{i}$ is the Signal-to-Noise ratio experienced by the STA of $\text{WN}_i$.
-We consider this model because it allows to properly capture the interference generated between WNs, which is sought to be minimized.
-
-We have considered the \emph{$\varepsilon$-greedy}, \emph{EXP3}, \emph{UCB} and \emph{Thompson sampling} action-selection strategies, which are described next in this section.
-While $\varepsilon$-greedy and EXP3 explicitly include the concepts of \emph{exploration coefficient} and \emph{learning rate}, respectively, UCB and Thompson sampling are parameter-free policies that extend the concept of exploration (actions are explored according to their estimated value and not by commitment).
-Henceforth, we are able to study the effects of these different kind of policies on the WNs behavior.
-Moreover, we chose the aforementioned policies because they are widely spread and considered of remarkable importance in the MABs literature.
-
-Furthermore, in order to provide a fair comparison, we have considered that all the policies use the same reward.
-Regarding the learning process, we assume that WNs select actions during the same time slot.
-The reward experienced by the WNs is computed once all of them have chosen their action for the current iteration.
-In practice the action-selection process at WNs will most probably not be synchronized but we leave the study of any possible effects of that desynchronization to future work.
-
-%------------------------
-% Bandits - e-greedy
-%------------------------
-\subsection{$\varepsilon$-greedy}
-\label{section:bandits_egreedy}	
-The \emph{$\varepsilon$-greedy} policy \cite{sutton1998reinforcement,auer2002finite} is arguably the simplest learning algorithm attempting to deal with exploration-exploitation trade-offs.
-In each round $t$, the $\varepsilon$-greedy algorithm explicitly decides whether to explore or exploit: with probability $\varepsilon$, the algorithm picks an arm uniformly at random (exploration), and otherwise it plays the arm with the highest empirical return $\hat{r}_{k,t}$ (exploitation).
-
-In case $\varepsilon$ is fixed for the entire process, the expected regret is obviously going to grow linearly as $\Omega\left(\varepsilon T\right)$ in general.
-Therefore, in order to obtain a sublinear regret guarantee (and thus an asymptotically optimal growth rate for the total rewards), it is critical to properly adjust the exploration coefficient.
-Thus, in our implementation of the $\varepsilon$-greedy algorithm, we use a time-dependent exploration rate of $\varepsilon_t = \varepsilon_0 / \sqrt{t}$, as suggested in the literature \cite{auer2002finite}.
-The adaptation of this policy to our setting is shown as Algorithm \ref{alg:egreedy}.
-
-\begin{algorithm}[H]	
-	\SetAlgoLined
-	\KwIn{SNR: information about the Signal-to-Noise Ratio received at the STA, $\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-	\textbf{Initialize:} $t=0$, $\varepsilon_t = \varepsilon_0$, $r_{k} = 0, \forall a_k \in \mathcal{A}$\\
-	\While{active}{
-		Select $a_k$  $\begin{cases}
-		\underset{k=1,...,K}{\text{argmax }} r_{k,t},& \text{with prob. } 1 - \varepsilon\\
-		k \sim \mathcal{U}(1, K),              & \text{otherwise}
-		\end{cases}$\\
-		Observe the throughput experienced $\Gamma_t$\\
-		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-		%$p_{k,t} \leftarrow r_{k,t}$\\
-		$\varepsilon_t \gets \varepsilon_0 / \sqrt{t}$ \\
-		$ t \gets t + 1$
-	}
-	\caption{Implementation of Multi-Armed Bandits ($\varepsilon$-greedy) in a WN. $\mathcal{U}(1, K)$ is a uniform distribution that randomly chooses from 1 to $K$.}
-	\label{alg:egreedy}			
-\end{algorithm}
-
-%\begin{algorithm}[h!]
-%	\SetKwInOut{Input}{Input}
-%	\SetKwInOut{Output}{Output}		
-%	Function EXP3 $(\text{SNR},\mathcal{A})$\;
-%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-%	initialize: $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 0, \forall a_k \in \mathcal{A}$\\
-%	\While{active}
-%	{
-%		$p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
-%		Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
-%		Observe the throughput experienced $\Gamma_t$\\
-%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		$\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
-%		$w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
-%		$w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
-%		%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
-%		$\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
-%		$t \leftarrow t + 1$\\
-%	}
-%	\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
-%	\label{alg:exp3}
-%\end{algorithm}
-%
-%
-%
-%	\begin{algorithm}
-%	\caption{Implementation of Multi-Armed Bandits ($\varepsilon$-greedy) in a WN. $\mathcal{U}(1, K)$ is a uniform distribution that randomly chooses from 1 to $K$.}
-%	\label{alg:egreedy}		
-%	\begin{algorithmic}[1]
-%		%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
-%		\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
-%		\While{active}
-%		\State Select $a_k$  $\begin{cases}
-%		\underset{k=1,...,K}{\text{argmax }} r_{k,t},& \text{with prob. } 1 - \varepsilon\\
-%		k \sim \mathcal{U}(1, K),              & \text{otherwise}
-%		\end{cases}$\\
-%		\State Observe the throughput experienced $\Gamma_t$\\
-%		\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		%$p_{k,t} \leftarrow r_{k,t}$\\
-%		\State $\varepsilon_t \gets \varepsilon_0 / \sqrt{t}$ \\
-%		\State $ t \gets t + 1$
-%		\EndWhile
-%		%\EndProcedure
-%	\end{algorithmic}
-%\end{algorithm}
-
-%------------------------
-% Bandits - EXP3
-%------------------------
-\subsection{EXP3}
-\label{section:bandits_exp3}	
-The EXP3 algorithm \cite{auer1995gambling,auer2002nonstochastic} is an adaptation of the weighted majority algorithm of \cite{LW94,FS97} to the non-stochastic bandit problem.
-EXP3 maintains a set of non-negative weights assigned to each arm and picks the actions randomly with a probability proportional to their respective weights (initialized to 1 for all arms).
-The aim of EXP3 is to provide higher weights to the best actions as the learning procedure proceeds.
-
-More formally, letting $w_{k,t}$ be the weight of arm $k$ at time $t \in \{1,2 ...\}$, EXP3 computes the probability $p_{k,t}$ of choosing arm $k$ in round $t$ as
-\begin{equation}
-\label{eq:exp3_prob}
-p_{k,t} = (1-\gamma) \frac{w_{k,t}}{\sum_{i=1}^{\text{K}}w_{i,t}} + \frac{\gamma}{K},
-\nonumber
-\end{equation}
-where $\gamma\in[0,1]$ is a parameter controlling the rate of exploration.
-Having selected arm $a_t$, the learner observes the generated pay-off $r_{a_t,t}$ and computes the importance-weighted reward estimates
-\begin{equation}
-\label{eq:exp3_estimated_reward}
-\widehat{r}_{k,t} = \frac{\mathbb{I}_{\left\{I_t = k\right\}}r_{k,t}}{p_{k,t}}
-\nonumber
-\end{equation}
-for all $k\in[K]$, where $\mathbb{I}_{\left\{A \right\}}$ denoting the indicator function of the event $A$ taking a value of $1$ if $A$ is true and $0$ otherwise.
-Finally, the weight of arm $k$ is updated as a function of the estimated reward:
-\begin{equation}
-\label{eq:exp3_weights}
-w_{k,t+1}=w_{k,t} e^{\frac{\eta \cdot \widehat{r}_{k,t}}{K}},
-\nonumber
-\end{equation}	
-where $\eta>0$ is a parameter of the algorithm often called the \emph{learning rate}.
-Intuitively, $\eta$ regulates the rate in which the algorithm incorporates new observations with large values of $\eta$ corresponding to more confident updates and smaller values leading to more conservative behavior.
-As we did for the exploration coefficient in \emph{$\varepsilon$-greedy}, we use a time-dependent learning rate of $\eta_t = \eta_0 / \sqrt{t}$ \cite{auer2002finite}.
-Our implementation of EXP3 to the WN problem is detailed in Algorithm \ref{alg:exp3}.
-%\begin{algorithm}[h!]
-%	Function EXP3 $(\text{SNR},\mathcal{A})$\\
-%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}\\
-%	initialize: $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 0, \forall a_k \in \mathcal{A}$\\
-%	\While{active}
-%	{
-%		$p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
-%		Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
-%		Observe the throughput experienced $\Gamma_t$\\
-%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		$\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
-%		$w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
-%		$w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
-%		%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
-%		$\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
-%		$t \leftarrow t + 1$\\
-%	}
-%	\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
-%	\label{alg:exp3}
-%\end{algorithm}
-
-\begin{algorithm}[H]	
-	\SetAlgoLined
-	\KwIn{SNR: information about the Signal-to-Noise Ratio received at the STA, $\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-	\textbf{Initialize:} $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 0, \forall a_k \in \mathcal{A}$\\
-	\While{active}{
-		$p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
-		Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
-		Observe the throughput experienced $\Gamma_t$\\
-		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-		$\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
-		$w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
-		$w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
-		%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
-		$\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
-		$t \leftarrow t + 1$\\
-	}		
-	\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
-	\label{alg:exp3}	
-\end{algorithm}
-%	\begin{algorithm}
-%		\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
-%		\label{alg:exp3}
-%		\begin{algorithmic}[1]
-%			%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
-%			\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
-%			\While{active}
-%			\State $p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
-%			\State Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
-%			\State Observe the throughput experienced $\Gamma_t$\\
-%			\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%			\State $\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
-%			\State $w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
-%			\State $w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
-%			%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
-%			\State $\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
-%			\State $t \leftarrow t + 1$\\
-%			\EndWhile
-%			%\EndProcedure
-%		\end{algorithmic}
-%	\end{algorithm}
-
-%------------------------
-% Bandits - UCB
-%------------------------
-\subsection{UCB}
-\label{section:bandits_ucb}		
-The \emph{upper confidence bound} (UCB) action-selection strategy \cite{Agr95,BuKa96,auer2002finite} is based on the principle of \emph{optimism in face of uncertainty}: in each round, UCB selects the arm with the highest statistically feasible mean reward given the past observations.
-Statistical feasibility here is represented by an upper confidence bound on the mean rewards which shrinks around the empirical rewards as the number of observations increases.
-Intuitively, UCB trades off exploration and exploitation very effectively, as upon every time a suboptimal arm is chosen, the corresponding confidence bound will shrink significantly, thus quickly decreasing the probability of drawing this arm in the future.
-The width of the confidence intervals is chosen carefully so that the true best arm never gets discarded accidentally by the algorithm, yet suboptimal arms are not drawn as few times as possible.
-To obtain the first estimates, each arm is played once at the initialization.
-
-Formally, let $n_k$ be the number of times that arm $k$ has been played, and $\Gamma_{k,t}$ the throughput obtained by playing arm $k$ at time $t$.
-The average experienced reward $\overline{r}_{k,t}$ by arm $k$ at time $t$ is therefore given by:
-\begin{equation}
-\label{eq:ucb}
-\overline{r}_{k,t} = \frac{1}{n_k} \sum_{s=1}^{n_k} r_{k,s}
-\nonumber
-\end{equation}	
-Based on these average rewards, UCB selects the action that maximizes $\overline{r}_{k,t} + \sqrt{\frac{2 \ln(t)}{n_k}}$.
-By doing so, UCB implicitly balances exploration and exploitation, as it focuses efforts on the arms that are $i)$ the most promising (with large estimated rewards) or $ii)$ not explored enough (with small $n_k$).
-Our implementation of UCB to the WN problem is detailed in Algorithm \ref{alg:ucb}.
-%Note as well, that UCB suffers a logarithmic regret, instead of the linear regret granted by ``$\varepsilon$-greedy" \cite{lai1985asymptotically}.	
-% According to \cite{auer2002nonstochastic}, the UCB algorithm provides a logarithmic asymptotic regret $R_{T}$ for a given time period $T > 0$, as shown in (\ref{eq:ucb_regret}):
-%	\begin{equation}
-%	\label{eq:ucb_regret}
-%	R_T = G_{max}(T)-\mathop{\mathbb{E}}(G_{\text{UCB}}(T)) \leq 8 \sum_{i:\mu_i < \mu^{*}} \frac{\ln T}{\Delta_i} + \Big(1+\frac{\pi^2}{3}\Big) \sum_{i=1}^{K}\Delta_i  ,
-%	\end{equation}	
-%	where $G_{max}(T)$ is the maximum achievable gain at $T$, $\mathbb{E}(G_{\text{UCB}}(T))$ is the expected gain obtained at $T$ by applying the UCB policy, $\Delta_i = \mu^{*} - \mu_i$ is the difference between the empirical mean of the best arm and the chosen one.
-In Equation \ref{eq:ucb_regret}, both expected losses and risks are embodied (first and second term, respectively).
-%\begin{algorithm}[h!]
-%	\SetKwInOut{Input}{Input}
-%	\SetKwInOut{Output}{Output}		
-%	Function UCB $(\text{SNR},\mathcal{A})$\;
-%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-%	initialize: $t=0$, play each arm $a_k \in \mathcal{A}$ once\\
-%	\While{active}
-%	{
-%		Draw $a_k = \underset{k=1,...,K}{\text{argmax }} \overline{r}_{k} + \sqrt{\frac{2 ln(t)}{n_{k}}} $ \\
-%		Observe the throughput experienced $\Gamma_t$\\			
-%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		$n_k \leftarrow n_k + 1$\\
-%		$ \overline{r}_{k} \leftarrow \frac{1}{n_{k}} \sum_{s=1}^{n_{k}} r_{k,s}$\\
-%		$t \leftarrow t + 1$
-%	}
-%	\caption{Implementation of Multi-Armed Bandits (UCB) in a WN}
-%	\label{alg:ucb}
-%\end{algorithm}
-
-\begin{algorithm}[]
-	\SetAlgoLined
-	\KwIn{SNR: information about the Signal-to-Noise Ratio received at the STA, $\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-	\textbf{Initialize:} $t=0$, play each arm $a_k \in \mathcal{A}$ once\\
-	\While{active}{
-		Draw $a_k = \underset{k=1,...,K}{\text{argmax }} \overline{r}_{k} + \sqrt{\frac{2 ln(t)}{n_{k}}} $ \\
-		Observe the throughput experienced $\Gamma_t$\\			
-		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-		$n_k \leftarrow n_k + 1$\\
-		$ \overline{r}_{k} \leftarrow \frac{1}{n_{k}} \sum_{s=1}^{n_{k}} r_{k,s}$\\
-		$t \leftarrow t + 1$
-	}		
-	\caption{Implementation of Multi-Armed Bandits (UCB) in a WN}
-	\label{alg:ucb}			
-\end{algorithm}	
-%	\begin{algorithm}
-%		\caption{Implementation of Multi-Armed Bandits (UCB) in a WN}
-%		\label{alg:ucb}	
-%		\begin{algorithmic}[1]
-%			%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
-%			\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
-%			\While{active}
-%			\State Draw $a_k = \underset{k=1,...,K}{\text{argmax }} \overline{r}_{k} + \sqrt{\frac{2 ln(t)}{n_{k}}} $ \\
-%			\State Observe the throughput experienced $\Gamma_t$\\			
-%			\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%			\State $n_k \leftarrow n_k + 1$\\
-%			\State $ \overline{r}_{k} \leftarrow \frac{1}{n_{k}} \sum_{s=1}^{n_{k}} r_{k,s}$\\
-%			\State $t \leftarrow t + 1$
-%			\EndWhile\label{euclidendwhile}
-%			%\EndProcedure
-%		\end{algorithmic}
-%	\end{algorithm}
-
-%------------------------
-% Bandits - Thompson sampling
-%------------------------
-\subsection{Thompson sampling}
-\label{section:bandits_thompsons}	
-Thompson sampling \cite{thompson1933likelihood} is a well-studied action-selection technique that had been known for its excellent empirical performance \cite{CL11} and was recently proven to achieve strong performance guarantees, often better than those warranted by UCB \cite{AG12,KKM12,KKM13}.
-Thompson sampling is a Bayesian algorithm: it constructs a probabilistic model of the rewards and assumes a prior distribution of the parameters of said model.
-Given the data collected during the learning procedure, this policy keeps track of the posterior distribution of the rewards, and pulls arms randomly in a way that the drawing probability of each arm matches the probability of the particular arm being optimal.
-In practice, this is implemented by sampling the parameter corresponding to each arm from the posterior distribution, and pulling the arm yielding the maximal expected reward under the sampled parameter value.
-
-For the sake of practicality, we aim to apply Thompson sampling using a Gaussian model for the rewards with a standard Gaussian prior as suggested in \cite{agrawal2013further}.
-By standard calculations, it can be verified that the posterior distribution of the rewards under this model is Gaussian with mean
-\begin{equation}
-\hat{r}_k(t) = \frac{\sum_{w=1:k}^{t-1} r_k(t) }{n_k(t) + 1}
-\nonumber
-\end{equation}
-and variance $\sigma_k^2(t) = \frac{1}{n_k + 1}$, where $n_k$ is the number of times that arm $k$ was drawn until the beginning of round $t$.
-Thus, implementing Thompson sampling in this model amounts to sampling a parameter $\theta_k$ from the Gaussian distribution $\mathcal{N}\left(\hat{r}_k(t),\sigma_k^2(t)\right)$ and choosing the action with the maximal parameter.
-Our implementation of Thompson sampling to the WN problem is detailed in Algorithm \ref{alg:thompsons}.
-%\begin{algorithm}[h!]
-%	\SetKwInOut{Input}{Input}
-%	\SetKwInOut{Output}{Output}		
-%	Function Thompson sampling $(\text{SNR},\mathcal{A})$\;
-%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-%	initialize: $t=0$,  for each arm $a_k \in \mathcal{A}$, set $\hat{r}_{k} = 0$ and $n_k = 0$ \\
-%	\While{active}
-%	{
-%		For each arm $a_k \in \mathcal{A}$, sample $\theta_k(t)$ from normal distribution $\mathcal{N}(\hat{r}_{k}, \frac{1}{n_k + 1})$ \\
-%		Play arm $a_{k} = \underset{k=1,...,K}{\text{argmax }} \theta_k(t) $ \\
-%		Observe the throughput experienced $\Gamma_t$\\			
-%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		$ \hat{r}_{k,t} \leftarrow \frac{\hat{r}_{k,t}  n_{k,t} + r_{k,t}}{n_{k,t} + 2}$\\
-%		$n_{k,t} \leftarrow n_{k,t} + 1$\\
-%		$t \leftarrow t + 1$
-%	}
-%	\caption{Implementation of Multi-Armed Bandits (Thompson sampling) in a WN}
-%	\label{alg:thompsons}
-%\end{algorithm}
-
-\begin{algorithm}[]
-	\SetAlgoLined
-	\KwIn{SNR: information about the Signal-to-Noise Ratio received at the STA, $\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-	\textbf{Initialize:} $t=0$,  for each arm $a_k \in \mathcal{A}$, set $\hat{r}_{k} = 0$ and $n_k = 0$ \\
-	\While{active}{
-		For each arm $a_k \in \mathcal{A}$, sample $\theta_k(t)$ from normal distribution $\mathcal{N}(\hat{r}_{k}, \frac{1}{n_k + 1})$ \\
-		Play arm $a_{k} = \underset{k=1,...,K}{\text{argmax }} \theta_k(t) $ \\
-		Observe the throughput experienced $\Gamma_t$\\			
-		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-		$ \hat{r}_{k,t} \leftarrow \frac{\hat{r}_{k,t}  n_{k,t} + r_{k,t}}{n_{k,t} + 2}$\\
-		$n_{k,t} \leftarrow n_{k,t} + 1$\\
-		$t \leftarrow t + 1$
-	}		
-	\caption{Implementation of Multi-Armed Bandits (Thompson sampling) in a WN}
-	\label{alg:thompsons}
-\end{algorithm}
-%	\begin{algorithm}
-%		\caption{Implementation of Multi-Armed Bandits (Thompson sampling) in a WN}
-%		\label{alg:thompsons}
-%		\begin{algorithmic}[1]
-%			%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
-%			\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
-%			\While{active}
-%			\State For each arm $a_k \in \mathcal{A}$, sample $\theta_k(t)$ from normal distribution $\mathcal{N}(\hat{r}_{k}, \frac{1}{n_k + 1})$ \\
-%			\State Play arm $a_{k} = \underset{k=1,...,K}{\text{argmax }} \theta_k(t) $ \\
-%			\State Observe the throughput experienced $\Gamma_t$\\			
-%			\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%			\State $ \hat{r}_{k,t} \leftarrow \frac{\hat{r}_{k,t}  n_{k,t} + r_{k,t}}{n_{k,t} + 2}$\\
-%			\State $n_{k,t} \leftarrow n_{k,t} + 1$\\
-%			\State $t \leftarrow t + 1$
-%			\EndWhile
-%			%\EndProcedure
-%		\end{algorithmic}
-%	\end{algorithm}
-
-%%%%%%%%%%%%%%%
-% III. SYSTEM MODEL %
-%%%%%%%%%%%%%%%
-\section{System model}
-\label{section:system_model}
-
-For the remainder of this work, we study the interactions between several WNs placed in a 3-D scenario that occur when applying MABs in a decentralized manner (with parameters described later in Section \ref{section:simulation_parameters}).
-For simplicity, we consider WNs to be composed by an Access Point (AP) transmitting to a single Station (STA) in a downlink manner.
-Additionally, to analyze the adversarial setting when WNs share scarce resources, we consider that the number of channels is equal to half the number of coexisting WNs, thus making the SR even more challenging.
-
-%------------------------
-% Channel modelling
-%------------------------
-\subsection{Channel modeling}
-\label{section:channel_modelling}		
-Path-loss and shadowing effects are modeled using the log-distance model for indoor communications. The path-loss between WN $i$ and WN $j$ is given by:	
-\begin{equation}
-\text{PL}_{i,j} = \text{P}_{{\rm tx},i} - \text{P}_{{\rm rx},j} = \text{PL}_0 + 10  \alpha  \log_{10}(d_{i,j}) + \text{G}_{{\rm s}} + \frac{d_{i,j}}{d_{{\rm obs}}} \text{G}_{{\rm o}}, \nonumber
-\nonumber
-\end{equation}
-where $\text{P}_{{\rm tx},i}$ is the transmitted power in dBm by the AP in $\text{WN}_i$, $\alpha$ is the path-loss exponent, $\text{P}_{{\rm rx},j}$ is the power in dBm received at the STA in $\text{WN}_j$, $\text{PL}_0$ is the path-loss at one meter in dB, $d_{i,j}$ is the distance between the transmitter and the receiver in meters, $\text{G}_{{\rm s}}$ is the log-normal shadowing loss in dB, and $\text{G}_{{\rm o}}$ is the obstacles loss in dB.
-Note that we include the factor $d_{{\rm obs}}$, which is the average distance between two obstacles in meters.
-
-%------------------------
-% Throughput calculation
-%------------------------
-\subsection{Throughput calculation}
-\label{section:throughput_calculation}
-As previously mentioned, we use the power received and the interference to calculate the maximum theoretical throughput of each WN $i$ at time $t$ by using the Shannon Capacity,
-\begin{equation}
-\Gamma_{i,t} = B  \log_{2}(1 + \text{SINR}_{i, t}),
-\nonumber
-\label{eq:shannon_capacity}
-\end{equation}
-where $B$ is the channel width and the experienced Signal to Interference plus Noise Ratio (SINR) is given by:
-\begin{equation}
-\text{SINR}_{i,t} = \frac{\text{P}_{i,t}}{\text{I}_{i,t}+\text{N}},
-\label{eq:sinr}
-\nonumber
-\end{equation}
-where $\text{P}_{i,t}$ and $\text{I}_{i,t}$ are the received power and the sum of the interference at WN $i$ at time $t$, respectively, and N is the floor noise power.
-For each WN, we consider the interference to be the total power received from all the APs in the same channel.
-For capturing the worst-case scenario, we consider that all WNs are continuously transmitting (i.e., we do not consider empty channel periods left by the medium access procedure).
-Adjacent channel interference is also considered in $\text{I}_{i,t}$, so that the transmitted power leaked to adjacent channels is $20$ dBm lower for each extra channel separation.
-
-%------------------------
-% Simulation Parameters
-%------------------------
-\subsection{Simulation Parameters}
-\label{section:simulation_parameters}
-According to \cite{bellalta2016ax}, which provides an overview of the IEEE 802.11ax-2019 standard, a typical high-density scenario for residential buildings contains $0.0033 \text{APs}/\text{m}^3$ (i.e., 100 APs in a $100 \times 20 \times 15$ m area).
-Accordingly, for simulation purposes, we define a map scenario with dimensions $10\times5\times10$ m, containing from 2 to 8 APs.
-In addition, for the first part of the simulations, we consider a setting containing 4 WNs that form a grid topology.
-In it, STAs are placed at the maximum possible distance from the other networks.
-
-Table \ref{tbl:simulation_parameters} details the parameters used.	
-\begin{table}[h!]
-	\centering
-	%\resizebox{\columnwidth}{!}{
-		\begin{tabular}{|l|l|}
-			\hline
-			\textbf{Parameter}             & \textbf{Value}                      \\ \hline
-			Map size (m)                    & $10\times5\times10$                  \\ \hline
-			Number of coexistent WNs      & \{2, 4, 6, 8\} \\ \hline
-			APs/STAs per WN                    & 1 / 1                                     \\ \hline
-			Distance AP-STA (m)     & $\sqrt{2}$                         \\ \hline
-			Number of Channels              & 2                               \\ \hline
-			Channel Bandwidth (MHz)         & 20                                    \\ \hline
-			Initial channel selection model & Uniformly distributed 
-			\\ \hline
-			TPC Values (dBm)                & \{5, 10, 15, 20\}                      \\ \hline				
-			$\text{PL}_0$ (dB)                   & 5
-			\\ \hline
-			$\text{G}_s$ (dB)                   & Normally distributed with mean 9.5 
-			\\ \hline
-			$\text{G}_o$ (dB)                  & Uniformly distributed with mean 30
-			\\ \hline
-			$d_{\rm obs}$  (meters between two obstacles)                 & 5                        
-			\\ \hline
-			Noise level (dBm)               & -100                                  \\ \hline
-			Traffic model                   & Full buffer (downlink)             \\ \hline          
-			Number of learning iterations                  & 10,000             \\ \hline   
-	\end{tabular}%}
-	\caption{Simulation parameters}
-	\label{tbl:simulation_parameters}
-\end{table}
-
-%%%%%%%%%%%%%%
-% V. SIMULATIONS   %
-%%%%%%%%%%%%%%
-\section{Performance Evaluation}
-\label{section:performance_evaluation}	
-In this Section, we evaluate the performance of each action-selection strategy presented in Section \ref{section:mabs} when applied to the decentralized SR problem in WNs.\footnote{All of the source code used in this work open \cite{fwilhelmi2017code}, encouraging sharing of algorithms between contributors and providing the ability for people to improve on the work of others under the GNU General Public License v3.0} For that purpose, we first evaluate the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling policies in a controlled environment.
-Without loss of generality, we consider a symmetric configuration in this scenario in order to analyze the competition effects when WNs have the same opportunities for accessing the channel.
-Then, in Section \ref{section:random}, we provide a performance comparison of the aforementioned scenarios with different densities and with randomly located WNs.
-
-\subsection{Toy Grid Scenario}		
-\label{section:toy_grid_scenario}	
-We start considering a toy scenario consisting in a grid of 4 WNs, as illustrated in Figure \ref{fig:scenario}.
-This scenario has the particularity of being symmetric, so that adversarial WNs have the same opportunities to compete for the channel resources.
-Henceforth, this scenario allows us to \emph{i)} simplify the evaluation of the proposed algorithms, \emph{ii)} frame the competition between WNs on equal terms.
-
-\begin{figure}[t!]
-	\centering											
-	\epsfig{file=images/4_WLANs_scenario.eps, width=8.5cm}
-	\caption{Grid scenario containing 4 WNs, each one composed by an AP and a STA.}
-	\label{fig:scenario}
-\end{figure}
-
-%------------------------
-% Optimality study
-%------------------------
-\subsubsection{Optimal Solution}
-\label{section:optimal_solution}	
-Before presenting the simulation results of applying a particular action-selection policy, we introduce the optimal solutions that: \emph{i)} maximize the aggregate throughput and \emph{ii)} correspond to proportional fairness\footnote{The proportional fairness solutions satisfy $\underset{a_k \in \mathcal{A}}{\rm max} \sum_{i \in \mathcal{WN}} \log(\Gamma_{i,a_k})$.} for the considered grid scenario, shown in Figure \ref{fig:scenario}.
-%Knowing the maximum achievable performance in the presented scenario allows us to provide a meaningful comparison of the introduced policies to be followed by the WNs.
-
-Let actions range from $a_1$ to $a_8$, and map to \{channel number, transmit power (dBm)\}: $a_1$ = \{1, 5\}, $a_2$ = \{2, 5\}, $a_3$ = \{1, 10\}, $a_4$ = \{2, 10\}, $a_5$ = \{1, 15\}, $a_6$ = \{2, 15\}, $a_7$ = \{1, 20\} and $a_8$ = \{2, 20\}.
-According to our model, the joint configuration of the 4 WNs that grants the maximum aggregate throughput is any combination of actions \{$a_1$, $a_7$, $a_8$\}, subject to the condition of two close WNs using $a_1$.
-Despite the scenario is symmetric, the distance between APs is not the same in all the cases.
-For instance, $d_{\text{AP}_1,\text{AP}_2} > d_{\text{AP}_1,\text{AP}_4}$.
-It is important to emphasize that the proposed scenario does not consider asymmetries between WNs, so that dominance relationships are not present.
-In case of suffering from such asymmetries, the performance of a given WN would depend on the configuration of its neighboring networks but it won't be able to affect their behavior.
-For instance, a WN in the middle of two others may suffer from flow starvation if the WNs in the extremes do not sense each other.
-In such a situation, the WN in the middle is not able to fairly compete for channel resources due to the asymmetric situation it suffers.
-
-In our symmetric scenario, the optimal aggregate throughput is 1124 Mbps, and is only achieved when two consecutive WNs sacrifice themselves by choosing a lower transmit power (action $a_1$).
-Moreover, to maximize the proportional fairness, the optimal joint configuration changes to any combination using the maximum transmit power (i.e., $a_7$ and $a_8$), so that frequency reuse is maximized; WNs using the same channel must be as much separated as possible.
-Such a configuration leads to an aggregate throughput of 891 Mbps, which is quite lower than in the former case, but allows experiencing a fairer configuration.
-Note that all WNs obtain the same throughput in this case as frequency reuse is achieved (closer WNs choose different channels), but power is kept equal for each WN and despite experiencing higher interference, none of the WNs sacrifice themselves.
-The aim of the following performance evaluation is to gain insight into whether a collaborative result, close to this equal division of resources given by the proportional fair action selection, is likely to be learned by the algorithms and if so, under which conditions.
-
-%------------------------
-% Study of MAB (e-greedy)
-%------------------------
-\subsubsection{Performance of the $\varepsilon$-greedy policy}
-\label{section:egreedy_study}	
-We first evaluate the performance of the $\varepsilon$-greedy policy when applied to the WNs problem, which allows us to study the purest form of the exploitation-exploration trade-off.
-First, we show the impact of modifying the initial exploration coefficient, $\varepsilon_0$ (recall that we have considered $\varepsilon_t = \varepsilon_0 / \sqrt{t}$), on the average throughput experienced by the overlapping WNs.
-Figure \ref{fig:egreedy_tuning_parameters} shows the aggregate throughput obtained in the grid scenario when applying $\varepsilon$-greedy during 10,000 iterations, and for each $\varepsilon_0$ value between 0 and 1 in 0.1 steps.
-The average and standard deviation of the throughput from 100 simulation runs are shown, which are compared with the optimal throughput presented in Section \ref{section:optimal_solution}.
-\begin{figure}[t!]
-	\centering							
-	\epsfig{file=images/egreedy_tuning_parameters_zoom.eps, width=6.5cm}
-	\caption{Average aggregate throughput and standard deviation obtained for each $\varepsilon_0$ value in $\varepsilon$-greedy.
-Results are from 100 simulations lasting 10,000 iterations each.
-The proportional fair solution is also shown (red dashed line).}
-	\label{fig:egreedy_tuning_parameters}
-\end{figure}		
-As shown in the figure, the aggregate throughput obtained in average is quite similar for all the provided values of $\varepsilon_0$, except for the complete random case where no exploration is done ($\varepsilon_0 = 0$).
-The lower the $\varepsilon_0$ parameter, the less exploration is performed.
-Consequently, for low $\varepsilon_0$, the average throughput is highly dependent on how good/bad were the actions taken at the beginning of the learning process, which results in a higher standard deviation as $\varepsilon_0$ goes to 0.
-
-Now, in order to provide a deeper analysis on the WNs behavior when implementing the $\varepsilon$-greedy policy, we focus on the actions probability and the temporal evolution of throughput derived from a single simulation run.
-To this aim, we use $\varepsilon_0 = \{0.1, 0.5, 1\}$, which correspond to three representative cases (low exploration, middle degree of exploration and intensive exploration).
-Figure \ref{fig:eg_actions_distr} shows the action probability distribution at each WN at the end of the 10,000 iteration-long simulation, and for each of the selected $\varepsilon_0$ values.
-
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e01} \\[\abovecaptionskip]
-		\small (a) $\varepsilon_0$ = 0.1
-		\label{fig:eg_e01_actions_distr}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e05} \\[\abovecaptionskip]
-		\small (b) $\varepsilon_0$ = 0.5
-		\label{fig:eg_e05_actions_distr}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e1} \\[\abovecaptionskip]
-		\small (c) $\varepsilon_0$ = 1
-		\label{fig:eg_1_actions_distr}
-	\end{tabular}
-	\caption{Probability of taking a given action in $\varepsilon$-greedy for different $\varepsilon_0$ values after a simulation of 10,000 iterations.}
-	\label{fig:eg_actions_distr}
-\end{figure*}
-
-We observe in this figure that more aggressive actions (i.e., the ones that use the maximum transmit power) are chosen with a higher rate in all the WNs as $\varepsilon_0$ increases.
-A higher degree of exploration allows WNs to observe the effects of the actions taken by the others, thus acting in consequence.
-Accordingly, WNs alternate good/poor performance depending on the actions of the others, which at the same time are also selected intermittently.
-Despite using a high transmit power allows obtaining a better SNR at the receivers, the generated interference at times becomes counter-productive in terms of individual and aggregate throughput.
-
-On the other hand, as $\varepsilon_0$ decreases (refer to Figure \ref{fig:eg_actions_distr}(a)), WNs are prone to exploit the same action more frequently, which are the ones that provide the highest known performance.
-This low degree of exploration results also in a smaller usage of suboptimal actions.
-
-Figure \ref{fig:eg_agg_tpt}  shows the aggregate throughput evolution, which suffers from higher temporal variability as $\varepsilon_0$ increases.
-The same observation can be done from the individual throughput evolution (shown in Figure \ref{fig:eg_ind_tpt}), which in addition shows larger differences between the individual patterns for lower $\varepsilon_0$ values.
-These differences correspond to unfair performance resulting from a low degree of exploration.
-% e-greedy: aggregate throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e01} \\[\abovecaptionskip]
-		\small (a) $\varepsilon_0$ = 0.1
-		\label{fig:eg_e01_agg_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e05} \\[\abovecaptionskip]
-		\small (b) $\varepsilon_0$ = 0.5
-		\label{fig:eg_e05_agg_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e1} \\[\abovecaptionskip]
-		\small (c) $\varepsilon_0$ = 1
-		\label{fig:eg_e1_agg_tpt}
-	\end{tabular}
-	\caption{Aggregate throughput evolution for a single $\varepsilon$-greedy 10,000-iterations simulation and for different $\varepsilon_0$ values.
-The proportional fair result is also shown (red dashed line).}
-	\label{fig:eg_agg_tpt}
-\end{figure*}
-
-% e-greedy: individual throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e01} \\[\abovecaptionskip]
-		\small (a) $\varepsilon_0$ = 0.1
-		\label{fig:eg_e01_ind_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e05} \\[\abovecaptionskip]
-		\small (b) $\varepsilon_0$ = 0.5
-		\label{fig:eg_e05_ind_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e1} \\[\abovecaptionskip]
-		\small (c) $\varepsilon_0$ = 1
-		\label{fig:eg_e1_ind_tpt}
-	\end{tabular}
-	\caption{Individual throughput evolution for a single $\varepsilon$-greedy 10,000-iterations simulation and for different $\varepsilon_0$ values.
-The proportional fair result is also shown (red dashed line).}
-	\label{fig:eg_ind_tpt}
-\end{figure*}
-
-To gain further insight into fairness, we depict in Figure \ref{fig:eg_avg_tpt} the average  and standard deviation of the throughput at each WN.
-We have now concentrated in the last 5,000 iterations of the simulation, disregarding the instability provoked during the transitory regime, so that we get a better picture of the long-term behavior.
-We see that as $\varepsilon_0$ increases, the experienced fairness becomes higher due to the temporal fluctuation that occurs as a consequence of performing more exploratory actions.
-Moreover, we also observe that the standard deviation of the throughput is similar at each WN.
-
-% e-greedy: average throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e01} \\[\abovecaptionskip]
-		\small (a) $\varepsilon_0$ = 0.1
-		\label{fig:eg_e01_avg_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e05} \\[\abovecaptionskip]
-		\small (b) $\varepsilon_0$ = 0.5
-		\label{fig:eg_e05_avg_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e1} \\[\abovecaptionskip]
-		\small (c) $\varepsilon_0$ = 1
-		\label{fig:eg_e1_avg_tpt}
-	\end{tabular}
-	\caption{Average throughput and standard deviation experienced per WN in the last 5,000 iterations of a single $\varepsilon$-greedy 10,000-iterations simulation run for different $\varepsilon_0$ values.
-The proportional fair result is also shown (red dashed line).}
-	\label{fig:eg_avg_tpt}
-\end{figure*}
-
-To sum up, we have seen that tuning $\varepsilon_0$ clearly entails a trade-off between the fairness and the temporal variation of throughput.
-Choosing a low $\varepsilon_0$ value grants low variability, but WNs are prone to fall into local maximums, as the experienced performance is just a consequence of the randomness in taking particular actions.
-This also generates a fairness problem, since the unlucky WNs end up experiencing lower performance, as well as they are not able to discover the best throughput actions.
-On the other side, choosing a high $\varepsilon_0$ value results in higher throughput and better long-term fairness but at the expense of intermittent good/poor performance.
-
-%------------------------
-% Study of MAB (EXP3)
-%------------------------
-\subsubsection{Performance of the EXP3 policy}
-\label{section:exp3_study}
-We now evaluate the trade-off between fairness and temporal throughput variability in the EXP3 policy, which includes the learning rate $\eta$, a parameter that controls how fast old beliefs are replaced by newer ones.
-In EXP3 we also find the $\gamma$ parameter, which regulates explicit exploration by tuning the importance of weights in the action-selection procedure.
-Setting $\gamma = 1$ results in completely neglecting weights (actions have the same probability to be chosen).
-On the other side, setting $\gamma = 0$, the effect of weights are  at its highest.
-Thus, in order to see clearly the effects of the EXP3 weights, which directly depend on $\eta$, we fix $\gamma$ to 0.
-
-As we did before for $\varepsilon$-greedy, we start analyzing the impact of modifying the input parameters of EXP3 on the average aggregate throughput (Figure \ref{fig:exp3_tuning_parameters}).
-We vary the initial learning rate, $\eta_0$, between 0 and 1 in 0.1 steps.
-As it can be observed, setting $\eta_0$ to 0 results in the lowest average throughput, and a low variability is obtained.
-In this case, action weights are never updated and the arms are randomly chosen with the same probability.
-As $\eta_0$ increases, the proportional fair solution is approximated at the expense of a higher variability between experiments, since less exploration is performed when $\eta_0$ increases.
-Note, as well, that the maximum average network throughput is reached for $\eta_0 = 0.6$ in this particular scenario.
-
-\begin{figure}[t!]
-	\centering											
-	\epsfig{file=images/exp3_tuning_parameters_zoom.eps, width=6.5cm}
-	\caption{Average aggregate throughput and standard deviation obtained for each $\eta_0$ value in MAB (EXP3).
-The aggregate throughput of the proportional fair solution is also shown (red dashed line).
-Results are from 100 simulations lasting 10,000 iterations each.}
-	\label{fig:exp3_tuning_parameters}
-\end{figure}
-
-Now, for a single 10,000-iteration simulation, we set $\eta_0 = \{0.1, 0.5, 1\}$ to closely study the implications of modifying the initial learning rate.
-Figure \ref{fig:exp3_actions_distr} compares the resulting actions probability for these low, medium and high $\eta_0$ values.
-% EXP3: action probabilities
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta01} \\[\abovecaptionskip]
-		\small (a) $\eta_0 = 0.1$
-		\label{fig:exp3_eta01_actions_distr}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta05} \\[\abovecaptionskip]
-		\small (b) $\eta_0 = 0.5$
-		\label{fig:exp3_eta05_actions_distr}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta1} \\[\abovecaptionskip]
-		\small (c) $\eta_0 = 1$
-		\label{fig:exp3_eta1_actions_distr}
-	\end{tabular}
-	\caption{Probability of taking a given action in EXP3 for different $\eta_0$ values after a simulation of 10,000 iterations.}
-	\label{fig:exp3_actions_distr}
-\end{figure*}
-
-We see that actions are tried with similar probability for $\eta_0 = 0.1$, since the usage of a low learning rate entails a high similarity between weights.
-This situation is significantly improved for $\eta_0 = 0.5$, in which few actions are selected most of the times.
-The increased learning rate allows to rapidly capture the effects of the others' actions, since more exploration is carried out.
-As a consequence, actions using the highest transmit power are clearly preferred to overcome the adversarial setting.
-Note, as well, that optimal channel allocation is learned by WNs despite competing with each other.
-Finally, for $\eta_0 = 1$, a single action is clearly preferred by each WN.
-However, unfair situations eventually occur due to the lack of exploration.
-In particular, we observe that $\text{WN}_1$ and $\text{WN}_3$, which share the same channel, use very different power levels in their favorite actions (5 and 15 dBm, respectively).
-This, of course, generates a fairness imbalance that favors $\text{WN}_3$, which enjoys a higher SINR.
-As mentioned, this behavior occurs eventually, since the variability in the output can be understood as a consequence of a fast convergence achieved during the transitory learning phase.
-So, results from different simulations will significantly vary.
-
-Figure \ref{fig:exp3_agg_tpt} shows the temporal aggregate throughput, which suffers from a higher variability when $\eta$ is lower.
-Regarding individual performance, the same behavior can be observed in the temporal throughput evolution (Figure \ref{fig:exp3_ind_tpt}).
-In this case, setting $\eta_0 = 1$ implies trusting best-performing actions for larger periods, i.e., higher weights are assigned even if actions are suboptimal.
-Therefore, as $\eta_0$ decreases, the temporal variability increases because the action-selection process becomes uniformly random.
-However, this variability does not entail that the proportional fair solution is approached.
-Thus, $\eta_0$ must be carefully set in order to provide a low temporal variability, at the same time that enough exploration is carried out for reaching the optimal fairness solution.
-
-% EXP3: aggregate throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta01} \\[\abovecaptionskip]
-		\small (a) $\eta_0 = 0.1$
-		\label{fig:exp3_eta01_agg_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta05} \\[\abovecaptionskip]
-		\small (b) $\eta_0 = 0.5$
-		\label{fig:exp3_eta05_agg_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta1} \\[\abovecaptionskip]
-		\small (c) $\eta_0 = 1$
-		\label{fig:exp3_eta1_agg_tpt}
-	\end{tabular}
-	\caption{Aggregate throughput evolution for a single EXP3 10000-iterations simulation and for different $\eta_0$ values. The proportional fair result is also shown (red dashed line).}
-	\label{fig:exp3_agg_tpt}
-\end{figure*}
-
-% EXP3: individual throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta01} \\[\abovecaptionskip]
-		\small (a) $\eta_0 = 0.1$
-		\label{fig:exp3_eta01_ind_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta05} \\[\abovecaptionskip]
-		\small (b) $\eta_0 = 0.5$
-		\label{fig:exp3_eta05_ind_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta1} \\[\abovecaptionskip]
-		\small (c) $\eta_0 = 1$
-		\label{fig:exp3_eta1_ind_tpt}
-	\end{tabular}
-	\caption{Individual throughput evolution for a single EXP3 10000-iterations simulation and for different $\eta_0$ values. The proportional fair result is also shown (red dashed line).}
-	\label{fig:exp3_ind_tpt}
-\end{figure*}
-
-One can notice a fairness imbalance by observing the individual throughput for $\eta_0 = 1$ in Figure \ref{fig:exp3_ind_tpt}, which is further illustrated in Figure \ref{fig:exp3_avg_tpt} (again, we have considered the last 5,000 iterations to avoid capturing the transitory phase).
-The average throughput is more evenly distributed for $\eta_0 = 0.1$ and $\eta_0 = 0.5$, but at the expense of the experienced throughput variability seen above.
-The unfairness suffered for $\eta_0 = 0.1$ can be understood as a lack of exploration that prevents finding a fair resource distribution.
-Thus, we conclude that a similar trade-off experienced in $\varepsilon$-greedy appears in EXP3 with parameter $\eta_0$.
-The main difference is that, in this case, a random action-selection process is approximated as $\eta_0$ decreases.
-% EXP3: average throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta01} \\[\abovecaptionskip]
-		\small (a) $\eta_0 = 0.1$
-		\label{fig:exp3_eta01_avg_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta05} \\[\abovecaptionskip]
-		\small (b) $\eta_0 = 0.5$
-		\label{fig:exp3_eta05_avg_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta1} \\[\abovecaptionskip]
-		\small (c) $\eta_0 = 1$
-		\label{fig:exp3_eta1_avg_tpt}
-	\end{tabular}
-	\caption{Average throughput and standard deviation experienced per WN in the last 5,000 iterations of a single EXP3 10000-iterations simulation for different $\eta_0$ values.
-The proportional fair result is also shown (red dashed line).}
-	\label{fig:exp3_avg_tpt}
-\end{figure*}
-
-%------------------------
-% Study of MAB (UCB)
-%------------------------
-\subsubsection{Performance of the UCB policy}
-\label{section:ucb_study}		
-Unlike $\varepsilon$-greedy and EXP3, the basic form of UCB does not include any input parameter to regulate variables such as the learning rate or the exploration coefficient.
-On the contrary, the action-selection process relies in the generated rewards only.
-We will study in this section how the previously seen trade-off between fair throughput and variability results for this parameter-free policy.
-
-We start by showing the action probability distribution (shown in Figure \ref{fig:actions_probability_ucb}) derived from the UCB implementation.
-We observe that WNs clearly prefer playing the actions corresponding to proportional fairness (i.e., the actions with highest transmit power and that result in frequency reuse).
-
-\begin{figure}[h!]
-	\centering							
-	\epsfig{file=images/NEW_actions_probability_UCB.eps, width=6.5cm}
-	\caption{Probability of taking a given action in UCB for a simulation of 10,000 iterations.}
-	\label{fig:actions_probability_ucb}
-\end{figure}
-
-Now, we concentrate in the temporal aggregate throughput (shown in Figure \ref{fig:ucb_agg_tpt}).
-The results show a very high variability, which slowly decreases as the number of iterations increases.
-The same observations can be done in the individual throughput evolution (Figure \ref{fig:ucb_tpt_evolution}).
-As a result, UCB provides long-term fairness but at the expense of a high temporal variability caused by exploration.
-In Figure \ref{fig:ucb_avg_individual} we show the average throughput experienced by each WN, as well as the standard deviation indicating the suffered variability (only for the last 5,000 iterations).
-As seen before, one can observe really high fairness but considerable variability due to the temporal evolution of throughput.
-
-% UCB: aggregate and individual 
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_aggregate_tpt_UCB}
-		\caption{Aggregate}\label{fig:ucb_agg_tpt}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_individual_tpt_UCB}
-		\caption{Individual}\label{fig:ucb_tpt_evolution}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_mean_tpt_UCB}
-		\caption{Average}\label{fig:ucb_avg_individual}
-	\end{subfigure}
-	\caption{Performance achieved for a single UCB 10,000-iterations simulation.
-The proportional fair result is also shown (red dashed line).
-(a) Aggregate throughput evolution, (b) Individual throughput evolution, (c) Average individual throughput (the last 5,000 iterations are considered).}
-	\label{fig:ucb_tpt}
-\end{figure*}
-
-Compared to $\varepsilon$-greedy and EXP3, UCB shows a clearer preference for selecting the proportional fair solutions.
-However, the intermittent good/poor performance of the actions due to the adversarial setting still keeps the degree of exploration very high, resulting in high temporal variability.
-
-%------------------------
-% Study of MAB (TS)
-%------------------------
-\subsubsection{Performance of the Thompson sampling policy}
-\label{section:ts_study}
-Similarly to UCB, in the basic form of Thompson sampling we do not have any tunable parameter.
-As with the other policies, we use a single 10,000-iteration simulation to show in detail the WNs behavior when applying Thompson sampling.
-We first show the actions probability in Figure \ref{fig:actions_probability_ts}.
-Note the well-pronounced preference for the proportional fair actions, which indicates fast convergence and little exploratory operations.
-
-% TS: actions probability
-\begin{figure}[t!]
-	\centering							
-	\epsfig{file=images/NEW_actions_probability_TS.eps, width=6.5cm}
-	\caption{Probability of taking a given action in Thompson sampling for a simulation of 10,000 iterations.}
-	\label{fig:actions_probability_ts}
-\end{figure}
-
-The temporal aggregate throughput is shown in Figure \ref{fig:ts_tpt_evolution}.
-As it can be observed, Thompson sampling achieves a lower variability in the temporal throughput with respect to UCB.
-The same observations can be done in the individual throughput evolution (Figure \ref{fig:ts_ind_tpt}).
-The low temporal variability observed on applying Thompson sampling is highlighted in Figure \ref{fig:ts_avg_individual}, which shows that the average experienced throughput enjoys a low standard deviation.
-Moreover, high fairness among WNs can be observed.
-
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_aggregate_tpt_TS}
-		\caption{Aggregate}\label{fig:ts_agg_tpt}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_individual_tpt_TS}
-		\caption{Individual}\label{fig:ts_ind_tpt}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_mean_tpt_TS}
-		\caption{Average}\label{fig:ts_avg_individual}
-	\end{subfigure}
-		\caption{Throughput evolution for a single Thompson sampling 10,000-iterations simulation.
-The proportional fair result is also shown (red dashed line).
-(a) Aggregate throughput evolution, (b) Individual throughput evolution, (c) Average individual throughput (the last 5,000 iterations are considered).}
-		\label{fig:ts_tpt_evolution}
-\end{figure*}
-
-These results show that even though the rewards encourage selfish behavior, the adversarial setting makes Thompson sampling to converge to collaborative actions while keeping the degree of exploration low.
-Again, this property holds for scenarios where no asymmetries can be found.
-While the excellent performance we observe echoes other published results that show the superiority of Thompson sampling in various settings \cite{LCLS10}, we highlight that this outstanding empirical performance is actually rather unexpected in our \emph{non-stochastic} setting.
-Indeed, existing theoretical results only explain the excellent performance of Thompson sampling in \emph{stochastic} bandit problems.
-On the other hand, the randomization employed by Thompson sampling is at least superficially related to techniques used in game-theoretic online learning \cite{FS97,CBLu06:book}, with the connection made clear only in a special case \cite{Gop13}.
-The behavior observed in our experiments may indicate a more profound relationship with such game-theoretic algorithms.
-We leave the investigation of this matter as an exciting direction for future work.
-
-%------------------------
-% Random Scenarios - Scalability
-%------------------------
-\subsection{Random Scenarios}
-\label{section:random}
-After studying the WNs interactions in the grid scenario, we now evaluate whether the previous conclusions generalize to random scenarios with an arbitrary number of WNs.
-To this aim, we use the same $10\times5\times 10$ m scenario and randomly allocate $N = \{2, 4, 6, 8\}$ WNs.
-%Different topologies are captured by placing WNs randomly.
-With that, we are able to study how the presented policies maintain fairness for different densities and topologies.
-
-We set $\varepsilon_0 = 1$ in $\varepsilon$-greedy, which is the value that granted the highest aggregate throughput in the experiment shown in Figure \ref{fig:egreedy_tuning_parameters}.
-We do the same for EXP3 and choose $\eta_0 = 0.6$, which grants the highest aggregate throughput in average (refer to Figure \ref{fig:exp3_tuning_parameters}).
-In Figure \ref{fig:hist_mean_tpt} we show, for each number of networks and action-selection strategy, an histogram of the mean throughput experienced by each WN during the last 5,000 iterations, and for each of the 100 repetitions.
-% Histogram mean throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_2_WNs} \\[\abovecaptionskip]
-		\small (a) N = 2 WNs
-		\label{fig:hist_mean_throughput_2}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_4_WNs} \\[\abovecaptionskip]
-		\small (b) N = 4 WNs
-		\label{fig:hist_mean_throughput_4}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_6_WNs} \\[\abovecaptionskip]
-		\small (c) N = 6 WNs
-		\label{fig:hist_mean_throughput_6}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_8_WNs} \\[\abovecaptionskip]
-		\small (c) N = 8 WNs
-		\label{fig:hist_imean_throughput_8}
-	\end{tabular}
-	\caption{Histogram of the average throughput experienced by each WN during the last 5,000 iterations. Results from 100 repetitions are considered.}
-	\label{fig:hist_mean_tpt}
-\end{figure*}
-
-As we can observe, histograms of UCB and Thompson sampling are slightly narrower in almost all the cases, which indicates a higher fairness experienced by the WNs with respect to the other policies.
-Note, as well, that for the $N = 2$, results are similar for all the policies because finding a good-performing configuration in low-density environments is more likely to occur.
-Thus, fewer exploration is required than for higher densities.
-Note, as well, that the abovementioned collaborative behavior is still present in random scenarios.
-In accordance to that, WNs acting selfishly are prone to find a configuration whereby SR is improved in a fair manner.
-We find the main cause of this issue to be the inter-WN interference sensed at a given transmitter-receiver pair, which is very likely to be similar in both devices for the proposed scenarios.
-Such a property is given when STAs are close to their associated AP, thus allowing to palliate the effects of asymmetries.
-
-To conclude, we evaluate temporal variability in random scenarios.
-For that, Table \ref{tbl:std_individual_tpt_experienced} shows the average standard deviation of the throughput experienced by each WN during the last 5,000 iterations (again, we concentrate on the regime after the initial learning phase).
-We consider the average results from 100 repetitions.
-With this, we are able to evaluate, for each network density, the variability in the temporal throughput provided by each of the policies in random topologies.
-% Mean std of the individual throughput	
-\begin{table}[h!]
-	\centering
-	%\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{|c|c|c|c|c|}
-			\hline
-			\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}Number of \\ WNs\end{tabular}}} & \multicolumn{4}{c|}{\textbf{$\overline{\sigma}(\Gamma_{i \in N})$ (Mbps)}} \\ \cline{2-5} 
-			& \textbf{$\varepsilon$-greedy} & \textbf{EXP3} & \textbf{UCB} & \textbf{Thompson s.} \\ \hline
-			\textbf{2} & 12.1314 & 31.2897 & 31.9422 & 12.2079 \\ \hline
-			\textbf{4} & 83.7318 & 95.4976 & 73.9136 & 50.6985 \\ \hline
-			\textbf{6} & 120.8570 & 81.3259 & 67.6045 & 62.8171 \\ \hline
-			\textbf{8} & 130.0322 & 73.5171 & 63.2272 & 68.8547 \\ \hline
-	\end{tabular}%}
-	\caption{Mean standard deviation of the throughput experienced $\Gamma_{i \in N}$ by each $WN_i$ during the last 5,000 iterations. 100 repetitions are considered for averaging purposes.}
-	\label{tbl:std_individual_tpt_experienced}
-\end{table}
-
-As previously seen in the toy grid scenario introduced in Section \ref{section:toy_grid_scenario}, both UCB and Thompson sampling provide the best results in terms of temporal throughput variability.
-Despite $\varepsilon$-greedy provides very good results for $N=2$, it does not properly scale up with the number of WNs.
-
-%%%%%%%%%%%%%%%
-%  VI. CONCLUSIONS  %
-%%%%%%%%%%%%%%%
-\section{Conclusions }
-\label{section:conclusions}
-In this paper, we provided a tutorial-like implementation of MABs to address the decentralized SR problem in dense WNs.
-Unlike previous literature, we have focused on a situation in which few resources are available, thus bringing out the competition issues raised from the adversarial setting.
-Our results show that decentralized learning allows improving SR in dense WN, so that collaborative results in symmetric scenarios, sometimes close to optimal proportional fairness, can be achieved.
-This result is achieved even though WNs act selfishly, aiming to maximize their own throughput.
-In addition, this behavior is observed for random scenarios, where the effects of asymmetries cannot be controlled.
-%However, using only local information in limited resources scenarios conducts to an adversarial setting in which a pure strategy does not exist, which prevents reaching a Nash Equilibrium.
-In the WNs case, applying decentralized learning in such an adversarial setting entails noticing a high temporal variability in the experienced throughput.
-These collaborative actions are, at times, accompanied by high temporal throughput variability, which can be understood as a consequence of the  rate at which networks change their configuration in response of the opponents behavior.
-A high temporal variability may provoke negative issues in a node's performance, as its effects may be propagated to higher layers of the protocol stack.
-For instance, a high throughput fluctuation may entail behavioral anomalies in protocols such as Transmission Control Protocol (TCP).
-%In this case, the temporal fluctuation of the throughput would directly affect the Contention Window (CW) used in TCP for congestion control, providing a poor performance.
-We have studied this trade-off between fair resource allocation and high temporal throughput variability in $\varepsilon$-greedy, EXP3, UCB and Thompson sampling action-selection strategies.
-Our results show that while this trade-off is hard to regulate via the learning parameters in $\varepsilon$-greedy and EXP3, UCB  and, especially, Thompson sampling are able to achieve fairness at a reduced temporal variability.
-We identify the root cause of this phenomena to the fact that both UCB and Thompson sampling consider the probability distribution of the rewards, and not only their magnitude.
-
-We left as future work to further study the MABs application to WNs through distributed (with message passing) and centralized (with complete information) approaches with shared reward.
-Furthermore, we would like to extend this work to enhance both throughput and stability by inferring the actions of the opponents and acting in consequence.
-Defining the resource allocation problem as an adversarial game is one possibility to do so.
-Finally, we intend to particularize to IEEE 802.11 WLANs to study the effects of applying RL when using a medium access protocol such as CSMA.
-In fact, this would let us consider dynamic Carrier Sense Threshold (CST) to further enable SR.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%  ACKNOWLEDGEMENT  		  %%%
-%%%%%%%%%%%%%%%%%%%%%%%%%
-% use section* for acknowledgment
-% The Computer Society usually uses the plural form
-\section*{Acknowledgments}
-This work has been partially supported by the Spanish Ministry of Economy and Competitiveness under the Maria de Maeztu Units of Excellence Programme (MDM-2015-0502), by the European Regional Development Fund under grant TEC2015-71303-R (MINECO/FEDER), and by a Gift from CISCO University Research Program (CG\#890107) \& Silicon Valley Community Foundation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%  BIBLIOGRAPHY    
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\bibliographystyle{unsrt}
-\bibliography{references}
+\section{Results - Random Scenario}
+In order to reduce the simulation time, we have considered 1,000 learning iterations, rather than 100,000.
 

### 2018-10-09 Code/constants.m

@@ -14,9 +14,9 @@ ind_tpt_optimal_prop_fairness = 222.7678;    % Mbps
 optimal_max_min = 222.7678;
 
 nWlans = 4;                         % Number of WLANs in the map
-totalIterations = 10000;            % Maximum convergence time (one period implies the participation of all WLANs)
-minimumIterationToConsider = 5000;  % Iteration from which to consider the obtained results
-totalRepetitions = 1;               % Number of TOTAL repetitions to take the average
+totalIterations = 1000;            % Maximum convergence time (one period implies the participation of all WLANs)
+minimumIterationToConsider = 500;  % Iteration from which to consider the obtained results
+totalScenarios = 100;               % Number of TOTAL repetitions to take the average
 
 % Define the transitory and the permanent intervals of iterations
 transitoryInterval = 1 : minimumIterationToConsider;

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Experiment_1_0_EG_find_best_epsilon.m

@@ -1,147 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-%%% EXPERIMENT EXPLANATION:
-%%% By using a simple grid of 4 WLANs sharing 2 channels, we want to test 
-%%% several values of the initial exploration coefficient (epsilon) to 
-%%% evaluate the performance of e-greedy for each of them. We compare the 
-%%% obtained results with the optimal configurations in terms of proportional 
-%%% fairness.
-
-%%% This Script generates the output shown in the article:
-%%% - Section 5.1.2 Performance of the e-greedy policy
-%%% - Figure 2
-
-clc
-clear all
-
-% Add paths to methods folders
-addpath(genpath('framework_throughput_calculation/power_management_methods/'));
-addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
-addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
-addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
-addpath(genpath('reinforcement_learning_methods/'));
-addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
-
-disp('-----------------------')
-disp('e-greedy: finding the best parameters')
-disp('-----------------------')
-
-% Generate constants from 'constants.m'
-constants
-
-totalRepetitions = 100;
-
-initialEpsilon = 0:.1:1;
-
-policy = EG_POLICY;
-  
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Experiment_1_1_egreedy.m

@@ -1,0 +1,58 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of TS. We display i) the actions probabilities, 
+%%% ii) the temporal aggregate throughput, iii) the temporal individual 
+%%% throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.5 Performance of the Thompson sampling policy
+%%% - Figure 15
+%%% - Figure 16
+%%% - Figure 17
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('SIM 1_1: e-greedy')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+initialEpsilon = 1;
+policy = EG_POLICY;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, drawMap); % SAFE CONFIGURATION
+    
+% Compute the throughput experienced per WLAN at each iteration
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Experiment_1_1_individual_performance_EG_parameters_4_WN.m

@@ -1,61 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-%%% EXPERIMENT EXPLANATION:
-%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
-%%% individual performance of e-greedy for e_0 = 0.1. We display i) the
-%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
-%%% temporal individual throughput, iv) the average throughput.
-
-%%% This Script generates the output shown in the article:
-%%% - Section 5.1.2 Performance of the e-greedy policy
-%%% - Figure 3
-%%% - Figure 4
-%%% - Figure 5
-%%% - Figure 6
-
-clc
-clear all
-
-% Add paths to methods folders
-addpath(genpath('framework_throughput_calculation/power_management_methods/'));
-addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
-addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
-addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
-addpath(genpath('reinforcement_learning_methods/'));
-addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
-
-disp('-----------------------')
-disp('e-greedy: Throughput Evolution')
-disp('-----------------------')
-
-% Generate constants from 'constants.m'
-constants
-
-initialEpsilon = .1;
-
-policy = EG_POLICY;
-
-% Setup the scenario: generate WLANs and initialize states and actions
-wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
-   
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Results/PLOT_RESULTS_SIM_1_2.m

@@ -1,153 +1,0 @@
-% FILE DESCRIPTION:
-% Script to plot the results of experiment 2.3 (Adversarial Issues in WLANs)
-% This script plots article's figures 11b and 11c 
-
-clc
-clear all
-
-disp('***********************************************************************')
-disp('*         Potential and Pitfalls of Multi-Armed Bandits for           *')
-disp('*               Decentralized Spatial Reuse in WLANs                  *')
-disp('*                                                                     *')
-disp('* Submission to Journal on Network and Computer Applications          *')
-disp('* Authors:                                                            *')
-disp('*   - Francesc Wilhelmi (francisco.wilhelmi@upf.edu)                  *')
-disp('*   - Sergio Barrachina-Muñoz  (sergio.barrachina@upf.edu)            *')
-disp('*   - Boris Bellalta (boris.bellalta@upf.edu)                         *')
-disp('*   - Cristina Cano (ccanobs@uoc.edu)                                 *')
-disp('*   - Anders Jonsson (anders.jonsson@upf.edu)                         *')
-disp('*   - Gergely Neu (gergely.neu@upf.edu)                               *')
-disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi         *')
-disp('* Repository:                                                         *')
-disp('*  https://github.com/fwilhelmi/potential_pitfalls_mabs_spatial_reuse *')
-disp('***********************************************************************')
-
-disp('----------------------------------------------')
-disp('PLOT RESULTS OF EXPERIMENT 1')
-disp('----------------------------------------------')
-
-constants
-
-% Set font type
-set(0,'defaultUicontrolFontName','Times New Roman');
-set(0,'defaultUitableFontName','Times New Roman');
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Tuning parameters/Experiment_1_1_0_0_EG_find_best_epsilon.m

@@ -1,0 +1,147 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we want to test 
+%%% several values of the initial exploration coefficient (epsilon) to 
+%%% evaluate the performance of e-greedy for each of them. We compare the 
+%%% obtained results with the optimal configurations in terms of proportional 
+%%% fairness.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.2 Performance of the e-greedy policy
+%%% - Figure 2
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('e-greedy: finding the best parameters')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+totalRepetitions = 100;
+
+initialEpsilon = 0:.1:1;
+
+policy = EG_POLICY;
+  
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Tuning parameters/Experiment_1_1_0_1_individual_performance_EG_parameters_4_WN.m

@@ -1,0 +1,61 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of e-greedy for e_0 = 0.1. We display i) the
+%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
+%%% temporal individual throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.2 Performance of the e-greedy policy
+%%% - Figure 3
+%%% - Figure 4
+%%% - Figure 5
+%%% - Figure 6
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('e-greedy: Throughput Evolution')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+initialEpsilon = .1;
+
+policy = EG_POLICY;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+   
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Tuning parameters/Experiment_1_1_0_3_individual_performance_EG_parameters_4_WN.m

@@ -1,0 +1,61 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of e-greedy for e_0 = 1. We display i) the
+%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
+%%% temporal individual throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.2 Performance of the e-greedy policy
+%%% - Figure 3
+%%% - Figure 4
+%%% - Figure 5
+%%% - Figure 6
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('e-greedy: Throughput Evolution')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+initialEpsilon = 1;
+
+policy = EG_POLICY;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+   
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Tuning parameters/PLOT_RESULTS_SIM_1_1_0_0.m

@@ -1,0 +1,97 @@
+% FILE DESCRIPTION:
+% Script to plot the results of experiment 2.3 (Adversarial Issues in WLANs)
+% This script plots article's figures 11b and 11c 
+
+clc
+clear all
+
+disp('***********************************************************************')
+disp('*         Potential and Pitfalls of Multi-Armed Bandits for           *')
+disp('*               Decentralized Spatial Reuse in WLANs                  *')
+disp('*                                                                     *')
+disp('* Submission to Journal on Network and Computer Applications          *')
+disp('* Authors:                                                            *')
+disp('*   - Francesc Wilhelmi (francisco.wilhelmi@upf.edu)                  *')
+disp('*   - Sergio Barrachina-Muñoz  (sergio.barrachina@upf.edu)            *')
+disp('*   - Boris Bellalta (boris.bellalta@upf.edu)                         *')
+disp('*   - Cristina Cano (ccanobs@uoc.edu)                                 *')
+disp('*   - Anders Jonsson (anders.jonsson@upf.edu)                         *')
+disp('*   - Gergely Neu (gergely.neu@upf.edu)                               *')
+disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi         *')
+disp('* Repository:                                                         *')
+disp('*  https://github.com/fwilhelmi/potential_pitfalls_mabs_spatial_reuse *')
+disp('***********************************************************************')
+
+disp('----------------------------------------------')
+disp('PLOT RESULTS OF EXPERIMENT 1.0')
+disp('----------------------------------------------')
+
+constants
+
+% Set font type
+set(0,'defaultUicontrolFontName','Times New Roman');
+set(0,'defaultUitableFontName','Times New Roman');
+set(0,'defaultAxesFontName','Times New Roman');
+set(0,'defaultTextFontName','Times New Roman');
+set(0,'defaultUipanelFontName','Times New Roman');
+
+% Load results from experiments in 2
+load('meanAggregateThroughputEgreedy.mat');
+load('meanThroughputExperiencedEgreedy.mat');
+
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.2. EXP3/EXP3_eta_06_WN.m

@@ -1,58 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-%%% EXPERIMENT EXPLANATION:
-%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
-%%% individual performance of EXP3 for eta_0 = 1. We display i) the
-%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
-%%% temporal individual throughput, iv) the average throughput.
-
-%%% This Script generates the output shown in the article:
-%%% - Section 5.1.3 Performance of the EXP3 policy
-%%% - Figure 8
-%%% - Figure 9
-%%% - Figure 10
-%%% - Figure 11
-
-clc
-clear all
-
-% Add paths to methods folders
-addpath(genpath('framework_throughput_calculation/power_management_methods/'));
-addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
-addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
-addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
-addpath(genpath('reinforcement_learning_methods/'));
-addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
-
-disp('-----------------------')
-disp('EXP3: Throughput Evolution')
-disp('-----------------------')
-
-constants
-
-% Define EXP3 parameters
-initialEta = 0.6;
-gamma = 0;
-
-% Setup the scenario: generate WLANs and initialize states and actions
-wlan = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
-    
-% Compute the throughput experienced per WLAN at each iteration
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.2. EXP3/Experiment_2_0_EXP3_find_best_eta_2_channels.m

@@ -1,128 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-%%% EXPERIMENT EXPLANATION:
-%%% By using a simple grid of 4 WLANs sharing 2 channels, we want to test 
-%%% several values of the initial learning rate (eta) to evaluate the
-%%% performance of e-greedy for each of them. We compare the obtained
-%%% results with the optimal configurations in terms of proportional fairness.
-
-%%% This Script generates the output shown in the article:
-%%% - Section 5.1.3 Performance of the EXP3 policy
-%%% - Figure 7
-
-clc
-clear all
-
-% Add paths to methods folders
-addpath(genpath('framework_throughput_calculation/power_management_methods/'));
-addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
-addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
-addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
-addpath(genpath('reinforcement_learning_methods/'));
-addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
-
-disp('-----------------------')
-disp('EXP3: finding the best parameters')
-disp('-----------------------')
-
-constants
-
-% Define EXP3 parameters
-initialEta = 0 : .1 : 1;
-gamma = 0;
-
-% Setup the scenario: generate WLANs and initialize states and actions
-wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
-
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.2. EXP3/Experiment_2_2_individual_performance_EXP3_parameters_4_WN.m

@@ -1,58 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-%%% EXPERIMENT EXPLANATION:
-%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
-%%% individual performance of EXP3 for eta_0 = 0.5. We display i) the
-%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
-%%% temporal individual throughput, iv) the average throughput.
-
-%%% This Script generates the output shown in the article:
-%%% - Section 5.1.3 Performance of the EXP3 policy
-%%% - Figure 8
-%%% - Figure 9
-%%% - Figure 10
-%%% - Figure 11
-
-clc
-clear all
-
-% Add paths to methods folders
-addpath(genpath('framework_throughput_calculation/power_management_methods/'));
-addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
-addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
-addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
-addpath(genpath('reinforcement_learning_methods/'));
-addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
-
-disp('-----------------------')
-disp('EXP3: Throughput Evolution')
-disp('-----------------------')
-
-constants
-
-% Define EXP3 parameters
-initialEta = 0.5;
-gamma = 0;
-
-% Setup the scenario: generate WLANs and initialize states and actions
-wlan = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
-    
-% Compute the throughput experienced per WLAN at each iteration
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.2. EXP3/Tuning parameters/Experiment_1_2_0_1_individual_performance_EXP3_parameters_4_WN.m

@@ -1,0 +1,58 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of EXP3 for eta_0 = 0.1. We display i) the
+%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
+%%% temporal individual throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.3 Performance of the EXP3 policy
+%%% - Figure 8
+%%% - Figure 9
+%%% - Figure 10
+%%% - Figure 11
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('EXP3: Throughput Evolution')
+disp('-----------------------')
+
+constants
+
+% Define EXP3 parameters
+initialEta = 0.1;
+gamma = 0;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlan = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+    
+% Compute the throughput experienced per WLAN at each iteration
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.2. EXP3/Tuning parameters/Experiment_1_2_0_2_individual_performance_EXP3_parameters_4_WN.m

@@ -1,0 +1,58 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of EXP3 for eta_0 = 0.5. We display i) the
+%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
+%%% temporal individual throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.3 Performance of the EXP3 policy
+%%% - Figure 8
+%%% - Figure 9
+%%% - Figure 10
+%%% - Figure 11
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('EXP3: Throughput Evolution')
+disp('-----------------------')
+
+constants
+
+% Define EXP3 parameters
+initialEta = 0.5;
+gamma = 0;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlan = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+    
+% Compute the throughput experienced per WLAN at each iteration
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.2. EXP3/Tuning parameters/Experiment_1_2_0_3_individual_performance_EXP3_parameters_4_WN.m

@@ -1,0 +1,58 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of EXP3 for eta_0 = 1. We display i) the
+%%% actions probabilities, ii) the temporal aggregate throughput, iii) the
+%%% temporal individual throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.3 Performance of the EXP3 policy
+%%% - Figure 8
+%%% - Figure 9
+%%% - Figure 10
+%%% - Figure 11
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('EXP3: Throughput Evolution')
+disp('-----------------------')
+
+constants
+
+% Define EXP3 parameters
+initialEta = 1;
+gamma = 0;
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlan = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+    
+% Compute the throughput experienced per WLAN at each iteration
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.3. UCB/Experiment_1_3_ucb.m

@@ -1,0 +1,56 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of UCB. We display i) the actions probabilities, 
+%%% ii) the temporal aggregate throughput, iii) the temporal individual 
+%%% throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.4 Performance of the UCB policy
+%%% - Figure 12
+%%% - Figure 13
+%%% - Figure 14
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('SIM_1_3: UCB')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+    
+policy = UCB_POLICY;
+% Compute the throughput experienced per WLAN at each iteration
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.4. Thompson sampling/Experiment_1_4_thompson_sampling.m

@@ -1,0 +1,56 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of TS. We display i) the actions probabilities, 
+%%% ii) the temporal aggregate throughput, iii) the temporal individual 
+%%% throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.5 Performance of the Thompson sampling policy
+%%% - Figure 15
+%%% - Figure 16
+%%% - Figure 17
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('SIM_1_4: Thompson Sampling')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, drawMap); % SAFE CONFIGURATION
+    
+policy = TS_POLICY;
+% Compute the throughput experienced per WLAN at each iteration
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.4. Thompson sampling/Experiment_1_individual_performance_TS_4_WN.m

@@ -1,54 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-%%% EXPERIMENT EXPLANATION:
-%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
-%%% individual performance of TS. We display i) the actions probabilities, 
-%%% ii) the temporal aggregate throughput, iii) the temporal individual 
-%%% throughput, iv) the average throughput.
-
-%%% This Script generates the output shown in the article:
-%%% - Section 5.1.5 Performance of the Thompson sampling policy
-%%% - Figure 15
-%%% - Figure 16
-%%% - Figure 17
-
-clc
-clear all
-
-% Add paths to methods folders
-addpath(genpath('framework_throughput_calculation/power_management_methods/'));
-addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
-addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
-addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
-addpath(genpath('reinforcement_learning_methods/'));
-addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
-
-disp('-----------------------')
-disp('Thompson Sampling: Throughput Evolution')
-disp('-----------------------')
-
-% Generate constants from 'constants.m'
-constants
-
-% Setup the scenario: generate WLANs and initialize states and actions
-wlans = generate_network_3D(nWlans, 'grid', 2, drawMap); % SAFE CONFIGURATION
-    
-policy = TS_POLICY;
-% Compute the throughput experienced per WLAN at each iteration
-[tpt_evolution_per_wlan_ts, times_arm_has_been_played_ts, regret_per_wlan_ts] = thompson_sampling(wlans);
-
[…]

### 2018-10-09 Code/experiments/Part 1 - Toy grid scenario/1.5. Other/1.7. Shared Thompson sampling/Experiment_1_7_individual_performance_proposed_solution_4_WN.m

@@ -1,0 +1,54 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of TS. We display i) the actions probabilities, 
+%%% ii) the temporal aggregate throughput, iii) the temporal individual 
+%%% throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.5 Performance of the Thompson sampling policy
+%%% - Figure 15
+%%% - Figure 16
+%%% - Figure 17
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('Thompson Sampling: Throughput Evolution')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
+constants
+
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, drawMap); % SAFE CONFIGURATION
+    
+policy = TS_POLICY;
+% Compute the throughput experienced per WLAN at each iteration
[…]

### 2018-10-09 Code/experiments/Part 2 - Random scenarios/2.1. Performance Comparison/Experiment_2_1_Performance_Comparison_Random_Network.m

@@ -1,0 +1,99 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% The script computes the performance of applying e-greedy, EXP3, UCB and
+%%% Thompson sampling in random scenarios. At the end, histograms of the 
+%%% average throughput experienced are displayed for each policy.
+
+%%% This Script generates the output shown in the article:
+%%% - Figure 18
+
+%%
+clc
+clear all
+
+disp('************************************************************************')
+disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
+disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
+disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
+disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
+disp('* GitHub repository:                                                   *')
+disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
+disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
+disp('************************************************************************')
+
+disp('-----------------------')
+disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
+disp('-----------------------')
+
+% Load constants
+%constants
+constants_more_actions
+% Update the nWlans variable to define an array
+nWlans = [2 4 6 8];
+
+% % Initialize variables to store results:
+% % - Each cell contains the throughput evolution experienced with each policy
[…]

### 2018-10-09 Code/experiments/Part 2 - Random scenarios/2.1. Performance Comparison/Experiment_2_2_Performance_Comparison_Random_Network.m

@@ -1,0 +1,95 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% The script computes the performance of applying e-greedy, EXP3, UCB and
+%%% Thompson sampling in random scenarios. At the end, histograms of the 
+%%% average throughput experienced are displayed for each policy.
+
+%%% This Script generates the output shown in the article:
+%%% - Figure 18
+
+%%
+clc
+clear all
+
+disp('************************************************************************')
+disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
+disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
+disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
+disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
+disp('* GitHub repository:                                                   *')
+disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
+disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
+disp('************************************************************************')
+
+disp('-----------------------')
+disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
+disp('-----------------------')
+
+% Load constants
+constants_more_actions
+
+% Update the nWlans variable to define an array
+nWlans = [2 4 6 8];
+
+% % Initialize variables to store results:
+% % - Each cell contains the throughput evolution experienced with each policy
[…]

### 2018-10-09 Code/experiments/Part 2 - Random scenarios/PLOT_RESULTS_PART_2.m

@@ -1,0 +1,398 @@
+% FILE DESCRIPTION:
+% Script to plot the results of Part 1 (Toy grid scenario)
+% This script plots article's figures ... (Section 5.1)
+
+clc
+clear all
+
+disp('***********************************************************************')
+disp('*         Potential and Pitfalls of Multi-Armed Bandits for           *')
+disp('*               Decentralized Spatial Reuse in WLANs                  *')
+disp('*                                                                     *')
+disp('* Submission to Journal on Network and Computer Applications          *')
+disp('* Authors:                                                            *')
+disp('*   - Francesc Wilhelmi (francisco.wilhelmi@upf.edu)                  *')
+disp('*   - Sergio Barrachina-Muñoz  (sergio.barrachina@upf.edu)            *')
+disp('*   - Boris Bellalta (boris.bellalta@upf.edu)                         *')
+disp('*   - Cristina Cano (ccanobs@uoc.edu)                                 *')
+disp('*   - Anders Jonsson (anders.jonsson@upf.edu)                         *')
+disp('*   - Gergely Neu (gergely.neu@upf.edu)                               *')
+disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi         *')
+disp('* Repository:                                                         *')
+disp('*  https://github.com/fwilhelmi/potential_pitfalls_mabs_spatial_reuse *')
+disp('***********************************************************************')
+
+disp('----------------------------------------------')
+disp('PLOT RESULTS OF PART 2: RANDOM SCENARIO (default vs sync. algs.)')
+disp('----------------------------------------------')
+
+constants
+
+ % Load constatns
+load('constants.mat')
+
+% Set font type
+set(0,'defaultUicontrolFontName','Times New Roman');
+set(0,'defaultUitableFontName','Times New Roman');
[…]

### 2018-10-09 Code/framework_throughput_calculation/auxiliary_methods/display_results_individual_performance.m

@@ -155,7 +155,6 @@ function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan
     %% Average tpt experienced per WLAN
     mean_tpt_per_wlan = mean(tptEvolutionPerWlan(minimumIterationToConsider:totalIterations,:),1);
     std_per_wlan = std(tptEvolutionPerWlan(minimumIterationToConsider:totalIterations,:),1);
-    figure
     figure('pos',[450 400 500 350])
     axes;
     axis([1 20 30 70]);
@@ -223,6 +222,5 @@ function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan
     fig_name = ['histogram_individual_throughput_' method_name];
     savefig(['./Output/' fig_name '.fig'])
     saveas(gcf,['./Output/' fig_name],'epsc')
-
     
 end

### 2018-10-09 Code/framework_throughput_calculation/auxiliary_methods/display_results_scalability.m

@@ -42,7 +42,7 @@ function [] = display_results_scalability( wlansSizes, throughputEvolutionPerWla
     % For each size of wlans, process data to be plotted
     for s = 1 : size(wlansSizes, 2)
         
-        for r = 1 : totalRepetitions
+        for r = 1 : totalScenarios
 
             %meanAggTptSingleSimulationRandom(r) = mean(sum(throughputEvolutionPerWlanRandom{s, r}(permanentInterval, :)'));
             meanAggTptSingleSimulationEgreedy(r) = mean(sum(throughputEvolutionPerWlanEgreedy{s, r}(permanentInterval, :)'));
@@ -58,7 +58,7 @@ function [] = display_results_scalability( wlansSizes, throughputEvolutionPerWla
 
         end
         
-        %meanAggTptTotalRepetitionsRandom(s) = mean(meanAggTptSingleSimulationRandom);
+        %meanAggTpttotalScenariosRandom(s) = mean(meanAggTptSingleSimulationRandom);
         meanAggTptTotalRepetitionsEgreedy(s) = mean(meanAggTptSingleSimulationEgreedy);
         meanAggTptTotalRepetitionsExp3(s) = mean(meanAggTptSingleSimulationExp3);
         meanAggTptTotalRepetitionsUcb(s) = mean(meanAggTptSingleSimulationUcb);
@@ -116,7 +116,7 @@ function [] = display_results_scalability( wlansSizes, throughputEvolutionPerWla
     
     for s = 1 : size(wlansSizes, 2)
         
-        for r = 1 : totalRepetitions
+        for r = 1 : totalScenarios
             % Random
             %meanThroughputPerWlanRandomConcat{s}(r, :) = ...
             %    mean(throughputEvolutionPerWlanRandom{s, r}(permanentInterval, :));
@@ -224,7 +224,7 @@ function [] = display_results_scalability( wlansSizes, throughputEvolutionPerWla
         std_temporal_tpt_ucb = [];
         std_temporal_tpt_ts = [];
 
-        for r = 1 : totalRepetitions
+        for r = 1 : totalScenarios
 
             %std_temporal_tpt_random = [std_temporal_tpt_random; std(throughputEvolutionPerWlanRandom{s, r})];
             std_temporal_tpt_eg = [std_temporal_tpt_eg; std(throughputEvolutionPerWlanEgreedy{s, r})];

### 2018-10-09 Code/reinforcement_learning_methods/alternative_thompson_sampling.m

@@ -1,0 +1,196 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
+	alternative_thompson_sampling( wlans, varargin )
+% thompson_sampling applies TS to maximize the experienced
+% throughput of a given scenario
+%
+%   OUTPUT: 
+%       * tptExperiencedByWlan - throughput experienced by each WLAN
+%         for each of the iterations done
+%       * timesArmHasBeenPlayed - times each action has been played
+%   INPUT: 
+%       * wlan - wlan object containing information about all the WLANs
+
+    constants
+    
+    try
+        if size(varargin, 2) == 3
+            % Update possible actions
+            nChannels = varargin{1};
+            channelActions = 1 : nChannels;
+            ccaActions = varargin{2};
+            txPowerActions = varargin{3};
+            % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
+            possibleActions = 1:(size(channelActions, 2) * ...
+                size(ccaActions, 2) * size(txPowerActions, 2));
+            K = size(possibleActions,2);   % Total number of actions
+            allCombs = allcomb(1:K, 1:K);    
+        end 
+    catch
+        if size(varargin, 2) ~= 3
+            disp('Wrong number of input arguments')
+        end
+    end
+    
+    %% INITIALIZE ALGORITHM
+    % Use a copy of wlan to make operations
+    wlansAux = wlans;
+    nWlans = size(wlansAux, 2);
+    
[…]

### 2018-10-09 Code/reinforcement_learning_methods/exp3.m

@@ -69,7 +69,7 @@ function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan
     previousAction = selectedArm;               % Initialize the previous action as the initial one
     timesArmHasBeenPlayed = zeros(nWlans, K);   % Initialize the number each arm has been played
     transitionsCounter = zeros(nWlans, K^2);    % Initialize the transitions counter   
-    armsProbabilities = zeros(nWlans, K);    % Initialize arms probabilities
+    armsProbabilities = (1/K)*ones(nWlans, K);       % Initialize arms probabilities
     estimated_reward = zeros(1, nWlans);        % Initialize the estimated reward for each WN
     % Initialize the regret experienced by each WLAN
     regretAfterAction = zeros(1, nWlans);
@@ -79,9 +79,7 @@ function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan
     previousEta = eta;
        
     %% ITERATE UNTIL CONVERGENCE OR MAXIMUM CONVERGENCE TIME           
-  
-    iteration = 1;
-    
+    iteration = 1;    
     while(iteration < totalIterations + 1) 
 
         % Assign turns to WLANs randomly 
@@ -89,66 +87,62 @@ function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan
                 
         for i = 1 : nWlans % Iterate sequentially for each agent in the random order   
      
-            armsProbabilities(order(i), :) = (1 - gamma) * (weightsPerArm(order(i), :) ./ ...
-                sum(weightsPerArm(order(i), :))) + gamma / K;
+            wlan_ix = order(i);
             
-            % To avoid errors in execution time
+            % Update arms probabilities according to weights      
             for k = 1 : K
-                if isnan(armsProbabilities(order(i), k))
-                    armsProbabilities(order(i), k) = 0;
+                armsProbabilities(wlan_ix, k) = (1 - gamma) * ...
+                    (weightsPerArm(wlan_ix, k) / ...
+                    sum(weightsPerArm(wlan_ix, :))) + (gamma / K);                
+                % To avoid errors in execution time
+                if isnan(armsProbabilities(wlan_ix, k))
+                    armsProbabilities(wlan_ix, k) = 1/K;
                 end
-            end            
-            if sum(armsProbabilities(order(i), :) == 0) == K
-                armsProbabilities(order(i), :) = ones(1, K)/K;
-            end
+            end             
[…]

### 2018-10-09 Code/reinforcement_learning_methods/ordered_exp3.m

@@ -1,0 +1,209 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan] = ...
+    ordered_exp3(wlans, gamma, initialEta, varargin)
+% exp3 applies EXP3 (basic formulation) to maximize the experienced
+% throughput of a given scenario
+%
+%   OUTPUT: 
+%       * tptExperiencedByWlan - throughput experienced by each WLAN
+%         for each of the iterations done
+%       * timesArmHasBeenPlayed - times each action has been played
+%   INPUT: 
+%       * wlan - wlan object containing information about all the WLANs
+%       * gamma - weigths regulator EXP3
+%       * eta - learning rate EXP3
+
+    constants
+    
+    try
+        if size(varargin, 2) == 3
+            % Update possible actions
+            nChannels = varargin{1};
+            channelActions = 1 : nChannels;
+            ccaActions = varargin{2};
+            txPowerActions = varargin{3};
+            % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
+            possibleActions = 1:(size(channelActions, 2) * ...
+                size(ccaActions, 2) * size(txPowerActions, 2));
+            K = size(possibleActions,2);   % Total number of actions
+            allCombs = allcomb(1:K, 1:K);    
+        end   
+    catch
+        if size(varargin, 2) ~= 3
+            disp('Wrong number of input arguments')
+        end
+    end
+    
+    %% INITIALIZE ALGORITHM
+    % Use a copy of wlan to make operations
+    wlansAux = wlans;
[…]

### 2018-10-09 Code/reinforcement_learning_methods/shared_thompson_sampling.m

@@ -1,0 +1,190 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
+    shared_thompson_sampling( wlans, varargin )
+% thompson_sampling applies TS to maximize the experienced
+% throughput of a given scenario
+%
+%   OUTPUT: 
+%       * tptExperiencedByWlan - throughput experienced by each WLAN
+%         for each of the iterations done
+%       * timesArmHasBeenPlayed - times each action has been played
+%   INPUT: 
+%       * wlan - wlan object containing information about all the WLANs
+
+    constants
+    
+    try
+        if size(varargin, 2) == 3
+            % Update possible actions
+            nChannels = varargin{1};
+            channelActions = 1 : nChannels;
+            ccaActions = varargin{2};
+            txPowerActions = varargin{3};
+            % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
+            possibleActions = 1:(size(channelActions, 2) * ...
+                size(ccaActions, 2) * size(txPowerActions, 2));
+            K = size(possibleActions,2);   % Total number of actions
+            allCombs = allcomb(1:K, 1:K);    
+        end 
+    catch
+        if size(varargin, 2) ~= 3
+            disp('Wrong number of input arguments')
+        end
+    end
+    
+    %% INITIALIZE ALGORITHM
+    % Use a copy of wlan to make operations
+    wlansAux = wlans;
+    nWlans = size(wlansAux, 2);
+    
[…]

### 2018-10-11 Ordered Learning/ordered_learning.tex
Simulations 11th, October

@@
 \section{Introduction}
+In order to decrease the temporal variability experienced by WNs applying online learning, we propose the following mechanism:
+\begin{itemize}
+	\item WNs are synchronized, so that they act at specific intervals.
+	\item In each iteration, only one WN is able to select an action. Of course, it can select the one that is currently using (exploitation).
+	\item Every WN that remains "static" in a given iteration is considered to choose the last selected action.
+\end{itemize}
+
+Two important implications are derived from the abovementioned mechanism: \emph{i)} the action-selection strategy of the learning algorithms are modified, \emph{ii)} the adversarial setting changes, so that the performance of every chosen action is potentially evaluated in a larger set of situations.
+According to the latter, a higher level of valuable knowledge is more likely to be provided to each arm.
+However, depending on the learning algorithm used, there can be other implications.
 
@@
 
+Figure \ref{fig:e_greedy} shows several results regarding the application of $\varepsilon$-greedy in the toy scenario (1,000 iterations are considered), both for the fully decentralized and the synchronized approaches.
+As shown, the latter allows to experience a lower temporal throughput variability (\ref{fig:temporal_individual_tpt_EG} vs \ref{fig:temporal_individual_tpt_OEG}), since a lower number of actions is being exploited (\ref{fig:actions_probability_EG} vs \ref{fig:actions_probability_OEG}).
+However, similar results are obtained with respect to the average throughput experienced per WN (\ref{fig:mean_tpt_EG} vs \ref{fig:mean_tpt_OEG}).
+The fact is that, for the synchronized approach, WNs tend to exploit sub-optimal actions for longer periods (while they wait for their turn).
+In contrast, WNs are able to rapidly discard these sub-optimal actions in their turn.
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_EG}
+		\caption{Actions prob. (default)}\label{fig:actions_probability_EG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_OEG}
+		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OEG}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_EG}
+		\caption{Temp. variability  (default)}\label{fig:temporal_individual_tpt_EG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OEG}
+		\caption{Temp. variability  (sync.)}\label{fig:temporal_individual_tpt_OEG}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_EG}
+		\caption{Mean tpt. (default)}\label{fig:mean_tpt_EG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_OEG}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OEG}
+	\end{subfigure}
+	\caption{Simulation results in $\varepsilon$-greedy (1,000 iterations)}
+	\label{fig:e_greedy}
+\end{figure*}
+
 \subsection{EXP3}
 \label{section:exp3}
+
+Figure \ref{fig:exp3} shows several results regarding the application of EXP3 in the toy scenario (1,000 iterations are considered), both for the fully decentralized and the synchronized approaches.
+Again, the synchronized version of EXP3 leads to a lower temporal variability (\ref{fig:temporal_individual_tpt_EXP3} vs \ref{fig:temporal_individual_tpt_OEXP3}).
+No significant conclusions can be drawn for the actions probability profile (\ref{fig:actions_probability_EXP3} vs \ref{fig:actions_probability_OEXP3}), since in EXP3 it appears to be slightly random (recall that different EXP3 simulations may lead to different results).
+Finally, regarding the average throughput experienced per WN, similar "pseudo-randomized" results are obtained (\ref{fig:mean_tpt_EXP3} vs \ref{fig:mean_tpt_OEXP3}).
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_EXP3}
+		\caption{Actions prob. (default)}\label{fig:actions_probability_EXP3}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_OEXP3}
+		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OEXP3}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_EXP3}
+		\caption{Temp. variability  (default)}\label{fig:temporal_individual_tpt_EXP3}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OEXP3}
+		\caption{Temp. variability  (sync.)}\label{fig:temporal_individual_tpt_OEXP3}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_EXP3}
+		\caption{Mean tpt. (default)}\label{fig:mean_tpt_EXP3}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_OEXP3}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OEXP3}
+	\end{subfigure}
+	\caption{Simulation results in EXP3 (1,000 iterations)}
+	\label{fig:exp3}
+\end{figure*}
 
@@
 
+Figure \ref{fig:ucb} shows several results regarding the application of UCB in the toy scenario (1,000 iterations are considered), both for the fully decentralized and the synchronized approaches.
+Unlike the previous cases, applying the synchronized approach to UCB is counter-productive, since its operational mode is altered by forcing WNs to choose undesired actions.
+As a result, the action-selection strategy is somehow randomized.
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_UCB}
+		\caption{Actions prob. (default)}\label{fig:actions_probability_UCB}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_OUCB}
+		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OUCB}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_UCB}
+		\caption{Temp. variability  (default)}\label{fig:temporal_individual_tpt_UCB}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OUCB}
+		\caption{Temp. variability  (sync.)}\label{fig:temporal_individual_tpt_OUCB}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_UCB}
+		\caption{Mean tpt. (default)}\label{fig:mean_tpt_UCB}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_OUCB}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OUCB}
+	\end{subfigure}
+	\caption{Simulation results in UCB (1,000 iterations)}
+	\label{fig:ucb}
+\end{figure*}
+
 \subsection{Thompson sampling}
 \label{section:ts}
+
+Figure \ref{fig:ts} shows several results regarding the application of Thompson sampling in the toy scenario (1,000 iterations are considered), both for the fully decentralized and the synchronized approaches.
+In this case, the temporal variability is significantly decreased (\ref{fig:temporal_individual_tpt_TS} vs \ref{fig:temporal_individual_tpt_OTS}).
+In contrast, the actions probability changes for the synchronized approach.
+In this case, some WNs (2 and 3) alternate two between actions.
+As it can be inferred from the temporal variability, one of the actions (the one granting lower performance) is selected until iteration 600 (approximately).
+At that moment, the best performing action (with respect to the adversarial environment) is chosen.
+This phenomena allegedly occurs when near-to-optimal actions are forced to be selected several times during the "static" periods.
+As a result, the algorithm provides high estimates to that actions, which are hard to be overtaken by the actual best-performing ones.
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_TS}
+		\caption{Actions prob. (default)}\label{fig:actions_probability_TS}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_OTS}
+		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OTS}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_TS}
+		\caption{Temp. variability  (default)}\label{fig:temporal_individual_tpt_TS}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OTS}
+		\caption{Temp. variability  (sync.)}\label{fig:temporal_individual_tpt_OTS}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_TS}
+		\caption{Mean tpt. (default)}\label{fig:mean_tpt_TS}
+	\end{subfigure}
+	\begin{subfigure}[b]{.33\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_OTS}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OTS}
+	\end{subfigure}
+	\caption{Simulation results in Thompson sampling (1,000 iterations)}
+	\label{fig:ts}
+\end{figure*}
 
@@
 
+First, we aim to show the effect of considering a higher number of actions, thus framing more realistic settings.
+For that, we have considered to use 3 orthogonal channels (as for the 2.4 GHz band), and 4 levels of power, which now range from -15 to 30 dBm (as defined in the IEEE 802.11 standard).
+As shown in Figure \ref{fig:scalability_more_actions}, using the new set of actions leads, in general, to much better and concentrated results for low densities (\ref{fig:hist_mean_tpt_2_WNs_actions}).
+However, as the number of WNs increases, the performance achieved by the new set of actions is worst than the achieved by the old set.
+Recall that the old set of actions considers that the number of orthogonal channels increases according to density (i.e., $n_{channels} = \frac{n_{WNs}}{2}$).
+Finally, it is interesting to observe the case where we have 4 WNs (\ref{fig:hist_mean_tpt_4_WNs_actions}).
+In this case, there are two clearly separated sets of throughputs when using the new set of actions, which is more evident for UCB and Thompson sampling.
+The fact is that there are 3 orthogonal channels and 4 WNs.
+Therefore, with a proper channel allocation, two WNs will enjoy full channel access, while the other two will compete for the remaining one.
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/hist_mean_tpt_2_WNs_actions}
+		\caption{2 WNs}\label{fig:hist_mean_tpt_2_WNs_actions}
+	\end{subfigure}
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/hist_mean_tpt_4_WNs_actions}
+		\caption{4 WNs}\label{fig:hist_mean_tpt_4_WNs_actions}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/hist_mean_tpt_6_WNs_actions}
+		\caption{6 WNs}\label{fig:hist_mean_tpt_6_WNs_actions}
+	\end{subfigure}
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/hist_mean_tpt_8_WNs_actions}
+		\caption{8 WNs}\label{fig:hist_mean_tpt_8_WNs_actions}
+	\end{subfigure}
+	\caption{Histogram of the mean throughput experienced by WNs for each algorithm.
+The results are computed from 100 different random scenarios for each of the WNs sizes, where 1,000 learning iterations are considered.
+In red, we have the results for the initial set of actions, which consider that the number of channels is half the number of WNs.
+In blue, the new set of actions is considered.}
+	\label{fig:scalability_more_actions}
+\end{figure*}
+
+Now, in order to further illustrate the effect of applying synchronized selfish learning, we compare it with the default decentralized approach in the random scenarios.
+In this case, we use the realistic range of actions in both situations.
+As shown in Figure \ref{fig:scalability_sync_vs_async}, the synchronized mechanisms lead to less variability than their default versions (the histogram tends to be narrower for all the cases).
+In contrast, some performance loss can be observed, especially for the UCB algorithm (note that the blue distribution is slightly shifted to the left, with respect to the red one).
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/hist_mean_tpt_2_WNs}
+		\caption{2 WNs}\label{fig:hist_mean_tpt_2_WNs}
+	\end{subfigure}
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/hist_mean_tpt_4_WNs}
+		\caption{4 WNs}\label{fig:hist_mean_tpt_4_WNs}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/hist_mean_tpt_6_WNs}
+		\caption{6 WNs}\label{fig:hist_mean_tpt_6_WNs}
+	\end{subfigure}
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/hist_mean_tpt_8_WNs}
+		\caption{8 WNs}\label{fig:hist_mean_tpt_8_WNs}
+	\end{subfigure}
+	\caption{Histogram of the mean throughput experienced by WNs for each algorithm.
+The results are computed from 100 different random scenarios for each of the WNs sizes, where 1,000 learning iterations are considered.
+In red, we have the results for the default algorithms implementation, while blue indicates their synchronized versions.}
+	\label{fig:scalability_sync_vs_async}
+\end{figure*}
+
+\section{Impact of modifying the range of actions}
+Here we aim to measure the impact of modifying the range of actions on the performance of the learning algorithms.
+For that, for each of the proposed action-selection strategies, we will compare the following performance measurements in the grid scenario, for different number of available actions: \emph{i)} the mean throughput experienced in average, \emph{ii)} the mean variability experienced in average.
+
+Firstly, Figures \ref{fig:impact_num_channels} and \ref{fig:impact_num_channels_on_variability} show the impact of using different number of orthogonal channels for each algorithm.
+As shown in \ref{fig:impact_num_channels}, the mean throughput increases until reaching 4 channels, so that each WN is able to properly access to a single channel.
+Such an ideal case is achieved by Thompson sampling and UCB.
+However, for $\varepsilon$-greedy and EXP3 we notice some performance anomalies when the number of available channels increases.
+Regarding the experienced variability (\ref{fig:impact_num_channels_on_variability}), we observe a peak when the number of channels is 3, situation in which at least two WNs are permanently in conflict, since they are competing for the same channel resources.
+Note that, for the other cases where the number of channels is not enough to accommodate all the WNs, a lower variability is experienced due to the impossibility of achieving a better performance.
+
+Secondly, the impact of modifying the available levels of transmit power is shown in both \ref{fig:impact_tx_power_levels_on_throughput} and \ref{fig:impact_tx_power_levels_on_variability}.
+In this case, we use the following sets of transmit power levels:
+\begin{itemize}
+	\item Set 1: \{5, 20\} dBm
+	\item Set 2: \{5, 10, 15, 20\} dBm
+	\item Set 3: from 2 to 20 dBm in steps of 2 dBm
+	\item Set 4: from 1 to 20 dBm in steps of 1 dBm
+\end{itemize}
+Regarding the throughput experienced (\ref{fig:impact_tx_power_levels_on_throughput}), we notice a very low variability when different sets of transmit power levels are used.
+In contrast, increasing the number of transmission power levels affects to the variability experienced by WNs.
+Such a variability increases in case of UCB and Thompson sampling.
+Different effects are noticed for $\varepsilon$-greedy and EXP3.
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/impact_num_channels}
+		\caption{Channel impact on the throughput}\label{fig:impact_num_channels}
+	\end{subfigure}
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/impact_num_channels_on_variability}
+		\caption{Channel impact on the variability}\label{fig:impact_num_channels_on_variability}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/impact_tx_power_levels_on_throughput}
+		\caption{TxPow impact on the throughput}\label{fig:impact_tx_power_levels_on_throughput}
+	\end{subfigure}
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{images/impact_tx_power_levels_on_variability}
+		\caption{TxPow impact on the variability}\label{fig:impact_tx_power_levels_on_variability}
+	\end{subfigure}
+	\caption{Mean and standard deviation of the throughput experienced in average when using different sets of actions.}
+	\label{fig:impact_actions}
+\end{figure*}
+
 \end{document}

### 2018-10-11 Code/constants.m

@@ -8,14 +8,9 @@
 %%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
 %%% ************************************************************************
 
-% Optimal values obtained from execution of Experiment_0_compute_optimal_configurations.m
-agg_tpt_optimal_prop_fairness = 891.0714;    % Mbps
-ind_tpt_optimal_prop_fairness = 222.7678;    % Mbps    
-optimal_max_min = 222.7678;
-
 nWlans = 4;                         % Number of WLANs in the map
-totalIterations = 1000;            % Maximum convergence time (one period implies the participation of all WLANs)
-minimumIterationToConsider = 500;  % Iteration from which to consider the obtained results
+totalIterations = 5000;            % Maximum convergence time (one period implies the participation of all WLANs)
+minimumIterationToConsider = 2500;  % Iteration from which to consider the obtained results
 totalScenarios = 100;               % Number of TOTAL repetitions to take the average
 
 % Define the transitory and the permanent intervals of iterations
@@ -24,10 +19,10 @@ permanentInterval = minimumIterationToConsider + 1 : totalIterations;
 
 NOISE_DBM = -100;                   % Floor NOISE_DBM in dBm
 
-nChannels = 2;                      % Number of available channels (from 1 to n_channels)
+nChannels = 4;                      % Number of available channels (from 1 to n_channels)
 channelActions = 1 : nChannels;     % Possible channels
 ccaActions = [-82];                 % CCA levels (dBm)
-txPowerActions = [5 10 15 20];      % Transmit power levels (dBm)
+txPowerActions = [-15 0 15 30];      % Transmit power levels (dBm)
 
 % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
 possibleActions = 1:(size(channelActions, 2) * ...
@@ -54,19 +49,22 @@ MaxRangeY = 1;
 MaxRangeZ = 1;
 MaxRange = sqrt(3);
 
-% Policies indexes
-RANDOM_POLICY = 0;
-EG_POLICY = 1;
-EXP3_POLICY = 2;
-UCB_POLICY = 3;
-TS_POLICY = 4;
-
 % Update modes of the exploration coefficient (epsilon-greedy)
 UPDATE_MODE_FAST = 0;   % epsilon = initial_epsilon / t 
[…]

### 2018-10-11 Code/experiments/Experiment_0_1_channels_impact.m

@@ -1,0 +1,121 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of TS. We display i) the actions probabilities, 
+%%% ii) the temporal aggregate throughput, iii) the temporal individual 
+%%% throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.5 Performance of the Thompson sampling policy
+%%% - Figure 15
+%%% - Figure 16
+%%% - Figure 17
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('SIM 1_1_0: e-greedy')
+disp('-----------------------')
+
+% Generate constants from 'constants.m'
[…]

### 2018-10-11 Code/experiments/Experiment_0_2_tx_power_impact.m

@@ -1,0 +1,126 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% By using a simple grid of 4 WLANs sharing 2 channels, we show the
+%%% individual performance of TS. We display i) the actions probabilities, 
+%%% ii) the temporal aggregate throughput, iii) the temporal individual 
+%%% throughput, iv) the average throughput.
+
+%%% This Script generates the output shown in the article:
+%%% - Section 5.1.5 Performance of the Thompson sampling policy
+%%% - Figure 15
+%%% - Figure 16
+%%% - Figure 17
+
+clc
+clear all
+
+% Add paths to methods folders
+addpath(genpath('framework_throughput_calculation/power_management_methods/'));
+addpath(genpath('framework_throughput_calculation/throughput_calculation_methods/'));
+addpath(genpath('framework_throughput_calculation/network_generation_methods/'));
+addpath(genpath('framework_throughput_calculation/auxiliary_methods/'));
+addpath(genpath('reinforcement_learning_methods/'));
+addpath(genpath('reinforcement_learning_methods/action_selection_methods/'));
+
+disp('-----------------------')
+disp('SIM 1_1_0: e-greedy')
+disp('-----------------------')
+
[…]

### 2018-10-11 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Experiment_1_1_egreedy.m

@@ -39,19 +39,29 @@ disp('-----------------------')
 constants
 
 initialEpsilon = 1;
-policy = EG_POLICY;
 
 % Setup the scenario: generate WLANs and initialize states and actions
 wlans = generate_network_3D(nWlans, 'grid', 2, drawMap); % SAFE CONFIGURATION
-    
+
+% Compute the maximum achievable throughput per WLAN
+upperBoundThroughputPerWlan = compute_max_selfish_throughput( wlans );
+
+load('workspace_throughput_all_combinations_cochannel_interference.mat')
+%load('workspace_throughput_all_combinations.mat')
+
 % Compute the throughput experienced per WLAN at each iteration
-[tpt_evolution_per_wlan_eg, times_arm_has_been_played_eg, regret_per_wlan_eg] = egreedy( wlans, initialEpsilon );
-[tpt_evolution_per_wlan_oeg, times_arm_has_been_played_oeg, regret_per_wlan_oeg] = ordered_egreedy( wlans, initialEpsilon );
+[tpt_evolution_per_wlan_eg, times_arm_has_been_played_eg, regret_per_wlan_eg , meanRewardPerAction] = ...
+    egreedy( wlans, initialEpsilon, upperBoundThroughputPerWlan );
+[tpt_evolution_per_wlan_oeg, times_arm_has_been_played_oeg, regret_per_wlan_oeg] = ...
+    ordered_egreedy( wlans, initialEpsilon, upperBoundThroughputPerWlan );
 
 % Plot the results
+plotResults = true;
 if plotResults
-    display_results_individual_performance(wlans, tpt_evolution_per_wlan_eg, times_arm_has_been_played_eg, 'EG');
-    display_results_individual_performance(wlans, tpt_evolution_per_wlan_oeg, times_arm_has_been_played_oeg, 'OEG');
+    display_results_individual_performance(wlans, tpt_evolution_per_wlan_eg, ...
+        times_arm_has_been_played_eg, upperBoundThroughputPerWlan, max_max_min, 'EG');
+    display_results_individual_performance(wlans, tpt_evolution_per_wlan_oeg, ...
+        times_arm_has_been_played_oeg, upperBoundThroughputPerWlan, max_max_min, 'OEG');
 end
 
 % Save the workspace

### 2018-10-11 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Tuning parameters/Experiment_1_1_0_0_EG_find_best_epsilon.m

@@ -35,14 +35,20 @@ disp('e-greedy: finding the best parameters')
 disp('-----------------------')
 
 % Generate constants from 'constants.m'
+load('workspace_throughput_all_combinations.mat')
 constants
 
-totalRepetitions = 100;
+% Setup the scenario: generate WLANs and initialize states and actions
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+% Compute the maximum achievable throughput per WLAN
+powerMatrix = power_matrix(wlans);     
+upperBoundThroughputPerWlan = compute_max_bound_throughput(wlans, ...
+    powerMatrix, NOISE_DBM, max(txPowerActions));
 
+
+totalRepetitions = 5;
 initialEpsilon = 0:.1:1;
 
-policy = EG_POLICY;
-  
 % Initialize variables at which to store information per repetition
 tptEvolutionPerWlanEgreedy = cell(1, totalRepetitions);
 averageThroughputEvolution = cell(1, totalRepetitions);
@@ -53,20 +59,20 @@ maxMinThroughput = cell(1, totalRepetitions);
 
 %% ITERATE FOR NUMBER OF REPETITIONS (TO TAKE THE AVERAGE)
 for r = 1 : totalRepetitions
+    
+    totalIterations
+    
     disp('------------------------------------')
     disp(['ROUND ' num2str(r) '/' num2str(totalRepetitions) ...
         ' (' num2str(totalIterations) ' iterations)'])
     disp('------------------------------------')   
-
-    % Setup the scenario: generate WLANs and initialize states and actions
-    wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
 
     % Iterate for each initial epsilon
     for e = 1 : size(initialEpsilon, 2)        
         
         disp(['    - \epsilon_0 = ' num2str(initialEpsilon(e))])
     
-        [tptEvolutionPerWlan, timesArmHasBeenPlayed] = egreedy( wlans, initialEpsilon(e) );
+        [tptEvolutionPerWlan, timesArmHasBeenPlayed] = egreedy( wlans, initialEpsilon(e), upperBoundThroughputPerWlan );
 
         tptEvolutionPerWlanEgreedy{r}  = tptEvolutionPerWlan;
         
[…]

### 2018-10-11 Code/experiments/Part 1 - Toy grid scenario/1.2. EXP3/Experiment_1_2_exp3.m

@@ -43,19 +43,26 @@ initialEta = 0.6;
 gamma = 0;
 
 % Setup the scenario: generate WLANs and initialize states and actions
-wlan = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
-    
+wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+
+% Compute the maximum achievable throughput per WLAN
+powerMatrix = power_matrix(wlans);     
+upperBoundThroughputPerWlan = compute_max_bound_throughput(wlans, ...
+    powerMatrix, NOISE_DBM, max(txPowerActions));
+
+load('workspace_throughput_all_combinations.mat')
+
 % Compute the throughput experienced per WLAN at each iteration
-[tpt_evolution_per_wlan_exp3, times_arm_has_been_played_exp3, regret_per_wlan_exp3]  = exp3(wlan, gamma, initialEta);
-[tpt_evolution_per_wlan_oexp3, times_arm_has_been_played_oexp3, regret_per_wlan_oexp3]  = ordered_exp3(wlan, gamma, initialEta);
+[tpt_evolution_per_wlan_exp3, times_arm_has_been_played_exp3, regret_per_wlan_exp3]  = exp3(wlans, gamma, initialEta, upperBoundThroughputPerWlan);
+%[tpt_evolution_per_wlan_oexp3, times_arm_has_been_played_oexp3, regret_per_wlan_oexp3]  = ordered_exp3(wlan, gamma, initialEta, upperBoundThroughputPerWlan);
 
 % Plot the results
-if plotResults
-    display_results_individual_performance(wlan, tpt_evolution_per_wlan_exp3, ...
-        times_arm_has_been_played_exp3, 'EXP3');
-    display_results_individual_performance(wlan, tpt_evolution_per_wlan_oexp3, ...
-        times_arm_has_been_played_oexp3, 'OEXP3');
-end
+%if plotResults
+    display_results_individual_performance(wlans, tpt_evolution_per_wlan_exp3, ...
+        times_arm_has_been_played_exp3, upperBoundThroughputPerWlan, max_max_min, 'EXP3');
+%    display_results_individual_performance(wlan, tpt_evolution_per_wlan_oexp3, ...
+%        times_arm_has_been_played_oexp3, upperBoundThroughputPerWlan, max_max_min, 'OEXP3');
+%end
 
 % Save the workspace
 save('./output/simulation_1_2_workspace.mat')

### 2018-10-11 Code/experiments/Part 1 - Toy grid scenario/1.3. UCB/Experiment_1_3_ucb.m

@@ -38,19 +38,27 @@ disp('-----------------------')
 % Generate constants from 'constants.m'
 constants
 
+load('workspace_throughput_all_combinations.mat')
+
 % Setup the scenario: generate WLANs and initialize states and actions
 wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
+
+% Compute the maximum achievable throughput per WLAN
+powerMatrix = power_matrix(wlans);     
+upperBoundThroughputPerWlan = compute_max_bound_throughput(wlans, ...
+    powerMatrix, NOISE_DBM, max(txPowerActions));
     
-policy = UCB_POLICY;
 % Compute the throughput experienced per WLAN at each iteration
-[tpt_evolution_per_wlan_ucb, times_arm_has_been_played_ucb, regret_per_wlan_ucb] = ucb(wlans);
-[tpt_evolution_per_wlan_oucb, times_arm_has_been_played_oucb, regret_per_wlan_oucb] = ucb(wlans);
+[tpt_evolution_per_wlan_ucb, times_arm_has_been_played_ucb, regret_per_wlan_ucb] = ucb(wlans, upperBoundThroughputPerWlan);
+%[tpt_evolution_per_wlan_oucb, times_arm_has_been_played_oucb, regret_per_wlan_oucb] = ordered_ucb(wlans, upperBoundThroughputPerWlan);
 
 % Plot the results
-if plotResults
-    display_results_individual_performance(wlans, tpt_evolution_per_wlan_ucb, times_arm_has_been_played_ucb, 'UCB');
-    display_results_individual_performance(wlans, tpt_evolution_per_wlan_oucb, times_arm_has_been_played_oucb, 'OUCB');
-end
+%if plotResults
+    display_results_individual_performance(wlans, tpt_evolution_per_wlan_ucb, ...
+        times_arm_has_been_played_ucb, upperBoundThroughputPerWlan, max_max_min, 'UCB');
+%    display_results_individual_performance(wlans, tpt_evolution_per_wlan_oucb, ...
+%        times_arm_has_been_played_oucb, upperBoundThroughputPerWlan, max_max_min, 'OUCB');
+%end
 
 % Save the workspace
 save('./Output/simulation_1_3_workspace.mat')

### 2018-10-11 Code/experiments/Part 1 - Toy grid scenario/1.4. Thompson sampling/Experiment_1_4_thompson_sampling.m

@@ -38,19 +38,27 @@ disp('-----------------------')
 % Generate constants from 'constants.m'
 constants
 
+load('workspace_throughput_all_combinations.mat')
+
 % Setup the scenario: generate WLANs and initialize states and actions
 wlans = generate_network_3D(nWlans, 'grid', 2, drawMap); % SAFE CONFIGURATION
+
+% Compute the maximum achievable throughput per WLAN
+powerMatrix = power_matrix(wlans);     
+upperBoundThroughputPerWlan = compute_max_bound_throughput(wlans, ...
+    powerMatrix, NOISE_DBM, max(txPowerActions));
     
-policy = TS_POLICY;
 % Compute the throughput experienced per WLAN at each iteration
-[tpt_evolution_per_wlan_ts, times_arm_has_been_played_ts, regret_per_wlan_ts] = thompson_sampling(wlans);
-[tpt_evolution_per_wlan_ots, times_arm_has_been_played_ots, regret_per_wlan_ots] = ordered_thompson_sampling(wlans);
+[tpt_evolution_per_wlan_ts, times_arm_has_been_played_ts, regret_per_wlan_ts] = thompson_sampling(wlans, upperBoundThroughputPerWlan);
+[tpt_evolution_per_wlan_ots, times_arm_has_been_played_ots, regret_per_wlan_ots] = ordered_thompson_sampling(wlans, upperBoundThroughputPerWlan);
 
 % Plot the results
-if plotResults
-    display_results_individual_performance(wlans, tpt_evolution_per_wlan_ts, times_arm_has_been_played_ts, 'TS');
-    display_results_individual_performance(wlans, tpt_evolution_per_wlan_ots, times_arm_has_been_played_ots, 'OTS');
-end
+%if plotResults
+display_results_individual_performance(wlans, tpt_evolution_per_wlan_ts, ...
+    times_arm_has_been_played_ts, upperBoundThroughputPerWlan, max_max_min, 'TS');
+display_results_individual_performance(wlans, tpt_evolution_per_wlan_ots, ...
+    times_arm_has_been_played_ots, upperBoundThroughputPerWlan, max_max_min, 'OTS');
+%end
 
 % Save the workspace
 save('./Output/simulation_1_4_workspace.mat')

### 2018-10-11 Code/experiments/Part 2 - Random scenarios/2.1. Performance Comparison/Experiment_2_0_Performance_Comparison_Random_Network.m

@@ -1,0 +1,100 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% The script computes the performance of applying e-greedy, EXP3, UCB and
+%%% Thompson sampling in random scenarios. At the end, histograms of the 
+%%% average throughput experienced are displayed for each policy.
+
+%%% This Script generates the output shown in the article:
+%%% - Figure 18
+
+%%
+clc
+clear all
+
+disp('************************************************************************')
+disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
+disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
+disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
+disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
+disp('* GitHub repository:                                                   *')
+disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
+disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
+disp('************************************************************************')
+
+disp('-----------------------')
+disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
+disp('-----------------------')
+
+% Load constants
+%constants
+constants
+% Update the nWlans variable to define an array
+nWlans = [2 4 6 8];
+
+% % Initialize variables to store results:
+% % - Each cell contains the throughput evolution experienced with each policy
[…]

### 2018-10-11 Code/experiments/Part 2 - Random scenarios/PLOT_RESULTS_PART_2.m

@@ -254,12 +254,16 @@ for i = 1 : size(wlansSizes, 2)
     h_oucb = hist(meanThroughputPerWlanOUcbConcat{i}(:), 30);
     h_ots = hist(meanThroughputPerWlanOTsConcat{i}(:), 30);
 
-    max_counts = max(max([h_eg h_exp3 h_ucb h_ts])); 
+    max_counts = max(max(max([h_eg h_exp3 h_ucb h_ts])), max(max([h_oeg h_oexp3 h_oucb h_ots]))); 
 
     max_tpt = max(max([meanThroughputPerWlanEgreedyConcat{i}(:) ...
         meanThroughputPerWlanExp3Concat{i}(:), ...
         meanThroughputPerWlanUcbConcat{i}(:), ...
-        meanThroughputPerWlanTsConcat{i}(:)]));
+        meanThroughputPerWlanTsConcat{i}(:), ...
+        meanThroughputPerWlanOEgreedyConcat{i}(:) ...
+        meanThroughputPerWlanOExp3Concat{i}(:), ...
+        meanThroughputPerWlanOUcbConcat{i}(:), ...
+        meanThroughputPerWlanOTsConcat{i}(:)]));
 
     fig = figure('pos',[450 400 500 350]);
     axes;
@@ -319,6 +323,7 @@ for i = 1 : size(wlansSizes, 2)
 
     % Legend
     legend('Async.','Sync.')
+    %legend('Default','More actions')
     % Set Axes labels
     AxesH    = findobj(fig, 'Type', 'Axes');       
     % Y-label

### 2018-10-11 Code/framework_throughput_calculation/auxiliary_methods/display_results_individual_performance.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan, ...
-    timesArmHasBeenPlayed, method_name )
+    timesArmHasBeenPlayed, upperBoundThroughputPerWlan, upperBoundAggregatePerformance, method_name )
 % display_results_individual_performance displays the results of experiments for
 % individual performance of each policy (e.g., "Experiment_2_1_individual_performance_EG_parameters_4_WN.m")
 %   INPUT: 
@@ -29,9 +29,6 @@ function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan
     set(0,'defaultAxesFontName','Times New Roman');
     set(0,'defaultTextFontName','Times New Roman');
     set(0,'defaultUipanelFontName','Times New Roman');
-    
-    agg_tpt_optimal_prop_fairness = 891.0714;    % Mbps
-    ind_tpt_optimal_prop_fairness = 222.7678;    % Mbps    
 
     % Compute data to be plotted
     mean_agg_tpt_entire_simulation = mean(sum(tptEvolutionPerWlan(1:totalIterations, :), 2));
@@ -41,9 +38,9 @@ function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan
     mean_fairness_entire_simulation = mean(jains_fairness(tptEvolutionPerWlan(1:totalIterations, :)));
     mean_prop_fairness_entire_simulation = mean(sum(log(tptEvolutionPerWlan(1:totalIterations, :)),2));
     mean_agg_tpt_comparison_optimal_entire_simulation = ...
-        mean_agg_tpt_entire_simulation / agg_tpt_optimal_prop_fairness;
+        mean_agg_tpt_entire_simulation / upperBoundAggregatePerformance;
     mean_ind_tpt_comparison_optimal_entire_simulation = ...
-        mean(mean(tptEvolutionPerWlan(1:totalIterations, :),2)) / ind_tpt_optimal_prop_fairness;
+        mean(mean(tptEvolutionPerWlan(1:totalIterations, :),2)) ./ upperBoundThroughputPerWlan;
     
     % Plot results of the entire simulation
[…]

### 2018-10-11 Code/framework_throughput_calculation/power_management_methods/compute_interference_per_wlan.m

@@ -1,0 +1,53 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function interference_per_wlan_mw = compute_interference_per_wlan(wlans, powerMatrix)
+% Interferences - Returns the interferences power received at each WLAN
+%   OUTPUT:
+%       * intMat: 1xN array (N is the number of WLANs) with the
+%       interferences noticed on each AP in mW
+%   INPUT:
+%       * wlans: contains information of each WLAN in the map. For instance,
+%       wlans(1) corresponds to the first one, so that it has unique
+%       parameters (x,y,z,BW,CCA,etc.).
+%       * powMat: matrix NxN (N is the number of WLANs) with the power
+%       received at each AP in dBm.
+
+% We assume that overlapping channels also create an interference with lower level (20dB/d) - 20 dB == 50 dBm
+
+    wlans_aux = wlans;
+   
+    load('constants.mat')
+    
+    num_wlans = size(wlans_aux, 2);
+    interference_per_wlan_mw = zeros(1, size(wlans_aux, 2)); 
+               
+    for i = 1 : num_wlans
+        for j = 1 : num_wlans
+            if i ~= j 
+                if COCHANNEL_INTERFERENCE
+                    adjacent_interference = 20 * (abs(wlans_aux(i).Channel - wlans_aux(j).Channel));
+                    if wlans_aux(i).Channel ~= wlans_aux(j).Channel
+                        interference_per_wlan_mw(i) = interference_per_wlan_mw(i) + ...
+                            db2pow(powerMatrix(i,j) - adjacent_interference);
+                    else
+                        interference_per_wlan_mw(i) = interference_per_wlan_mw(i) + ...
+                            db2pow(powerMatrix(i,j));
+                    end  
+                else
[…]

### 2018-10-11 Code/framework_throughput_calculation/power_management_methods/interferences.m

@@ -1,41 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-function interferences = Interferences(wlans, powerMatrix)
-% Interferences - Returns the interferences power received at each WLAN
-%   OUTPUT:
-%       * intMat: 1xN array (N is the number of WLANs) with the
-%       interferences noticed on each AP in mW
-%   INPUT:
-%       * wlans: contains information of each WLAN in the map. For instance,
-%       wlans(1) corresponds to the first one, so that it has unique
-%       parameters (x,y,z,BW,CCA,etc.).
-%       * powMat: matrix NxN (N is the number of WLANs) with the power
-%       received at each AP in dBm.
-
-% We assume that overlapping channels also create an interference with lower level (20dB/d) - 20 dB == 50 dBm
-
-    interferences = zeros(1, size(wlans, 2)); 
-    
-    for i = 1:size(wlans, 2)
-        
-        for j = 1:size(wlans, 2)
-            
-            if i ~= j && wlans(j).transmitting == 1
-                
-                interferences(i) = interferences(i) + db2pow(powerMatrix(i,j) - db2pow(20 * (abs(wlans(i).Channel - wlans(j).Channel))));
-            
-            end
-            
-        end
-        
-    end
-
-end

### 2018-10-11 Code/framework_throughput_calculation/throughput_calculation_methods/compute_max_selfish_throughput.m

@@ -1,0 +1,42 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function optimalThroughputPerWlan = compute_max_selfish_throughput( wlans )
+% Given an WLAN (AP+STA), compute the maximum capacity achievable according
+% to the power obtained at the receiver without interference
+%
+% OUTPUT:
+%   * optimalThroughputPerWlan - maximum achievable throughput per WLAN (Mbps)
+% INPUT:
+%   * wlan - object containing all the WLANs information 
+%   * powerMatrix - power received from each AP
+%   * noise - floor noise in dBm
+
+    load('constants.mat')
+
+    wlans_aux = wlans;
+    num_wlans = size(wlans_aux, 2);
+    optimalThroughputPerWlan = zeros(1, num_wlans);    
+    
+    % Iterate for each WLAN
+    for i = 1 : num_wlans
+        for j = 1 : num_wlans
+            if j ~= i
+                wlans_aux(j).TxPower = min(txPowerActions);
+                wlans_aux(j).Channel = max(channelActions);
+            end
+        end
+        wlans_aux(i).TxPower = max(txPowerActions);
+        wlans_aux(i).Channel = min(channelActions);
+        tpt = compute_throughput_from_sinr(wlans_aux, NOISE_DBM); % Mbps
+        optimalThroughputPerWlan(i) = tpt(i);
+    end
+    
+end

### 2018-10-11 Code/reinforcement_learning_methods/egreedy.m

@@ -8,8 +8,8 @@
 %%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
 %%% ************************************************************************
 
-function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
-    egreedy( wlans, initialEpsilon, varargin )
+function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan, meanRewardPerAction ] = ...
+    egreedy( wlans, initialEpsilon, upperBoundThroughputPerWlan, varargin )
 % EGREEDY - Given a WN, applies e-greedy to maximize the experienced throughput
 %
 %   OUTPUT: 
@@ -54,14 +54,9 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
         initialActionIxPerWlan(i) = indexes2val(wlansAux(i).Channel, ...
             indexCca, indexTpc, size(channelActions,2), size(ccaActions,2));
     end
+    
     % Initialize the indexes of the taken action
     actionIndexPerWlan = initialActionIxPerWlan;                           
-    
-    % Compute the maximum achievable throughput per WLAN
-    powerMatrix = power_matrix(wlansAux);     
-    upperBoundThroughputPerWlan = compute_max_bound_throughput(wlansAux, ...
-        powerMatrix, NOISE_DBM, max(txPowerActions));
-    
     % Initialize arm selection for each WLAN by using the initial action
     selectedArm = actionIndexPerWlan;             
     % Keep track of current and previous actions for getting the transitions probabilities
@@ -75,6 +70,8 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
     rewardPerArm = zeros(nWlans, K); 
     % Initialize the regret experienced by each WLAN
     regretAfterAction = zeros(1, nWlans);
+    
+    cumulative_reward_per_action = zeros(nWlans, K);
     
     % Initialize epsilon
     epsilon = initialEpsilon; 
@@ -109,22 +106,26 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
             % Update WN configuration
             wlansAux(order(i)).Channel = a;   
             %wlan_aux(order(i)).CCA = ccaActions(b);
-            wlansAux(order(i)).TxPower = txPowerActions(c); 
-            % Compute the throughput noticed after applying the action
[…]

### 2018-10-11 Code/reinforcement_learning_methods/exp3.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan] = ...
-    exp3(wlans, gamma, initialEta, varargin)
+    exp3(wlans, gamma, initialEta, upperBoundThroughputPerWlan, varargin)
 % exp3 applies EXP3 (basic formulation) to maximize the experienced
 % throughput of a given scenario
 %
@@ -56,14 +56,9 @@ function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan
         initialActionIxPerWlan(i) = indexes2val(wlansAux(i).Channel, ...
             indexCca, indexTpc, size(channelActions,2), size(ccaActions,2));
     end
+    
     % Initialize the indexes of the taken action
-    actionIndexPerWlan = initialActionIxPerWlan;                           
-    
-    % Compute the maximum achievable throughput per WLAN
-    powerMatrix = power_matrix(wlansAux);     
-    upperBoundRewardPerWlan = compute_max_bound_throughput(wlansAux, ...
-        powerMatrix, NOISE_DBM, max(txPowerActions));
-    
+    actionIndexPerWlan = initialActionIxPerWlan;                              
     selectedArm = actionIndexPerWlan;           % Initialize arm selection for each WLAN by using the initial action
     weightsPerArm = ones(nWlans, K);            % Initialize weight to 1 for each action
     previousAction = selectedArm;               % Initialize the previous action as the initial one
@@ -115,37 +110,35 @@ function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan
             % Update WN configuration
             wlansAux(wlan_ix).Channel = a;   
             wlansAux(wlan_ix).TxPower = txPowerActions(c);  
-
-            % Compute the reward with the throughput obtained in the round after applying the action
-            powerMatrix = power_matrix(wlansAux);
-            tptAfterAction = compute_throughput_from_sinr(wlansAux, powerMatrix, NOISE_DBM);  % bps    
-            
-            % Update the reward of each WN
-            rw = tptAfterAction ./ upperBoundRewardPerWlan;
-            regretAfterAction = 1 - rw;
-                     
+        end 
+        
+        % Compute the reward with the throughput obtained in the round after applying the action
+        tptAfterAction = compute_throughput_from_sinr(wlansAux, NOISE_DBM);  % bps    
[…]

### 2018-10-11 Code/reinforcement_learning_methods/ordered_egreedy.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
-    ordered_egreedy( wlans, initialEpsilon, varargin )
+    ordered_egreedy( wlans, initialEpsilon, upperBoundThroughputPerWlan, varargin )
 % EGREEDY - Given a WN, applies e-greedy to maximize the experienced throughput
 %
 %   OUTPUT: 
@@ -57,15 +57,8 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
     % Initialize the indexes of the taken action
     actionIndexPerWlan = initialActionIxPerWlan;                           
     
-    % Compute the maximum achievable throughput per WLAN
-    powerMatrix = power_matrix(wlansAux);     
-    upper_bound_reward_per_wlan = compute_max_bound_throughput(wlansAux, ...
-       powerMatrix, NOISE_DBM, max(txPowerActions));
-    %upperBoundRewardPerWlan = optimal_max_min;
-    
     % Initialize arm selection for each WLAN by using the initial action
-    selectedArm = actionIndexPerWlan;   
-    
+    selectedArm = actionIndexPerWlan;
     % Keep track of current and previous actions for getting the transitions probabilities
     currentAction = zeros(1, nWlans);
     previousAction = selectedArm;
@@ -112,10 +105,10 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
         
         % Compute the throughput noticed after applying the action
         powerMatrix = power_matrix(wlansAux);
-        tptAfterAction = compute_throughput_from_sinr(wlansAux, powerMatrix, NOISE_DBM);  % bps  
+        tptAfterAction = compute_throughput_from_sinr(wlansAux, NOISE_DBM);  % bps  
         
         % Update the reward of each WN
-        rw = tptAfterAction./upper_bound_reward_per_wlan;    
+        rw = tptAfterAction./upperBoundThroughputPerWlan;    
                
         for wlan_ix_aux = 1 : nWlans
             rewardPerArm(wlan_ix_aux, selectedArm(wlan_ix_aux)) = rw(wlan_ix_aux);

### 2018-10-11 Code/reinforcement_learning_methods/ordered_thompson_sampling.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
-    ordered_thompson_sampling( wlans, varargin )
+    ordered_thompson_sampling( wlans, upperBoundThroughputPerWlan, varargin )
 % thompson_sampling applies TS to maximize the experienced
 % throughput of a given scenario
 %
@@ -57,13 +57,7 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
     end
 
     % Initialize the indexes of the taken action
-    actionIndexPerWlan = initialActionIndexPerWlan;                           
-    
-    % Compute the maximum achievable throughput per WLAN
-    powerMatrix = power_matrix(wlansAux);     
-    upperBoundRewardPerWlan = compute_max_bound_throughput(wlansAux, ...
-        powerMatrix, NOISE_DBM, max(txPowerActions));
-    
+    actionIndexPerWlan = initialActionIndexPerWlan;                              
     selectedArm = actionIndexPerWlan;               % Initialize arm selection for each WLAN by using the initial action
     timesArmHasBeenPlayed = zeros(nWlans, K);       % Initialize the times an arm has been played
     currentAction = zeros(1, nWlans);
@@ -103,12 +97,11 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
         %wlan_aux(wlan_ix).CCA = ccaActions(b);
         wlansAux(wlan_ix).TxPower = txPowerActions(c);  
         % Compute the reward with the throughput obtained in the round after applying the action
-        powerMatrix = power_matrix(wlansAux);                
-        tptAfterAction = compute_throughput_from_sinr(wlansAux, powerMatrix, NOISE_DBM);  % bps  
+        tptAfterAction = compute_throughput_from_sinr(wlansAux, NOISE_DBM);  % bps  
         % Update the reward of each WN
         rw = zeros(1, nWlans);
         for wlan_ix_aux = 1 : nWlans
-            rw(wlan_ix_aux) = tptAfterAction(wlan_ix_aux)/((upperBoundRewardPerWlan(wlan_ix_aux)));       
[…]

### 2018-10-11 Code/reinforcement_learning_methods/ordered_ucb.m

@@ -82,7 +82,6 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
         for w = 1 : nWlans              
             [a, ~, c] = val2indexes(order_actions(k), size(channelActions,2), size(ccaActions,2), size(txPowerActions,2));
             wlansAux(order_wlans(w)).Channel = a;   
-            %wlan_aux(i).CCA = ccaActions(b);
             wlansAux(order_wlans(w)).TxPower = txPowerActions(c);  
             powerMatrix = power_matrix(wlansAux);
             tptAfterAction = compute_throughput_from_sinr(wlansAux, powerMatrix, NOISE_DBM);  % bps   
@@ -116,17 +115,16 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
         [a, ~, c] = val2indexes(selectedArm(wlan_ix), size(channelActions,2), size(ccaActions,2), size(txPowerActions,2));
         % Update WN configuration
         wlansAux(wlan_ix).Channel = a;   
-        %wlan_aux(wlan_ix).CCA = ccaActions(b);
         wlansAux(wlan_ix).TxPower = txPowerActions(c);  
         % Compute the throughput noticed after applying the action           
         powerMatrix = power_matrix(wlansAux);                
         tptAfterAction = compute_throughput_from_sinr(wlansAux, powerMatrix, NOISE_DBM);  % bps         
         % Update the reward of each WN
-        rw = zeros(1, nWlans);        
+        rw = tptAfterAction./upperBoundRewardPerWlan; 
+        % Update the mean reward experienced by each WN
         for wlan_ix_aux = 1 : nWlans 
             timesArmHasBeenPlayed(wlan_ix_aux, selectedArm(wlan_ix_aux)) = ...
-                timesArmHasBeenPlayed(wlan_ix_aux, selectedArm(wlan_ix_aux)) + 1;  
-            rw(wlan_ix_aux) = (tptAfterAction(wlan_ix_aux)/((upperBoundRewardPerWlan(wlan_ix_aux))));                                       
+                timesArmHasBeenPlayed(wlan_ix_aux, selectedArm(wlan_ix_aux)) + 1;                                                    
             cumulativeRewardPerWlanPerArm(wlan_ix_aux, selectedArm(wlan_ix_aux)) = ...
[…]

### 2018-10-11 Code/reinforcement_learning_methods/thompson_sampling.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
-thompson_sampling( wlans, varargin )
+thompson_sampling( wlans, upperBoundThroughputPerWlan, varargin )
 % thompson_sampling applies TS to maximize the experienced
 % throughput of a given scenario
 %
@@ -57,11 +57,6 @@ thompson_sampling( wlans, varargin )
     % Initialize the indexes of the taken action
     actionIndexPerWlan = initialActionIndexPerWlan;                           
     
-    % Compute the maximum achievable throughput per WLAN
-    powerMatrix = power_matrix(wlansAux);     
-    upperBoundRewardPerWlan = compute_max_bound_throughput(wlansAux, ...
-        powerMatrix, NOISE_DBM, max(txPowerActions));
-    
     selectedArm = actionIndexPerWlan;               % Initialize arm selection for each WLAN by using the initial action
     timesArmHasBeenPlayed = zeros(nWlans, K);       % Initialize the times an arm has been played
     currentAction = zeros(1, nWlans);
@@ -101,31 +96,29 @@ thompson_sampling( wlans, varargin )
             % Update WN configuration
             wlansAux(order(i)).Channel = a;   
             %wlan_aux(order(i)).CCA = ccaActions(b);
-            wlansAux(order(i)).TxPower = txPowerActions(c);  
-            % Compute the reward with the throughput obtained in the round after applying the action
-            powerMatrix = power_matrix(wlansAux);                
-            tptAfterAction = compute_throughput_from_sinr(wlansAux, powerMatrix, NOISE_DBM);  % bps  
-            % Update the reward of each WN
-            rw = zeros(1, nWlans);
-            for wlan_i = 1 : nWlans     
-                rw(wlan_i) = tptAfterAction(wlan_i)/((upperBoundRewardPerWlan(wlan_i)));       
-                estimatedRewardPerWlan(wlan_i, selectedArm(wlan_i)) = ...
-                    (estimatedRewardPerWlan(wlan_i, selectedArm(wlan_i)) * ...
-                    timesArmHasBeenPlayed(wlan_i, selectedArm(wlan_i)) + rw(wlan_i)) / ...
[…]

### 2018-10-11 Code/reinforcement_learning_methods/ucb.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
-ucb( wlans, varargin )
+    ucb( wlans, upperBoundThroughputPerWlan, varargin )
 % ucb applies UCB to maximize the experienced throughput of a given scenario
 %
 %   OUTPUT: 
@@ -53,14 +53,9 @@ ucb( wlans, varargin )
         initialActionIxPerWlan(i) = indexes2val(wlansAux(i).Channel, ...
             indexCca, indexTpc, size(channelActions,2), size(ccaActions,2));
     end
+    
     % Initialize the indexes of the taken action
     actionIndexPerWlan = initialActionIxPerWlan;                           
-    
-    % Compute the maximum achievable throughput per WLAN
-    powerMatrix = power_matrix(wlansAux);     
-    upperBoundRewardPerWlan = compute_max_bound_throughput(wlansAux, ...
-        powerMatrix, NOISE_DBM, max(txPowerActions));
-    
     selectedArm = actionIndexPerWlan;              % Initialize arm selection for each WLAN by using the initial action
     timesArmHasBeenPlayed = ones(nWlans, K);   % Initialize the times an arm has been played
     currentAction = zeros(1, nWlans);
@@ -87,13 +82,12 @@ ucb( wlans, varargin )
             %wlan_aux(i).CCA = ccaActions(b);
             wlansAux(order_wlans(w)).TxPower = txPowerActions(c);  
             powerMatrix = power_matrix(wlansAux);
-            tptAfterAction = compute_throughput_from_sinr(wlansAux, powerMatrix, NOISE_DBM);  % bps   
+            tptAfterAction = compute_throughput_from_sinr(wlansAux, NOISE_DBM);  % bps   
             cumulativeRewardPerWlanPerArm(order_wlans(w), order_actions(k)) = ...
-                (tptAfterAction(order_wlans(w))/((upperBoundRewardPerWlan(order_wlans(w)))));
-            throughput = compute_throughput_from_sinr(wlansAux, powerMatrix, NOISE_DBM);  % bps 
-            tptExperiencedPerWlan(iteration, order_wlans(w)) = throughput(order_wlans(w));
+                (tptAfterAction(order_wlans(w))/((upperBoundThroughputPerWlan(order_wlans(w)))));
+            tptExperiencedPerWlan(iteration, order_wlans(w)) = tptAfterAction(order_wlans(w));
[…]

### 2018-10-11 Code/reinforcement_learning_methods_old/action_selection_methods/select_action_ucb.m

@@ -1,39 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-function [ arm ] = select_action_ucb( rewards_per_configuration, t, times_arm_has_been_played )
-% selectActionUCB: returns the best possible arm given the current distribution
-%   OUTPUT:
-%       * arm - chosen arm to be played - configuration composed by [channel,CCA,TPC]
-%   INPUT:
-%       - rewards_per_configuration: rewards noticed at each configuration
-%       - t: current iteration
-%       - times_arm_has_been_played: number of plays of each arm
-
-    rewards_with_bounds = rewards_per_configuration + sqrt(2 * log(t) ./ times_arm_has_been_played);
-   
-    [val, ~] = max(rewards_with_bounds);
-    
-    % Break ties randomlyselected_armtime_arm_is_played
-    
-    if sum(rewards_with_bounds==val) > 1
-        if val ~= Inf
-            indexes = find(rewards_with_bounds == val);
-            arm = randsample(indexes,1);
-        else
-            arm = randsample(1:size(rewards_with_bounds, 2), 1);
-        end
-        
-    % Select arm with maximum reward
-    else
-        [~, arm] = max(rewards_with_bounds);
-    end
-    
-end

### 2018-10-11 Code/reinforcement_learning_methods_old/thompson_sampling.m

@@ -1,191 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
-thompson_sampling( wlans, varargin )
-% thompson_sampling applies TS to maximize the experienced
-% throughput of a given scenario
-%
-%   OUTPUT: 
-%       * tptExperiencedByWlan - throughput experienced by each WLAN
-%         for each of the iterations done
-%       * timesArmHasBeenPlayed - times each action has been played
-%   INPUT: 
-%       * wlan - wlan object containing information about all the WLANs
-
-    constants
-    
-    try
-        if size(varargin, 2) == 3
-            % Update possible actions
-            nChannels = varargin{1};
-            channelActions = 1 : nChannels;
-            ccaActions = varargin{2};
-            txPowerActions = varargin{3};
-            % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
-            possibleActions = 1:(size(channelActions, 2) * ...
-                size(ccaActions, 2) * size(txPowerActions, 2));
-            K = size(possibleActions,2);   % Total number of actions
-            allCombs = allcomb(1:K, 1:K);    
-        end 
-    catch
-        if size(varargin, 2) ~= 3
-            disp('Wrong number of input arguments')
-        end
-    end
-    
-    %% INITIALIZE ALGORITHM
-    % Use a copy of wlan to make operations
-    wlansAux = wlans;
-    nWlans = size(wlansAux, 2);
-    
[…]

### 2018-10-12 Ordered Learning/ordered_learning.tex
Bug fixing + simulations for the "new results" document

--- 2018-10-09 Ordered Learning/ordered_learning.tex
@@
 
+Figure \ref{fig:e_greedy} shows several results regarding the application of $\varepsilon$-greedy in the toy scenario (1,000 iterations are considered), both for the fully decentralized and the synchronized approaches.
+As shown, the latter allows to experience a lower temporal throughput variability (\ref{fig:temporal_individual_tpt_EG} vs \ref{fig:temporal_individual_tpt_OEG}), since a lower number of actions is being exploited (\ref{fig:actions_probability_EG} vs \ref{fig:actions_probability_OEG}).
+However, similar results are obtained with respect to the average throughput experienced per WN (\ref{fig:mean_tpt_EG} vs \ref{fig:mean_tpt_OEG}).
+The fact is that, for the synchronized approach, WNs tend to exploit sub-optimal actions for longer periods (while they wait for their turn).
+In contrast, WNs are able to rapidly discard these sub-optimal actions in their turn.
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_EG}
+		\caption{Actions prob. (default)}\label{fig:actions_probability_EG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_OEG}
+		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OEG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_CEG}
+		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CEG}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_EG}
+		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_EG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OEG}
+		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OEG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CEG}
+		\caption{Temp. var.  (sync. 2)}\label{fig:temporal_individual_tpt_CEG}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_EG}
+		\caption{Mean tpt. (default)}\label{fig:mean_tpt_EG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_OEG}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OEG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_CEG}
+		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CEG}
+	\end{subfigure}
+	\caption{Simulation results in $\varepsilon$-greedy (1,000 iterations)}
+	\label{fig:e_greedy}
+\end{figure*}
+
 \subsection{EXP3}
 \label{section:exp3}
+
+Figure \ref{fig:exp3} shows several results regarding the application of EXP3 in the toy scenario (1,000 iterations are considered), both for the fully decentralized and the synchronized approaches.
+Again, the synchronized version of EXP3 leads to a lower temporal variability (\ref{fig:temporal_individual_tpt_EXP3} vs \ref{fig:temporal_individual_tpt_OEXP3}).
+No significant conclusions can be drawn for the actions probability profile (\ref{fig:actions_probability_EXP3} vs \ref{fig:actions_probability_OEXP3}), since in EXP3 it appears to be slightly random (recall that different EXP3 simulations may lead to different results).
+Finally, regarding the average throughput experienced per WN, similar "pseudo-randomized" results are obtained (\ref{fig:mean_tpt_EXP3} vs \ref{fig:mean_tpt_OEXP3}).
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_EXP3}
+		\caption{Actions prob. (default)}\label{fig:actions_probability_EXP3}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_OEXP3}
+		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OEXP3}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_CEXP3}
+		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CEXP3}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_EXP3}
+		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_EXP3}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OEXP3}
+		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OEXP3}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CEXP3}
+		\caption{Temp. var.  (sync.  2)}\label{fig:temporal_individual_tpt_CEXP3}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_EXP3}
+		\caption{Mean tpt. (default)}\label{fig:mean_tpt_EXP3}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_OEXP3}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OEXP3}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_CEXP3}
+		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CEXP3}
+	\end{subfigure}
+	\caption{Simulation results in EXP3 (1,000 iterations)}
+	\label{fig:exp3}
+\end{figure*}
 
@@
 
+Figure \ref{fig:ucb} shows several results regarding the application of UCB in the toy scenario (1,000 iterations are considered), both for the fully decentralized and the synchronized approaches.
+Unlike the previous cases, applying the synchronized approach to UCB is counter-productive, since its operational mode is altered by forcing WNs to choose undesired actions.
+As a result, the action-selection strategy is somehow randomized.
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_UCB}
+		\caption{Actions prob. (default)}\label{fig:actions_probability_UCB}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_OUCB}
+		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OUCB}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_CUCB}
+		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CUCB}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_UCB}
+		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_UCB}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OUCB}
+		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OUCB}
+	\end{subfigure}
+		\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CUCB}
+		\caption{Temp. var.  (sync. 2)}\label{fig:temporal_individual_tpt_CUCB}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_UCB}
+		\caption{Mean tpt. (default)}\label{fig:mean_tpt_UCB}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_OUCB}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OUCB}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_CUCB}
+		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CUCB}
+	\end{subfigure}
+	\caption{Simulation results in UCB (1,000 iterations)}
+	\label{fig:ucb}
+\end{figure*}
+
 \subsection{Thompson sampling}
@@
 
-\section{Results - Random Scenario}
-In order to reduce the simulation time, we have considered 1,000 learning iterations, rather than 100,000.
+Figure \ref{fig:ts} shows several results regarding the application of Thompson sampling in the toy scenario (1,000 iterations are considered), both for the fully decentralized and the synchronized approaches.
+In this case, the temporal variability is significantly decreased (\ref{fig:temporal_individual_tpt_TS} vs \ref{fig:temporal_individual_tpt_OTS}).
+In contrast, the actions probability changes for the synchronized approach.
+In this case, some WNs (2 and 3) alternate two between actions.
+As it can be inferred from the temporal variability, one of the actions (the one granting lower performance) is selected until iteration 600 (approximately).
+At that moment, the best performing action (with respect to the adversarial environment) is chosen.
+This phenomena allegedly occurs when near-to-optimal actions are forced to be selected several times during the "static" periods.
+As a result, the algorithm provides high estimates to that actions, which are hard to be overtaken by the actual best-performing ones.
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_TS}
+		\caption{Actions prob. (default)}\label{fig:actions_probability_TS}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_OTS}
+		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OTS}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_CTS}
+		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CTS}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_TS}
+		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_TS}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OTS}
+		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OTS}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CTS}
+		\caption{Temp. var.  (sync. 2)}\label{fig:temporal_individual_tpt_CTS}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_TS}
+		\caption{Mean tpt. (default)}\label{fig:mean_tpt_TS}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_OTS}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OTS}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_CTS}
+		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CTS}
+	\end{subfigure}
+	\caption{Simulation results in Thompson sampling (1,000 iterations)}
+	\label{fig:ts}
+\end{figure*}
+
+\section{Learning with penalties}
+One promising possibility is to explore the effect of applying penalties to the reward, based on the transmit power or the saturation of a given channel (for that, we must know the number of users in each channel).
+Such penalties are not trivial to be derived, and when the problem becomes non-convex, the complexity increases.
+For that, we can provide some evidences about their usefulness when applying pure decentralized learning, but left its proper analysis as future work.
+
+Here are some results for e-greedy when applying a penalty ($\alpha = 0.1$) to the transmit power used. The reward is now computed as:
+\begin{equation}
+	R = \frac{\Gamma}{\Gamma^*} - \alpha (\frac{TxPower}{max(TxPower)})
+\end{equation}
+
+As shown, WNs focus on few actions, which grant highest performance by considering the trade-off between the throughput and the power transmitted.
+
+\begin{figure*}[h!]
+	\centering
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/actions_probability_PEG}
+		\caption{Actions prob. (penalty)}\label{fig:actions_probability_PEG}
+	\end{subfigure}	
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_PEG}
+		\caption{Temp. var.  (penalty)}\label{fig:temporal_individual_tpt_PEG}
+	\end{subfigure}
+	\begin{subfigure}[b]{.3\textwidth}
+		\includegraphics[width=\textwidth]{images/mean_tpt_PEG}
+		\caption{Mean tpt. (penalty)}\label{fig:mean_tpt_PEG}
+	\end{subfigure}
+	\caption{Simulation results in Thompson sampling (1,000 iterations)}
+	\label{fig:ts}
+\end{figure*}
+
+%\section{Results - Random Scenario}
+%In order to reduce the simulation time, we have considered 1,000 learning iterations, rather than 10,000.
+In order to further illustrate the effect of applying synchronized selfish learning, we compare it with the default decentralized approach in the random scenarios.
+In this case, we use the realistic range of actions in both situations.
+As shown in Figure \ref{fig:scalability_sync_vs_async}, the synchronized mechanisms lead to less variability than their default versions (the histogram tends to be narrower for all the cases).
+In contrast, some performance loss can be observed, especially for the UCB algorithm (note that the blue distribution is slightly shifted to the left, with respect to the red one).
+%
+%\begin{figure*}[h!]
+%	\centering
+%	\begin{subfigure}[b]{.4\textwidth}
+%		\includegraphics[width=\textwidth]{images/hist_mean_tpt_2_WNs}
+%		\caption{2 WNs}\label{fig:hist_mean_tpt_2_WNs}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{.4\textwidth}
+%		\includegraphics[width=\textwidth]{images/hist_mean_tpt_4_WNs}
+%		\caption{4 WNs}\label{fig:hist_mean_tpt_4_WNs}
+%	\end{subfigure}\\
+%	\begin{subfigure}[b]{.4\textwidth}
+%		\includegraphics[width=\textwidth]{images/hist_mean_tpt_6_WNs}
+%		\caption{6 WNs}\label{fig:hist_mean_tpt_6_WNs}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{.4\textwidth}
+%		\includegraphics[width=\textwidth]{images/hist_mean_tpt_8_WNs}
+%		\caption{8 WNs}\label{fig:hist_mean_tpt_8_WNs}
+%	\end{subfigure}
+%	\caption{Histogram of the mean throughput experienced by WNs for each algorithm.
+The results are computed from 100 different random scenarios for each of the WNs sizes, where 1,000 learning iterations are considered.
+In red, we have the results for the default algorithms implementation, while blue indicates their synchronized versions.}
+%	\label{fig:scalability_sync_vs_async}
+%\end{figure*}
+%
+%\section{Impact of modifying the range of actions}
+%Here we aim to measure the impact of modifying the range of actions on the performance of the learning algorithms.
+For that, for each of the proposed action-selection strategies, we will compare the following performance measurements in the grid scenario, for different number of available actions: \emph{i)} the mean throughput experienced in average, \emph{ii)} the mean variability experienced in average.
+%
+%Firstly, Figures \ref{fig:impact_num_channels} and \ref{fig:impact_num_channels_on_variability} show the impact of using different number of orthogonal channels for each algorithm.
+As shown in \ref{fig:impact_num_channels}, the mean throughput increases until reaching 4 channels, so that each WN is able to properly access to a single channel.
+Such an ideal case is achieved by Thompson sampling and UCB.
+However, for $\varepsilon$-greedy and EXP3 we notice some performance anomalies when the number of available channels increases.
+Regarding the experienced variability (\ref{fig:impact_num_channels_on_variability}), we observe a peak when the number of channels is 3, situation in which at least two WNs are permanently in conflict, since they are competing for the same channel resources.
+Note that, for the other cases where the number of channels is not enough to accommodate all the WNs, a lower variability is experienced due to the impossibility of achieving a better performance.
+%
+%Secondly, the impact of modifying the available levels of transmit power is shown in both \ref{fig:impact_tx_power_levels_on_throughput} and \ref{fig:impact_tx_power_levels_on_variability}.
+In this case, we use the following sets of transmit power levels:
+%\begin{itemize}
+%	\item Set 1: \{5, 20\} dBm
+%	\item Set 2: \{5, 10, 15, 20\} dBm
+%	\item Set 3: from 2 to 20 dBm in steps of 2 dBm
+%	\item Set 4: from 1 to 20 dBm in steps of 1 dBm
+%\end{itemize}
+%Regarding the throughput experienced (\ref{fig:impact_tx_power_levels_on_throughput}), we notice a very low variability when different sets of transmit power levels are used.
+In contrast, increasing the number of transmission power levels affects to the variability experienced by WNs.
+Such a variability increases in case of UCB and Thompson sampling.
+Different effects are noticed for $\varepsilon$-greedy and EXP3.
+%
+%\begin{figure*}[h!]
+%	\centering
+%	\begin{subfigure}[b]{.4\textwidth}
+%		\includegraphics[width=\textwidth]{images/impact_num_channels}
+%		\caption{Channel impact on the throughput}\label{fig:impact_num_channels}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{.4\textwidth}
+%		\includegraphics[width=\textwidth]{images/impact_num_channels_on_variability}
+%		\caption{Channel impact on the variability}\label{fig:impact_num_channels_on_variability}
+%	\end{subfigure}\\
+%	\begin{subfigure}[b]{.4\textwidth}
+%		\includegraphics[width=\textwidth]{images/impact_tx_power_levels_on_throughput}
+%		\caption{TxPow impact on the throughput}\label{fig:impact_tx_power_levels_on_throughput}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{.4\textwidth}
+%		\includegraphics[width=\textwidth]{images/impact_tx_power_levels_on_variability}
+%		\caption{TxPow impact on the variability}\label{fig:impact_tx_power_levels_on_variability}
+%	\end{subfigure}
+%	\caption{Mean and standard deviation of the throughput experienced in average when using different sets of actions.}
+%	\label{fig:impact_actions}
+%\end{figure*}
 

### 2018-10-12 Code/constants.m

@@ -9,8 +9,8 @@
 %%% ************************************************************************
 
 nWlans = 4;                         % Number of WLANs in the map
-totalIterations = 1000;            % Maximum convergence time (one period implies the participation of all WLANs)
-minimumIterationToConsider = 500;  % Iteration from which to consider the obtained results
+totalIterations = 1000;             % Maximum convergence time (one period implies the participation of all WLANs)
+minimumIterationToConsider = 500;   % Iteration from which to consider the obtained results
 totalScenarios = 100;               % Number of TOTAL repetitions to take the average
 
 % Define the transitory and the permanent intervals of iterations
@@ -19,10 +19,10 @@ permanentInterval = minimumIterationToConsider + 1 : totalIterations;
 
 NOISE_DBM = -100;                   % Floor NOISE_DBM in dBm
 
-nChannels = 2;                      % Number of available channels (from 1 to n_channels)
+nChannels = 3;                      % Number of available channels (from 1 to n_channels)
 channelActions = 1 : nChannels;     % Possible channels
 ccaActions = [-82];                 % CCA levels (dBm)
-txPowerActions = [-15 0 15 30];          % Transmit power levels (dBm)
+txPowerActions = [-15 0 15 30];     % Transmit power levels (dBm)
 
 % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
 possibleActions = 1:(size(channelActions, 2) * ...

### 2018-10-12 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Experiment_1_1_egreedy.m

@@ -39,28 +39,25 @@ wlans = generate_network_3D(nWlans, 'grid', 2, drawMap); % SAFE CONFIGURATION
 upperBoundThroughputPerWlan = compute_max_selfish_throughput( wlans );
 
 load('workspace_throughput_all_combinations_toy_scenario.mat')
-
-% Find the best configuration for each WLAN and display it
-for i = 1 : size(throughputPerConfiguration, 1)
-    agg_tpt(i) = sum(throughputPerConfiguration(i,:));
-    fairness(i) = jains_fairness(throughputPerConfiguration(i,:));
-    prop_fairness(i) = sum(log(throughputPerConfiguration(i,:)));
-    max_min(i) = min(throughputPerConfiguration(i,:));
-end    
-
+% JFI
+[max_f, ix_max_f] = max(jains_fairness(throughputPerConfiguration));
 % Proportional fairness
-[val, ix] = max(prop_fairness);
-max_pf = agg_tpt(ix);    
+[max_pf, ix_max_pf] = max(sum(log(throughputPerConfiguration)'));
+agg_tpt_max_pf = sum(throughputPerConfiguration(ix_max_pf,:));
 % Aggregate throughput
-[max_agg, ix2] = max(agg_tpt);
+[max_agg, ix_max_agg] = max(sum(throughputPerConfiguration'));
 % Max-min throughput
-[max_max_min, ix3] = max(max_min);
+[max_max_min, ix_max_min] = max(min(throughputPerConfiguration'));
 
 % Compute the throughput experienced per WLAN at each iteration
 [tpt_evolution_per_wlan_eg, times_arm_has_been_played_eg, regret_per_wlan_eg , meanRewardPerAction] = ...
     egreedy( wlans, initialEpsilon, upperBoundThroughputPerWlan );
 [tpt_evolution_per_wlan_oeg, times_arm_has_been_played_oeg, regret_per_wlan_oeg] = ...
+    ordered_egreedy( wlans, initialEpsilon, upperBoundThroughputPerWlan );
+[tpt_evolution_per_wlan_ceg, times_arm_has_been_played_ceg, regret_per_wlan_ceg] = ...
     ordered_egreedy_cumulative( wlans, initialEpsilon, upperBoundThroughputPerWlan );
+[tpt_evolution_per_wlan_peg, times_arm_has_been_played_peg, regret_per_wlan_peg] = ...
+    egreedy_with_penalty( wlans, initialEpsilon, upperBoundThroughputPerWlan, 0.1 );
 
[…]

### 2018-10-12 Code/experiments/Part 1 - Toy grid scenario/1.3. UCB/Experiment_1_3_ucb.m

@@ -38,35 +38,30 @@ disp('-----------------------')
 % Generate constants from 'constants.m'
 constants
 
-load('throughput_per_configuration_cochannel_interference_on.mat')
-%load('throughput_per_configuration_cochannel_interference_off.mat')
-% Find the best configuration for each WLAN and display it
-for i = 1 : size(throughputPerConfiguration, 1)
-    agg_tpt(i) = sum(throughputPerConfiguration(i,:));
-    fairness(i) = jains_fairness(throughputPerConfiguration(i,:));
-    prop_fairness(i) = sum(log(throughputPerConfiguration(i,:)));
-    max_min(i) = min(throughputPerConfiguration(i,:));
-end    
-
-% Proportional fairness
-[val, ix] = max(prop_fairness);
-max_pf = agg_tpt(ix);    
-% Aggregate throughput
-[max_agg, ix2] = max(agg_tpt);
-% Max-min throughput
-[max_max_min, ix3] = max(max_min);
-
 % Setup the scenario: generate WLANs and initialize states and actions
 wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
 
 % Compute the maximum achievable throughput per WLAN
 upperBoundThroughputPerWlan = compute_max_selfish_throughput( wlans );
+
+load('workspace_throughput_all_combinations_toy_scenario.mat')
+% JFI
+[max_f, ix_max_f] = max(jains_fairness(throughputPerConfiguration));
+% Proportional fairness
+[max_pf, ix_max_pf] = max(sum(log(throughputPerConfiguration)'));
+agg_tpt_max_pf = sum(throughputPerConfiguration(ix_max_pf,:));
+% Aggregate throughput
+[max_agg, ix_max_agg] = max(sum(throughputPerConfiguration'));
+% Max-min throughput
+[max_max_min, ix_max_min] = max(min(throughputPerConfiguration'));
     
 % Compute the throughput experienced per WLAN at each iteration
 [tpt_evolution_per_wlan_ucb, times_arm_has_been_played_ucb, regret_per_wlan_ucb] = ...
     ucb(wlans, upperBoundThroughputPerWlan);
 [tpt_evolution_per_wlan_oucb, times_arm_has_been_played_oucb, regret_per_wlan_oucb] = ...
     ordered_ucb(wlans, upperBoundThroughputPerWlan);
[…]

### 2018-10-12 Code/experiments/Part 1 - Toy grid scenario/1.4. Thompson sampling/Experiment_1_4_thompson_sampling.m

@@ -38,35 +38,30 @@ disp('-----------------------')
 % Generate constants from 'constants.m'
 constants
 
-load('throughput_per_configuration_cochannel_interference_on.mat')
-%load('throughput_per_configuration_cochannel_interference_off.mat')
-% Find the best configuration for each WLAN and display it
-for i = 1 : size(throughputPerConfiguration, 1)
-    agg_tpt(i) = sum(throughputPerConfiguration(i,:));
-    fairness(i) = jains_fairness(throughputPerConfiguration(i,:));
-    prop_fairness(i) = sum(log(throughputPerConfiguration(i,:)));
-    max_min(i) = min(throughputPerConfiguration(i,:));
-end    
-
-% Proportional fairness
-[val, ix] = max(prop_fairness);
-max_pf = agg_tpt(ix);    
-% Aggregate throughput
-[max_agg, ix2] = max(agg_tpt);
-% Max-min throughput
-[max_max_min, ix3] = max(max_min);
-
 % Setup the scenario: generate WLANs and initialize states and actions
 wlans = generate_network_3D(nWlans, 'grid', 2, 0); % SAFE CONFIGURATION
 
 % Compute the maximum achievable throughput per WLAN
 upperBoundThroughputPerWlan = compute_max_selfish_throughput( wlans );
+
+load('workspace_throughput_all_combinations_toy_scenario.mat')
+% JFI
+[max_f, ix_max_f] = max(jains_fairness(throughputPerConfiguration));
+% Proportional fairness
+[max_pf, ix_max_pf] = max(sum(log(throughputPerConfiguration)'));
+agg_tpt_max_pf = sum(throughputPerConfiguration(ix_max_pf,:));
+% Aggregate throughput
+[max_agg, ix_max_agg] = max(sum(throughputPerConfiguration'));
+% Max-min throughput
+[max_max_min, ix_max_min] = max(min(throughputPerConfiguration'));
     
 % Compute the throughput experienced per WLAN at each iteration
 [tpt_evolution_per_wlan_ts, times_arm_has_been_played_ts, regret_per_wlan_ts] = ...
     thompson_sampling(wlans, upperBoundThroughputPerWlan);
 [tpt_evolution_per_wlan_ots, times_arm_has_been_played_ots, regret_per_wlan_ots] = ...
     ordered_thompson_sampling(wlans, upperBoundThroughputPerWlan);
[…]

### 2018-10-12 Code/experiments/Part 2 - Random scenarios/2.1. Performance Comparison/Experiment_2_0_Performance_Comparison_Random_Network.m

@@ -1,100 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-%%% EXPERIMENT EXPLANATION:
-%%% The script computes the performance of applying e-greedy, EXP3, UCB and
-%%% Thompson sampling in random scenarios. At the end, histograms of the 
-%%% average throughput experienced are displayed for each policy.
-
-%%% This Script generates the output shown in the article:
-%%% - Figure 18
-
-%%
-clc
-clear all
-
-disp('************************************************************************')
-disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
-disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
-disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
-disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
-disp('* GitHub repository:                                                   *')
-disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
-disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
-disp('************************************************************************')
-
-disp('-----------------------')
-disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
-disp('-----------------------')
-
-% Load constants
-%constants
-constants
-% Update the nWlans variable to define an array
-nWlans = [2 4 6 8];
-
-% % Initialize variables to store results:
-% % - Each cell contains the throughput evolution experienced with each policy
[…]

### 2018-10-12 Code/experiments/Part 2 - Random scenarios/2.1. Performance Comparison/Experiment_2_1_Performance_Comparison_Random_Network.m

@@ -1,99 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-%%% EXPERIMENT EXPLANATION:
-%%% The script computes the performance of applying e-greedy, EXP3, UCB and
-%%% Thompson sampling in random scenarios. At the end, histograms of the 
-%%% average throughput experienced are displayed for each policy.
-
-%%% This Script generates the output shown in the article:
-%%% - Figure 18
-
-%%
-clc
-clear all
-
-disp('************************************************************************')
-disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
-disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
-disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
-disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
-disp('* GitHub repository:                                                   *')
-disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
-disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
-disp('************************************************************************')
-
-disp('-----------------------')
-disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
-disp('-----------------------')
-
-% Load constants
-%constants
-constants_more_actions
-% Update the nWlans variable to define an array
-nWlans = [2 4 6 8];
-
-% % Initialize variables to store results:
-% % - Each cell contains the throughput evolution experienced with each policy
[…]

### 2018-10-12 Code/experiments/Part 2 - Random scenarios/2.1. Performance Comparison/Experiment_2_1_scalability_default.m

@@ -1,0 +1,102 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% The script computes the performance of applying e-greedy, EXP3, UCB and
+%%% Thompson sampling in random scenarios. At the end, histograms of the 
+%%% average throughput experienced are displayed for each policy.
+
+%%% This Script generates the output shown in the article:
+%%% - Figure 18
+
+%%
+clc
+clear all
+
+disp('************************************************************************')
+disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
+disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
+disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
+disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
+disp('* GitHub repository:                                                   *')
+disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
+disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
+disp('************************************************************************')
+
+disp('-----------------------')
+disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
+disp('-----------------------')
+
+% Load constants
+%constants
+constants
+% Update the nWlans variable to define an array
+nWlans = [2 4 6 8];
+
+% % Initialize variables to store results:
+% % - Each cell contains the throughput evolution experienced with each policy
[…]

### 2018-10-12 Code/experiments/Part 2 - Random scenarios/2.1. Performance Comparison/Experiment_2_2_Performance_Comparison_Random_Network.m

@@ -1,95 +1,0 @@
-%%% ************************************************************************
-%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
-%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
-%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
-%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
-%%% * GitHub repository:                                                   *
-%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
-%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
-%%% ************************************************************************
-
-%%% EXPERIMENT EXPLANATION:
-%%% The script computes the performance of applying e-greedy, EXP3, UCB and
-%%% Thompson sampling in random scenarios. At the end, histograms of the 
-%%% average throughput experienced are displayed for each policy.
-
-%%% This Script generates the output shown in the article:
-%%% - Figure 18
-
-%%
-clc
-clear all
-
-disp('************************************************************************')
-disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
-disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
-disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
-disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
-disp('* GitHub repository:                                                   *')
-disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
-disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
-disp('************************************************************************')
-
-disp('-----------------------')
-disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
-disp('-----------------------')
-
-% Load constants
-constants_more_actions
-
-% Update the nWlans variable to define an array
-nWlans = [2 4 6 8];
-
-% % Initialize variables to store results:
-% % - Each cell contains the throughput evolution experienced with each policy
[…]

### 2018-10-12 Code/experiments/Part 2 - Random scenarios/2.1. Performance Comparison/Experiment_2_2_scalability_synchronized.m

@@ -1,0 +1,102 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% The script computes the performance of applying e-greedy, EXP3, UCB and
+%%% Thompson sampling in random scenarios. At the end, histograms of the 
+%%% average throughput experienced are displayed for each policy.
+
+%%% This Script generates the output shown in the article:
+%%% - Figure 18
+
+%%
+clc
+clear all
+
+disp('************************************************************************')
+disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
+disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
+disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
+disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
+disp('* GitHub repository:                                                   *')
+disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
+disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
+disp('************************************************************************')
+
+disp('-----------------------')
+disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
+disp('-----------------------')
+
+% Load constants
+constants
+
+% Update the nWlans variable to define an array
+nWlans = [2 4 6 8];
+
+% % Initialize variables to store results:
+% % - Each cell contains the throughput evolution experienced with each policy
[…]

### 2018-10-12 Code/experiments/Part 2 - Random scenarios/2.1. Performance Comparison/Experiment_2_3_scalability_penalties.m

@@ -1,0 +1,104 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+%%% EXPERIMENT EXPLANATION:
+%%% The script computes the performance of applying e-greedy, EXP3, UCB and
+%%% Thompson sampling in random scenarios. At the end, histograms of the 
+%%% average throughput experienced are displayed for each policy.
+
+%%% This Script generates the output shown in the article:
+%%% - Figure 18
+
+%%
+clc
+clear all
+
+disp('************************************************************************')
+disp('* Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *')
+disp('* Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *')
+disp('* Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *')
+disp('* Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *')
+disp('* GitHub repository:                                                   *')
+disp('*   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *')
+disp('* More info on https://www.upf.edu/en/web/fwilhelmi                    *')
+disp('************************************************************************')
+
+disp('-----------------------')
+disp('FINAL COMPARISON: RANDOM SCENARIO & DIFFERENT DENSITIES')
+disp('-----------------------')
+
+% Load constants
+constants_more_actions
+
+% Update the nWlans variable to define an array
+nWlans = [2 4 6 8];
+
+% % Initialize variables to store results:
+% % - Each cell contains the throughput evolution experienced with each policy
[…]

### 2018-10-12 Code/framework_throughput_calculation/auxiliary_methods/display_results_individual_performance.m

@@ -40,7 +40,7 @@ function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan
     mean_agg_tpt_comparison_optimal_entire_simulation = ...
         mean_agg_tpt_entire_simulation / upperBoundAggregatePerformance;
     mean_ind_tpt_comparison_optimal_entire_simulation = ...
-        mean(mean(tptEvolutionPerWlan(1:totalIterations, :),2)) ./ upperBoundThroughputPerWlan;
+        mean(mean(tptEvolutionPerWlan(1:totalIterations, :),2)) ./ upperBoundAggregatePerformance;
     
     % Plot results of the entire simulation
     disp(['------------' newline 'Results (entire simulation):' newline '------------'])
@@ -70,7 +70,7 @@ function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan
             mean_agg_tpt_last_iterations / upperBoundAggregatePerformance;
         % Mean average tpt. / individual throughput (optimal prop. fairness)
         mean_ind_tpt_comparison_optimal_last_iterations = ...
-            mean(mean(tptEvolutionPerWlan(minimumIterationToConsider:totalIterations, :),2)) ./ upperBoundThroughputPerWlan;
+            mean(mean(tptEvolutionPerWlan(minimumIterationToConsider:totalIterations, :),2)) ./ upperBoundAggregatePerformance;
                 
         disp(['------------' newline 'Results (last iterations):' newline '------------'])
 
@@ -109,7 +109,7 @@ function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan
     set(gca,'FontSize', 22)
     xlabel([method_name ' iteration'], 'fontsize', 24)
     ylabel('Network Throughput (Mbps)', 'fontsize', 24)
-    axis([1 totalIterations 0 1.1 * max(upperBoundAggregatePerformance)])    
+    axis([1 totalIterations 0 num_wlans * 1.1 * max(upperBoundAggregatePerformance)])    
     hold on
     h1 = plot(1 : totalIterations, num_wlans * upperBoundAggregatePerformance * ones(1, totalIterations), 'r--', 'linewidth',2);
     %legend(h1, {'Optimal (Max. Prop. Fairness)'});
[…]

### 2018-10-12 Code/reinforcement_learning_methods/Penalties/egreedy_with_penalty.m

@@ -1,0 +1,182 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan, meanRewardPerAction ] = ...
+    egreedy_with_penalty( wlans, initialEpsilon, upperBoundThroughputPerWlan, alpha_penalty, varargin )
+% EGREEDY - Given a WN, applies e-greedy to maximize the experienced throughput
+%
+%   OUTPUT: 
+%       * tptExperiencedByWlan - throughput experienced by each WLAN
+%         for each of the iterations done
+%       * timesArmHasBeenPlayed - times each action has been played
+%   INPUT: 
+%       * wlan - wlan object containing information about all the WLANs
+%       * initialEpsilon - initial exploration coefficient
+
+    load('constants.mat')
+    
+    try
+        if size(varargin, 2) == 3
+            % Update possible actions
+            nChannels = varargin{1};
+            channelActions = 1 : nChannels;
+            ccaActions = varargin{2};
+            txPowerActions = varargin{3};
+            % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
+            possibleActions = 1:(size(channelActions, 2) * ...
+                size(ccaActions, 2) * size(txPowerActions, 2));
+            K = size(possibleActions,2);   % Total number of actions
+            allCombs = allcomb(1:K, 1:K);    
+        end
+    catch
+        if size(varargin, 2) ~= 3
+            disp('Wrong number of input arguments')
+        end
+    end
+    
+    %% INITIALIZE ALGORITHM
[…]

### 2018-10-12 Code/reinforcement_learning_methods/Penalties/thompson_sampling_with_penalty.m

@@ -1,0 +1,182 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
+thompson_sampling( wlans, upperBoundThroughputPerWlan, alpha_penalty, varargin )
+% thompson_sampling applies TS to maximize the experienced
+% throughput of a given scenario
+%
+%   OUTPUT: 
+%       * tptExperiencedByWlan - throughput experienced by each WLAN
+%         for each of the iterations done
+%       * timesArmHasBeenPlayed - times each action has been played
+%   INPUT: 
+%       * wlan - wlan object containing information about all the WLANs
+
+    load('constants.mat')
+    
+    try
+        if size(varargin, 2) == 3
+            % Update possible actions
+            nChannels = varargin{1};
+            channelActions = 1 : nChannels;
+            ccaActions = varargin{2};
+            txPowerActions = varargin{3};
+            % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
+            possibleActions = 1:(size(channelActions, 2) * ...
+                size(ccaActions, 2) * size(txPowerActions, 2));
+            K = size(possibleActions,2);   % Total number of actions
+            allCombs = allcomb(1:K, 1:K);    
+        end 
+    catch
+        if size(varargin, 2) ~= 3
+            disp('Wrong number of input arguments')
+        end
+    end
+    
+    %% INITIALIZE ALGORITHM
+    % Use a copy of wlan to make operations
+    wlansAux = wlans;
[…]

### 2018-10-12 Code/reinforcement_learning_methods/Penalties/ucb_with_penalty.m

@@ -1,0 +1,197 @@
+%%% ************************************************************************
+%%% * Collaborative Spatial Reuse in Wireless Networks via Selfish MABs    *
+%%% * Author: Francesc Wilhelmi (francesc.wilhelmi@upf.edu)                *
+%%% * Co-authors: C. Cano, G. Neu, B. Bellalta, A. Jonsson & S. Barrachina *
+%%% * Copyright (C) 2017-2022, and GNU GPLd, by Francesc Wilhelmi          *
+%%% * GitHub repository:                                                   *
+%%% *   https://github.com/wn-upf/Collaborative_SR_in_WNs_via_Selfish_MABs *
+%%% * More info on https://www.upf.edu/en/web/fwilhelmi                    *
+%%% ************************************************************************
+
+function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
+    ucb( wlans, upperBoundThroughputPerWlan, alpha_penalty, varargin )
+% ucb applies UCB to maximize the experienced throughput of a given scenario
+%
+%   OUTPUT: 
+%       * tptExperiencedByWlan - throughput experienced by each WLAN
+%         for each of the iterations done
+%       * timesArmHasBeenPlayed - times each action has been played
+%   INPUT: 
+%       * wlan - wlan object containing information about all the WLANs
+
+    load('constants.mat')
+    
+    try
+        if size(varargin, 2) == 3
+            % Update possible actions
+            nChannels = varargin{1};
+            channelActions = 1 : nChannels;
+            ccaActions = varargin{2};
+            txPowerActions = varargin{3};
+            % Each state represents an [i,j,k] combination for indexes on "channels", "cca" and "tx_power"
+            possibleActions = 1:(size(channelActions, 2) * ...
+                size(ccaActions, 2) * size(txPowerActions, 2));
+            K = size(possibleActions,2);   % Total number of actions
+            allCombs = allcomb(1:K, 1:K);    
+        end 
+    catch
+        if size(varargin, 2) ~= 3
+            disp('Wrong number of input arguments')
+        end
+    end
+    
+    %% INITIALIZE ALGORITHM
+    % Use a copy of wlan to make operations
+    wlansAux = wlans;
+    nWlans = size(wlansAux, 2);
+
[…]

### 2018-10-12 Code/reinforcement_learning_methods/ordered_exp3.m

@@ -121,9 +121,9 @@ function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan
                         weightsPerArm(wlan_ix_aux, k) = weightsPerArm(wlan_ix_aux, k)^...
                             (eta/previous_eta) * ...
                             exp((eta * estimated_reward(wlan_ix_aux)));
-%                     else
-%                         weightsPerArm(wlan_ix_aux, k) = weightsPerArm(wlan_ix_aux, k)^...
-%                             (eta / previous_eta);
+                    else
+                        weightsPerArm(wlan_ix_aux, k) = weightsPerArm(wlan_ix_aux, k)^...
+                            (eta / previous_eta);
                     end                
                 end
                 % Bound the weight assigned to each arm

### 2018-10-12 Code/reinforcement_learning_methods/ordered_exp3_cumulative.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan] = ...
-    ordered_exp3(wlans, gamma, initialEta, upperBoundThroughputPerWlan, varargin)
+    ordered_exp3_cumulative(wlans, gamma, initialEta, upperBoundThroughputPerWlan, varargin)
 % exp3 applies EXP3 (basic formulation) to maximize the experienced
 % throughput of a given scenario
 %
@@ -66,13 +66,24 @@ function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan
     armsProbabilities = (1/K)*ones(nWlans, K);  % Initialize arms probabilities
     estimated_reward = zeros(1, nWlans);        % Initialize the estimated reward for each WN    
     regretAfterAction = zeros(1, nWlans);       % Initialize the regret experienced by each WLAN
-    eta = initialEta;  % Initialize the learning rate
+    eta = initialEta * ones(1, nWlans);  % Initialize the learning rate
     previous_eta = eta;
+    
+    cumulative_reward = zeros(1, nWlans);
+    iterations_without_acting = ones(1, nWlans);        
+    iteration_per_wlan = zeros(1, nWlans);    
     
     %% ITERATE UNTIL CONVERGENCE OR MAXIMUM CONVERGENCE TIME
     iteration = 1;
+    order = [];
     while(iteration < totalIterations + 1) 
-        wlan_ix = mod(iteration, nWlans) + 1;
+        
+        if isempty(order)
+            order = randperm(nWlans);
+        end        
+        wlan_ix = order(1);
+        order(1) = [];
+        
         % Update arms probabilities according to weights      
         for k = 1 : K
             armsProbabilities(wlan_ix, k) = (1 - gamma) * ...
@@ -99,51 +110,54 @@ function [tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan
         % Compute the reward with the throughput obtained in the round after applying the action
         tptAfterAction = compute_throughput_from_sinr(wlansAux, NOISE_DBM);  % bps    
         % Update the reward of each WN
-        rw = tptAfterAction./upperBoundThroughputPerWlan;         
-        % Store the throughput at the end of the iteration for statistics
-        tptExperiencedPerWlan(iteration, :) = tptAfterAction;
[…]

### 2018-10-12 Code/reinforcement_learning_methods/ordered_thompson_sampling_cumulative.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
-    ordered_thompson_sampling( wlans, upperBoundThroughputPerWlan, varargin )
+    ordered_thompson_sampling_cumulative( wlans, upperBoundThroughputPerWlan, varargin )
 % thompson_sampling applies TS to maximize the experienced
 % throughput of a given scenario
 %
@@ -64,11 +64,20 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
     cumulativeRewardPerWlan = zeros(nWlans, K);     % Initialize the cumulative reward obtained by each WLAN for each arm
     meanRewardPerWlan = zeros(nWlans, K);           % Initialize the mean reward obtained by each WLAN for each arm
     estimatedRewardPerWlan = zeros(nWlans, K);      % Initialize the mean reward obtained by each WLAN for each arm
-             
+    
+    cumulative_reward = zeros(1, nWlans);
+    iterations_without_acting = ones(1, nWlans);        
+    iteration_per_wlan = zeros(1, nWlans);    
+    
     %% ITERATE UNTIL CONVERGENCE OR MAXIMUM CONVERGENCE TIME  
     iteration = 1;
+    order = [];
     while(iteration < totalIterations + 1)    
-        wlan_ix = mod(iteration, nWlans) + 1;
+        if isempty(order)
+            order = randperm(nWlans);
+        end        
+        wlan_ix = order(1);
+        order(1) = [];
         % Select an action according to the policy
         selectedArm(wlan_ix) = select_action_ts(estimatedRewardPerWlan(wlan_ix, :), ...
             timesArmHasBeenPlayed(wlan_ix, :));  
@@ -90,20 +99,23 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
         % Compute the reward with the throughput obtained in the round after applying the action
         tptAfterAction = compute_throughput_from_sinr(wlansAux, NOISE_DBM);  % bps  
         % Update the reward of each WN
[…]

### 2018-10-12 Code/reinforcement_learning_methods/ordered_ucb_cumulative.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
-    ordered_ucb( wlans, upperBoundThroughputPerWlan, varargin )
+    ordered_ucb_cumulative( wlans, upperBoundThroughputPerWlan, varargin )
 % ucb applies UCB to maximize the experienced throughput of a given scenario
 %
 %   OUTPUT: 
@@ -62,9 +62,11 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
     transitionsCounter = zeros(nWlans, K^2);
     cumulativeRewardPerWlanPerArm = zeros(nWlans, K);     % Initialize the cumulative reward obtained by each WLAN for each arm
     meanRewardPerWlanPerArm = zeros(nWlans, K);           % Initialize the mean reward obtained by each WLAN for each arm
-   % Initialize the regret experienced by each WLAN
-    regretAfterAction = zeros(1, nWlans);     
 
+    cumulative_reward = zeros(1, nWlans);
+    iterations_without_acting = ones(1, nWlans);        
+    iteration_per_wlan = zeros(1, nWlans);    
+    
     %% INITIALIZE THE PAYOFF OF EACH ARM        
     iteration = 1;    
     %disp(['WLAN ' num2str(w)])
@@ -92,9 +94,16 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
         iteration = iteration + 1;
     end 
         
-    %% ITERATE UNTIL CONVERGENCE OR MAXIMUM CONVERGENCE TIME     
+    %% ITERATE UNTIL CONVERGENCE OR MAXIMUM CONVERGENCE TIME  
+    order = [];
     while(iteration < totalIterations + 1) 
-        wlan_ix = mod(iteration, nWlans) + 1;
+        
+        if isempty(order)
+            order = randperm(nWlans);
+        end        
+        wlan_ix = order(1);
+        order(1) = [];
+        
         % Select an action according to the policy
         selectedArm(wlan_ix) = select_action_ucb(meanRewardPerWlanPerArm(wlan_ix,:), ...
             iteration, timesArmHasBeenPlayed(wlan_ix,:));   
[…]

### 2018-10-12 Code/reinforcement_learning_methods/ucb.m

@@ -47,10 +47,10 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
 
     % Find the index of the initial action taken by each WLAN
     initialActionIxPerWlan = zeros(1, nWlans);
-    for w = 1 : nWlans
-        [~,indexCca] = find(ccaActions==wlansAux(w).CCA);
-        [~,indexTpc] = find(txPowerActions==wlansAux(w).TxPower);
-        initialActionIxPerWlan(w) = indexes2val(wlansAux(w).Channel, ...
+    for wlan_i = 1 : nWlans
+        [~,indexCca] = find(ccaActions==wlansAux(wlan_i).CCA);
+        [~,indexTpc] = find(txPowerActions==wlansAux(wlan_i).TxPower);
+        initialActionIxPerWlan(wlan_i) = indexes2val(wlansAux(wlan_i).Channel, ...
             indexCca, indexTpc, size(channelActions,2), size(ccaActions,2));
     end
     
@@ -70,26 +70,26 @@ function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWla
     
     %disp(['WLAN ' num2str(w)])
     order_actions = zeros(nWlans, K);
-    for w = 1 : nWlans
-        order_actions(w, :) = randperm(K); 
+    for wlan_i = 1 : nWlans
+        order_actions(wlan_i, :) = randperm(K); 
     end
     
     % for each action k in K 
     for k = 1 : K       
         % for each WLAN w in nWlans
-        for w = 1 : nWlans   
-            selectedArm(w) = order_actions(w,k);
-            [a, ~, c] = val2indexes(selectedArm(w), size(channelActions,2), size(ccaActions,2), size(txPowerActions,2));
-            wlansAux(w).Channel = a;   
-            wlansAux(w).TxPower = txPowerActions(c);              
+        for wlan_i = 1 : nWlans   
+            selectedArm(wlan_i) = order_actions(wlan_i,k);
+            [a, ~, c] = val2indexes(selectedArm(wlan_i), size(channelActions,2), size(ccaActions,2), size(txPowerActions,2));
+            wlansAux(wlan_i).Channel = a;   
+            wlansAux(wlan_i).TxPower = txPowerActions(c);              
         end
         tptAfterAction = compute_throughput_from_sinr(wlansAux, NOISE_DBM);  % bps  
[…]

### 2018-10-15 Ordered Learning/ordered_learning.tex
New results toy scenario + start implementing dynamic scenarios

@@
 
-Two important implications are derived from the abovementioned mechanism: \emph{i)} the action-selection strategy of the learning algorithms are modified, \emph{ii)} the adversarial setting changes, so that the performance of every chosen action is potentially evaluated in a larger set of situations.
+Two important implications are derived from the abovementioned mechanism: \emph{i)} the action-selection strategies of the learning algorithms are modified, \emph{ii)} the adversarial setting changes, so that the performance of every chosen action is potentially evaluated in a larger set of situations.
 According to the latter, a higher level of valuable knowledge is more likely to be provided to each arm.
@@
 		\includegraphics[width=\textwidth]{images/actions_probability_EG}
-		\caption{Actions prob. (default)}\label{fig:actions_probability_EG}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/actions_probability_OEG}
-		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OEG}
+		\caption{Actions prob. (default)}\label{fig:hist_actions_EG}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{images/actions_probability_CEG}
-		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CEG}
+		\caption{Actions prob. (sync.)}\label{fig:hist_actions_CEG}
 	\end{subfigure}\\
@@
 	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OEG}
-		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OEG}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
 		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CEG}
-		\caption{Temp. var.  (sync. 2)}\label{fig:temporal_individual_tpt_CEG}
+		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_CEG}
 	\end{subfigure}\\
@@
 	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/mean_tpt_OEG}
-		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OEG}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
 		\includegraphics[width=\textwidth]{images/mean_tpt_CEG}
-		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CEG}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_CEG}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{images/actions_probability_EXP3}
-		\caption{Actions prob. (default)}\label{fig:actions_probability_EXP3}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/actions_probability_OEXP3}
-		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OEXP3}
+		\caption{Actions prob. (default)}\label{fig:hist_actions_EXP3}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{images/actions_probability_CEXP3}
-		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CEXP3}
+		\caption{Actions prob. (sync.)}\label{fig:hist_actions_CEXP3}
 	\end{subfigure}\\
@@
 	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OEXP3}
-		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OEXP3}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
 		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CEXP3}
-		\caption{Temp. var.  (sync.  2)}\label{fig:temporal_individual_tpt_CEXP3}
+		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_CEXP3}
 	\end{subfigure}\\
@@
 	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/mean_tpt_OEXP3}
-		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OEXP3}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
 		\includegraphics[width=\textwidth]{images/mean_tpt_CEXP3}
-		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CEXP3}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_CEXP3}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{images/actions_probability_UCB}
-		\caption{Actions prob. (default)}\label{fig:actions_probability_UCB}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/actions_probability_OUCB}
-		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OUCB}
+		\caption{Actions prob. (default)}\label{fig:hist_actions_UCB}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{images/actions_probability_CUCB}
-		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CUCB}
+		\caption{Actions prob. (sync.)}\label{fig:hist_actions_CUCB}
 	\end{subfigure}\\
@@
 	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OUCB}
-		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OUCB}
-	\end{subfigure}
-		\begin{subfigure}[b]{.3\textwidth}
 		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CUCB}
-		\caption{Temp. var.  (sync. 2)}\label{fig:temporal_individual_tpt_CUCB}
+		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_CUCB}
 	\end{subfigure}\\
@@
 	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/mean_tpt_OUCB}
-		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OUCB}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
 		\includegraphics[width=\textwidth]{images/mean_tpt_CUCB}
-		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CUCB}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_CUCB}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{images/actions_probability_TS}
-		\caption{Actions prob. (default)}\label{fig:actions_probability_TS}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/actions_probability_OTS}
-		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OTS}
+		\caption{Actions prob. (default)}\label{fig:hist_actions_TS}
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{images/actions_probability_CTS}
-		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CTS}
+		\caption{Actions prob. (sync.)}\label{fig:hist_actions_CTS}
 	\end{subfigure}\\
@@
 	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OTS}
-		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OTS}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
 		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CTS}
-		\caption{Temp. var.  (sync. 2)}\label{fig:temporal_individual_tpt_CTS}
+		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_CTS}
 	\end{subfigure}\\
@@
 	\begin{subfigure}[b]{.3\textwidth}
-		\includegraphics[width=\textwidth]{images/mean_tpt_OTS}
-		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OTS}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
 		\includegraphics[width=\textwidth]{images/mean_tpt_CTS}
-		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CTS}
+		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_CTS}
 	\end{subfigure}
@@
 
-\section{Learning with penalties}
+\section{Learning with penalties (OPTIONAL)}
 One promising possibility is to explore the effect of applying penalties to the reward, based on the transmit power or the saturation of a given channel (for that, we must know the number of users in each channel).

### 2018-10-15 Code/experiments/Part 1 - Toy grid scenario/1.1. e-greedy/Experiment_1_1_egreedy.m

@@ -38,7 +38,7 @@ wlans = generate_network_3D(nWlans, 'grid', 2, drawMap); % SAFE CONFIGURATION
 % Compute the maximum achievable throughput per WLAN
 upperBoundThroughputPerWlan = compute_max_selfish_throughput( wlans );
 
-load('workspace_throughput_all_combinations_toy_scenario.mat')
+load('workspace_throughput_all_combinations.mat')
 % JFI
 [max_f, ix_max_f] = max(jains_fairness(throughputPerConfiguration));
 % Proportional fairness
@@ -52,23 +52,23 @@ agg_tpt_max_pf = sum(throughputPerConfiguration(ix_max_pf,:));
 % Compute the throughput experienced per WLAN at each iteration
 [tpt_evolution_per_wlan_eg, times_arm_has_been_played_eg, regret_per_wlan_eg , meanRewardPerAction] = ...
     egreedy( wlans, initialEpsilon, upperBoundThroughputPerWlan );
-[tpt_evolution_per_wlan_oeg, times_arm_has_been_played_oeg, regret_per_wlan_oeg] = ...
-    ordered_egreedy( wlans, initialEpsilon, upperBoundThroughputPerWlan );
+% [tpt_evolution_per_wlan_oeg, times_arm_has_been_played_oeg, regret_per_wlan_oeg] = ...
+%     ordered_egreedy( wlans, initialEpsilon, upperBoundThroughputPerWlan );
 [tpt_evolution_per_wlan_ceg, times_arm_has_been_played_ceg, regret_per_wlan_ceg] = ...
     ordered_egreedy_cumulative( wlans, initialEpsilon, upperBoundThroughputPerWlan );
-[tpt_evolution_per_wlan_peg, times_arm_has_been_played_peg, regret_per_wlan_peg] = ...
-    egreedy_with_penalty( wlans, initialEpsilon, upperBoundThroughputPerWlan, 0.1 );
+% [tpt_evolution_per_wlan_peg, times_arm_has_been_played_peg, regret_per_wlan_peg] = ...
+%     egreedy_with_penalty( wlans, initialEpsilon, upperBoundThroughputPerWlan, 0.1 );
 
 % Plot the results
 if plotResults
     display_results_individual_performance(wlans, tpt_evolution_per_wlan_eg, ...
-        times_arm_has_been_played_eg, upperBoundThroughputPerWlan, max_max_min, 'EG');
-    display_results_individual_performance(wlans, tpt_evolution_per_wlan_oeg, ...
[…]

### 2018-10-15 Code/experiments/Part 1 - Toy grid scenario/1.2. EXP3/Tuning parameters/Experiment_1_2_0_0_EXP3_find_best_eta_2_channels.m

@@ -135,4 +135,5 @@ axis([min(initialEta) max(initialEta) 0 1.1 * agg_tpt_max_pf])
 xticks(initialEta)
 legend({'Mean agg. throughput', 'Optimal (max. prop. fairness)'})
 
-save('./Output/exp3_exp1_workspace.mat')
+% Save the workspace
+save('simulation_1_2_0_workspace.mat')

### 2018-10-15 Code/experiments/Part 1 - Toy grid scenario/PLOT_RESULTS_PART_1.m

@@ -41,156 +41,167 @@ load('simulation_1_2_workspace.mat');
 load('simulation_1_3_workspace.mat');
 load('simulation_1_4_workspace.mat');
 
-num_wlans = 4;
+load('workspace_throughput_all_combinations.mat')
+% JFI
+[max_f, ix_max_f] = max(jains_fairness(throughputPerConfiguration));
+% Proportional fairness
+[max_pf, ix_max_pf] = max(sum(log(throughputPerConfiguration)'));
+agg_tpt_max_pf = sum(throughputPerConfiguration(ix_max_pf,:));
+% Aggregate throughput
+[max_agg, ix_max_agg] = max(sum(throughputPerConfiguration'));
+% Max-min throughput
+[max_max_min, ix_max_min] = max(min(throughputPerConfiguration'));
+
+nWlans = 4;
 
 % e-greedy
 permanent_throughput_egreedy = tpt_evolution_per_wlan_eg(permanentInterval, :);
 mean_tpt_per_wlan_egreedy = mean(permanent_throughput_egreedy);
 std_per_wlan_egreedy = std(permanent_throughput_egreedy);
 % ordered e-greedy
-permanent_throughput_oegreedy = tpt_evolution_per_wlan_oeg(permanentInterval, :);
-mean_tpt_per_wlan_oegreedy = mean(permanent_throughput_oegreedy);
-std_per_wlan_oegreedy = std(permanent_throughput_oegreedy);
+permanent_throughput_cegreedy = tpt_evolution_per_wlan_ceg(permanentInterval, :);
+mean_tpt_per_wlan_cegreedy = mean(permanent_throughput_cegreedy);
+std_per_wlan_cegreedy = std(permanent_throughput_cegreedy);
 
 % EXP3
 permanent_throughput_exp3 = tpt_evolution_per_wlan_exp3(permanentInterval, :);
 mean_tpt_per_wlan_exp3 = mean(permanent_throughput_exp3);
 std_per_wlan_exp3 = std(permanent_throughput_exp3);
 % ordered EXP3
-permanent_throughput_oexp3 = tpt_evolution_per_wlan_oexp3(permanentInterval, :);
-mean_tpt_per_wlan_oexp3 = mean(permanent_throughput_oexp3);
[…]

### 2018-10-15 Code/framework_throughput_calculation/auxiliary_methods/display_results_individual_performance.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan, ...
-    timesArmHasBeenPlayed, upperBoundThroughputPerWlan, upperBoundAggregatePerformance, method_name )
+    timesArmHasBeenPlayed, maxIndividualPerformance, maxAggregatePerformance, method_name )
 % display_results_individual_performance displays the results of experiments for
 % individual performance of each policy (e.g., "Experiment_2_1_individual_performance_EG_parameters_4_WN.m")
 %   INPUT: 
@@ -38,9 +38,9 @@ function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan
     mean_fairness_entire_simulation = mean(jains_fairness(tptEvolutionPerWlan(1:totalIterations, :)));
     mean_prop_fairness_entire_simulation = mean(sum(log(tptEvolutionPerWlan(1:totalIterations, :)),2));
     mean_agg_tpt_comparison_optimal_entire_simulation = ...
-        mean_agg_tpt_entire_simulation / upperBoundAggregatePerformance;
+        mean_agg_tpt_entire_simulation / maxAggregatePerformance;
     mean_ind_tpt_comparison_optimal_entire_simulation = ...
-        mean(mean(tptEvolutionPerWlan(1:totalIterations, :),2)) ./ upperBoundAggregatePerformance;
+        mean(mean(tptEvolutionPerWlan(1:totalIterations, :),2)) ./ maxAggregatePerformance;
     
     % Plot results of the entire simulation
     disp(['------------' newline 'Results (entire simulation):' newline '------------'])
@@ -67,10 +67,10 @@ function [] = display_results_individual_performance( wlans, tptEvolutionPerWlan
         mean_prop_fairness_last_iterations = mean(sum(log(tptEvolutionPerWlan(minimumIterationToConsider:totalIterations, :)),2));
         % Mean aggregate tpt. / Aggregate throughput (optimal prop. fairness)
         mean_agg_tpt_comparison_optimal_last_iterations = ...
-            mean_agg_tpt_last_iterations / upperBoundAggregatePerformance;
[…]

### 2018-10-15 Code/reinforcement_learning_methods/Penalties/ucb_with_penalty.m

@@ -9,7 +9,7 @@
 %%% ************************************************************************
 
 function [ tptExperiencedPerWlan, timesArmHasBeenPlayed, regretExperiencedPerWlan ] = ...
-    ucb( wlans, upperBoundThroughputPerWlan, alpha_penalty, varargin )
+    ucb_with_penalty( wlans, upperBoundThroughputPerWlan, alpha_penalty, varargin )
 % ucb applies UCB to maximize the experienced throughput of a given scenario
 %
 %   OUTPUT: 

### 2018-11-13 Article - LaTeX files/collaborative_spatial_reuse_via_mabs.tex
Added authors biographies and photos.
Version submitted on 13th, November 2018. Includes the new version of the manuscript and the response letter.

@@
 \makesavenoteenv{tabular}
+\usepackage[utf8]{inputenc}
 
@@
 
-\journal{Computer Networks}
+\journal{Ad-hoc Networks}
 
@@
 		\author[label1]{Sergio~Barrachina-Mu\~noz}
-\address[label1]{Wireless Networking Research Group (WN-UPF), 08002 Barcelona, Spain}
+		\address[label1]{Wireless Networking Research Group (WN-UPF), 08018 Barcelona, Spain}
 		\address[label2]{Wireless Networks Research Group (WINE-UOC), 08860 Castelldefels (Barelona), Spain}
-\address[label3]{Artificial Intelligence and Machine Learning Research Group (AIML-UPF), 08002 Barcelona, Spain}
+		\address[label3]{Artificial Intelligence and Machine Learning Research Group (AIML-UPF), 08018 Barcelona, Spain}
 
@@
 To solve this, we envision the utilization of completely decentralized mechanisms to enable Spatial Reuse (SR).
-In particular, we concentrate in Reinforcement Learning (RL), and more specifically, in Multi-Armed Bandits (MABs), to allow networks to modify both their transmission power and channel based on their experienced throughput.
-In this work, we study the exploration-exploitation trade-off by means of the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling action-selection strategies.
-Our results show that optimal proportional fairness can be achieved, even if no information about neighboring networks is available to the learners and WNs operate selfishly.
-However, there is high temporal variability in the throughput experienced by the individual networks, specially for $\varepsilon$-greedy and EXP3.
-We identify the cause of this variability to be the adversarial setting of our setup in which the set of most played actions provide intermittent good/poor performance depending on the neighboring decisions.
-We also show that this variability is reduced using UCB and Thompson sampling, which are parameter-free policies that perform exploration according to the reward distribution of each action.
+\textcolor{blue}{In particular, we focus on dynamic channel selection and Transmission Power Control (TPC).
+We rely on Reinforcement Learning (RL), and more specifically on Multi-Armed Bandits (MABs), to allow networks to learn their best configuration}.
+In this work, we study the exploration-exploitation trade-off by means of the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling action-selection, and compare their performance.
+\textcolor{blue}{In addition, we study the implications of selecting actions simultaneously in an adversarial setting \textcolor{blue}{(i.e., concurrently)}, \textcolor{blue}{and compare it with a sequential approach}.} Our results show that optimal proportional fairness can be achieved, even when no information about neighboring networks is available to the learners and Wireless Networks (WNs) operate selfishly.
+However, there is high temporal variability in the throughput experienced by the individual networks, especially for $\varepsilon$-greedy and EXP3.
+\textcolor{blue}{These strategies, contrary to UCB and Thompson sampling, base their operation on the absolute experienced reward, rather than on its distribution.} We identify the cause of this variability to be the adversarial setting of our setup in which the set of most played actions provide intermittent good/poor performance depending on the neighboring decisions.
+\textcolor{blue}{We also show that \textcolor{blue}{learning sequentially, even if using a selfish strategy,} contributes to minimize this variability.
+\textcolor{blue}{The sequential approach is therefore shown to effectively deal with the challenges posed by the adversarial settings that are typically found in decentralized WNs.}}% The latter} are parameter-free policies that perform exploration according to the reward distribution of each action.
 		\end{abstract}
@@
 		\begin{keyword}
-High-Density Wireless Networks, Interference, Decentralized learning, Multi Armed Bandits, Spatial Reuse, Resource Allocation.
+			High-Density Wireless Networks; Spatial Reuse; Resource Allocation; Decentralized learning; Multi-Armed Bandits 
 		\end{keyword}
@@
 	Due to the growing popularity of wireless deployments, especially the ones based on the IEEE 802.11 standard (i.e., Wi-Fi), it is very common to find independent overlapping Wireless Networks (WNs) sharing the same channel resources.
-Due to the decentralized nature of such kind of deployments, the lack of organization and/or agreement on sharing policies leads to inefficient resources allocation, both in spectral and spatial domains.
-An illustrative example about the inefficiency noticed in WNs regarding channel sharing can be found in \cite{akella2007self}, where the authors show that the power level used by wireless devices is typically set, by default, to the maximum, regardless of the distance between communicating nodes, and of the channel occupancy \cite{akella2007self}.
-In decentralized environments, providing a model to obtain the optimal solution can be extremely complex.
-In WNs, the interactions between devices depend on many features (such as position, environment, transmit power) and are hard to derive.
-On top of this, network dynamics, in terms of user arrivals and departures, makes the resource allocation problem even harder.
-
-In order to address the SR problem in decentralized WNs, we focus attention on Reinforcement Learning (RL), which has recently become very popular to solve many well-known problems in wireless communications.
-Some examples can be found for packet routing \cite{littman1993distributed}, Access Point (AP) selection \cite{bojovic2011supervised, bojovic2012neural}, optimal rate sampling \cite{combes2014optimal}, or energy harvesting in heterogeneous networks \cite{miozzo2015distributed}.
-Using online learning, a learner (or agent) obtains data in a sequential order and uses it to predict future good-performing actions.
-Online learning is, therefore, useful to cope with complex and dynamic environments.
+\textcolor{blue}{The decentralized nature of such kind of deployments leads to a significant lack of organization and/or agreement on sharing policies.
+As a result, resources are typically used inefficiently.
+An illustrative example of this can be found in \cite{akella2007self}, where the authors show that the power level used by wireless devices is typically set, by default, to the maximum, regardless of the distance between communicating nodes, and the channel occupancy.
+Consequently, increasing the capacity of such networks has become very challenging.}
+
+	\textcolor{blue}{Wireless networks operate in three main domains: time, frequency and space.
+While the first two have been largely exploited, the spatial domain still shows plenty of room for improvement.
+According to \cite{alawieh2009improving}, Spatial Reuse (SR) can be addressed by means of Transmission Power Control (TPC), Carrier Sense Threshold (CST) adjustment, rate adaptation (related to power control), and directional transmissions.
+In addition, interference cancellation can play a key role on spectral efficiency optimization \cite{miridakis2013survey}.
+On one side, TPC and CST adjustment aim at increasing spectral efficiency omnidirectionally.
+On the other hand, beamforming is meant for directional transmissions.
+Both beamforming and interference cancellation can be categorized as multiple antenna strategies.
+While the former allows to reduce the interference levels, the second one is useful to perform multiple simultaneous transmissions.}
+
+	\textcolor{blue}{In this work, we focus on Dynamic Channel Allocation (DCA) and TPC to address the decentralized SR problem.
+A proper frequency planning allows to reduce the interference between wireless devices, and tuning the transmit power adds an extra level of SR that can result in improved throughput and fairness.
+The application of TPC and DCA is particularly challenging by itself.
+The interactions among devices depend on many features (such as position, environment or transmit power) and are hard to derive.
+%On top of this, user arrivals and departures make the resource allocation problem even harder.
+		Including beamforming and/or interference cancellation techniques \cite{dovelos2018breaking}, on the other hand, requires first a clear understanding of TCP and DCA performance alone, and is therefore left as future work.}
+
+	\textcolor{blue}{Motivated by these challenges,} we focus attention on Reinforcement Learning (RL), which has recently emerged as a very popular method to solve many well-known problems in wireless communications.
+\textcolor{blue}{RL allows to reduce the complexity generated in wireless environments by finding practical solutions.
+By applying RL, optimal (or near-to-optimal) solutions can be obtained without having a full understanding on the problem in advance.
+So, one of the main goals of this paper is to show its feasibility for the decentralized SR problem.} Some RL-based applications can be found for packet routing \cite{littman1993distributed}, Access Point (AP) selection \cite{bojovic2011supervised, bojovic2012neural}, optimal rate sampling \cite{combes2014optimal}, or energy harvesting in heterogeneous networks \cite{miozzo2015distributed}.
+All these applications make use of online learning, where a learner (or agent) obtains data periodically and uses it to predict future good-performing actions.
+Online learning is particularly useful to cope with complex and dynamic environments.
 This background encourages us to approach a solution for the decentralized SR problem in WNs through online learning techniques.
-In particular, we exploit dynamic channel selection and transmit power adjustment for dealing with the performance issues resulting from uncoordinated resource sharing in WNs.
-While a proper frequency planning allows to reduce the interference between wireless devices, tuning the transmit power adds an extra level of SR that can result in improved throughput and fairness.
-
-From the family of online algorithms, we propose the utilization of Multi-Armed Bandits (MABs) \cite{BCB12}, which is a well-known model in the online learning literature for solving resource allocation problems.
+
+	From the family of online algorithms, we \textcolor{blue}{are interested on analyzing the performance of} Multi-Armed Bandits (MABs) \cite{BCB12} \textcolor{blue}{when applied to WNs.
+The MAB model is well-known} in the online learning literature for solving resource allocation problems.
 In MABs, a given agent seeks to learn a hidden reward distribution while maximizing the gains.
 This is known as the exploration-exploitation trade-off.
-%(exploitation focuses on obtaining the maximum instantaneous reward, while exploration aims to maximize the long-term reward)
-While exploitation selects actions with the goal of maximizing long-term reward given the current estimate, exploration selects actions with the goal of improving the estimate.
-Unlike for classical RL, MABs do not consider states\footnote{A state refers to a particular situation experienced by a given agent, which is defined by a set of conditions.
-By having an accurate knowledge on its current situation, an agent can define state-specific strategies that maximize its profits.} in general, which can be hard to define for the decentralized SR problem.
-On the one hand, spatial interference cannot be binary treated, thus leading to complex interactions between nodes.
-On the other hand, the adversarial setting unleashed by decentralized deployments increases the system complexity, since the state not only depends on the actions taken by a given node, but also on the adversaries behavior.
-
-This work extends our previous results presented in \cite{wilhelmi2017implications}, which were obtained by applying a stateless variation of Q-learning to the SR problem in WNs.
-Here we generalize the contributions done by implementing several action-selection strategies to allow WNs choose the channel and transmit power to use based on the resulting performance.
-In this paper, then, we provide a tutorial-based application of MABs to the decentralized SR problem, in order to maximize performance while observing the result from using different SR settings.
-According to that, we aim to illustrate the main benefits and drawbacks of applying different well-known learning techniques in a selfish way, i.e., independent WNs base their strategy on their own experienced performance.
-On the one hand, we evaluate the impact of varying parameters intrinsic to the proposed algorithms on the resulting throughput and fairness.
-In addition, we analyze the effects of learning selfishly, in order to shed some light on the future of decentralized approaches.
-Notably, we observe that even though players act selfishly, there are algorithms %learn to play collaborative actions
-learn to play actions that enhance the overall performance, some times at the cost of high temporal variability.
-Considering selfish WNs and still obtaining collaborative behaviors is appealing to typical chaotic and dynamic deployments as we get rid of the need for message passing, or inference of neighboring conditions.
-
-The main contributions of this work are summarized below:
+Exploitation is meant to maximize the long-term reward given the current estimate, and exploration aims to improve the estimate.
+Unlike classical RL, MABs do not consider states\footnote{A state refers to a particular situation experienced by a given agent, which is defined by a set of conditions.
+By having an accurate knowledge of its current situation, an agent can define state-specific strategies that maximize its profits.} in general, which can be hard to define for the decentralized SR problem presented in this work.
+On the one hand, spatial interference cannot be binary treated, thus leading to complex interactions among nodes.
+On the other hand, the adversarial setting unleashed by decentralized deployments increases the system complexity.
+Therefore, the obtained reward does not only depends on the actions taken by a given node, but also on the adversaries behavior.
+
+	\textcolor{blue}{This article extends our previous results presented in \cite{wilhelmi2017implications}.
+Here we generalize the contributions done by implementing several action-selection strategies to find the best combination of frequency channel and transmit power in WNs.
+These strategies are applied to the decentralized SR problem, where independent WNs learn selfishly, based on their own experienced performance.} On the one hand, we evaluate the impact of varying parameters intrinsic to the proposed algorithms on the resulting throughput and fairness.
+In addition, we analyze the effects of learning selfishly, and shed light on the future of decentralized approaches.
+Notably, we observe that even though players act selfishly, some of the algorithms learn to play actions that enhance the overall performance, some times at the cost of high temporal variability.
+Considering selfish WNs and still obtaining collaborative behaviors is appealing to typical chaotic and dynamic deployments.
+\textcolor{blue}{Finally, the adversarial setting in WNs is studied under two learning implementations: namely \textit{concurrent} and \textit{sequential}.
+Both procedures rule the operation followed by learners (based on the proposed action-selection strategies).
+In particular, WNs select an action at the same time for the concurrent approach.
+In contrast, an ordered action-selection procedure is followed for the sequential case.
+We study the performance of the aforementioned techniques in terms of convergence speed, average throughput and variability.} The main contributions of this work are summarized below:
 	\begin{itemize}		
@@
 		\item We study the impact of different parameters intrinsic to the action-selection strategies considered (e.g., exploration coefficients, learning rates) on network performance.
-	\item We show that there are algorithms learn to play collaborative actions even though the WNs act selfishly, which is appealing to practical application in chaotic and dynamic environments.
-In addition, we shed some light on the root causes of this phenomena.
+\textcolor{blue}{In addition, we analyze the implications derived from the application of different learning procedures, referred to as \textit{concurrent} and \textit{sequential}, which rule the moment at which WNs act.}
+		\item \textcolor{blue}{We show the impact of learning concurrently and sequentially.
+In particular, the former leads to a high throughput variability experienced by WNs, which is significantly reduced by the sequential approach.} \textcolor{blue}{Accordingly, we envision the utilization of sequential approaches to achieve decentralized learning in adversarial wireless networks.}
+		\item Finally, we show that there are algorithms that learn to play collaborative actions even though the WNs act selfishly, which is appealing to practical application in chaotic and dynamic environments.
+In addition, we shed light on the root causes of this phenomena.
 	\end{itemize}
@@
 The simulation results are later presented in Section \ref{section:performance_evaluation}.
-Finally, Section \ref{section:conclusions} provides some final remarks.
+Finally, Section \ref{section:conclusions} provides the final remarks.
 
@@
 	\label{section:related_work}
-In this paper we approach the decentralized SR problem through Dynamic Channel Allocation (DCA) and Transmit Power Control (TPC).
-While the former aims to allocate the available frequency range among potentially overlapping WNs, the latter attempts to increase the number of parallel transmissions by adjusting the power transmitted by each WN.
-While DCA operates at the frequency level, TPC deals with more complex spatial interactions.
-For that, an approach that dynamically tunes the transmit power may severely affect higher communication layers such as network (routing) or transport (congestion).
-TPC directly affects the transmission range, the data rate and the energy consumption, and it may create unidirectional links that unleash fairness issues.
-In fact, acknowledgments (ACKs) and RTS/CTS frames assume bidirectionality.
-
-DCA has been extensively exploited from the centralized perspective, especially through techniques based on graph coloring \cite{riihijarvi2005frequency, mishra2005weighted}.
+
+	\textcolor{blue}{Decentralized SR has been considerably studied by the wireless research community.
+The authors in \cite{argyriou2010collision} propose using relay nodes to re-transmit packets lost as a result of a collision.
+The relay node is able to decode different signals from the environment and to detect if a collision took place.
+Then, with the aim of improving the re-transmissions operation, it benefits from the current transmission to forward the decoded packets to their original destinations.
+Although this method shows performance improvements in dense scenarios where collisions are very likely to occur, its effectiveness is subject to the network topology.
+Regarding directional transmissions, the authors in \cite{babich2015design} propose two novel access schemes to allow multiple simultaneous transmissions.
+In particular, nodes' activity information is sensed, which, together with antenna's directionality information, allows to build a new set of channel access rules.}
+
+	\textcolor{blue}{Despite approaches based on directional transmissions and interference cancellation are very powerful and allow to significantly increase SR, they strongly rely on having multiple antennas.
+Such a requirement is not mandatory for the SR operation based on TPC and CST adjustment.
+In this work, we focus on the former because tuning the transmit power has a direct impact on the generated interference.
+This allows to purely study the interactions that occur among nodes implementing decentralized SR.
+Moreover, we consider DCA to be combined with TPC, so that further potential gains can be achieved.}
+
+	\textcolor{blue}{DCA has been extensively studied from the centralized perspective, especially through techniques based on graph coloring \cite{riihijarvi2005frequency, mishra2005weighted}.
 Despite these kind of approaches allow to effectively reduce the interference between WNs, a certain degree of communication is required.
 Regarding decentralized methods, the authors in \cite{akl2007dynamic} propose a very simple approach in which each AP maintains an interference map of their neighbors, so that channel assignment is done through interference minimization.
-Unfortunately, the interactions between APs due to decentralization are not studied.
-Separately, \cite{chen2007improved} proposes two decentralized approaches that rely in the interference measured at both APs and STAs to calculate the best frequency channels for dynamic channel allocation.
-To do so, a WN, in addition to the interference sensed by its associated devices, considers other metrics such as the amount of traffic, so that some kind of coordination is required at the neighbor level (periodic reporting).
-
-For the case of TPC, one of the first works in studying power management is \cite{elbatt2000power}, which shows that large improvements can be achieved if selecting the appropriate transmit power level in ad-hoc WNs.
-A centralized approach for TPC is presented in \cite{tang2014joint}, which performs power control and Rate Adaptation (RA) in subgroups of Wireless Local Area Networks (WLANs).
+Unfortunately, the interactions among APs in the decentralized setting are not studied.
+Separately, \cite{chen2007improved} proposes two decentralized approaches that rely on the interference measured at both APs and stations (STAs) to calculate the best frequency channels for dynamic channel allocation.
+To do so, a WN, in addition to the interference sensed by its associated devices, considers other metrics such as the amount of traffic, so that some coordination is required at the neighbor level (e.g., periodic reporting).
+The authors in \cite{yue2011cacao} show that the decentralized DCA problem is NP-hard.
+In addition, they propose a distributed algorithm whereby APs select the best channel according to the observed traffic information (i.e., channel sensing is considered).}
+
+	\textcolor{blue}{In this work we aim to extend the approach in \cite{yue2011cacao} in two ways.
+\textcolor{blue}{First, we aim to provide a flexible solution based on the performance achieved by a given WN.} Second, we aim to tackle the spatial domain through TPC\textcolor{blue}{, which has been shown to provide large improvements in wireless networks \cite{elbatt2000power}}.
+\textcolor{blue}{However}, dealing with the spatial dimension leads to unpredictable interactions in terms of interference.
+\textcolor{blue}{Such a complexity is illustrated} in \cite{tang2014joint}, which performs power control and rate adaptation in subgroups of Wireless Local Area Networks (WLANs).
 The creation of clusters allows defining independent power levels between devices in the same group, which are useful to avoid asymmetric links.
-However, to represent all the possible combinations, graphs can become very large, specially in high-density deployments.
-Furthermore, we find a decentralized approach that relies on real-time channel measurements \cite{gandarillas2014dynamic}.
-The proposed mechanism (so called Dynamic Transmission Power Control) is based on a set of triggered thresholds that increase/decrease the transmit power according to the situation.
-The main problem is that thresholds are set empirically (based on simulations), so the mechanism may not always improve performance.
-
-%------------------------
-% Decentralised Learning: Previous work
-%------------------------
-\subsection{Solving WNs Resource Allocation Problems via Bandits}
-\label{section:previous_work}
+However, to represent all the possible combinations, graphs can become very large, especially in high-density deployments.
+\textcolor{blue}{When it comes to decentralized mechanisms, we find the work in \cite{gandarillas2014dynamic}, which applies TPC based on real-time channel measurements \cite{gandarillas2014dynamic}}.
+The proposed mechanism (so called Dynamic Transmission Power Control) is based on a set of triggered thresholds that increase/decrease the transmit power according to the state of the system.
+The main problem is that thresholds are set empirically (based on simulations), which limits the potential of the mechanisms in front of multiple scenarios.}
+
+	\textcolor{blue}{\textcolor{blue}{As shown by previous research, the optimal decentralized SR in WNs through TPC and DCA is very hard to be derived analytically, mostly because of the adversarial setting and the lack of information at nodes.
+The existing decentralized solutions barely provide flexibility with respect to the scenario, so that potential use cases are disregarded.} For that, we focus on online learning, and more precisely Multi-Armed Bandits (MABs).
+The MAB framework allows to reduce the complexity of the SR problem, since detailed information about the scenario is not considered.
+In contrast, learners gain knowledge on all the adversaries as a whole, thus facing a single environment.} To the best of our knowledge, there is very little related work on applying MAB techniques to the problem of resource allocation in WNs.
+In \cite{coucheney2015multi}, the authors propose modeling a resource allocation problem in Long Term Evolution (LTE) networks through MABs.
+In particular, a set of Base Stations (BS) learn the best configuration of Resource Blocks (RBs) in a decentralized way.
+For that purpose, a variation of EXP3 (so-called Q-EXP3) is proposed, which is shown to reduce the strategy set.
+Despite a regret bound is provided, it is subject to the fact that an optimal resource allocation exists, i.e., every BS obtains the necessary resources.
+In addition, a large number of iterations is required to find the optimal solution in a relatively small scenario, thus revealing the difficulties shown by decentralized settings.
+
+	More related to the problem proposed here, the authors in \cite{maghsudi2015joint} show a channel selection and power control approach in infrastructureless networks, which is modeled through bandits.
+In particular, two different strategies are provided to improve the performance of two Device to Device (D2D) users (each one composed by a transmitter and a receiver), which must learn the best channel and transmit power to be selected.
+Similarly to our problem, users do not have any knowledge on the channel or the other's configuration, so they rely on the experienced performance in order to find the best configuration.
+An extension of \cite{maghsudi2015joint} is provided by the same authors in \cite{maghsudi2015channel}, which includes a calibrated predictor (referred in the work as \textit{forecaster}) to infer the behavior of the other devices in order to counter act their actions.
+In each agent, the information of the forecaster is used to choose the highest-rewarding action with a certain probability, while the rest of actions are randomly selected.
+Henceforth, assuming that all the networks use a given strategy $\mathcal{X}$, fast convergence is ensured.
+Results show that channel resources are optimally distributed in a very short time frame through a fully decentralized algorithm that does not require any kind of coordination.
+Both aforementioned works rely on the existence of a unique Nash Equilibrium, which favors convergence.
+In contrast, in this article we aim to extend Bandits utilization to denser deployments, and, what is more important, to scenarios with limited available resources in which there is not a unique Nash Equilibrium (NE) that allows fast-convergence.
+Thus, we aim to capture the effects of applying selfish strategies in a decentralized way (i.e., agent $i$ follows a strategy $\mathcal{X}_i$ that does not consider the strategies of the others) and we also provide insight about the importance of past information for learning in dense WNs, which has not been studied before.
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%III. MABs APPLICATION									    %	
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\section{Multi-Armed Bandits for Improving Spatial Reuse in WNs}
+	\label{section:mabs}
+
+	In this work, we address the decentralized SR problem through online learning because of the uncertainty generated in an adversarial setting.
+The practical application of MABs in WNs is detailed next:
+
+	% MABs
+	\subsection{The Multi-Armed Bandits Framework}
 	In the online learning literature, several MAB settings have been considered such as stochastic bandits \cite{thompson1933likelihood,lai1985asymptotically,auer2002finite}, adversarial bandits \cite{auer1995gambling,auer2002nonstochastic}, restless bandits \cite{whittle1988restless}, contextual bandits \cite{LCLS10} and linear bandits \cite{abe2003reinforcement,APS11}, and numerous exploration-exploitation strategies have been proposed such as \textit{$\varepsilon$-greedy} \cite{sutton1998reinforcement,auer2002finite}, \textit{upper confidence bound} (UCB) \cite{lai1985asymptotically,Agr95,BuKa96,auer2002finite}, \textit{exponential weight algorithm for exploration and exploitation} (EXP3) \cite{auer1995gambling,auer2002finite} and \textit{Thompson sampling} \cite{thompson1933likelihood}.
@@
 
-To the best of our knowledge, there is very little related work on applying multi-armed bandit techniques to the problem of resource allocation in WNs.
-In \cite{coucheney2015multi}, the authors propose modeling a resource allocation problem in LTE networks through MABs.
-In particular, a set of Base Stations (BS) learn the best configuration of Resource Blocks (RBs) in a decentralized way.
-For that purpose, a variation of EXP3 (so-called Q-EXP3) is proposed, which allows to reduce the strategy set.
-Despite a regret bound is provided, it is subject to the fact that an optimal resource allocation exists, i.e., every BS obtains the necessary resources.
-In addition, a large number of iterations is required to find the optimal solution in a relatively small scenario, thus revealing the difficulties shown by decentralized settings.
-
-More related to the problem proposed here, the authors in \cite{maghsudi2015joint} show a channel selection and power control approach in infrastructureless networks, which is modeled through bandits.
-In particular, two different strategies are provided to improve the performance of two Device to Device (D2D) users (each one composed by a transmitter and a receiver), which must learn the best channel and transmit power to be selected.
-Similarly to our problem, users do not have any knowledge on the channel or the other's configuration, so they rely on the experienced performance in order to find the best configuration.
-An extension of \cite{maghsudi2015joint} is provided by the same authors in \cite{maghsudi2015channel}, which includes a calibrated predictor (referred in the work as \textit{forecaster}) to infer the behavior of the other devices in order to counter act their actions.
-In each agent, the information of the forecaster is used to choose the highest-rewarding action with a certain probability, while the rest of actions are randomly selected.
-Henceforth, assuming that all the networks use a given strategy $\mathcal{X}$, fast convergence is ensured.
-Results show that channel resources are optimally distributed in a very short time frame through a fully decentralized algorithm that does not require any kind of coordination.
-Both aforementioned works rely in the existence of a unique Nash Equilibrium, which favors convergence.
-In contrast, in this article we aim to extend Bandits utilization to denser deployments, and, what is more important, to scenarios with limited available resources in which there is not a unique Nash Equilibrium (NE) that allows fast-convergence.
-Thus, we aim to capture the effects of applying selfish strategies in a decentralized way (i.e., agent $i$ follows a strategy $\mathcal{X}_i$ that does not consider the strategies of the others) and we also provide insight about the importance of past information for learning in dense WNs, which has not been studied before.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%III. MABs APPLICATION									    %	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Multi-Armed Bandits for Improving Spatial Reuse in WNs}
-\label{section:mabs}	
-The decentralized resource allocation problem in WNs we aim to solve in this work can be modeled as an approximation of contextual bandits.
-Originally, the contextual bandits problem considers the existence of a context (or a state) that influences the action-selection process.
-As a consequence, the set of available strategies varies with the context and the probability distribution of a given reward depends both on the chosen actions and also on the context.
-In the resource allocation problem at hand, the context could include information such as the number of neighboring WNs, their position, their current channel selection, the transmission power they use as well as their action-selection strategies, among other.
-However, we are interested in the case where no context can be inferred given that such information is hard and costly to obtain in practice, especially in dynamic scenarios.
-Thus, we model the decentralized SR problem in WNs as an adversarial bandit problem, in which the actions of a given WN affect the pay-off distributions of the others' actions.
-Such model requires the existence of a NE with a pure strategy,\footnote{A pure strategy NE is conformed by a set of strategies and payoffs, so that no player can obtain further benefits by deviating from its strategy.} which does not always hold for unplanned deployments due to the scarcity of the available resources and the number of overlapping WNs.
-Understanding the implications derived from such an adversarial setting in the absence of a NE is one the main goals of this paper, which, to the best of our knowledge, has been barely considered in the previous literature.
-
-We model this adversarial problem as follows.
-Let arm $a \in \mathcal{A}$ (we denote the size of $\mathcal{A}$ with K) be a configuration that a WN may choose.
-Each configuration is a combination of channel and transmit power (e.g., $a_1$ = \{Channel: 1, TPC: 5 dBm\}), and grants a reward that depends on the others' configuration.
-Let $\Gamma_{i,t}$ be the throughput experienced by $\text{WN}_i$ at time $t$, and $\Gamma_{i}^*$ the maximum achievable throughput by $\text{WN}_i$ in case of isolation (i.e., no interference is experienced in the selected channel).
-We then define the reward $r_{i,t}$ experienced by $\text{WN}_i$ at time $t$ as:
+	%------------------------
+	% Problem formulation
+	%------------------------
+	\subsection{Multi-Armed Bandits Formulation for Decentralized Spatial Reuse}
+
+	\textcolor{blue}{We model the decentralized SR problem through adversarial bandits.
+In such a model, the reward experienced by a given agent (WN) is influenced by the whole action profile, i.e., the configurations used by other competing WNs.
+From a decentralized perspective, the adversarial setting poses several challenges with respect to the existence of a NE.
+Ideally, the problem is solved if all the competitors implement a pure strategy\footnote{A pure strategy NE is conformed by a set of strategies and payoffs, so that no player can obtain further benefits by deviating from its strategy.} that allows maximizing a certain performance metric.
+However, finding such a strategy may not be possible in unplanned deployments, due to the competition among nodes and the scarcity of the available resources.
+Understanding the implications derived from such an adversarial setting in the absence of a NE is one the main goals of this paper, which, to the best of our knowledge, has been barely considered in the previous literature.}
+
+	\textcolor{blue}{In particular,} we model this adversarial problem as follows.
+Let arm $a \in \mathcal{A}$ (we denote the size of $\mathcal{A}$ with K) be a configuration \textcolor{blue}{in terms of channel and transmit power (e.g., $a_1$ = \{Channel: 1, TPC: -15 dBm\})}.
+Let $\Gamma_{i,t}$ be the throughput experienced by $\text{WN}_i$ at time $t$, and $\Gamma_{i}^*$ \textcolor{blue}{the optimal throughput.}\footnote{\textcolor{blue}{The optimal throughput is achieved in case of isolation (i.e., when no interference is experienced in the selected channel).}} We then define the reward $r_{i,t}$ experienced by $\text{WN}_i$ at time $t$ as:
 
@@
 
-For simplicity, we consider that each WN is composed by an AP and a single STA, so that downlink traffic is held.
-Note that in typical uncoordinated wireless deployments (e.g., residential buildings), STAs are typically close to the AP to which they are associated.
-Thus, having several STAs associated to the same AP does not significantly impact the inter-WNs interference we study in this work.
-According to that, $\Gamma_{i}^*$ is computed as $B \cdot \log_{2}(1 + \text{SNR}_{i})$, where $B$ is the bandwidth, and $\text{SNR}_{i}$ is the Signal-to-Noise ratio experienced by the STA of $\text{WN}_i$.
-We consider this model because it allows to properly capture the interference generated between WNs, which is sought to be minimized.
-
-We have considered the \emph{$\varepsilon$-greedy}, \emph{EXP3}, \emph{UCB} and \emph{Thompson sampling} action-selection strategies, which are described next in this section.
+	In order to attempt to maximize the reward, we have considered the \emph{$\varepsilon$-greedy}, \emph{EXP3}, \emph{UCB} and \emph{Thompson sampling} action-selection strategies, which are described next in this section.
 While $\varepsilon$-greedy and EXP3 explicitly include the concepts of \emph{exploration coefficient} and \emph{learning rate}, respectively, UCB and Thompson sampling are parameter-free policies that extend the concept of exploration (actions are explored according to their estimated value and not by commitment).
-Henceforth, we are able to study the effects of these different kind of policies on the WNs behavior.
-Moreover, we chose the aforementioned policies because they are widely spread and considered of remarkable importance in the MABs literature.
-
-Furthermore, in order to provide a fair comparison, we have considered that all the policies use the same reward.
-Regarding the learning process, we assume that WNs select actions during the same time slot.
-The reward experienced by the WNs is computed once all of them have chosen their action for the current iteration.
-In practice the action-selection process at WNs will most probably not be synchronized but we leave the study of any possible effects of that desynchronization to future work.
+\textcolor{blue}{The aforementioned policies are widely spread and considered of remarkable importance in the MAB literature.}
 
@@
 	%------------------------
-\subsection{$\varepsilon$-greedy}
+	\subsubsection{$\varepsilon$-greedy}
 	\label{section:bandits_egreedy}	
@@
 Therefore, in order to obtain a sublinear regret guarantee (and thus an asymptotically optimal growth rate for the total rewards), it is critical to properly adjust the exploration coefficient.
-Thus, in our implementation of the $\varepsilon$-greedy algorithm, we use a time-dependent exploration rate of $\varepsilon_t = \varepsilon_0 / \sqrt{t}$, as suggested in the literature \cite{auer2002finite}.
+Thus, in our \textcolor{blue}{$\varepsilon$-greedy} implementation, we use a time-dependent exploration rate of $\varepsilon_t = \varepsilon_0 / \sqrt{t}$, as suggested in the literature \cite{auer2002finite}.
 The adaptation of this policy to our setting is shown as Algorithm \ref{alg:egreedy}.
@@
 
-%\begin{algorithm}[h!]
-%	\SetKwInOut{Input}{Input}
-%	\SetKwInOut{Output}{Output}		
-%	Function EXP3 $(\text{SNR},\mathcal{A})$\;
-%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-%	initialize: $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 0, \forall a_k \in \mathcal{A}$\\
-%	\While{active}
-%	{
-%		$p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
-%		Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
-%		Observe the throughput experienced $\Gamma_t$\\
-%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		$\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
-%		$w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
-%		$w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
-%		%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
-%		$\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
-%		$t \leftarrow t + 1$\\
-%	}
-%	\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
-%	\label{alg:exp3}
-%\end{algorithm}
-%
-%
-%
-%	\begin{algorithm}
-%	\caption{Implementation of Multi-Armed Bandits ($\varepsilon$-greedy) in a WN. $\mathcal{U}(1, K)$ is a uniform distribution that randomly chooses from 1 to $K$.}
-%	\label{alg:egreedy}		
-%	\begin{algorithmic}[1]
-%		%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
-%		\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
-%		\While{active}
-%		\State Select $a_k$  $\begin{cases}
-%		\underset{k=1,...,K}{\text{argmax }} r_{k,t},& \text{with prob. } 1 - \varepsilon\\
-%		k \sim \mathcal{U}(1, K),              & \text{otherwise}
-%		\end{cases}$\\
-%		\State Observe the throughput experienced $\Gamma_t$\\
-%		\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		%$p_{k,t} \leftarrow r_{k,t}$\\
-%		\State $\varepsilon_t \gets \varepsilon_0 / \sqrt{t}$ \\
-%		\State $ t \gets t + 1$
-%		\EndWhile
-%		%\EndProcedure
-%	\end{algorithmic}
-%\end{algorithm}
-
 	%------------------------
@@
 	%------------------------
-\subsection{EXP3}
+	\subsubsection{EXP3}
 	\label{section:bandits_exp3}	
@@
 	where $\gamma\in[0,1]$ is a parameter controlling the rate of exploration.
-Having selected arm $a_t$, the learner observes the generated pay-off $r_{a_t,t}$ and computes the importance-weighted reward estimates
+	Having selected arm $a_t$, the learner observes the generated pay-off $r_{a_t,t}$ and computes the importance-weighted reward estimates for all $k\in[K]$
 	\begin{equation}
 	\label{eq:exp3_estimated_reward}
-\widehat{r}_{k,t} = \frac{\mathbb{I}_{\left\{I_t = k\right\}}r_{k,t}}{p_{k,t}}
+	\widehat{r}_{k,t} = \frac{\mathbb{I}_{\left\{I_t = k\right\}}r_{k,t}}{p_{k,t}},
 	\nonumber
 	\end{equation}
-for all $k\in[K]$, where $\mathbb{I}_{\left\{A \right\}}$ denoting the indicator function of the event $A$ taking a value of $1$ if $A$ is true and $0$ otherwise.
+	where $\mathbb{I}_{\left\{A \right\}}$ denoting the indicator function of the event $A$ taking a value of $1$ if $A$ is true and $0$ otherwise.
 	Finally, the weight of arm $k$ is updated as a function of the estimated reward:
@@
 	where $\eta>0$ is a parameter of the algorithm often called the \emph{learning rate}.
-Intuitively, $\eta$ regulates the rate in which the algorithm incorporates new observations with large values of $\eta$ corresponding to more confident updates and smaller values leading to more conservative behavior.
+Intuitively, $\eta$ regulates the rate in which the algorithm incorporates new observations.
+\textcolor{blue}{Large values of $\eta$ correspond to more confident updates and small values lead to more conservative behaviors}.
 As we did for the exploration coefficient in \emph{$\varepsilon$-greedy}, we use a time-dependent learning rate of $\eta_t = \eta_0 / \sqrt{t}$ \cite{auer2002finite}.
-Our implementation of EXP3 to the WN problem is detailed in Algorithm \ref{alg:exp3}.
-%\begin{algorithm}[h!]
-%	Function EXP3 $(\text{SNR},\mathcal{A})$\\
-%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}\\
-%	initialize: $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 0, \forall a_k \in \mathcal{A}$\\
-%	\While{active}
-%	{
-%		$p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
-%		Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
-%		Observe the throughput experienced $\Gamma_t$\\
-%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		$\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
-%		$w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
-%		$w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
-%		%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
-%		$\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
-%		$t \leftarrow t + 1$\\
-%	}
-%	\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
-%	\label{alg:exp3}
-%\end{algorithm}
+Our implementation of EXP3 is detailed in Algorithm \ref{alg:exp3}.
 
@@
 		\KwIn{SNR: information about the Signal-to-Noise Ratio received at the STA, $\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-	\textbf{Initialize:} $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 0, \forall a_k \in \mathcal{A}$\\
+		\textbf{Initialize:} $t=0$, $\eta_t = \eta_0$, $w_{k,t} = 1, \forall a_k \in \mathcal{A}$\\
 		\While{active}{
@@
 			$w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
-		$w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
+			$w_{k',t} \leftarrow w_{k',t-1}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
 			%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
@@
 	\end{algorithm}
-%	\begin{algorithm}
-%		\caption{Implementation of Multi-Armed Bandits (EXP3) in a WN}
-%		\label{alg:exp3}
-%		\begin{algorithmic}[1]
-%			%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
-%			\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
-%			\While{active}
-%			\State $p_{k,t} \leftarrow (1-\gamma) \frac{w_{k,t}}{\sum^K_{i=1} w_{i,t}} + \frac{\gamma}{K}$ \\
-%			\State Draw $a_k \sim p_{k,t} = (p_{1,t}, p_{2,t}, ... , p_{K,t})$\\
-%			\State Observe the throughput experienced $\Gamma_t$\\
-%			\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%			\State $\widehat{r}_{k,t} \leftarrow \frac{r_{k,t}}{p_{k,t}}$ \\
-%			\State $w_{k,t} \leftarrow w_{k,t-1}^{\frac{\eta_{t}}{\eta_{t-1}}} \cdot e^{\eta_{t} \cdot \widehat{r}_{k,t}}$\\
-%			\State $w_{t,k'} \leftarrow w_{t-1,k'}^{\eta_t / \eta_{t-1}}, \forall k' \neq k$\\
-%			%$w_{k',t} = w_{k',t-1}$, $\forall k' \neq k$\\
-%			\State $\eta_{t} \leftarrow \frac{\eta_0}{\sqrt{t}}$\\
-%			\State $t \leftarrow t + 1$\\
-%			\EndWhile
-%			%\EndProcedure
-%		\end{algorithmic}
-%	\end{algorithm}
 
@@
 	%------------------------
-\subsection{UCB}
+	\subsubsection{UCB}
 	\label{section:bandits_ucb}		
@@
 Intuitively, UCB trades off exploration and exploitation very effectively, as upon every time a suboptimal arm is chosen, the corresponding confidence bound will shrink significantly, thus quickly decreasing the probability of drawing this arm in the future.
-The width of the confidence intervals is chosen carefully so that the true best arm never gets discarded accidentally by the algorithm, yet suboptimal arms are not drawn as few times as possible.
+The width of the confidence intervals is chosen carefully so that the true best arm never gets discarded accidentally by the algorithm, yet suboptimal arms are drawn as few times as possible.
 To obtain the first estimates, each arm is played once at the initialization.
@@
 	Formally, let $n_k$ be the number of times that arm $k$ has been played, and $\Gamma_{k,t}$ the throughput obtained by playing arm $k$ at time $t$.
-The average experienced reward $\overline{r}_{k,t}$ by arm $k$ at time $t$ is therefore given by:
+The average reward $\overline{r}_{k,t}$ \textcolor{blue}{of} arm $k$ at time $t$ is therefore given by:
 	\begin{equation}
@@
 By doing so, UCB implicitly balances exploration and exploitation, as it focuses efforts on the arms that are $i)$ the most promising (with large estimated rewards) or $ii)$ not explored enough (with small $n_k$).
-Our implementation of UCB to the WN problem is detailed in Algorithm \ref{alg:ucb}.
-%Note as well, that UCB suffers a logarithmic regret, instead of the linear regret granted by ``$\varepsilon$-greedy" \cite{lai1985asymptotically}.	
-% According to \cite{auer2002nonstochastic}, the UCB algorithm provides a logarithmic asymptotic regret $R_{T}$ for a given time period $T > 0$, as shown in (\ref{eq:ucb_regret}):
-%	\begin{equation}
-%	\label{eq:ucb_regret}
-%	R_T = G_{max}(T)-\mathop{\mathbb{E}}(G_{\text{UCB}}(T)) \leq 8 \sum_{i:\mu_i < \mu^{*}} \frac{\ln T}{\Delta_i} + \Big(1+\frac{\pi^2}{3}\Big) \sum_{i=1}^{K}\Delta_i  ,
-%	\end{equation}	
-%	where $G_{max}(T)$ is the maximum achievable gain at $T$, $\mathbb{E}(G_{\text{UCB}}(T))$ is the expected gain obtained at $T$ by applying the UCB policy, $\Delta_i = \mu^{*} - \mu_i$ is the difference between the empirical mean of the best arm and the chosen one.
-In Equation \ref{eq:ucb_regret}, both expected losses and risks are embodied (first and second term, respectively).
-%\begin{algorithm}[h!]
-%	\SetKwInOut{Input}{Input}
-%	\SetKwInOut{Output}{Output}		
-%	Function UCB $(\text{SNR},\mathcal{A})$\;
-%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-%	initialize: $t=0$, play each arm $a_k \in \mathcal{A}$ once\\
-%	\While{active}
-%	{
-%		Draw $a_k = \underset{k=1,...,K}{\text{argmax }} \overline{r}_{k} + \sqrt{\frac{2 ln(t)}{n_{k}}} $ \\
-%		Observe the throughput experienced $\Gamma_t$\\			
-%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		$n_k \leftarrow n_k + 1$\\
-%		$ \overline{r}_{k} \leftarrow \frac{1}{n_{k}} \sum_{s=1}^{n_{k}} r_{k,s}$\\
-%		$t \leftarrow t + 1$
-%	}
-%	\caption{Implementation of Multi-Armed Bandits (UCB) in a WN}
-%	\label{alg:ucb}
-%\end{algorithm}
+Our implementation of UCB is detailed in Algorithm \ref{alg:ucb}.
 
@@
 	\end{algorithm}
-%	\begin{algorithm}
-%		\caption{Implementation of Multi-Armed Bandits (UCB) in a WN}
-%		\label{alg:ucb}	
-%		\begin{algorithmic}[1]
-%			%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
-%			\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
-%			\While{active}
-%			\State Draw $a_k = \underset{k=1,...,K}{\text{argmax }} \overline{r}_{k} + \sqrt{\frac{2 ln(t)}{n_{k}}} $ \\
-%			\State Observe the throughput experienced $\Gamma_t$\\			
-%			\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%			\State $n_k \leftarrow n_k + 1$\\
-%			\State $ \overline{r}_{k} \leftarrow \frac{1}{n_{k}} \sum_{s=1}^{n_{k}} r_{k,s}$\\
-%			\State $t \leftarrow t + 1$
-%			\EndWhile\label{euclidendwhile}
-%			%\EndProcedure
-%		\end{algorithmic}
-%	\end{algorithm}
 
@@
 	%------------------------
-\subsection{Thompson sampling}
+	\subsubsection{Thompson sampling}
 	\label{section:bandits_thompsons}	
@@
 
-For the sake of practicality, we aim to apply Thompson sampling using a Gaussian model for the rewards with a standard Gaussian prior as suggested in \cite{agrawal2013further}.
-By standard calculations, it can be verified that the posterior distribution of the rewards under this model is Gaussian with mean
+	For the sake of practicality, we \textcolor{blue}{assume that rewards follow a Gaussian distribution with a standard Gaussian prior,} as suggested in \cite{agrawal2013further}.
+By standard calculations, it can be verified that the posterior distribution of the rewards under this model is Gaussian with mean \textcolor{blue}{and variance}
 	\begin{equation}
-\hat{r}_k(t) = \frac{\sum_{w=1:k}^{t-1} r_k(t) }{n_k(t) + 1}
+	\textcolor{blue}{\hat{r}_k(t) = \frac{\sum_{w=1:k}^{t-1} r_k(t) }{n_k(t) + 1} \Big/ \sigma_k^2(t) = \frac{1}{n_k + 1}},
 	\nonumber
 	\end{equation}
-and variance $\sigma_k^2(t) = \frac{1}{n_k + 1}$, where $n_k$ is the number of times that arm $k$ was drawn until the beginning of round $t$.
+	where $n_k$ is the number of times that arm $k$ was drawn until the beginning of round $t$.
 Thus, implementing Thompson sampling in this model amounts to sampling a parameter $\theta_k$ from the Gaussian distribution $\mathcal{N}\left(\hat{r}_k(t),\sigma_k^2(t)\right)$ and choosing the action with the maximal parameter.
 Our implementation of Thompson sampling to the WN problem is detailed in Algorithm \ref{alg:thompsons}.
-%\begin{algorithm}[h!]
-%	\SetKwInOut{Input}{Input}
-%	\SetKwInOut{Output}{Output}		
-%	Function Thompson sampling $(\text{SNR},\mathcal{A})$\;
-%	\Input{SNR: information about the Signal-to-Noise Ratio received at the STA\\$\mathcal{A}$: set of possible actions in \{$a_1, ..., a_K$\}}
-%	initialize: $t=0$,  for each arm $a_k \in \mathcal{A}$, set $\hat{r}_{k} = 0$ and $n_k = 0$ \\
-%	\While{active}
-%	{
-%		For each arm $a_k \in \mathcal{A}$, sample $\theta_k(t)$ from normal distribution $\mathcal{N}(\hat{r}_{k}, \frac{1}{n_k + 1})$ \\
-%		Play arm $a_{k} = \underset{k=1,...,K}{\text{argmax }} \theta_k(t) $ \\
-%		Observe the throughput experienced $\Gamma_t$\\			
-%		Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%		$ \hat{r}_{k,t} \leftarrow \frac{\hat{r}_{k,t}  n_{k,t} + r_{k,t}}{n_{k,t} + 2}$\\
-%		$n_{k,t} \leftarrow n_{k,t} + 1$\\
-%		$t \leftarrow t + 1$
-%	}
-%	\caption{Implementation of Multi-Armed Bandits (Thompson sampling) in a WN}
-%	\label{alg:thompsons}
-%\end{algorithm}
 
@@
 		}		
-	\caption{Implementation of Multi-Armed Bandits (Thompson sampling) in a WN}
+		\caption{Implementation of Multi-Armed Bandits (Thompson \textcolor{blue}{s.}) in a WN}
 		\label{alg:thompsons}
 	\end{algorithm}
-%	\begin{algorithm}
-%		\caption{Implementation of Multi-Armed Bandits (Thompson sampling) in a WN}
-%		\label{alg:thompsons}
-%		\begin{algorithmic}[1]
-%			%\Procedure{$\varepsilon$-greedy }{$\text{SNR},\mathcal{A}$\;}
-%			\State Function $\varepsilon$-greedy ($\text{SNR},\mathcal{A}$)\;
-%			\While{active}
-%			\State For each arm $a_k \in \mathcal{A}$, sample $\theta_k(t)$ from normal distribution $\mathcal{N}(\hat{r}_{k}, \frac{1}{n_k + 1})$ \\
-%			\State Play arm $a_{k} = \underset{k=1,...,K}{\text{argmax }} \theta_k(t) $ \\
-%			\State Observe the throughput experienced $\Gamma_t$\\			
-%			\State Compute the reward $r_{k,t} = \frac{\Gamma_t}{\Gamma^*}$, where $\Gamma^* = B \log_{2}(1+\text{SNR})$ \\
-%			\State $ \hat{r}_{k,t} \leftarrow \frac{\hat{r}_{k,t}  n_{k,t} + r_{k,t}}{n_{k,t} + 2}$\\
-%			\State $n_{k,t} \leftarrow n_{k,t} + 1$\\
-%			\State $t \leftarrow t + 1$
-%			\EndWhile
-%			%\EndProcedure
-%		\end{algorithmic}
-%	\end{algorithm}
 
@@
 
-For the remainder of this work, we study the interactions between several WNs placed in a 3-D scenario that occur when applying MABs in a decentralized manner (with parameters described later in Section \ref{section:simulation_parameters}).
-For simplicity, we consider WNs to be composed by an Access Point (AP) transmitting to a single Station (STA) in a downlink manner.
-Additionally, to analyze the adversarial setting when WNs share scarce resources, we consider that the number of channels is equal to half the number of coexisting WNs, thus making the SR even more challenging.
+	For the remainder of this work, we study the interactions among several WNs placed in a 3-D scenario that occur when applying MABs in a decentralized manner (with parameters described later in Section \ref{section:simulation_parameters}).
+For simplicity, we consider WNs to be composed by an AP transmitting to a single Station (STA) in a downlink manner.
+\textcolor{blue}{Note that in typical uncoordinated wireless deployments (e.g., residential buildings), STAs are typically close to the AP to which they are associated.
+Thus, having several STAs associated to the same AP does not significantly impact the inter-WNs interference \textcolor{blue}{studied} in this work.}
 
@@
 	\label{section:throughput_calculation}
-As previously mentioned, we use the power received and the interference to calculate the maximum theoretical throughput of each WN $i$ at time $t$ by using the Shannon Capacity,
-\begin{equation}
-\Gamma_{i,t} = B  \log_{2}(1 + \text{SINR}_{i, t}),
-\nonumber
-\label{eq:shannon_capacity}
-\end{equation}
-where $B$ is the channel width and the experienced Signal to Interference plus Noise Ratio (SINR) is given by:
-\begin{equation}
-\text{SINR}_{i,t} = \frac{\text{P}_{i,t}}{\text{I}_{i,t}+\text{N}},
-\label{eq:sinr}
-\nonumber
-\end{equation}
-where $\text{P}_{i,t}$ and $\text{I}_{i,t}$ are the received power and the sum of the interference at WN $i$ at time $t$, respectively, and N is the floor noise power.
-For each WN, we consider the interference to be the total power received from all the APs in the same channel.
-For capturing the worst-case scenario, we consider that all WNs are continuously transmitting (i.e., we do not consider empty channel periods left by the medium access procedure).
-Adjacent channel interference is also considered in $\text{I}_{i,t}$, so that the transmitted power leaked to adjacent channels is $20$ dBm lower for each extra channel separation.
+	\textcolor{blue}{The throughput experienced by WN $i$ at time $t$ is given by $\Gamma_{i,t} = B  \log_{2}(1 + \text{SINR}_{i, t})$,
+		%\begin{equation}
+		%\Gamma_{i,t} = B  \log_{2}(1 + %\text{SINR}_{i, t}),
+		%\nonumber
+		%\label{eq:shannon_capacity}
+		%\end{equation}
+		where $B$ is the channel width and SINR is the experienced Signal to Interference plus Noise Ratio. The latter is computed as $\text{SINR}_{i,t} = \frac{\text{P}_{i,t}}{\text{I}_{i,t}+\text{N}}$,
+		%\begin{equation}
+		%\text{SINR}_{i,t} = %\frac{\text{P}_{i,t}}{\text{I}_{i,t}+\text{N}},
+		%\label{eq:sinr}
+		%\nonumber
+		%\end{equation}
+		where $\text{P}_{i,t}$ and $\text{I}_{i,t}$ are the received power and the sum of the interference at WN $i$ at time $t$, respectively, and N is the floor noise power.} Adjacent channel interference is also considered in $\text{I}_{i,t}$, so that the transmitted power leaked to adjacent channels is $20$ dBm lower for each extra channel separation.
+\textcolor{blue}{Similarly, the optimal throughput is computed as $\Gamma_{i}^* = B  \log_{2}(1 + \text{SNR}_{i})$, which frames the operation of a given WN in isolation.}
+
+	%------------------------
+	% Learning procedure
+	%------------------------
+	\subsection{Learning procedure}
+	\label{section:learning_procedure}
+
+	\textcolor{blue}{We frame the decentralized learning procedure in two different ways, namely \textit{concurrent} and \textit{sequential}.
+Figure \ref{fig:async_vs_sync} illustrates the procedure followed by agents to carry out decentralized SR learning.
+As shown, in each iteration\footnote{\textcolor{blue}{The time between iterations ($T$) must be large enough to provide an accurate estimation of the throughput experienced for a given action profile.}} there is a monitoring phase (shown in grey), where the current selected action is analyzed by each agent to quantify the hidden reward (which depends on the adversarial setting).
+Such a reward is the same for all the policies presented in this work, so that a fair comparison can be provided.
+After the monitoring phase is completed, agents update their knowledge (shown in purple) and choose a new action (shown in yellow).
+Note, as well, that both approaches rely on a synchronization phase (shown in green), which can be achieved  through message passing \cite{sanghavi2009message, yang2011message} and/or environment sensing.\footnote{\textcolor{blue}{The IEEE 802.11k amendment, which is devoted to measurement reporting, may enable the environment sensing operation.}}}
+
+	\begin{figure}[h!]
+		\centering				
+		\epsfig{file=images/async_vs_sync.png, width=11cm}
+		\caption{Concurrent and sequential procedures.}
+		\label{fig:async_vs_sync}
+	\end{figure}
+
+	\textcolor{blue}{In the concurrent approach, agents (or WNs) make decisions simultaneously, thus leading to a more variable (and chaotic) environment.
+In practice the fully decentralized learning process will most probably not be synchronized but we leave the study of any possible effects of that desynchronization to future work.
+In contrast, \textcolor{blue}{for the sequential approach, WNs need to wait for their turn in order to pick a new action.
+As a result, the performance of their last selected action (arm) is measured for several iterations (equal to the number of overlapping networks).
+In particular, during the update phase, a WN computes the reward of its last selected arm according to the throughput experienced in average.
+Accordingly, the performance of a given action is measured against different adversarial settings, since the environment changes gradually.
+Despite agents still learn selfishly, they can better assess how robust an action is against the joint actions profile, in comparison to the concurrent approach.}}
 
@@
 In it, STAs are placed at the maximum possible distance from the other networks.
-
 Table \ref{tbl:simulation_parameters} details the parameters used.
@@
 		\centering
-	%\resizebox{\columnwidth}{!}{
+		\resizebox{0.6\columnwidth}{!}{
 			\begin{tabular}{|l|l|}
@@
 				Distance AP-STA (m)     & $\sqrt{2}$                         \\ \hline
-			Number of Channels              & 2                               \\ \hline
-			Channel Bandwidth (MHz)         & 20                                    \\ \hline
+				Number of \textcolor{blue}{orthogonal} channels              & \textcolor{blue}{3}                               \\ \hline
+				Channel bandwidth (MHz)         & 20                                    \\ \hline
 				Initial channel selection model & Uniformly distributed 
 				\\ \hline
-			TPC Values (dBm)                & \{5, 10, 15, 20\}                      \\ \hline				
+				\textcolor{blue}{Transmit power values (dBm)}                & \textcolor{blue}{\{-15, 0, 15, 30\}}                      \\ \hline
 				$\text{PL}_0$ (dB)                   & 5
@@
 	%%%%%%%%%%%%%%
-% V. SIMULATIONS   %
+	% V. SIMULATION
 	%%%%%%%%%%%%%%
@@
 	\label{section:performance_evaluation}
-In this Section, we evaluate the performance of each action-selection strategy presented in Section \ref{section:mabs} when applied to the decentralized SR problem in WNs.\footnote{All of the source code used in this work open \cite{fwilhelmi2017code}, encouraging sharing of algorithms between contributors and providing the ability for people to improve on the work of others under the GNU General Public License v3.0} For that purpose, we first evaluate the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling policies in a controlled environment.
-Without loss of generality, we consider a symmetric configuration in this scenario in order to analyze the competition effects when WNs have the same opportunities for accessing the channel.
-Then, in Section \ref{section:random}, we provide a performance comparison of the aforementioned scenarios with different densities and with randomly located WNs.
-
+
+	In this Section, we evaluate the performance of each action-selection strategy presented in Section \ref{section:mabs} when applied to the decentralized SR problem in WNs.\footnote{The source code used in this work is open \cite{fwilhelmi2017code}, encouraging sharing of \textcolor{blue}{knowledge} with potential contributors under the GNU General Public License v3.0.} For that purpose, we first evaluate in Section \ref{section:toy_grid_scenario} the $\varepsilon$-greedy, EXP3, UCB and Thompson sampling policies in a fixed adversarial environment.
+\textcolor{blue}{This allows us to provide insights on the decentralized learning problem in a competitive scenario.
+Accordingly, we are able to analyze in detail the effect of applying each learning policy on the network's performance.} Without loss of generality, we consider a symmetric configuration and analyze the competition effects when WNs have the same opportunities for accessing the channel.
+Finally, Section \ref{section:random} provides a performance comparison of the aforementioned scenarios with different densities and with randomly located WNs.
 	\subsection{Toy Grid Scenario}		
 	\label{section:toy_grid_scenario}
-We start considering a toy scenario consisting in a grid of 4 WNs, as illustrated in Figure \ref{fig:scenario}.
+
+	The toy grid scenario contains 4 WNs and is illustrated in Figure \ref{fig:scenario}.
 This scenario has the particularity of being symmetric, so that adversarial WNs have the same opportunities to compete for the channel resources.
-Henceforth, this scenario allows us to \emph{i)} simplify the evaluation of the proposed algorithms, \emph{ii)} frame the competition between WNs on equal terms.
-
-\begin{figure}[t!]
+\textcolor{blue}{The optimal solution in terms of proportional fairness\footnote{\textcolor{blue}{The proportional fairness (PF) result accomplishes that the logarithmic sum of each individual throughput is maximized: $\max \sum_{i \in \text{WN}} \log(\Gamma_i)$.}} is achieved when channel reuse is maximized and WNs sharing the channel moderate their transmit power.
+The PF solution provides an aggregate performance of $440.83$ Mbps (i.e., $106.212$ Mbps per WN on average).
+The optimal solution is computed by brute force (i.e., trying all the combinations), and it is used as a baseline.}
+
+	\begin{figure}[h!]
 		\centering								
@@
 	%------------------------
-% Optimality study
-%------------------------
-\subsubsection{Optimal Solution}
-\label{section:optimal_solution}	
-Before presenting the simulation results of applying a particular action-selection policy, we introduce the optimal solutions that: \emph{i)} maximize the aggregate throughput and \emph{ii)} correspond to proportional fairness\footnote{The proportional fairness solutions satisfy $\underset{a_k \in \mathcal{A}}{\rm max} \sum_{i \in \mathcal{WN}} \log(\Gamma_{i,a_k})$.} for the considered grid scenario, shown in Figure \ref{fig:scenario}.
-%Knowing the maximum achievable performance in the presented scenario allows us to provide a meaningful comparison of the introduced policies to be followed by the WNs.
-
-Let actions range from $a_1$ to $a_8$, and map to \{channel number, transmit power (dBm)\}: $a_1$ = \{1, 5\}, $a_2$ = \{2, 5\}, $a_3$ = \{1, 10\}, $a_4$ = \{2, 10\}, $a_5$ = \{1, 15\}, $a_6$ = \{2, 15\}, $a_7$ = \{1, 20\} and $a_8$ = \{2, 20\}.
-According to our model, the joint configuration of the 4 WNs that grants the maximum aggregate throughput is any combination of actions \{$a_1$, $a_7$, $a_8$\}, subject to the condition of two close WNs using $a_1$.
-Despite the scenario is symmetric, the distance between APs is not the same in all the cases.
-For instance, $d_{\text{AP}_1,\text{AP}_2} > d_{\text{AP}_1,\text{AP}_4}$.
-It is important to emphasize that the proposed scenario does not consider asymmetries between WNs, so that dominance relationships are not present.
-In case of suffering from such asymmetries, the performance of a given WN would depend on the configuration of its neighboring networks but it won't be able to affect their behavior.
-For instance, a WN in the middle of two others may suffer from flow starvation if the WNs in the extremes do not sense each other.
-In such a situation, the WN in the middle is not able to fairly compete for channel resources due to the asymmetric situation it suffers.
-
-In our symmetric scenario, the optimal aggregate throughput is 1124 Mbps, and is only achieved when two consecutive WNs sacrifice themselves by choosing a lower transmit power (action $a_1$).
-Moreover, to maximize the proportional fairness, the optimal joint configuration changes to any combination using the maximum transmit power (i.e., $a_7$ and $a_8$), so that frequency reuse is maximized; WNs using the same channel must be as much separated as possible.
-Such a configuration leads to an aggregate throughput of 891 Mbps, which is quite lower than in the former case, but allows experiencing a fairer configuration.
-Note that all WNs obtain the same throughput in this case as frequency reuse is achieved (closer WNs choose different channels), but power is kept equal for each WN and despite experiencing higher interference, none of the WNs sacrifice themselves.
-The aim of the following performance evaluation is to gain insight into whether a collaborative result, close to this equal division of resources given by the proportional fair action selection, is likely to be learned by the algorithms and if so, under which conditions.
-
-%------------------------
-% Study of MAB (e-greedy)
-%------------------------
-\subsubsection{Performance of the $\varepsilon$-greedy policy}
-\label{section:egreedy_study}	
-We first evaluate the performance of the $\varepsilon$-greedy policy when applied to the WNs problem, which allows us to study the purest form of the exploitation-exploration trade-off.
-First, we show the impact of modifying the initial exploration coefficient, $\varepsilon_0$ (recall that we have considered $\varepsilon_t = \varepsilon_0 / \sqrt{t}$), on the average throughput experienced by the overlapping WNs.
-Figure \ref{fig:egreedy_tuning_parameters} shows the aggregate throughput obtained in the grid scenario when applying $\varepsilon$-greedy during 10,000 iterations, and for each $\varepsilon_0$ value between 0 and 1 in 0.1 steps.
-The average and standard deviation of the throughput from 100 simulation runs are shown, which are compared with the optimal throughput presented in Section \ref{section:optimal_solution}.
+	% Preliminary Analysis
+	%------------------------
+	\textcolor{blue}{\subsubsection{Configuration of the Learning Parameters}}
+
+	\textcolor{blue}{Before comparing the performance of each algorithm, we first analyze the effect of modifying each one's internal parameters.
+Since the versions of UCB and Thompson sampling analyzed in this work are parameter-less, in this section we focus only on $\varepsilon$-greedy and EXP3 methods.}
+
+	\textcolor{blue}{Firstly, $\varepsilon$-greedy allows to regulate the explicit exploration rate at which the agent operates, which is referred to as $\varepsilon$.
+In this paper, $\varepsilon$ is dynamically adjusted as $\varepsilon_t = \frac{\varepsilon_0}{\sqrt{t}}$, with the aim of exploring more efficiently.
+Accordingly, we study the impact of modifying the initial exploration coefficient in the experienced performance by a WN.
+Secondly, when it comes to EXP3, we find two parameters, namely $\eta$ and $\gamma$.
+While $\eta$ controls how fast old beliefs are replaced by newer ones, $\gamma$ regulates explicit exploration by tuning the importance of weights in the action-selection procedure.
+Setting $\gamma = 1$ results in completely neglecting weights (actions have the same probability to be chosen).
+On the other side, by setting $\gamma = 0$, the effect of weights are at its highest importance.
+Thus, in order to clearly analyze the effects of the EXP3 weights, which directly depend on $\eta$, we fix $\gamma$ to 0.
+As we did for $\varepsilon$-greedy, we analyze the impact of modifying the parameter $\eta_0$ in EXP3 on the WN's performance.}
+
+	\textcolor{blue}{Figure \ref{fig:tuning_parameters} shows the aggregate throughput obtained in the grid scenario when applying both $\varepsilon$-greedy and EXP3 during 10,000 iterations, and for each $\varepsilon_0$ and $\eta_0$ values, respectively.
+The results are presented for values $\varepsilon_0$ and $\eta_0$ between 0 and 1 in 0.1 steps.
+The average and standard deviation of the throughput from 100 simulation runs are also shown, and compared with the proportional fair solution.}
+
+	\begin{figure}[h!]
+		\centering
+		\epsfig{file=images/tuning_parameters.png, width=7cm}
+		\label{fig:tuning_parameters}
+		\caption{\textcolor{blue}{Average network throughput and standard deviation obtained for each $\varepsilon_0$ and $\eta_0$ value in $\varepsilon$-greedy and EXP3, respectively.
+Results are from 100 simulations lasting 10,000 iterations each.
+The proportional fair solution is also shown (red dashed line).}}
+		\label{fig:tuning_parameters}
+	\end{figure}
+
+	\textcolor{blue}{As shown, the aggregate throughput obtained on average is quite similar for all $\varepsilon_0$ and $\eta_0$ values, except for the complete random case where no exploration is done (i.e., when $\varepsilon_0$ and $\eta_0$ are equal to 0).
+For $\varepsilon$-greedy, the lower the $\varepsilon_0$ parameter, the less exploration is performed.
+Consequently, for low $\varepsilon_0$, the average throughput is highly dependent on how good/bad were the actions taken at the beginning of the learning process, which results in a higher standard deviation as $\varepsilon_0$ goes to 0.
+As for EXP3, the lower $\eta_0$, the more slowly weights are updated.
+For $\eta_0 = 0$, weights are never updated, so that arms have always the same probability to be chosen.
+To conclude, we choose $\varepsilon_0 = 1$ and $\eta_0 = 0.1$, respectively, for the rest of simulations, which provide the highest ratio between the aggregate throughput and the variability among different runs.}
+
+	%------------------------
+	% Study of MABs
+	%------------------------
+	\textcolor{blue}{\subsubsection{Performance of the MAB-based Policies}}
+
+	\textcolor{blue}{Once we established the initial parameters to be used by both $\varepsilon$-greedy and EXP3, we now compare the performance of all the studied action-selection strategies when applied to decentralized WNs.
+First, we focus on the average throughput achieved by each WN in the toy grid scenario, for each of the methods (Figure \ref{fig:results_part_1_variability_default}).
+As shown, the proportional fair solution is almost achieved by all the learning methods.
+However, Thompson sampling is shown to be much more stable than the other mechanisms, since its variability in the aggregate throughput is much lower (depicted in Figure \ref{fig:results_part_1_agg_variability_default}).}
+
+	\begin{figure}[h!]
+		\centering
+		\begin{subfigure}[b]{0.45\textwidth}
+			\includegraphics[width=\textwidth]{images/results_part_1_mean_tpt_default}
+			\caption{Mean throughput}
+			\label{fig:results_part_1_variability_default}
+		\end{subfigure}
+		\begin{subfigure}[b]{0.45\textwidth}
+			\includegraphics[width=\textwidth]{images/results_part_1_agg_variability_default}
+			\caption{Temporal network throughput}
+			\label{fig:results_part_1_agg_variability_default}
+		\end{subfigure}
+		\caption{\textcolor{blue}{Mean throughput achieved per WN, for each action-selection strategy (the standard deviation is shown in red). The black dashed line indicates the PF result.}}
+		\label{fig:results_part_1_mean_tpt}
+	\end{figure}
+
+	\textcolor{blue}{In order to dig deeper into the behavior of agents for each policy, Figure \ref{fig:actions_probabilities} shows the probability of each WN to choose each action.
+Regarding $\varepsilon$-greedy, EXP3 and UCB, a large set of actions is chosen with similar probabilities.
+Note that there are only three frequency channels, so that two WNs need to share one of them, thus leading to a lower performance with respect to the other two.
+Therefore, WNs are constantly changing their channel and experiencing intermittent good/poor performance.
+Thus, the degree of exploration is kept very high, resulting in high temporal variability.
+In contrast, Thompson sampling shows a clearer preference for selecting a single action, which allows reducing the aforementioned variability.}
+
+	% actions probability
 	\begin{figure}[t!]
 		\centering
-	\epsfig{file=images/egreedy_tuning_parameters_zoom.eps, width=6.5cm}
-	\caption{Average aggregate throughput and standard deviation obtained for each $\varepsilon_0$ value in $\varepsilon$-greedy.
-Results are from 100 simulations lasting 10,000 iterations each.
-The proportional fair solution is also shown (red dashed line).}
-	\label{fig:egreedy_tuning_parameters}
+		\begin{subfigure}[b]{0.43\textwidth}
+			\includegraphics[width=\textwidth]{images/actions_probability_EG}
+			\caption{$\varepsilon$-greedy ($\varepsilon_0  = 0.1$)}
+			\label{fig:actions_probability_EG}
+		\end{subfigure}
+		\begin{subfigure}[b]{0.43\textwidth}
+			\includegraphics[width=\textwidth]{images/actions_probability_EXP3}
+			\caption{EXP3 ($\eta_0 = 0.1$)}
+			\label{fig:actions_probability_EXP3}
+		\end{subfigure}
+		\begin{subfigure}[b]{0.43\textwidth}
+			\includegraphics[width=\textwidth]{images/actions_probability_UCB}
+			\caption{UCB}
+			\label{fig:actions_probability_UCB}
+		\end{subfigure}
+		\begin{subfigure}[b]{0.43\textwidth}
+			\includegraphics[width=\textwidth]{images/actions_probability_TS}
+			\caption{TS}
+			\label{fig:actions_probability_TS}
+		\end{subfigure}
+		\caption{\textcolor{blue}{Probability of selecting each given action for a simulation of 10,000 iterations.}}
+		\label{fig:actions_probabilities}
 	\end{figure}
-As shown in the figure, the aggregate throughput obtained in average is quite similar for all the provided values of $\varepsilon_0$, except for the complete random case where no exploration is done ($\varepsilon_0 = 0$).
-The lower the $\varepsilon_0$ parameter, the less exploration is performed.
-Consequently, for low $\varepsilon_0$, the average throughput is highly dependent on how good/bad were the actions taken at the beginning of the learning process, which results in a higher standard deviation as $\varepsilon_0$ goes to 0.
-
-Now, in order to provide a deeper analysis on the WNs behavior when implementing the $\varepsilon$-greedy policy, we focus on the actions probability and the temporal evolution of throughput derived from a single simulation run.
-To this aim, we use $\varepsilon_0 = \{0.1, 0.5, 1\}$, which correspond to three representative cases (low exploration, middle degree of exploration and intensive exploration).
-Figure \ref{fig:eg_actions_distr} shows the action probability distribution at each WN at the end of the 10,000 iteration-long simulation, and for each of the selected $\varepsilon_0$ values.
-
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e01} \\[\abovecaptionskip]
-		\small (a) $\varepsilon_0$ = 0.1
-		\label{fig:eg_e01_actions_distr}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e05} \\[\abovecaptionskip]
-		\small (b) $\varepsilon_0$ = 0.5
-		\label{fig:eg_e05_actions_distr}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_e-greedy_e1} \\[\abovecaptionskip]
-		\small (c) $\varepsilon_0$ = 1
-		\label{fig:eg_1_actions_distr}
-	\end{tabular}
-	\caption{Probability of taking a given action in $\varepsilon$-greedy for different $\varepsilon_0$ values after a simulation of 10,000 iterations.}
-	\label{fig:eg_actions_distr}
-\end{figure*}
-
-We observe in this figure that more aggressive actions (i.e., the ones that use the maximum transmit power) are chosen with a higher rate in all the WNs as $\varepsilon_0$ increases.
-A higher degree of exploration allows WNs to observe the effects of the actions taken by the others, thus acting in consequence.
-Accordingly, WNs alternate good/poor performance depending on the actions of the others, which at the same time are also selected intermittently.
-Despite using a high transmit power allows obtaining a better SNR at the receivers, the generated interference at times becomes counter-productive in terms of individual and aggregate throughput.
-
-On the other hand, as $\varepsilon_0$ decreases (refer to Figure \ref{fig:eg_actions_distr}(a)), WNs are prone to exploit the same action more frequently, which are the ones that provide the highest known performance.
-This low degree of exploration results also in a smaller usage of suboptimal actions.
-
-Figure \ref{fig:eg_agg_tpt}  shows the aggregate throughput evolution, which suffers from higher temporal variability as $\varepsilon_0$ increases.
-The same observation can be done from the individual throughput evolution (shown in Figure \ref{fig:eg_ind_tpt}), which in addition shows larger differences between the individual patterns for lower $\varepsilon_0$ values.
-These differences correspond to unfair performance resulting from a low degree of exploration.
-% e-greedy: aggregate throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e01} \\[\abovecaptionskip]
-		\small (a) $\varepsilon_0$ = 0.1
-		\label{fig:eg_e01_agg_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e05} \\[\abovecaptionskip]
-		\small (b) $\varepsilon_0$ = 0.5
-		\label{fig:eg_e05_agg_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_e-greedy_e1} \\[\abovecaptionskip]
-		\small (c) $\varepsilon_0$ = 1
-		\label{fig:eg_e1_agg_tpt}
-	\end{tabular}
-	\caption{Aggregate throughput evolution for a single $\varepsilon$-greedy 10,000-iterations simulation and for different $\varepsilon_0$ values.
-The proportional fair result is also shown (red dashed line).}
-	\label{fig:eg_agg_tpt}
-\end{figure*}
-
-% e-greedy: individual throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e01} \\[\abovecaptionskip]
-		\small (a) $\varepsilon_0$ = 0.1
-		\label{fig:eg_e01_ind_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e05} \\[\abovecaptionskip]
-		\small (b) $\varepsilon_0$ = 0.5
-		\label{fig:eg_e05_ind_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_e-greedy_e1} \\[\abovecaptionskip]
-		\small (c) $\varepsilon_0$ = 1
-		\label{fig:eg_e1_ind_tpt}
-	\end{tabular}
-	\caption{Individual throughput evolution for a single $\varepsilon$-greedy 10,000-iterations simulation and for different $\varepsilon_0$ values.
-The proportional fair result is also shown (red dashed line).}
-	\label{fig:eg_ind_tpt}
-\end{figure*}
-
-To gain further insight into fairness, we depict in Figure \ref{fig:eg_avg_tpt} the average  and standard deviation of the throughput at each WN.
-We have now concentrated in the last 5,000 iterations of the simulation, disregarding the instability provoked during the transitory regime, so that we get a better picture of the long-term behavior.
-We see that as $\varepsilon_0$ increases, the experienced fairness becomes higher due to the temporal fluctuation that occurs as a consequence of performing more exploratory actions.
-Moreover, we also observe that the standard deviation of the throughput is similar at each WN.
-
-% e-greedy: average throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e01} \\[\abovecaptionskip]
-		\small (a) $\varepsilon_0$ = 0.1
-		\label{fig:eg_e01_avg_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e05} \\[\abovecaptionskip]
-		\small (b) $\varepsilon_0$ = 0.5
-		\label{fig:eg_e05_avg_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_e-greedy_e1} \\[\abovecaptionskip]
-		\small (c) $\varepsilon_0$ = 1
-		\label{fig:eg_e1_avg_tpt}
-	\end{tabular}
-	\caption{Average throughput and standard deviation experienced per WN in the last 5,000 iterations of a single $\varepsilon$-greedy 10,000-iterations simulation run for different $\varepsilon_0$ values.
-The proportional fair result is also shown (red dashed line).}
-	\label{fig:eg_avg_tpt}
-\end{figure*}
-
-To sum up, we have seen that tuning $\varepsilon_0$ clearly entails a trade-off between the fairness and the temporal variation of throughput.
-Choosing a low $\varepsilon_0$ value grants low variability, but WNs are prone to fall into local maximums, as the experienced performance is just a consequence of the randomness in taking particular actions.
-This also generates a fairness problem, since the unlucky WNs end up experiencing lower performance, as well as they are not able to discover the best throughput actions.
-On the other side, choosing a high $\varepsilon_0$ value results in higher throughput and better long-term fairness but at the expense of intermittent good/poor performance.
-
-%------------------------
-% Study of MAB (EXP3)
-%------------------------
-\subsubsection{Performance of the EXP3 policy}
-\label{section:exp3_study}
-We now evaluate the trade-off between fairness and temporal throughput variability in the EXP3 policy, which includes the learning rate $\eta$, a parameter that controls how fast old beliefs are replaced by newer ones.
-In EXP3 we also find the $\gamma$ parameter, which regulates explicit exploration by tuning the importance of weights in the action-selection procedure.
-Setting $\gamma = 1$ results in completely neglecting weights (actions have the same probability to be chosen).
-On the other side, setting $\gamma = 0$, the effect of weights are  at its highest.
-Thus, in order to see clearly the effects of the EXP3 weights, which directly depend on $\eta$, we fix $\gamma$ to 0.
-
-As we did before for $\varepsilon$-greedy, we start analyzing the impact of modifying the input parameters of EXP3 on the average aggregate throughput (Figure \ref{fig:exp3_tuning_parameters}).
-We vary the initial learning rate, $\eta_0$, between 0 and 1 in 0.1 steps.
-As it can be observed, setting $\eta_0$ to 0 results in the lowest average throughput, and a low variability is obtained.
-In this case, action weights are never updated and the arms are randomly chosen with the same probability.
-As $\eta_0$ increases, the proportional fair solution is approximated at the expense of a higher variability between experiments, since less exploration is performed when $\eta_0$ increases.
-Note, as well, that the maximum average network throughput is reached for $\eta_0 = 0.6$ in this particular scenario.
+
+	%------------------------
+	% Proposed Method
+	%------------------------
+	\textcolor{blue}{\subsubsection{Learning Sequentially}}
+	\label{section:proposed_method}
+
+	\textcolor{blue}{In order to alleviate the strong throughput variability experienced when applying decentralized learning, we now focus on the sequential approach introduced in Section \ref{section:learning_procedure}.
+Now, only one WN is able to select an action at a time.
+With that, we aim to reduce the adversarial effect on the estimated rewards.
+Therefore, by having a more stable environment (not all the WNs learn simultaneously), the actual reward of a given selected action can be estimated more accurately.
+Figure \ref{fig:results_part_1_async_vs_sync} shows the differences between learning through concurrent and sequential mechanisms.
+Firstly, the throughput experienced on average along the entire simulation is depicted in Figure \ref{fig:results_part_1_async_vs_sync_meant_tpt}.
+Secondly, without loss of generality, Figure \ref{fig:results_part_1_async_vs_sync_variability} shows the temporal variability experienced by $\text{WN}_4$ when applying Thompson sampling.
+Note that showing the performance of a single WN is representative enough for the entire set of WNs (the scenario is symmetric), and allows us to analyze in detail the behavior of the algorithms.}
+
+	\textcolor{blue}{On the one hand, a lower throughput is experienced on average when learning in a sequential way, but the differences are very small.
+In such a situation, WNs spend more time observing sub-optimal actions, since they need to wait for their turn.
+Note, as well, that the time between iterations ($T$) depends on the implementation.
+In this particular case, we assume that $T$ is the same for both sequential and concurrent approaches.}
+
+	\textcolor{blue}{On the other hand, the temporal variability shown by the sequential approach is much lower than for the concurrent one (Figure \ref{fig:results_part_1_async_vs_sync_variability}).
+The high temporal variability may negatively impact on the user's experience and the operation of upper layer protocols (e.g., TCP) may be severely affected.
+Notice that a similar effect is achieved for the rest of algorithms.}
 
@@
 		\centering	
-	\epsfig{file=images/exp3_tuning_parameters_zoom.eps, width=6.5cm}
-	\caption{Average aggregate throughput and standard deviation obtained for each $\eta_0$ value in MAB (EXP3).
-The aggregate throughput of the proportional fair solution is also shown (red dashed line).
-Results are from 100 simulations lasting 10,000 iterations each.}
-	\label{fig:exp3_tuning_parameters}
+		\begin{subfigure}[b]{0.44\textwidth}
+			\includegraphics[width=\textwidth]{images/results_part_1_async_vs_sync}
+			\caption{Average throughput}
+			\label{fig:results_part_1_async_vs_sync_meant_tpt}
+		\end{subfigure}
+		\begin{subfigure}[b]{0.44\textwidth}
+			\includegraphics[width=\textwidth]{images/results_part_1_async_vs_sync_variability}
+			\caption{Temporal variability in $\text{WN}_4$}
+			\label{fig:results_part_1_async_vs_sync_variability}
+		\end{subfigure}
+		\caption{\textcolor{blue}{Concurrent vs sequential approaches performance.
+(a) Mean average throughput achieved for each learning procedure.
+(b) Temporal variability experienced by $\text{WN}_4$ for the Thompson sampling action-selection strategy and for each learning procedure.}}
+		\label{fig:results_part_1_async_vs_sync}
 	\end{figure}
 
-Now, for a single 10,000-iteration simulation, we set $\eta_0 = \{0.1, 0.5, 1\}$ to closely study the implications of modifying the initial learning rate.
-Figure \ref{fig:exp3_actions_distr} compares the resulting actions probability for these low, medium and high $\eta_0$ values.
-% EXP3: action probabilities
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta01} \\[\abovecaptionskip]
-		\small (a) $\eta_0 = 0.1$
-		\label{fig:exp3_eta01_actions_distr}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta05} \\[\abovecaptionskip]
-		\small (b) $\eta_0 = 0.5$
-		\label{fig:exp3_eta05_actions_distr}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_actions_probability_EXP3_eta1} \\[\abovecaptionskip]
-		\small (c) $\eta_0 = 1$
-		\label{fig:exp3_eta1_actions_distr}
-	\end{tabular}
-	\caption{Probability of taking a given action in EXP3 for different $\eta_0$ values after a simulation of 10,000 iterations.}
-	\label{fig:exp3_actions_distr}
-\end{figure*}
-
-We see that actions are tried with similar probability for $\eta_0 = 0.1$, since the usage of a low learning rate entails a high similarity between weights.
-This situation is significantly improved for $\eta_0 = 0.5$, in which few actions are selected most of the times.
-The increased learning rate allows to rapidly capture the effects of the others' actions, since more exploration is carried out.
-As a consequence, actions using the highest transmit power are clearly preferred to overcome the adversarial setting.
-Note, as well, that optimal channel allocation is learned by WNs despite competing with each other.
-Finally, for $\eta_0 = 1$, a single action is clearly preferred by each WN.
-However, unfair situations eventually occur due to the lack of exploration.
-In particular, we observe that $\text{WN}_1$ and $\text{WN}_3$, which share the same channel, use very different power levels in their favorite actions (5 and 15 dBm, respectively).
-This, of course, generates a fairness imbalance that favors $\text{WN}_3$, which enjoys a higher SINR.
-As mentioned, this behavior occurs eventually, since the variability in the output can be understood as a consequence of a fast convergence achieved during the transitory learning phase.
-So, results from different simulations will significantly vary.
-
-Figure \ref{fig:exp3_agg_tpt} shows the temporal aggregate throughput, which suffers from a higher variability when $\eta$ is lower.
-Regarding individual performance, the same behavior can be observed in the temporal throughput evolution (Figure \ref{fig:exp3_ind_tpt}).
-In this case, setting $\eta_0 = 1$ implies trusting best-performing actions for larger periods, i.e., higher weights are assigned even if actions are suboptimal.
-Therefore, as $\eta_0$ decreases, the temporal variability increases because the action-selection process becomes uniformly random.
-However, this variability does not entail that the proportional fair solution is approached.
-Thus, $\eta_0$ must be carefully set in order to provide a low temporal variability, at the same time that enough exploration is carried out for reaching the optimal fairness solution.
-
-% EXP3: aggregate throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta01} \\[\abovecaptionskip]
-		\small (a) $\eta_0 = 0.1$
-		\label{fig:exp3_eta01_agg_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta05} \\[\abovecaptionskip]
-		\small (b) $\eta_0 = 0.5$
-		\label{fig:exp3_eta05_agg_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_aggregate_tpt_EXP3_eta1} \\[\abovecaptionskip]
-		\small (c) $\eta_0 = 1$
-		\label{fig:exp3_eta1_agg_tpt}
-	\end{tabular}
-	\caption{Aggregate throughput evolution for a single EXP3 10000-iterations simulation and for different $\eta_0$ values. The proportional fair result is also shown (red dashed line).}
-	\label{fig:exp3_agg_tpt}
-\end{figure*}
-
-% EXP3: individual throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta01} \\[\abovecaptionskip]
-		\small (a) $\eta_0 = 0.1$
-		\label{fig:exp3_eta01_ind_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta05} \\[\abovecaptionskip]
-		\small (b) $\eta_0 = 0.5$
-		\label{fig:exp3_eta05_ind_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_temporal_individual_tpt_EXP3_eta1} \\[\abovecaptionskip]
-		\small (c) $\eta_0 = 1$
-		\label{fig:exp3_eta1_ind_tpt}
-	\end{tabular}
-	\caption{Individual throughput evolution for a single EXP3 10000-iterations simulation and for different $\eta_0$ values. The proportional fair result is also shown (red dashed line).}
-	\label{fig:exp3_ind_tpt}
-\end{figure*}
-
-One can notice a fairness imbalance by observing the individual throughput for $\eta_0 = 1$ in Figure \ref{fig:exp3_ind_tpt}, which is further illustrated in Figure \ref{fig:exp3_avg_tpt} (again, we have considered the last 5,000 iterations to avoid capturing the transitory phase).
-The average throughput is more evenly distributed for $\eta_0 = 0.1$ and $\eta_0 = 0.5$, but at the expense of the experienced throughput variability seen above.
-The unfairness suffered for $\eta_0 = 0.1$ can be understood as a lack of exploration that prevents finding a fair resource distribution.
-Thus, we conclude that a similar trade-off experienced in $\varepsilon$-greedy appears in EXP3 with parameter $\eta_0$.
-The main difference is that, in this case, a random action-selection process is approximated as $\eta_0$ decreases.
-% EXP3: average throughput
-\begin{figure*}
-	\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta01} \\[\abovecaptionskip]
-		\small (a) $\eta_0 = 0.1$
-		\label{fig:exp3_eta01_avg_tpt}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta05} \\[\abovecaptionskip]
-		\small (b) $\eta_0 = 0.5$
-		\label{fig:exp3_eta05_avg_tpt}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.3\textwidth]{images/NEW_mean_tpt_EXP3_eta1} \\[\abovecaptionskip]
-		\small (c) $\eta_0 = 1$
-		\label{fig:exp3_eta1_avg_tpt}
-	\end{tabular}
-	\caption{Average throughput and standard deviation experienced per WN in the last 5,000 iterations of a single EXP3 10000-iterations simulation for different $\eta_0$ values.
-The proportional fair result is also shown (red dashed line).}
-	\label{fig:exp3_avg_tpt}
-\end{figure*}
-
-%------------------------
-% Study of MAB (UCB)
-%------------------------
-\subsubsection{Performance of the UCB policy}
-\label{section:ucb_study}		
-Unlike $\varepsilon$-greedy and EXP3, the basic form of UCB does not include any input parameter to regulate variables such as the learning rate or the exploration coefficient.
-On the contrary, the action-selection process relies in the generated rewards only.
-We will study in this section how the previously seen trade-off between fair throughput and variability results for this parameter-free policy.
-
-We start by showing the action probability distribution (shown in Figure \ref{fig:actions_probability_ucb}) derived from the UCB implementation.
-We observe that WNs clearly prefer playing the actions corresponding to proportional fairness (i.e., the actions with highest transmit power and that result in frequency reuse).
+	%------------------------
+	% Dynamic environment
+	%------------------------
+	\subsubsection{Learning in a Dynamic Environment}
+	\label{section:dynamic_environment}
+
+	\textcolor{blue}{Finally, we show the performance of the proposed learning mechanisms in a dynamic scenario.
+For that, we propose the following situation.
+Firstly, $\text{WN}_1$ and $\text{WN}_2$ are active for the whole simulation.
+Secondly, $\text{WN}_3$ turns on at iteration 2,500, when $\text{WN}_1$ and $\text{WN}_2$ are supposed to have acquired enough knowledge to maximize SR.
+Finally, $\text{WN}_4$ turns on at iteration 5,000, similarly than for $\text{WN}_3$.}
+
+	\textcolor{blue}{Through this simulation, we aim to show how each learning algorithm adapts to changes in the environment, which highly impact on the rewards distributions.
+Figure \ref{fig:dynamic_enviroment} shows the temporal aggregate throughput achieved by each action-selection strategy.
+As done in Subsection \ref{section:proposed_method}, we only plot the results of the best-performing algorithm, i.e., Thompson sampling, both for the concurrent and the sequential procedures.}
 
@@
 		\centering
-	\epsfig{file=images/NEW_actions_probability_UCB.eps, width=6.5cm}
-	\caption{Probability of taking a given action in UCB for a simulation of 10,000 iterations.}
-	\label{fig:actions_probability_ucb}
+		\begin{subfigure}[b]{0.45\textwidth}
+			\includegraphics[width=\textwidth]{images/temporal_aggregate_tpt_dynamic_scenario_async_TS}
+			\caption{Concurrent approach}
+			\label{fig:temporal_aggregate_tpt_dynamic_scenario_async_TS}
+		\end{subfigure}
+		\begin{subfigure}[b]{0.45\textwidth}
+			\includegraphics[width=\textwidth]{images/temporal_aggregate_tpt_dynamic_scenario_ordered_TS}
+			\caption{Sequential approach}
+			\label{fig:temporal_aggregate_tpt_dynamic_scenario_ordered_TS}
+		\end{subfigure}
+		\caption{\textcolor{blue}{Temporal aggregate throughput experienced for a 10,000-iteration Thompson sampling simulation.}}
+		\label{fig:dynamic_enviroment}
 	\end{figure}
 
-Now, we concentrate in the temporal aggregate throughput (shown in Figure \ref{fig:ucb_agg_tpt}).
-The results show a very high variability, which slowly decreases as the number of iterations increases.
-The same observations can be done in the individual throughput evolution (Figure \ref{fig:ucb_tpt_evolution}).
-As a result, UCB provides long-term fairness but at the expense of a high temporal variability caused by exploration.
-In Figure \ref{fig:ucb_avg_individual} we show the average throughput experienced by each WN, as well as the standard deviation indicating the suffered variability (only for the last 5,000 iterations).
-As seen before, one can observe really high fairness but considerable variability due to the temporal evolution of throughput.
-
-% UCB: aggregate and individual 
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_aggregate_tpt_UCB}
-		\caption{Aggregate}\label{fig:ucb_agg_tpt}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_individual_tpt_UCB}
-		\caption{Individual}\label{fig:ucb_tpt_evolution}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_mean_tpt_UCB}
-		\caption{Average}\label{fig:ucb_avg_individual}
-	\end{subfigure}
-	\caption{Performance achieved for a single UCB 10,000-iterations simulation.
-The proportional fair result is also shown (red dashed line).
-(a) Aggregate throughput evolution, (b) Individual throughput evolution, (c) Average individual throughput (the last 5,000 iterations are considered).}
-	\label{fig:ucb_tpt}
-\end{figure*}
-
-Compared to $\varepsilon$-greedy and EXP3, UCB shows a clearer preference for selecting the proportional fair solutions.
-However, the intermittent good/poor performance of the actions due to the adversarial setting still keeps the degree of exploration very high, resulting in high temporal variability.
-
-%------------------------
-% Study of MAB (TS)
-%------------------------
-\subsubsection{Performance of the Thompson sampling policy}
-\label{section:ts_study}
-Similarly to UCB, in the basic form of Thompson sampling we do not have any tunable parameter.
-As with the other policies, we use a single 10,000-iteration simulation to show in detail the WNs behavior when applying Thompson sampling.
-We first show the actions probability in Figure \ref{fig:actions_probability_ts}.
-Note the well-pronounced preference for the proportional fair actions, which indicates fast convergence and little exploratory operations.
-
-% TS: actions probability
-\begin{figure}[t!]
-	\centering							
-	\epsfig{file=images/NEW_actions_probability_TS.eps, width=6.5cm}
-	\caption{Probability of taking a given action in Thompson sampling for a simulation of 10,000 iterations.}
-	\label{fig:actions_probability_ts}
-\end{figure}
-
-The temporal aggregate throughput is shown in Figure \ref{fig:ts_tpt_evolution}.
-As it can be observed, Thompson sampling achieves a lower variability in the temporal throughput with respect to UCB.
-The same observations can be done in the individual throughput evolution (Figure \ref{fig:ts_ind_tpt}).
-The low temporal variability observed on applying Thompson sampling is highlighted in Figure \ref{fig:ts_avg_individual}, which shows that the average experienced throughput enjoys a low standard deviation.
-Moreover, high fairness among WNs can be observed.
-
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_aggregate_tpt_TS}
-		\caption{Aggregate}\label{fig:ts_agg_tpt}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_temporal_individual_tpt_TS}
-		\caption{Individual}\label{fig:ts_ind_tpt}
-	\end{subfigure}
-	\begin{subfigure}[b]{.3\textwidth}
-		%\rule{\linewidth}{\linewidth}
-		\includegraphics[width=\textwidth]{images/NEW_mean_tpt_TS}
-		\caption{Average}\label{fig:ts_avg_individual}
-	\end{subfigure}
-		\caption{Throughput evolution for a single Thompson sampling 10,000-iterations simulation.
-The proportional fair result is also shown (red dashed line).
-(a) Aggregate throughput evolution, (b) Individual throughput evolution, (c) Average individual throughput (the last 5,000 iterations are considered).}
-		\label{fig:ts_tpt_evolution}
-\end{figure*}
-
-These results show that even though the rewards encourage selfish behavior, the adversarial setting makes Thompson sampling to converge to collaborative actions while keeping the degree of exploration low.
-Again, this property holds for scenarios where no asymmetries can be found.
-While the excellent performance we observe echoes other published results that show the superiority of Thompson sampling in various settings \cite{LCLS10}, we highlight that this outstanding empirical performance is actually rather unexpected in our \emph{non-stochastic} setting.
-Indeed, existing theoretical results only explain the excellent performance of Thompson sampling in \emph{stochastic} bandit problems.
-On the other hand, the randomization employed by Thompson sampling is at least superficially related to techniques used in game-theoretic online learning \cite{FS97,CBLu06:book}, with the connection made clear only in a special case \cite{Gop13}.
-The behavior observed in our experiments may indicate a more profound relationship with such game-theoretic algorithms.
-We leave the investigation of this matter as an exciting direction for future work.
-
-%------------------------
-% Random Scenarios - Scalability
+	\textcolor{blue}{As shown, WNs are able to adapt to the changes in the environment.
+In particular, for the concurrent case (see Figure \ref{fig:temporal_aggregate_tpt_dynamic_scenario_async_TS}), changes are harder to be captured as the network size increases.
+In contrast, learning in an ordered way (see Figure \ref{fig:temporal_aggregate_tpt_dynamic_scenario_ordered_TS}) allows reducing the temporal variability, even if new WNs turn on.
+However, there is a little loss in the aggregate performance with respect to the concurrent approach.
+The difference between the maximum network performance is mostly provoked by the reduced exploration shown by the sequential approach.}
+	%------------------------
+	% Random Scenarios 
 	%------------------------
@@
 	\label{section:random}
-After studying the WNs interactions in the grid scenario, we now evaluate whether the previous conclusions generalize to random scenarios with an arbitrary number of WNs.
-To this aim, we use the same $10\times5\times 10$ m scenario and randomly allocate $N = \{2, 4, 6, 8\}$ WNs.
-%Different topologies are captured by placing WNs randomly.
-With that, we are able to study how the presented policies maintain fairness for different densities and topologies.
-
-We set $\varepsilon_0 = 1$ in $\varepsilon$-greedy, which is the value that granted the highest aggregate throughput in the experiment shown in Figure \ref{fig:egreedy_tuning_parameters}.
-We do the same for EXP3 and choose $\eta_0 = 0.6$, which grants the highest aggregate throughput in average (refer to Figure \ref{fig:exp3_tuning_parameters}).
-In Figure \ref{fig:hist_mean_tpt} we show, for each number of networks and action-selection strategy, an histogram of the mean throughput experienced by each WN during the last 5,000 iterations, and for each of the 100 repetitions.
-% Histogram mean throughput
-\begin{figure*}
+
+	We now evaluate whether the previous conclusions generalize to random scenarios with an arbitrary number of WNs.
+To this aim, we use the same $10\times5\times 10$ m scenario and randomly allocate N = \{2, 4, 6, 8\} WNs.
+\textcolor{blue}{Figures \ref{fig:random_scenarios_results} and \ref{fig:random_scenarios_results_variability} show the mean throughput and variability experienced for each learning strategy, and for each number of coexistent WNs, respectively.
+The variability is measured as the standard deviation that a given WN experiences along an entire simulation.
+We consider the average results of 100 different random scenarios for each number of networks.
+In particular, we are interested on analyzing the gains achieved by each algorithm, even if convergence cannot be provided due to the competition between networks.
+For that, we display the average performance for the following learning intervals: [1-100, 101-500, 501-1000, 1001-2500, 2501-10000].
+Note that the first intervals represent few iterations.
+This allows us to observe the performance achieved during the transitory phase in more detail.
+In addition, the performance achieved in a static situation (i.e., when no learning is performed) is shown in Figure \ref{fig:random_scenarios_results}.
+With that, we aim to compare the gains obtained by each learning strategy with respect to the current IEEE 802.11 operation in unplanned and chaotic deployments.}
+
+	\begin{figure}[h!]
 		\centering
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_2_WNs} \\[\abovecaptionskip]
-		\small (a) N = 2 WNs
-		\label{fig:hist_mean_throughput_2}
-	\end{tabular}	
-	\hspace{\floatsep}	
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_4_WNs} \\[\abovecaptionskip]
-		\small (b) N = 4 WNs
-		\label{fig:hist_mean_throughput_4}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_6_WNs} \\[\abovecaptionskip]
-		\small (c) N = 6 WNs
-		\label{fig:hist_mean_throughput_6}
-	\end{tabular}
-	\hspace{\floatsep}
-	\begin{tabular}{@{}c@{}}
-		\includegraphics[width=.35\textwidth]{images/hist_mean_tpt_8_WNs} \\[\abovecaptionskip]
-		\small (c) N = 8 WNs
-		\label{fig:hist_imean_throughput_8}
-	\end{tabular}
-	\caption{Histogram of the average throughput experienced by each WN during the last 5,000 iterations. Results from 100 repetitions are considered.}
-	\label{fig:hist_mean_tpt}
-\end{figure*}
-
-As we can observe, histograms of UCB and Thompson sampling are slightly narrower in almost all the cases, which indicates a higher fairness experienced by the WNs with respect to the other policies.
-Note, as well, that for the $N = 2$, results are similar for all the policies because finding a good-performing configuration in low-density environments is more likely to occur.
-Thus, fewer exploration is required than for higher densities.
-Note, as well, that the abovementioned collaborative behavior is still present in random scenarios.
-In accordance to that, WNs acting selfishly are prone to find a configuration whereby SR is improved in a fair manner.
-We find the main cause of this issue to be the inter-WN interference sensed at a given transmitter-receiver pair, which is very likely to be similar in both devices for the proposed scenarios.
-Such a property is given when STAs are close to their associated AP, thus allowing to palliate the effects of asymmetries.
-
-To conclude, we evaluate temporal variability in random scenarios.
-For that, Table \ref{tbl:std_individual_tpt_experienced} shows the average standard deviation of the throughput experienced by each WN during the last 5,000 iterations (again, we concentrate on the regime after the initial learning phase).
-We consider the average results from 100 repetitions.
-With this, we are able to evaluate, for each network density, the variability in the temporal throughput provided by each of the policies in random topologies.
-% Mean std of the individual throughput	
-\begin{table}[h!]
+		\includegraphics[width=0.8\textwidth]{images/random_scenarios_results}
+		\caption{\textcolor{blue}{Average throughput experienced in each learning interval for each action-selection strategy.
+Results from 100 repetitions are considered for each different number of overlapping WNs (N = \{2, 4, 6, 8\}).
+The black dashed line indicates the default IEEE 802.11 performance (static situation).}}
+		\label{fig:random_scenarios_results}
+	\end{figure}
+
+	\begin{figure}[h!]
 		\centering
-	%\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{|c|c|c|c|c|}
-			\hline
-			\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}Number of \\ WNs\end{tabular}}} & \multicolumn{4}{c|}{\textbf{$\overline{\sigma}(\Gamma_{i \in N})$ (Mbps)}} \\ \cline{2-5} 
-			& \textbf{$\varepsilon$-greedy} & \textbf{EXP3} & \textbf{UCB} & \textbf{Thompson s.} \\ \hline
-			\textbf{2} & 12.1314 & 31.2897 & 31.9422 & 12.2079 \\ \hline
-			\textbf{4} & 83.7318 & 95.4976 & 73.9136 & 50.6985 \\ \hline
-			\textbf{6} & 120.8570 & 81.3259 & 67.6045 & 62.8171 \\ \hline
-			\textbf{8} & 130.0322 & 73.5171 & 63.2272 & 68.8547 \\ \hline
-	\end{tabular}%}
-	\caption{Mean standard deviation of the throughput experienced $\Gamma_{i \in N}$ by each $WN_i$ during the last 5,000 iterations. 100 repetitions are considered for averaging purposes.}
-	\label{tbl:std_individual_tpt_experienced}
-\end{table}
-
-As previously seen in the toy grid scenario introduced in Section \ref{section:toy_grid_scenario}, both UCB and Thompson sampling provide the best results in terms of temporal throughput variability.
-Despite $\varepsilon$-greedy provides very good results for $N=2$, it does not properly scale up with the number of WNs.
+		\includegraphics[width=0.77\textwidth]{images/random_scenarios_results_variability}
+		\caption{\textcolor{blue}{Average variability experienced in each learning interval for each action-selection strategy.
+Results from 100 repetitions are considered for each different number of overlapping WNs (N = \{2, 4, 6, 8\}).}}
+		\label{fig:random_scenarios_results_variability}
+	\end{figure}
+
+	\textcolor{blue}{First of all, let us focus on the throughput improvements achieved with respect to the static situation.
+As shown in Figure \ref{fig:random_scenarios_results}, each learning strategy easily outperforms the static scenario for low densities (i.e., 2 and 4 overlapping WNs).
+However, as density increases, improving the average throughput becomes more challenging.
+This is clearly evidenced for N = \{6, 8\} WNs, where EXP3 performs worse than the static situation.}
+
+	\textcolor{blue}{Secondly, we concentrate on the concurrent learning procedure.
+As shown in Figure \ref{fig:random_scenarios_results}, Thompson sampling outperforms the other action-selection strategies for all the scenarios, provided that enough exploration is done (up to 500 iterations).
+On the other hand, $\varepsilon$-greedy allows to increase the average performance very quickly, but its growth stalls from iteration 200.
+Note that $\varepsilon$-greedy is based on the absolute throughput value, thus preventing to find a collaborative behavior in which the scarce resources are optimally shared.
+Finally, EXP3 and UCB are shown to improve the average throughput linearly, but offering poor performance.}
+
+	\textcolor{blue}{When it comes to the sequential approach, we find the following:}
+	\begin{itemize}
+		\item \textcolor{blue}{On the one hand, the average throughput is reduced in almost all the cases in comparison with the concurrent approach (see Figure \ref{fig:random_scenarios_results}).
+We find that this is due to the larger phases in which agents exploit sub-optimal actions.
+As previously pointed out, the time between iterations is considered to be the same for both sequential and concurrent learning approaches.}
+		\item \textcolor{blue}{On the other hand, the sequential procedure is shown to substantially improve the variability experienced by $\varepsilon$-greedy, EXP3 and UCB (see Figure \ref{fig:random_scenarios_results_variability}).
+The performance of the latter is particularly shown to be improved when the learning procedure is ordered.
+The sequential approach, therefore, allows UCB to produce more accurate estimates on the actions rewards.
+In contrast, learning sequentially does not improve the concurrent version of Thompson sampling in any performance metric.
+We attribute this suboptimal behavior to the way in which Thompson sampling performs estimates of the played actions, which depends on the number of times each one is selected.
+In particular, suboptimal actions can eventually provide good enough performance according to the adversarial setting.
+The same issue can lead to underestimate optimal actions, so that their actual potential is not observed.
+Since Thompson sampling bases its estimates on the number of times each action is selected, the aforementioned effect may lead to increase the exploitation on suboptimal actions.}
+	\end{itemize}
 
 	%%%%%%%%%%%%%%%
-%  VI. CONCLUSIONS  %
+	%  VI. CONCLUSIONS  
 	%%%%%%%%%%%%%%%
@@
 	\label{section:conclusions}
-In this paper, we provided a tutorial-like implementation of MABs to address the decentralized SR problem in dense WNs.
+	In this paper, we provided an implementation of MABs to address the decentralized SR problem in dense WNs.
 Unlike previous literature, we have focused on a situation in which few resources are available, thus bringing out the competition issues raised from the adversarial setting.
@@
 For instance, a high throughput fluctuation may entail behavioral anomalies in protocols such as Transmission Control Protocol (TCP).
-%In this case, the temporal fluctuation of the throughput would directly affect the Contention Window (CW) used in TCP for congestion control, providing a poor performance.
+
 	We have studied this trade-off between fair resource allocation and high temporal throughput variability in $\varepsilon$-greedy, EXP3, UCB and Thompson sampling action-selection strategies.
@@
 
+	\textcolor{blue}{Furthermore, for the sake of alleviating the temporal variability, we studied the effects of learning concurrent and sequentially.
+We have shown that learning in an ordered way is very effective to reduce the throughput variability for almost all the proposed learning strategies, even if WNs maintain a selfish behavior.
+By learning sequentially, more knowledge is attained on a given action, thus allowing to differentiate quickly between good and bad performing actions.
+\textcolor{blue}{Apart from that, we found that Thompson sampling grants significantly better results than the other examined algorithms since it is able to capture meaningful information from chaotic environments.}}
+
 	We left as future work to further study the MABs application to WNs through distributed (with message passing) and centralized (with complete information) approaches with shared reward.
-Furthermore, we would like to extend this work to enhance both throughput and stability by inferring the actions of the opponents and acting in consequence.
+In particular, we would like to extend this work to enhance both throughput and stability by inferring the actions of the opponents and acting in consequence, as well as further investigating dynamic scenarios.
 Defining the resource allocation problem as an adversarial game is one possibility to do so.
-Finally, we intend to particularize to IEEE 802.11 WLANs to study the effects of applying RL when using a medium access protocol such as CSMA.
-In fact, this would let us consider dynamic Carrier Sense Threshold (CST) to further enable SR.
+\textcolor{blue}{In addition to this, the utilization of multiple antenna strategies (i.e., single and multi-user beamforming and interference cancellation) is expected to further improve the spectral efficiency in future WNs.
+Through these techniques, the SR problem can be relaxed in a similar way than using several non-overlapping frequency channels.
+However, its application would significantly increase the problem's complexity, and its analysis is also left as future work.}
 
 	%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%  ACKNOWLEDGEMENT  		  %%%
+	%%%  ACKNOWLEDGEMENT 
 	%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\section*{Acknowledgments}
-This work has been partially supported by the Spanish Ministry of Economy and Competitiveness under the Maria de Maeztu Units of Excellence Programme (MDM-2015-0502), by the European Regional Development Fund under grant TEC2015-71303-R (MINECO/FEDER), and by a Gift from CISCO University Research Program (CG\#890107) \& Silicon Valley Community Foundation.
+	This work has been partially supported by the Spanish Ministry of Economy and Competitiveness under the Maria de Maeztu Units of Excellence Programme (MDM-2015-0502), by a Gift from CISCO University Research Program (CG\#890107) \& Silicon Valley Community Foundation, by the European Regional Development Fund under grant TEC2015-71303-R (MINECO/FEDER), and by the Catalan Government under grant SGR-2017-1188.
+
+	\textcolor{blue}{The authors would like to thank the anonymous reviewers. Their dedication and insightful comments were of great help to improve this paper. 
+		We would also like to show our gratitude to Andrés Burbano, who also contributed to improve the quality of this document through his thorough revision.
+	}
 
